### 2011-06-07 scribblings/primitive yee cell.tex
Added subgrid Yee cell documentation.

\documentclass{article}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{graphicx}

\newcommand{\be}{\begin{equation}}
\newcommand{\ee}{\end{equation}}
\newcommand{\grad}{\nabla}
\newcommand{\dvg}{\nabla\cdot}
\newcommand{\curl}{\nabla\times}
\newcommand{\eps}{\epsilon}
\newcommand{\inv}{\frac{1}}
\newcommand{\del}{\partial}
\newcommand{\dt}{\frac{\del}{\del t}}
\newcommand{\BI}{\begin{itemize}}
\newcommand{\I}{\item}
\newcommand{\EI}{\end{itemize}}

\title{The Primitive Yee Cell}
\author{Jesse Lu, \texttt{jesselu@stanford.edu}}

\begin{document}
\maketitle
\tableofcontents

\section{The Yee cell}
The Yee cell\cite{yee} is simply a way of shifting the different field components of the electric and magnetic field in order to make an electromagnetic finite-differenc time-domain (FDTD) simulation stable.

\begin{figure}[hbt]
\centering\includegraphics[width=0.5\textwidth]{pyc.png}
\caption{The primitive Yee cell. Borrowed from \url{http://tx.technion.ac.il/~graanan/Project/Theory.htm}}\label{pyc}
\end{figure}

Figure~\ref{pyc} shows the shifts to the field components used in the primitive Yee cell. Specifically, if the grid spacing in all three dimensions is 1, then the location of the six field components are
\BI
\I $E_x[i,j,k] \to (i+0.5,j,k)$,
\I $E_y[i,j,k] \to (i, j+0.5,k)$,
\I $E_z[i,j,k] \to (i, j, k+0.5)$,
\I $H_x[i,j,k] \to (i,j+0.5,k+0.5)$,
\I $H_y[i,j,k] \to (i+0.5,j,k+0.5)$, and
\I $H_z[i,j,k] \to (i+0.5,j+0.5,k)$,
\EI
where the notation is $A[\text{index}] \to (\text{location in grid})$.

Lastly, note that this scheme of offsets naturally fits the two update equations used in electromagnetic FDTD\cite{TH}, 
\be \dt \eps E = \curl H - J, \text{ and} \ee
\be \dt \mu H = -\curl E - M,\ee
where $J$ and $M$ are electric and magnetic current sources, respectively.

\section{Local grids (subgrids) of Yee cells}
For applications where deep sub-wavelength accuracy is required, it is beneficial to have a local grid (or subgrid) with increased resolution at the point of interest. While many different subgridding techniques exist for electromagnetic FDTD schemes, the technique presented in ref.~\cite{CLC} is summarized here.

\subsection{Chevalier's subgridding scheme}
The basic idea behind Chevalier's technique\cite{CLC} is to use the $H$-fields to ``knit'' the high-resolution subgrid to the low-resolution main grid. The main advantage gained is that arbitrary non-magnetic materials can traverse the subgrid and main grid boundary.

Notably, this scheme allows for arbitrary \emph{odd}-integer refinement factors. That is, the ratios of the spatial and temporal resolution between main and subgrids must be either 1:3, 1:5, 1:7, etc...

Here, we describe the locations of the $E$-field components of the subgrid, relative to the main grid. We refer the reader to the original paper\cite{CLC} for the details of the subgrid $H$-field components.

\subsection{Location of the subgrid electric fields}
We will use the following notation: $E_x$, $E_y$, and $E_z$ will denote the \emph{main} grid electric field components, and $e_x$, $e_y$, and $e_z$ will denote the \emph{sub}grid electric field components.

Additionally, we assume that for the main grid $\Delta x, \Delta y, \Delta z = 1$. 
This implies that for the subgrid $\Delta x, \Delta y, \Delta z = \inv{\kappa}$, where $\kappa$ is the \emph{refinement factor} and must be a positive, odd integer greater than 1.

Now suppose that we want to place a subgrid over the cube with corners $(i_0, j_0, k_0)$ and $(i_1, j_1, k_1)$, then the subgrid $e$-field components will be located in the following way:
\BI
\I $e_x$ at 
    $(  i_0 - 0.5 + \frac{(n_i + 0.5)}{\kappa}, 
        j_0 - 0.5 + \frac{n_j}{\kappa}, 
        k_0 - 0.5 + \frac{n_k}{\kappa})$, 
\I $e_y$ at 
    $(  i_0 - 0.5 + \frac{n_i}{\kappa}, 
        j_0 - 0.5 + \frac{(n_j + 0.5)}{\kappa}, 
        k_0 - 0.5 + \frac{n_k}{\kappa})$, 
\I $e_z$ at 
    $(  i_0 - 0.5 + \frac{n_i}{\kappa}, 
        j_0 - 0.5 + \frac{n_j}{\kappa}, 
        k_0 - 0.5 + \frac{(n_k + 0.5)}{\kappa})$,
\EI
where
\BI
\I $n_i = 1, 2, \ldots, \kappa (i_1 - i_0 + 1)$,
\I $n_j = 1, 2, \ldots, \kappa (j_1 - j_0 + 1)$,
\I $n_k = 1, 2, \ldots, \kappa (k_1 - k_0 + 1)$.
\EI

\subsection{Other fields}
Additional fields are often required to produce an FDTD simulation. If the values of $\epsilon$ are needed on the subgrid (as they often are), these should be co-located with their respective $e$-field components.
Note that this is also how the components of $\epsilon$ are placed on the main grid.

Secondary fields needed to simulate dispersive materials should also be co-located with their respective $e$-field component.

\begin{thebibliography}{99}
\bibitem{yee} K. Yee, ``Numerical solution of initial boundary value problems involving maxwell's equations in isotropic media,'' IEEE Trans. Antennas Propag. Mag. \textbf{14}, 302-307 (1966).
\bibitem{TH} Allen Taflove, Susan C. Hagness, \emph{Computational Electrodynamics, Third Edition} (Artech House, 2005). 
\bibitem{CLC} Chevalier, Luebbers, and Cable, ``FDTD Local Grid with Material Traverse,'' IEEE Trans. Antennas and Propag. Mag., \textbf{45}, (1997).
\end{thebibliography}
\end{document}

### 2011-07-27 presentations/figuresandcode.tex
Templates and presentations added.

\documentclass[12pt]{article}
\usepackage{fullpage,graphicx,psfrag,url}
\usepackage[small,bf]{caption}
\usepackage{verbatim}
\setlength{\captionmargin}{30pt}

\input defs.tex
\newcommand{\sign}{\mathop{\bf sign}}

\title{Including figures and code}

\begin{document}
\maketitle

\section{Including figures}
To include a figure in your document, you can use \textbf{includegraphics}.
The example below includes a figure from figures directory.   
\begin{figure}
\begin{center}
\includegraphics[width=0.6\textwidth]{figures/problem.eps}
\end{center}
\caption{Problem figure.}
\label{f-problem}
\end{figure}

\section{Including code}
To include code, you can use \textbf{verbatiminput}.  (This command requires
the \textbf{verbatim} package. The following command includes code from 
matlab directory. 
\verbatiminput{matlab/problem.m}

\end{document}

### 2011-07-27 presentations/group-pres_2011-08-04.tex
Templates and presentations added.

\documentclass[dvips,landscape]{foils}
\usepackage{graphicx,psfrag}
\input defs.tex
\raggedright
\special{! TeXDict begin /landplus90{true}store end }
\renewcommand{\oursection}[1]{
\foilhead[-1.0cm]{#1}
}

\title{Stochastic Subgradient Method}
\author{}
\MyLogo{Prof.\ S.\ Boyd, EE364b, Stanford University}
\date{}

\begin{document}
\setlength{\parskip}{0cm}
\maketitle

\BIT \itemsep -1pt
\item noisy unbiased subgradient
\item stochastic subgradient method
\item convergence proof
\item stochastic programming
\item expected value of convex function
\item on-line learning and adaptive signal processing
\EIT

\vfill

\oursection{Noisy unbiased subgradient}

\BIT
\item
random vector $\tilde g \in \reals^n$ is a
\textbf{noisy unbiased subgradient} for
$f:\reals^n \rightarrow \reals$ at $x$ if for all $z$
\[
f(z) \geq f(x)+ (\Expect \tilde g)^T(z-x)
\]
\ie, $g = \Expect \tilde g \in \partial f(x)$

\item
same as $\tilde g= g+v$, where $g \in \partial f(x)$, $\Expect v=0$

\item $v$ can represent error in
computing $g$, measurement noise, Monte Carlo sampling error, etc.
\EIT
\newpage

\BIT
\item
if $x$ is also random, $\tilde g$ is a noisy unbiased
subgradient of $f$ at $x$ if
\[
\forall z \qquad f(z) \geq f(x)+ \Expect (\tilde g|x)^T(z-x)
\]
holds almost surely

\item
same as $\Expect (\tilde g|x) \in \partial f(x)$ (a.s.)
\EIT

\oursection{Stochastic subgradient method}

\textbf{stochastic subgradient method} is
the subgradient method, using noisy unbiased subgradients

\[
x^{(k+1)} = x^{(k)} - \alpha_k \tilde g^{(k)}
\]
\BIT\itemsep -3pt
\item $x^{(k)}$ is $k$th iterate
\item $\tilde g^{(k)}$ is any noisy unbiased
subgradient of (convex) $f$ at  $x^{(k)}$, \ie,
\[
\Expect (\tilde g^{(k)}|x^{(k)})  = g^{(k)} \in \partial f(x^{(k)})
\]
\item $\alpha_k>0$ is the $k$th step size
\item define $f_\mathrm{best}^{(k)} = \min \{
f(x^{(1)}), \ldots, f(x^{(k)}) \}$
\EIT

\oursection{Assumptions}

\BIT
\item $f^\star = \inf_x f(x) > -\infty$, with $f(x^\star)=f^\star$
\item $\Expect \|g^{(k)} \|_2^2 \leq G^2$ for all $k$
\item $\Expect \|x^{(1)}-x^\star \|_2^2 \leq R^2$ (can take $=$ here)
\item step sizes are square-summable but not summable
\[
\alpha_k \geq 0, \qquad
\sum_{k=1}^\infty \alpha^2_k = \|\alpha\|_2^2< \infty,  \qquad
\sum_{k=1}^\infty \alpha_k = \infty
\]
\EIT

\vfill

these assumptions are stronger than needed, just to simplify proofs

\oursection{Convergence results}

\BIT
\item convergence in expectation:
\[
\lim _{k\rightarrow \infty} \Expect f^{(k)}_\mathrm{best} = f^\star
\]

\item convergence in probability: for any $\epsilon> 0$,
\[
\lim _{k\rightarrow \infty} \Prob (f^{(k)}_\mathrm{best} \geq f^\star+
\epsilon) = 0
\]
\item almost sure convergence:
\[
\lim _{k\rightarrow \infty} f^{(k)}_\mathrm{best} = f^\star
\]
a.s. (we won't show this)
\EIT

\oursection{Convergence proof}

\textbf{key quantity:}
\emph{expected Euclidean distance squared to the optimal set}

\vskip 3ex

$\Expect \left. \left( \|x^{(k+1)} - x^\star\|_2^2 \;\right|\; x^{(k)}
\right) = \Expect \left. \left( \|x^{(k)}-\alpha_k \tilde
g^{(k)}-x^\star\|_2^2 \;\right|\; x^{(k)} \right)$
\begin{eqnarray*}
\quad & = & \|x^{(k)}-x^\star\|_2^2
-2\alpha_k \Expect \left. \left( \tilde g^{(k)T}
(x^{(k)}-x^\star) \,\right|\, x^{(k)} \right)
        +\alpha_k^2\Expect \left. \left( \|\tilde g^{(k)} \|_2^2
\,\right|\, x^{(k)} \right) \\
&=& \|x^{(k)}-x^\star\|_2^2
        -2\alpha_k \Expect (\tilde g^{(k)} | x^{(k)})^T
(x^{(k)}-x^\star)
        +\alpha_k^2\Expect \left. \left( \|\tilde g^{(k)} \|_2^2
\;\right|\; x^{(k)} \right) \\
&\leq& \|x^{(k)}-x^\star\|_2^2
        -2\alpha_k (f(x^{(k)})-f^\star)+
\alpha_k^2 \Expect \left. \left( \|\tilde g^{(k)}\|_2^2
\;\right|\; x^{(k)} \right)
\end{eqnarray*}
using $\Expect (\tilde g^{(k)}|x^{(k)}) \in \partial f(x^{(k)})$

\newpage
now take expectation:
\[
\Expect \|x^{(k+1)}-x^\star\|_2^2
\leq \Expect \|x^{(k)}-x^\star\|_2^2
            -2\alpha_k (\Expect f(x^{(k)})-f^\star)
            +\alpha_k^2 \Expect \|\tilde g^{(k)}\|_2^2
\]

apply recursively, and use $\Expect \|\tilde g^{(k)}\|_2^2 \leq G^2$
to get
\[
\Expect \|x^{(k+1)}-x^\star\|_2^2 \leq
\Expect\|x^{(1)}-x^\star\|_2^2
-2\sum_{i=1}^k \alpha_i  (\Expect f(x^{(i)})-f^\star)
+G^2\sum_{i=1}^k \alpha_i^2
\]

%using $\Expect \|x^{(k+1)}-x^\star\|_2^2 \geq 0$,
%$\Expect \|x^{(1)}-x^\star\|_2^2 \leq R^2$,
%and $\sum_{i=1}^k \alpha_i^2 \leq \|\alpha \|_2^2$
%hence we have
%\[
%2 \sum_{i=1}^k \alpha_i  (\Expect f(x^{(i)})-f^\star)
%\leq R^2 +G^2\| \alpha \|_2^2
%\]
and so
\[
\min_{i=1,\ldots,k} (\Expect f(x^{(i)})-f^\star) \leq
\frac{R^2+G^2\|\alpha\|_2^2}{2 \sum_{i=1}^k \alpha_i}
\]

\newpage
\BIT
\item we conclude
$ \min_{i=1,\ldots,k} \Expect f(x^{(i)}) \rightarrow f^\star $

\item
Jensen's inequality and concavity of minimum yields
\[
\Expect f^{(k)}_\mathrm{best}
= \Expect \min_{i=1,\ldots,k} f(x^{(i)})
\leq \min_{i=1,\ldots,k} \Expect f(x^{(i)})
\]
so $\Expect f^{(k)}_\mathrm{best} \rightarrow f^\star$
(convergence in expectation)

\item
Markov's inequality: for $\epsilon>0$
\[
\Prob(f^{(k)}_\mathrm{best} - f^\star \geq \epsilon) \leq
\frac{\Expect (f^{(k)}_\mathrm{best} - f^\star)}{\epsilon}
\]
righthand side goes to zero, so we get convergence in probability
\EIT

\oursection{Example}
piecewise linear minimization

\[
\begin{array}{ll} \mbox{minimize} &
f(x) = \max_{i=1,\ldots,m} (a_i^T x + b_i)
\end{array}
\]

we use stochastic subgradient algorithm with noisy subgradient
\[
\tilde g^{(k)} = g^{(k)} + v^{(k)}, \qquad
g^{(k)}\in \partial f(x^{(k)})
\]
$v^{(k)}$ independent zero mean random variables

\vfill

\newpage
problem instance: $n=20$ variables, $m=100$ terms,
$f^\star \approx 1.1$, $\alpha_k=1/k$

$v^{(k)}$ are IID $\mathcal N(0,0.5I)$ ($25\%$ noise
since $ \|g \| \approx 4.5$)

\vfill
\end{document}

### 2011-07-27 presentations/group-pres_2011-08-04.tex
Updated group presentation.
Updated presentation.

@@
 \usepackage{graphicx,psfrag}
+\usepackage{amsmath}
 \input defs.tex
@@
 
-\title{Stochastic Subgradient Method}
+\title{Objective-first optimization for nanophotonics}
 \author{}
-\MyLogo{Prof.\ S.\ Boyd, EE364b, Stanford University}
+\MyLogo{Jesse Lu, Jelena Vuckovic group, Stanford University}
 \date{}
@@
 \BIT \itemsep -1pt
-\item noisy unbiased subgradient
-\item stochastic subgradient method
-\item convergence proof
-\item stochastic programming
-\item expected value of convex function
-\item on-line learning and adaptive signal processing
+\item adjoint method
+\item objective-first approach
+\item field setup: boundary-value problem
+\item structure setup: level-set formulation
+\item example
+\item ongoing and future work
 \EIT
@@
 
-\oursection{Noisy unbiased subgradient}
-
+\oursection{Adjoint method}
+Typical formulation of a structural optimization problem:
+\BEAS
+\mbox{decrease} & f(x) \\
+\subjectto & g(x,p) = 0
+\EEAS
 \BIT
-\item
-random vector $\tilde g \in \reals^n$ is a
-\textbf{noisy unbiased subgradient} for
-$f:\reals^n \rightarrow \reals$ at $x$ if for all $z$
-\[
-f(z) \geq f(x)+ (\Expect \tilde g)^T(z-x)
-\]
-\ie, $g = \Expect \tilde g \in \partial f(x)$
-
-\item
-same as $\tilde g= g+v$, where $g \in \partial f(x)$, $\Expect v=0$
-
-\item $v$ can represent error in
-computing $g$, measurement noise, Monte Carlo sampling error, etc.
+\item $f(x): \comps^n \to \reals$ is the \emph{design objective}
+\item $g(x,p): \comps^n \times \reals^n \to \comps^n$ is the \emph{governing physics}
+\item $x \in \comps^n$ is the field 
+\item $p \in \reals^n$ is the structure 
+\item $x$ is the dependant variable, $p$ is the independant variable
 \EIT
@@
 \BIT
-\item
-if $x$ is also random, $\tilde g$ is a noisy unbiased
-subgradient of $f$ at $x$ if
-\[
-\forall z \qquad f(z) \geq f(x)+ \Expect (\tilde g|x)^T(z-x)
-\]
-holds almost surely
+\item problem is non-convex, so optimize using first-order approximations
+\BEAS
+f(x_0+dx) \approx f(x_0) + \pf{f}{x} dx \\
+g(x_0+dx,p_0+dp) \approx g(x_0,p_0) + \pf{g}{x} dx + \pf{g}{p} dp
+\EEAS
+\item assuming that $g(x_0,p_0) = 0$, the equality constraint is satisfied via
+    \BEQ  dx = -\left(\pf{g}{x}\right)^{-1} \pf{g}{p} dp \EEQ
+\EIT
+\newpage
 
-\item
-same as $\Expect (\tilde g|x) \in \partial f(x)$ (a.s.)
+\BIT
+\item now we can decrease $f(x_0+dx)$,
+    \begin{align} 
+    f(x_0+dx) & \approx f(x_0) + \pf{f}{x} dx \\
+        & \approx f(x_0) - \pf{f}{x} \left(\pf{g}{x}\right)^{-1} \pf{g}{p} dp \\
+        & \approx f(x_0) + \pf{f}{p} dp
+    \end{align}
+    by choosing $dp$ in the direction of $dp \propto -\pf{f}{p}$
+\item computing $\pf{f}{p}$ can be reduced to a single field solve (\ie solving $g(x,p)$ for $x$ given $p$)
 \EIT
 
-\oursection{Stochastic subgradient method}
-
-\textbf{stochastic subgradient method} is
-the subgradient method, using noisy unbiased subgradients
-
-\[
-x^{(k+1)} = x^{(k)} - \alpha_k \tilde g^{(k)}
-\]
-\BIT\itemsep -3pt
-\item $x^{(k)}$ is $k$th iterate
-\item $\tilde g^{(k)}$ is any noisy unbiased
-subgradient of (convex) $f$ at  $x^{(k)}$, \ie,
-\[
-\Expect (\tilde g^{(k)}|x^{(k)})  = g^{(k)} \in \partial f(x^{(k)})
-\]
-\item $\alpha_k>0$ is the $k$th step size
-\item define $f_\mathrm{best}^{(k)} = \min \{
-f(x^{(1)}), \ldots, f(x^{(k)}) \}$
-\EIT
-
-\oursection{Assumptions}
-
-\BIT
-\item $f^\star = \inf_x f(x) > -\infty$, with $f(x^\star)=f^\star$
-\item $\Expect \|g^{(k)} \|_2^2 \leq G^2$ for all $k$
-\item $\Expect \|x^{(1)}-x^\star \|_2^2 \leq R^2$ (can take $=$ here)
-\item step sizes are square-summable but not summable
-\[
-\alpha_k \geq 0, \qquad
-\sum_{k=1}^\infty \alpha^2_k = \|\alpha\|_2^2< \infty,  \qquad
-\sum_{k=1}^\infty \alpha_k = \infty
-\]
-\EIT
-
-\vfill
-
-these assumptions are stronger than needed, just to simplify proofs
-
-\oursection{Convergence results}
-
-\BIT
-\item convergence in expectation:
-\[
-\lim _{k\rightarrow \infty} \Expect f^{(k)}_\mathrm{best} = f^\star
-\]
-
-\item convergence in probability: for any $\epsilon> 0$,
-\[
-\lim _{k\rightarrow \infty} \Prob (f^{(k)}_\mathrm{best} \geq f^\star+
-\epsilon) = 0
-\]
-\item almost sure convergence:
-\[
-\lim _{k\rightarrow \infty} f^{(k)}_\mathrm{best} = f^\star
-\]
-a.s. (we won't show this)
-\EIT
-
-\oursection{Convergence proof}
-
-\textbf{key quantity:}
-\emph{expected Euclidean distance squared to the optimal set}
-
-\vskip 3ex
-
-$\Expect \left. \left( \|x^{(k+1)} - x^\star\|_2^2 \;\right|\; x^{(k)}
-\right) = \Expect \left. \left( \|x^{(k)}-\alpha_k \tilde
-g^{(k)}-x^\star\|_2^2 \;\right|\; x^{(k)} \right)$
-\begin{eqnarray*}
-\quad & = & \|x^{(k)}-x^\star\|_2^2
--2\alpha_k \Expect \left. \left( \tilde g^{(k)T}
-(x^{(k)}-x^\star) \,\right|\, x^{(k)} \right)
-        +\alpha_k^2\Expect \left. \left( \|\tilde g^{(k)} \|_2^2
-\,\right|\, x^{(k)} \right) \\
-&=& \|x^{(k)}-x^\star\|_2^2
-        -2\alpha_k \Expect (\tilde g^{(k)} | x^{(k)})^T
-(x^{(k)}-x^\star)
-        +\alpha_k^2\Expect \left. \left( \|\tilde g^{(k)} \|_2^2
-\;\right|\; x^{(k)} \right) \\
-&\leq& \|x^{(k)}-x^\star\|_2^2
-        -2\alpha_k (f(x^{(k)})-f^\star)+
-\alpha_k^2 \Expect \left. \left( \|\tilde g^{(k)}\|_2^2
-\;\right|\; x^{(k)} \right)
-\end{eqnarray*}
-using $\Expect (\tilde g^{(k)}|x^{(k)}) \in \partial f(x^{(k)})$
-
-\newpage
-now take expectation:
-\[
-\Expect \|x^{(k+1)}-x^\star\|_2^2
-\leq \Expect \|x^{(k)}-x^\star\|_2^2
-            -2\alpha_k (\Expect f(x^{(k)})-f^\star)
-            +\alpha_k^2 \Expect \|\tilde g^{(k)}\|_2^2
-\]
-
-apply recursively, and use $\Expect \|\tilde g^{(k)}\|_2^2 \leq G^2$
-to get
-\[
-\Expect \|x^{(k+1)}-x^\star\|_2^2 \leq
-\Expect\|x^{(1)}-x^\star\|_2^2
--2\sum_{i=1}^k \alpha_i  (\Expect f(x^{(i)})-f^\star)
-+G^2\sum_{i=1}^k \alpha_i^2
-\]
-
-%using $\Expect \|x^{(k+1)}-x^\star\|_2^2 \geq 0$,
-%$\Expect \|x^{(1)}-x^\star\|_2^2 \leq R^2$,
-%and $\sum_{i=1}^k \alpha_i^2 \leq \|\alpha \|_2^2$
-%hence we have
-%\[
-%2 \sum_{i=1}^k \alpha_i  (\Expect f(x^{(i)})-f^\star)
-%\leq R^2 +G^2\| \alpha \|_2^2
-%\]
-and so
-\[
-\min_{i=1,\ldots,k} (\Expect f(x^{(i)})-f^\star) \leq
-\frac{R^2+G^2\|\alpha\|_2^2}{2 \sum_{i=1}^k \alpha_i}
-\]
-
-\newpage
-\BIT
-\item we conclude
-$ \min_{i=1,\ldots,k} \Expect f(x^{(i)}) \rightarrow f^\star $
-
-\item
-Jensen's inequality and concavity of minimum yields
-\[
-\Expect f^{(k)}_\mathrm{best}
-= \Expect \min_{i=1,\ldots,k} f(x^{(i)})
-\leq \min_{i=1,\ldots,k} \Expect f(x^{(i)})
-\]
-so $\Expect f^{(k)}_\mathrm{best} \rightarrow f^\star$
-(convergence in expectation)
-
-\item
-Markov's inequality: for $\epsilon>0$
-\[
-\Prob(f^{(k)}_\mathrm{best} - f^\star \geq \epsilon) \leq
-\frac{\Expect (f^{(k)}_\mathrm{best} - f^\star)}{\epsilon}
-\]
-righthand side goes to zero, so we get convergence in probability
-\EIT
-
-\oursection{Example}
-piecewise linear minimization
-
-\[
-\begin{array}{ll} \mbox{minimize} &
-f(x) = \max_{i=1,\ldots,m} (a_i^T x + b_i)
-\end{array}
-\]
-
-we use stochastic subgradient algorithm with noisy subgradient
-\[
-\tilde g^{(k)} = g^{(k)} + v^{(k)}, \qquad
-g^{(k)}\in \partial f(x^{(k)})
-\]
-$v^{(k)}$ independent zero mean random variables
-
-\vfill
-
-\newpage
-problem instance: $n=20$ variables, $m=100$ terms,
-$f^\star \approx 1.1$, $\alpha_k=1/k$
-
-$v^{(k)}$ are IID $\mathcal N(0,0.5I)$ ($25\%$ noise
-since $ \|g \| \approx 4.5$)
-
-\vfill
 \end{document}

### 2011-07-27 presentations/group-pres_2011-08-04.tex
Added Ob-1 section to presentation.

@@
 Typical formulation of a structural optimization problem:
-\BEAS
-\mbox{decrease} & f(x) \\
-\subjectto & g(x,p) = 0
-\EEAS
+\begin{align}
+\mbox{decrease} & \quad f(x) \\
+\subjectto & \quad g(x,p) = 0
+\end{align}
 \BIT
@@
 \item $p \in \reals^n$ is the structure 
-\item $x$ is the dependant variable, $p$ is the independant variable
+\item $x$ is the dependent variable, $p$ is the independent variable
 \EIT
@@
 \BIT
-\item problem is non-convex, so optimize using first-order approximations
-\BEAS
-f(x_0+dx) \approx f(x_0) + \pf{f}{x} dx \\
-g(x_0+dx,p_0+dp) \approx g(x_0,p_0) + \pf{g}{x} dx + \pf{g}{p} dp
-\EEAS
+\item problem is generally non-convex, so we optimize using only the first-order approximations,
+\begin{align}
+f(x_0+dx) & \approx f(x_0) + \pf{f}{x} dx \\
+g(x_0+dx,p_0+dp) & \approx g(x_0,p_0) + \pf{g}{x} dx + \pf{g}{p} dp
+\end{align}
 \item assuming that $g(x_0,p_0) = 0$, the equality constraint is satisfied via
@@
     by choosing $dp$ in the direction of $dp \propto -\pf{f}{p}$
-\item computing $\pf{f}{p}$ can be reduced to a single field solve (\ie solving $g(x,p)$ for $x$ given $p$)
+\item computing $\pf{f}{p}$ can be reduced to a single field solve (\ie solving $g(x,p)$ for $x$, given $p$)
+\EIT
+\newpage
+
+Characteristics of the adjoint method:
+\BIT
+\item can use existing field solvers 
+\item each iteration requires two solves, one to calculate $\pf{f}{p}$, and the other to calculate the new $x$
+\item need good initial guess, since this heavily influences what the final structure will be
+\item optimization generally ``stalls'' on local minima
 \EIT
 
+\oursection{Objective-first approach}
+Ob-1 means that we prioritize the design objective over satisfying physics
+\begin{align}
+\mbox{decrease} & \quad \|g(x,p)\|^2 \\
+\subjectto & \quad f(x) = 0
+\end{align}
+\BIT
+\item $r(x,p) = \|g(x,p)\|^2$ is the \emph{physics residual}
+\item $x$ always satisfies our design objective, we change $x$ and $p$ only to increasingly satisfy physics
+\item $x$ and $p$ are both independent variables
+\EIT
+\newpage
+
+\BIT
+\item this problem is still non-convex, use linear approximation 
+\begin{align}
+r(x_0+dx,p_0+dp) & \approx r(x_0,p_0) + \pf{r}{x} dx + \pf{r}{p} dp \\
+f(x_0+dx) & \approx f(x_0) + \pf{f}{x} dx 
+\end{align}
+\item decrease $r$ by choosing $dp \propto -\pf{r}{p}$
+\item decrease $r$ by choosing 
+    $dx \propto - (I - P_{f_x}) \pf{r}{x}$
+\item $P_{f_x}$ is the projector onto the vector space defined by $\pf{f}{x}$, this satisfies the equality constraint
+\item computing $P_{f_x}$ requires solving for $\left(\pf{f}{x}^T \pf{f}{x}\right)^{-1}$, but this is often \emph{trivial}
+\EIT
+\newpage
+
+Ob-1 requires only matrix multiplication (and trivial matrix solve)
+\BIT
+\item For 3D structures, most field solvers are based on (often $>10,000$) matrix multiplies
+\item this means that is may be possible to solve larger design problems in the same amount of time needed for a field solve
+\EIT
+
+\vspace{3ex}
+
+Ob-1 should be less dependent on starting guess 
+\BIT
+\item some previous problems (using a similar approach) did not depend at all on initial structure
+\item such a formulation may result in fewer local minima to stall on
+\EIT
+\vfill
+
 \end{document}

### 2011-07-28 presentations/group-pres_2011-08-04.tex
Finished field constraint section for group presentation.

@@
-\documentclass[dvips,landscape]{foils}
-\usepackage{graphicx,psfrag}
+\documentclass[landscape]{foils}
+\usepackage{graphicx}
 \usepackage{amsmath}
+\usepackage{hyperref}
 \input defs.tex
@@
 \item objective-first approach
-\item field setup: boundary-value problem
-\item structure setup: level-set formulation
+\item field constraints: boundary-value problem
+\item structure constraints: level-set formulation
 \item example
@@
 \oursection{Objective-first approach}
-Ob-1 means that we prioritize the design objective over satisfying physics
+ob-1 means that we prioritize the design objective over satisfying physics
 \begin{align}
@@
 
-Ob-1 requires only matrix multiplication (and trivial matrix solve)
+ob-1 requires only matrix multiplication (and trivial matrix solve)
 \BIT
@@
 
-Ob-1 should be less dependent on starting guess 
+ob-1 should be less dependent on starting guess 
 \BIT
@@
 
+\oursection{Field constraints: boundary-value problem}
+\BIT
+\item formulation of the constraint is the key issue
+\item a sufficient constraint for most devices is to match field values along the border
+\BEQ f(x) = \| x^\text{border} - x^\text{border}_0 \|^2 = 0 \EEQ
+\item physics residual is the error in Maxwell's sourceless, time-harmonic equations
+\BEQ \|g(x,p)\|^2 = \|A(p)x\|^2 = 
+    \left\| \left[ 
+    \begin{array}{cc}
+        \nabla\times & i\mu\omega \\
+        -ip\omega & \nabla\times
+    \end{array}
+    \right] 
+    \left[ \begin{array}{c} x_E \\ x_H \end{array} \right] 
+    \right\|^2
+\EEQ
+\item here $p$ determines the values of $\epsilon$
+\EIT
+\newpage
+
+\BIT
+\item to experiment, we fix $p = p_0$, which convexifies the ob-1 formulation
+\begin{align}
+\mbox{minimize} & \quad \|A(p_0)x\|^2 \\
+\subjectto & \quad x^\text{border} = x^\text{border}_0
+\end{align}
+\begin{center}
+\includegraphics[width=0.8\textwidth]{../figures/waveguide.png}
+\end{center}
+\item here, $p_0$ is a waveguide structure, and the design objective is a perfect waveguide mode at input and output
+\EIT
+\newpage
+
+\BIT
+\item for general structures and design objectives, this results in a ``soft physics'' field solve
+\begin{center}
+\includegraphics[width=0.8\textwidth]{../figures/crossbar.png}
+\end{center}
+\item matlab files available at \url{https://github.com/JesseLu/wave-tools}, look for \texttt{em\_bval\_2dte/demo.m}
+\EIT
+\newpage
+
+\BIT
+\item
+\EIT
+
 \end{document}

### 2011-07-29 presentations/group-pres_2011-08-04.tex
Edited field constraint section. Changed pictures to jpeg format.

@@
 \item objective-first approach
-\item field constraints: boundary-value problem
-\item structure constraints: level-set formulation
+\item field constraint: boundary-value problem
+\item structure constraint: level-set formulation
 \item example
@@
     $dx \propto - (I - P_{f_x}) \pf{r}{x}$
-\item $P_{f_x}$ is the projector onto the vector space defined by $\pf{f}{x}$, this satisfies the equality constraint
+\item $P_{f_x}$ is the projector onto the vector space defined by $\pf{f}{x}$, used to satisfy equality constraint
 \item computing $P_{f_x}$ requires solving for $\left(\pf{f}{x}^T \pf{f}{x}\right)^{-1}$, but this is often \emph{trivial}
@@
 
-\oursection{Field constraints: boundary-value problem}
+\oursection{Field constraint: boundary-value problem}
 \BIT
-\item formulation of the constraint is the key issue
-\item a sufficient constraint for most devices is to match field values along the border
-\BEQ f(x) = \| x^\text{border} - x^\text{border}_0 \|^2 = 0 \EEQ
+\item our problem is
+\begin{align}
+\mbox{decrease} & \quad \|g(x,p)\|^2 \\
+\subjectto & \quad f(x) = 0
+\end{align}
 \item physics residual is the error in Maxwell's sourceless, time-harmonic equations
@@
 \BIT
+\item key issue: formulation of the constraint
+\item a sufficient constraint for most devices is to match field values along the border
+\BEQ f(x) = \| x^\text{border} - x^\text{border}_0 \|^2 = 0 \EEQ
+\begin{center}
+\includegraphics[width=0.8\textwidth]{../figures/waveguide.jpg}
+\end{center}
+\item here, $p$ is a waveguide structure, and the design objective is a perfect waveguide mode at input and output
+\EIT
+\newpage
+
+\BIT
 \item to experiment, we fix $p = p_0$, which convexifies the ob-1 formulation
@@
 \end{align}
+\item for general structures and design objectives, this results in a ``soft physics'' field solve
 \begin{center}
-\includegraphics[width=0.8\textwidth]{../figures/waveguide.png}
+\includegraphics[width=0.8\textwidth]{../figures/crossbar.jpg}
 \end{center}
-\item here, $p_0$ is a waveguide structure, and the design objective is a perfect waveguide mode at input and output
 \EIT
@@
 \BIT
-\item for general structures and design objectives, this results in a ``soft physics'' field solve
+\item prioritizing the design objective means we allow physics to be ``bent''
+\item here, reflected waves from the junction magically disappear as they approach the border
 \begin{center}
-\includegraphics[width=0.8\textwidth]{../figures/crossbar.png}
+\includegraphics[width=0.8\textwidth]{../figures/mode_converter.jpg}
 \end{center}
@@
 \EIT
-\newpage
 
+\oursection{Structure constraint: level-set method}
 \BIT
-\item
+\item a more detailed statement of our problem is
+\begin{align}
+\mbox{decrease} & \quad \|g(x,p)\|^2 \\
+\subjectto & \quad f(x) = 0 \\
+        & \quad p \in \{p_\text{can be made}\}
+\end{align}
+\item need to constrain possible $p$ to what can be fabricated
+\item for nanophotonics this means two distinct materials only
+\item using $p \in \{\epsilon_1, \epsilon_2\}$ defeats the purpose of using linear approximations
+\item need to \emph{incrementally} update the topology of the structure
 \EIT

### 2011-07-29 presentations/group-pres_2011-08-04.tex
Started on structure constraint section.

@@
 \subjectto & \quad f(x) = 0 \\
-        & \quad p \in \{p_\text{can be made}\}
+        & \quad p \in \{p_\text{manufacturable}\}
 \end{align}
@@
 \item for nanophotonics this means two distinct materials only
-\item using $p \in \{\epsilon_1, \epsilon_2\}$ defeats the purpose of using linear approximations
-\item need to \emph{incrementally} update the topology of the structure
+\item however, using $p \in \{\epsilon_1, \epsilon_2\}$ defeats the purpose of using linear approximations
+\EIT
+\newpage
+
+\BIT
+\item need ability to \emph{incrementally} update the topology of the structure
+\item describe $p$ using the \emph{interface} between the two materials
+\item implicitly describe boundary using the \emph{level-set} of a higher-dimensional function
+\begin{center}
+\includegraphics[width=0.45\textwidth]{../figures/level-set.jpg} \\
+source: \url{http://en.wikipedia.org/wiki/Level_set_method}
+\end{center}
+\EIT
+\newpage
+
+\BIT
+\item ...
+\begin{center}
+\includegraphics[width=0.8\textwidth]{../figures/structure-progression.jpg} \\
+\end{center}
 \EIT

### 2011-07-30 presentations/group-pres_2011-08-04.tex
Finished structure constraint section.

@@
 \item for nanophotonics this means two distinct materials only
-\item however, using $p \in \{\epsilon_1, \epsilon_2\}$ defeats the purpose of using linear approximations
+\item however, using $p_i \in \{\epsilon_1, \epsilon_2\}$ defeats the purpose of using linear approximations
 \EIT
@@
 \item describe $p$ using the \emph{interface} between the two materials
-\item implicitly describe boundary using the \emph{level-set} of a higher-dimensional function
+\item implicitly describe boundary using the \emph{level-set} of higher-dimensional function $\phi$
 \begin{center}
@@
 \BIT
-\item ...
+\item updating $p(\phi)$ proceeds in the following way:
+\BEQ
+\phi^n \xrightarrow{\text{interp.}} \gamma 
+    \xrightarrow{\text{ratio}} p
+    \xrightarrow{-\pf{r}{p}} dp
+    \xrightarrow{\left(\pf{p}{\phi}\right)^{-1}dp} d\phi
+    \xrightarrow{\phi + d\phi} \phi^{n+1}
+\EEQ
+\item $\phi = 0$ defines the boundary between materials
+\item boundary points $\gamma$ are linearly interpolated between adjacent $\phi$ of opposite sign
+\item $p_i$ approximated by ratio of each material within cell
+\item solve least-squares problem $\pf{p}{\phi} d\phi = dp$ to obtain $d\phi$
+\EIT
+\newpage
+
+\BIT
+\item to test, hold $x$ constant, and update $p$ 
 \begin{center}
-\includegraphics[width=0.8\textwidth]{../figures/structure-progression.jpg} \\
+\includegraphics[width=0.6\textwidth]{../figures/structure-progression.jpg} \\
 \end{center}
+\item code at \url{https://github.com/JesseLu/level-set} (\texttt{demo.m})
+\item new code at \url{https://github.com/JesseLu/lset-opt}
 \EIT
 
+\oursection{Example}
+put it all together and let'er rip!
+
 \end{document}

### 2011-08-02 presentations/group-pres_2011-08-04.tex
Corrected wrong reference to matlab file on slide 15.
Changed figure source to public domain.

@@
 \includegraphics[width=0.45\textwidth]{../figures/level-set.jpg} \\
-source: \url{http://en.wikipedia.org/wiki/Level_set_method}
+source: public domain
 \end{center}
@@
 \BIT
-\item to test, hold $x$ constant, and update $p$ 
+\item to test, hold $x$ constant, and update $p$ (iterations 0, 5, 10, 15, 20 shown)
 \begin{center}
-\includegraphics[width=0.6\textwidth]{../figures/structure-progression.jpg} \\
+\includegraphics[width=0.5\textwidth]{../figures/structure-progression.jpg} \\
 \end{center}
-\item code at \url{https://github.com/JesseLu/level-set} (\texttt{demo.m})
+\item code at \url{https://github.com/JesseLu/level-set} (\texttt{demo\_indep\_levelset.m})
 \item new code at \url{https://github.com/JesseLu/lset-opt}

### 2011-08-04 presentations/ob1_aug-2011/objective-first.tex
Re-organized and finalized ob-1 presentation.

--- 2011-08-02 presentations/group-pres_2011-08-04.tex
@@
 \begin{center}
-\includegraphics[width=0.8\textwidth]{../figures/waveguide.jpg}
+\includegraphics[width=0.8\textwidth]{figures/waveguide.jpg}
 \end{center}
@@
 \begin{center}
-\includegraphics[width=0.8\textwidth]{../figures/crossbar.jpg}
+\includegraphics[width=0.8\textwidth]{figures/crossbar.jpg}
 \end{center}
@@
 \begin{center}
-\includegraphics[width=0.8\textwidth]{../figures/mode_converter.jpg}
+\includegraphics[width=0.8\textwidth]{figures/mode_converter.jpg}
 \end{center}
@@
 \begin{center}
-\includegraphics[width=0.45\textwidth]{../figures/level-set.jpg} \\
+\includegraphics[width=0.45\textwidth]{figures/level-set.jpg} \\
 source: public domain
@@
 \begin{center}
-\includegraphics[width=0.5\textwidth]{../figures/structure-progression.jpg} \\
+\includegraphics[width=0.5\textwidth]{figures/structure-progression.jpg} 
 \end{center}
@@
 \oursection{Example}
-put it all together and let'er rip!
+\BIT
+\item alternately update $x$, then $p$
+\begin{align}
+\mbox{decrease} & \quad \|g(x,p)\|^2 \\
+\subjectto & \quad f(x) = 0 \\
+        & \quad p \in \{p_\text{level-set}\}
+\end{align}
+\item test on a simple, 2D example on a $30\times30$ grid
+\item 10,000 iterations take 3 minutes in Matlab
+\item code at \url{https://github.com/JesseLu/objective-first}, look for \texttt{demo\_alternate\_levelset.m}
+\EIT
+\newpage
+
+\begin{center}
+\includegraphics[width=0.7\textwidth]{figures/example.jpg} 
+\end{center}
+\BIT
+\item initial checker-board structure allows for islands to be formed
+\EIT
+\newpage
+
+\BIT
+\item verify by inserting into larger grid with absorbing boundaries, and excite waveguide mode
+\begin{center}
+\includegraphics[width=0.7\textwidth]{figures/verify.jpg} 
+\end{center}
+\item slightly more power transmitted than reflected, a lot of room for improvement
+\EIT
+
+\oursection{Ongoing and future work}
+\BIT
+\item currently working out some kinks in level-set code which cause the structure update to ``jam''
+\EIT
+
+Next milestones:
+\BIT
+\item successful waveguide converters in 2D
+\item multi-wavelength waveguide devices in 2D
+\item implement in 3D, on multi-GPU system
+\EIT
 

### 2011-10-03 presentations/fios_2011/abstract/abstract.tex
Finished figures for fios abstract submission.

\documentclass{letter}
\usepackage{graphicx}
\begin{document}
\includegraphics[width=\textwidth]{fig/fiber.jpg}
\includegraphics[width=\textwidth]{fig/mode-conv.jpg}
\includegraphics[width=\textwidth]{fig/air-core.jpg}
\end{document}

### 2011-10-03 presentations/fios_2011/abstract/abstract.tex
Draft of abstract for fios 2011.

@@
-\documentclass{letter}
+\documentclass[letterpaper,10pt]{article}
 \usepackage{graphicx}
+\usepackage{osameet2}
+\usepackage{amsmath,amssymb}
+
 \begin{document}
+\title{Automated Design of Nanophotonic Waveguide-to-Waveguide Couplers}
+\author{Jesse Lu and Jelena Vu\v{c}kovi\'{c}}
+\address{Stanford University, Stanford, California, USA.}
+\email{jesselu@stanford.edu}
+
+\maketitle
+\begin{abstract}
+We demonstrate a design algorithm which automatically generates 
+wavelength-scale coupling devices between arbitrary waveguide modes with high
+efficiency.
+Our algorithm is fast ($\sim$20 min.), can be extended to multiple dimensions,
+ and requires no trial-and-error.
+\end{abstract}
+\ocis{000.0000.}
+
+% Importance of problem.
+\section{Motivation}
+In order to route and process optical information on-chip, it is absolutely
+critical to be able to efficiently transfer photons from one waveguide mode
+to another.
+% NEED TO CITE HERE!
+However, current strategies either 
+1) require large device areas and tunable material parameters,
+2) are only applicable to effectively 1D systems, or 
+3) operate on brute force parameter search.
+
+% Capabilities of our algorithm.
+We present an algorithm that quickly ($\sim$20 min.) designs high efficiency
+($\sim$95\% conversion) nanophotonic waveguide couplers in two dimensions.
+The resulting devices are extremely compact, on the order of only 1-2 vacuum 
+wavelengths per side, and can couple between seemingly arbitrary waveguide 
+modes.
+Notably, neither trial-and-error nor the modeling of device subcomponents 
+are utilized.
+
+% How it works.
+\section{Method}
+The algorithm operates by calculating the boundary electromagnetic fields
+needed for perfect operation (100\% conversion), and then varying the 
+interior fields and permittivities to reproduce the boundary fields.  
+Numerically, we fix $H({border}) = H_\text{perfect}$,
+and then minimize the residual in the electromagnetic wave equation,
+$\| \nabla \times \epsilon^{-1} \nabla \times H - \mu \omega^2 H \|^2$, 
+by varying both $H({interior})$ (interior magnetic field) and 
+$\epsilon$ (permittivity).
+
+Note that the algorithm actually places much greater emphasis on achieving 
+perfect device performance than even satisfying physics (the wave equation)!
+Specifically, it is this ``objective-first'' approach, 
+coupled with the boundary field formulation, 
+that greatly speeds up the design process by eliminating the need to  
+repeatedly solve the wave equation.
+
+Lastly, we validate our designs in simulation (finite-difference 
+frequency-domain) by exciting the input waveguide mode and then calculating
+the transmitted power in the desired output waveguide mode.
+
+\section{Results}
+Figs. 1, 2 and 3 show the result of our algorithm, as applied to the design 
+of nanophotonic waveguide couplers in two dimensions.
+
+Note that we allow $\epsilon$ to vary continuously between the
+permittivity of air and silicon, even though discrete values are more
+amenable to fabrication.
+\begin{figure}[htbp]
     \includegraphics[width=\textwidth]{fig/fiber.jpg}
-\includegraphics[width=\textwidth]{fig/mode-conv.jpg}
-\includegraphics[width=\textwidth]{fig/air-core.jpg}
+    \caption{caption test}
+\end{figure}
+% \includegraphics[width=\textwidth]{fig/mode-conv.jpg}
+% \includegraphics[width=\textwidth]{fig/air-core.jpg}
 \end{document}

### 2011-10-04 presentations/ob1_wg_paper/paper.tex
Started on wg coupler paper.

\documentclass[letterpaper,10pt]{article}
\usepackage{graphicx}
% \usepackage{osameet2}
\usepackage{amsmath,amssymb}

\begin{document}
\title{Automated Design of Nanophotonic Waveguide Couplers}
\author{Jesse Lu and Jelena Vu\v{c}kovi\'{c}}
% \address{Stanford University, Stanford, California, USA.}
% \email{jesselu@stanford.edu}

\maketitle
\begin{abstract}
We demonstrate a design algorithm which automatically generates 
    wavelength-scale coupling devices between arbitrary waveguide modes 
    with high efficiency.
Our algorithm is computationally fast, 
    can be extended to multiple dimensions,
    and requires no trial-and-error.
\end{abstract}
% \ocis{230.7370, 130.3990.}

% \begin{thebibliography}{99}
% \bibitem{lipson} Almeida et al, Optics Letters \textbf{28}, 1302-1304 (2003).
% \end{thebibliography}
% Importance of problem.

\section{Motivation}

% Why is waveguide mode conversion important?
\subsection{The importance of waveguide mode conversion}
Optical mode conversion, 
    the efficient transfer of photons from one guided mode to another,
    is a fundamental requirement in nanophotonics.
Efficient conversion between waveguides modes
    is critical in the many cases, including:
\begin{enumerate}
    \item Coupling to and from optical fiber\cite{}, 
        to communicate with the outside world.
    \item Coupling between various nanophotonic waveguides, 
        since different waveguides are best suited for different applications.
        For example, ridge waveguides seem ideal for low-loss transport\cite{},
            but other waveguides, 
            such as photonic crystal waveguides or slot waveguides,
            may be better suited for slow-light\cite{} 
            or energy-focusing devices\cite{}.
    \item Coupling between different materials.
       This is to couple between passive, active\cite{}, 
        and non-linear\cite{} materials. 
\end{enumerate}

% Why are current solutions insufficient?
\subsection{Common approaches to designing waveguide couplers}
% Brute force
Brute-force parameter search is the most popular nanophotonic design strategy 
    to-date because of its sheer simplicity\cite{}.
Although it may be suitable for tuning existing designs\cite{},
    the parameter space for most practical devices is simply too large
    for such a strategy to be tractable.

% Adiabatic mode conversion (large devices, symmetry breaking)
Adiabtic mode conversion strategies have been succesful
    for certain fiber-waveguide\cite{} and waveguide-waveguide\cite{} couplers,
    although resulting devices are quite large.
However, adiabatic strategy cannot be used in many important cases such as
    coupling from ridge to some photonic crystal waveguides,
    coupling in the out-of-plane direction, and
    coupling between modes of opposite symmetry.

% Local optimization
Optimization methods based on local derivatives seem very promising\cite{},
    in that they are both much faster than brute-force methods and
    more adaptable than adiabatic strategies.
However, these methods still require that every updated design be simulated
    at least once,
    and for the user to supply an initial design.

% How does your algorithm solve this problem?
\subsection{Advantages of objective-first design}
We present an ``objective-first'' approach to nanophotonic design, 
    and apply it to the problem of high-efficiency waveguide couplers.
The resulting algorithm
\begin{itemize}
    \item does not employ brute-force parameter searches,
    \item does not require a good initial design,
    \item is computationally fast (no simulations required),
    \item generates couplers between seemingly arbitrary waveguide modes, and
    \item generates these couplers in a very small footprint. 
\end{itemize}

\section{Design Method}
% What is objective-first optimization?
\subsection{Objective-first optimization}
The typical approach to designing physical structures can be formulated 
    in the following way, 
    where $x$ is the field variable and $p$ is the structure variable,
    \begin{subequations}\label{eq:adj}
    \begin{align} 
    \text{decrease} & \quad f(x) \label{eq:adj:obj} \\ 
    \text{subject to} & \quad g(x,p) = 0. \label{eq:adj:con}
    \end{align}
    \end{subequations}
Here, $f(x)$, the \emph{design objective}, 
    calculates the performance of the device 
    (e.g. amount of power not coupled to output mode); 
    while $g(x,p)$ is the underlying physical equation for the system
    (e.g. the electromagnetic wave equation).

In contrast, the objective-first formulation is
    \begin{subequations}\label{eq:ob1}
    \begin{align} 
    \text{decrease} & \quad \|g(x,p)\|^2 \label{eq:ob1:obj} \\ 
    \text{subject to} & \quad f(x) = 0, \label{eq:ob1:con}
    \end{align}
    \end{subequations}
where $\|g(x,p)\|^2$ is called the \emph{physics residual}.

Such a formulation naturally lends itself to a local derivative strategy where 
    $x$ is a dependent variable and 
    $p$ is an independent variable. 
The optimization then proceeds by 
    \begin{enumerate}
    \item computing $x$, given $p$, via $g(x,p) = 0$
        (i.e. finding $x$ via simulation),
    \item updating $p$ to decrease $f(x)$ (details in appendix).
    \end{enumerate}

Not, satisfying the design objective actually has a higher priority than 
    satisfying the underlying physical equation,
    hence the name ``objective-first''.

Notice that the design objective is now a constraint (Eq.~\ref{eq:ob1:con}),
and that the quantity to be decreased is now the 
% What are the numerical advantages?
% How is it applied to waveguide coupler design?

% 
% \section{Method}
% The algorithm operates by calculating the boundary electromagnetic fields
% needed for perfect operation (100\% coupling efficiency), and then varying the 
% interior fields and permittivities to reproduce those boundary fields.  
% Numerically, we fix $H({border}) = H_\text{perfect}$,
% and then minimize the residual in the electromagnetic wave equation,
% $\| \nabla \times \epsilon^{-1} \nabla \times H - \mu \omega^2 H \|^2$, 
% by varying both $H({interior})$ (interior magnetic field) and 
% $\epsilon$ (permittivity).
% 
% Note that the algorithm actually places much greater emphasis on achieving 
% perfect device performance than even satisfying physics (the wave equation)!
% Specifically, it is this ``objective-first'' approach, 
% coupled with the boundary field formulation, 
% that greatly speeds up the design process by eliminating the need to  
% repeatedly solve the wave equation.
% 
% Lastly, we validate our designs in simulation 
% (finite-difference frequency-domain, 2D tranverse electric mode) 
% by exciting the input waveguide mode and then calculating the transmitted power
% in the desired output waveguide mode.
% 
% \section{Results}
% Figs. 1, 2 and 3 show the result of our algorithm, as applied to the design 
% of nanophotonic waveguide couplers in two dimensions.  
% All devices are extremely compact, and yet exhibit high coupling efficiency; 
% even in spite of significant differences in mode size and mode symmetry.
% 
% Lastly, for numerical reasons, we allow values of $\epsilon$ to vary 
% continuously between $\epsilon_\text{air} = 1$ and 
% $\epsilon_\text{silicon} = 12.25$, even though discrete values are more
% amenable to fabrication. 
% Forcing discreteness in $\epsilon$ will be investigated in future work.
% 
% 
% This work has been supported in part by the 
% AFOSR MURI for Complex and Robust On-chip Nanophotonics (Dr. Gernot Pomrenke),
% grant number FA9550-09-1-0704.

% Coupling efficiency
% Design time
% Size of the device
% Frequency
% \begin{figure}[htbp]
%     \centering
%     \includegraphics[width=0.9\textwidth]{fig/fiber.jpg}
%     \caption{Waveguide coupler for a wide, low-index waveguide. 
%         The dielectric structure of the coupler and surrounding input and
%         output waveguides is shown on the left, while the simulation
%         validating our results is shown on the right.
%         The coupler converts $96.3\%$ of the input power to the
%         designated output mode.
%         The device is extremely compact, 
%         convering only $36 \times 66$ grid points,
%         where the vacuum wavelength is 42 grid points.
%         Computation time was 20 minutes on a personal computer.}
% \end{figure}
% \begin{figure}[htbp]
%     \centering
%     \includegraphics[width=0.9\textwidth]{fig/mode-conv.jpg}
%     \caption{Coupler that converts the fundamental waveguide mode to the
%         second-order waveguide mode.
%         This problem is quite difficult since the two modes are of 
%         opposite symmetry.
%         For example, adiabatic approaches cannot be applied to this case.
%         However, our method produces a device 
%         (which has the same dimensions and vacuum wavelength as Fig. 1) 
%         which achieves a coupling efficiency of $95.5\%$. 
%         Computation time was extended to 50 minutes to improve efficiency.
%         }
% \end{figure}
% \begin{figure}[htbp]
%     \centering
%     \includegraphics[width=0.9\textwidth]{fig/air-core.jpg}
%     \caption{Coupler to an air-core mode.
%         Here, not only are the modes of opposite symmetry,
%         but the output waveguide operates on a fundamentally different
%         principle (guided by Bragg reflection) than the input waveguide 
%         (index guided).
%         The device still achieves an efficiency of $83.3\%$, demonstrating the
%         versatility of our method.
%         The vacuum wavelength is 25 grid points, 
%         while the device footprint is still $36 \times 66$ grid points.
%         Computation time was 20 minutes.
%         }
% \end{figure}

\end{document}

### 2011-10-06 presentations/ob1_wg_paper/paper.tex
Finished Methods section (wg paper).

@@
     \item generates couplers between seemingly arbitrary waveguide modes, and
-    \item generates these couplers in a very small footprint. 
+    \item can generate these couplers in a very small footprint. 
 \end{itemize}
 
-\section{Design Method}
+\section{Methods}
 % What is objective-first optimization?
@@
     \end{subequations}
-where $\|g(x,p)\|^2$ is called the \emph{physics residual}.
+    where $\|g(x,p)\|^2$ is the \emph{physics residual}.
+We term this formulation ``objective-first''
+    because the design objective is prioritized even above satisfying physics;
+    specifically, we force our design to always exhibit the desired performance
+    ($f(x) = 0$).
 
-Such a formulation naturally lends itself to a local derivative strategy where 
-    $x$ is a dependent variable and 
-    $p$ is an independent variable. 
-The optimization then proceeds by 
+The differences between Eqs.~\ref{eq:adj} and \ref{eq:ob1} are
 \begin{enumerate}
-    \item computing $x$, given $p$, via $g(x,p) = 0$
-        (i.e. finding $x$ via simulation),
-    \item updating $p$ to decrease $f(x)$ (details in appendix).
+    \item in Eq.~\ref{eq:adj}, we attempt to decrease the design objective 
+            (Eq.~\ref{eq:adj:obj}), 
+        while in Eq.~\ref{eq:ob1}, the design objective is kept at zero 
+            (Eq.~\ref{eq:ob1:con}); 
+    \item in Eq.~\ref{eq:adj}, we always satisfy the underlying physics 
+            (Eq.~\ref{eq:adj:con}),
+        while in Eq.~\ref{eq:ob1}, physics is not satisfied,
+            since the physics residual is generally non-zero
+            (Eq.~\ref{eq:ob1:obj}).
 \end{enumerate}
 
-Not, satisfying the design objective actually has a higher priority than 
-    satisfying the underlying physical equation,
-    hence the name ``objective-first''.
+Thus, the fundamental innovation in the objective-first approach
+    is simply this:
+    we forcibly impose the desired performance on the device at the expense of
+    breaking the physics which govern its operation.
 
-Notice that the design objective is now a constraint (Eq.~\ref{eq:ob1:con}),
-and that the quantity to be decreased is now the 
-% What are the numerical advantages?
+% What are the implications of the objective-first approach?
+\subsection{Numerical implications of the objective-first approach}
+
+While the differences between the design strategies presented in 
+    Eqs.~\ref{eq:adj} and \ref{eq:ob1} are straightforward,
+    the numerical implications are more subtle.
+
+The first practical implication of the objective-first approach 
+    is that the number of independent variables is increased to include
+    both $x$ and $p$.
+In Eq.~\ref{eq:adj}, the constraint that physics must be satisfied, $g(x,p)=0$, 
+    essentially forces $x$ to be dependent on $p$,
+    since the choice of $p$ implicitly determines the value of $x$
+    (there is generally a one-to-one mapping from $p$ to $x$).
+In contrast, Eq.~\ref{eq:ob1} allows both $x$ and $p$ to vary independently,
+    because the constraint, $f(x)=0$, is only a function of $x$.
+
+Secondly, the amount of computation needed to enforce the constraint is
+    drastically reduced in the objective-first approach.
+This is because Eq.~\ref{eq:adj} requires a full solution of $g(x,p)=0$
+    (i.e. a full simulation of the structure, $p$) to compute $x$.
+In contrast, the constraint $f(x)=0$ in Eq.~\ref{eq:ob1} 
+    can often be enforced so quickly (as shown below) that 
+    future implementations may even produce designs in the same amount of time
+    as required to simulate them!
+
+Lastly, the objective-first approach eliminates the need for even a reasonable
+    initial design.
+Generally, methods based on Eq.~\ref{eq:adj} require an initial design which
+    already provides some limited functionality
+    (e.g. a coupler which already transfers 
+    a non-zero amount of power to the desired output mode).
+In constrast, methods based on Eq.~\ref{eq:ob1} perform just as well
+    when started from a completely non-functional design 
+    (e.g. a coupler which transfers no power into the desired output mode).
+
+Together, these implications result in a method
+    that is computationally fast (since it does not require simulation), and
+    that can be applied to non-intuitive problems 
+    where a functional starting design is not readily available.
+
 % How is it applied to waveguide coupler design?
+\subsection{Objective-first approach to waveguide coupler design}
+We apply an objective-first approach to the problem of designing 
+    two-dimensional nanophotonic waveguide couplers.
 
+We choose to work in the two-dimensional transverse electric mode,
+    which only couples $E_x$, $E_y$, and $H_z$ ($E_z, H_x, H_y = 0$),
+    since it is most relevant for on-chip devices\cite{}.
+We choose to use $H_z$ as the field variable, 
+    and $\epsilon^{-1}$ (inverse of the permittivity) 
+    as the structure variable.
+This results in the following representation of the physics residual, 
+    based on the time-harmonic electromagnetic wave equation without sources;
+    \begin{equation}
+    \|g(H_z, \epsilon^{-1})\|^2 = 
+    \| \nabla \times \epsilon^{-1} \nabla \times H_z - \mu \omega^2 H_z \|^2,
+    \end{equation}
+    where $\omega$ is the angular frequency,
+    and $\mu$ is the permeability of free-space.
+
+For the design objective, we choose a boundary element formulation
+    based on $H_z^\text{perfect}$,
+    where $H_z^\text{perfect}$ is constructed 
+    of the exact input and output waveguide modes at the input and output ports,
+    repectively, and of zero-amplitude fields at the unused ports.
+The actual form of the design objective is simply, 
+    \begin{equation}
+    f(H_z) = \begin{bmatrix}
+        H_z - H_z^\text{perfect} \\
+        \frac{\partial H_z}{\partial n} - 
+            \frac{\partial H_z^\text{perfect}}{\partial n}
+        \end{bmatrix}_\text{boundary}
+        = 0.
+    \end{equation}
+That is to say,
+    the values of $H_z$ and $\partial H_z / \partial n$
+    (spatial derivative along normal direction)
+    along the device boundary are forced to be 
+    those of a device with perfect performance 
+    (100\% coupling efficiency).
+
+Such a design objective is both extremely simple and widely adaptable 
+    to the design of nearly every kind of nanophotonic device.
+Most importantly, it is trivial to enforce,
+    requiring only that we overwrite boundary field values.
+Although there is ambiguity in the relative phases of 
+    the input and output boundary fields,
+    our experience suggests that successful designs are possible for 
+    arbitrary choice of relative phase.
+
+Finally, in any objective-first approach,
+    the physics residual is never guaranteed to decrease to zero.
+Thus, it is entirely possible to never achieve 
+    a physically realizable field, $H_z$.
+In such cases, which are the norm rather than the exception,
+    we find that a relatively small residual usually leads to
+    fairly good, although imperfect, device performance.
+
+\subsection{Numerical methods used to solve the objective-first design problem}
+The design problem is now
+    \begin{subequations}\label{eq:act}
+    \begin{align} 
+    \text{decrease} & \quad  
+        \| \nabla \times \epsilon^{-1} \nabla \times H_z - \mu \omega^2 H_z \|^2
+        \label{eq:act:obj} \\ 
+    \text{subject to} & \quad 
+        \left. H_z - H_z^\text{perfect} \right| _\text{boundary} = 0 
+        \label{eq:act:con1} \\
+        & \quad 
+        \left. \frac{\partial H_z}{\partial n} - 
+        \frac{\partial H_z^\text{perfect}}{\partial n} \right|_\text{boundary}
+            = 0. \label{eq:act:con2}
+    \end{align}
+    \end{subequations}
+
+This problem contains many local minima (it is non-convex\cite{});
+    however, when either the field ($H_z$) or the structure ($\epsilon^{-1}$)
+    variable is considered separately Eq.~\ref{eq:act} has only one minimum
+    (it is convex), and can be easily solved using standard methods.
+We employ such an alternating directions strategy,
+    where both $H_z$ and $\epsilon^{-1}$ are solved independently.
+This process is extremely inefficient,
+    but is employed because the underlying numerical methods
+    do not require any tuning.
+We expect considerable improvements in computational efficiency
+    when more sophisticated algorithms are applied,
+    especially those which can update $H_z$ and $\epsilon^{-1}$ independently.
+
+Lastly, we limit the allowable values of $\epsilon$ to be between
+    the permittivity of vacuum and of silicon,
+    \begin{equation}
+    \epsilon_0 \le \epsilon \le \epsilon_\text{silicon}.
+    \end{equation}
+A completely binary structure would be preferred,
+    $\epsilon = \{\epsilon_0, \epsilon_\text{silicon}\}$,
+    and will be pursued in a future work.
+That said, the final designs presented here 
+    all have significant portions which are already binary.
+
+\section{Results}
+The method described above is applied to 
+    the design of three different waveguide couplers.
 % 

### 2011-10-06 presentations/ob1_wg_paper/paper.tex
Added figures.

@@
 The method described above is applied to 
-    the design of three different waveguide couplers.
-% 
-% \section{Method}
-% The algorithm operates by calculating the boundary electromagnetic fields
-% needed for perfect operation (100\% coupling efficiency), and then varying the 
-% interior fields and permittivities to reproduce those boundary fields.  
-% Numerically, we fix $H({border}) = H_\text{perfect}$,
-% and then minimize the residual in the electromagnetic wave equation,
-% $\| \nabla \times \epsilon^{-1} \nabla \times H - \mu \omega^2 H \|^2$, 
-% by varying both $H({interior})$ (interior magnetic field) and 
-% $\epsilon$ (permittivity).
-% 
-% Note that the algorithm actually places much greater emphasis on achieving 
-% perfect device performance than even satisfying physics (the wave equation)!
-% Specifically, it is this ``objective-first'' approach, 
-% coupled with the boundary field formulation, 
-% that greatly speeds up the design process by eliminating the need to  
-% repeatedly solve the wave equation.
-% 
-% Lastly, we validate our designs in simulation 
-% (finite-difference frequency-domain, 2D tranverse electric mode) 
-% by exciting the input waveguide mode and then calculating the transmitted power
-% in the desired output waveguide mode.
-% 
-% \section{Results}
-% Figs. 1, 2 and 3 show the result of our algorithm, as applied to the design 
-% of nanophotonic waveguide couplers in two dimensions.  
-% All devices are extremely compact, and yet exhibit high coupling efficiency; 
-% even in spite of significant differences in mode size and mode symmetry.
-% 
-% Lastly, for numerical reasons, we allow values of $\epsilon$ to vary 
-% continuously between $\epsilon_\text{air} = 1$ and 
-% $\epsilon_\text{silicon} = 12.25$, even though discrete values are more
-% amenable to fabrication. 
-% Forcing discreteness in $\epsilon$ will be investigated in future work.
-% 
-% 
-% This work has been supported in part by the 
-% AFOSR MURI for Complex and Robust On-chip Nanophotonics (Dr. Gernot Pomrenke),
-% grant number FA9550-09-1-0704.
+    the design of three different waveguide couplers
+    as shown in Figs.~\ref{fig:fiber}, \ref{fig:mode} and \ref{fig:aircore}.
 
@@
 % Frequency
-% \begin{figure}[htbp]
-%     \centering
-%     \includegraphics[width=0.9\textwidth]{fig/fiber.jpg}
-%     \caption{Waveguide coupler for a wide, low-index waveguide. 
-%         The dielectric structure of the coupler and surrounding input and
-%         output waveguides is shown on the left, while the simulation
-%         validating our results is shown on the right.
-%         The coupler converts $96.3\%$ of the input power to the
-%         designated output mode.
-%         The device is extremely compact, 
-%         convering only $36 \times 66$ grid points,
-%         where the vacuum wavelength is 42 grid points.
-%         Computation time was 20 minutes on a personal computer.}
-% \end{figure}
-% \begin{figure}[htbp]
-%     \centering
-%     \includegraphics[width=0.9\textwidth]{fig/mode-conv.jpg}
-%     \caption{Coupler that converts the fundamental waveguide mode to the
-%         second-order waveguide mode.
-%         This problem is quite difficult since the two modes are of 
-%         opposite symmetry.
-%         For example, adiabatic approaches cannot be applied to this case.
-%         However, our method produces a device 
-%         (which has the same dimensions and vacuum wavelength as Fig. 1) 
-%         which achieves a coupling efficiency of $95.5\%$. 
-%         Computation time was extended to 50 minutes to improve efficiency.
-%         }
-% \end{figure}
-% \begin{figure}[htbp]
-%     \centering
-%     \includegraphics[width=0.9\textwidth]{fig/air-core.jpg}
-%     \caption{Coupler to an air-core mode.
-%         Here, not only are the modes of opposite symmetry,
-%         but the output waveguide operates on a fundamentally different
-%         principle (guided by Bragg reflection) than the input waveguide 
-%         (index guided).
-%         The device still achieves an efficiency of $83.3\%$, demonstrating the
-%         versatility of our method.
-%         The vacuum wavelength is 25 grid points, 
-%         while the device footprint is still $36 \times 66$ grid points.
-%         Computation time was 20 minutes.
-%         }
-% \end{figure}
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width=\textwidth]{fig/fiber} 
+    \caption{Waveguide coupler for a wide, low-index waveguide. 
+        The dielectric structure of the coupler and surrounding input and
+        output waveguides is shown on the left, while the simulation
+        validating our results is shown on the right.
+        The coupler converts $96.3\%$ of the input power to the
+        designated output mode.
+        The device is extremely compact, 
+        convering only $36 \times 66$ grid points,
+        where the vacuum wavelength is 42 grid points.
+        Computation time was 20 minutes on a personal computer.}
+    \label{fig:fiber}
+\end{figure}
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width=\textwidth]{fig/mode-conv} 
+    \caption{Coupler that converts the fundamental waveguide mode to the
+        second-order waveguide mode.
+        This problem is quite difficult since the two modes are of 
+        opposite symmetry.
+        For example, adiabatic approaches cannot be applied to this case.
+        However, our method produces a device 
+        (which has the same dimensions and vacuum wavelength as Fig. 1) 
+        which achieves a coupling efficiency of $95.5\%$. 
+        Computation time was extended to 50 minutes to improve efficiency.
+        }
+    \label{fig:mode}
+    \end{figure}
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width=\textwidth]{fig/air-core}
+    \caption{Coupler to an air-core mode.
+        Here, not only are the modes of opposite symmetry,
+        but the output waveguide operates on a fundamentally different
+        principle (guided by Bragg reflection) than the input waveguide 
+        (index guided).
+        The device still achieves an efficiency of $83.3\%$, demonstrating the
+        versatility of our method.
+        The vacuum wavelength is 25 grid points, 
+        while the device footprint is still $36 \times 66$ grid points.
+        Computation time was 20 minutes.
+        }
+        \label{fig:aircore}
+\end{figure}
+
+This work has been supported in part by the 
+    AFOSR MURI for Complex and Robust On-chip Nanophotonics 
+    (Dr. Gernot Pomrenke), grant number FA9550-09-1-0704.
 

### 2011-10-07 presentations/ob1_wg_paper/paper.tex
Added a bunch of figures.

@@
 
+% For all designs mention
+% fast - 20 minutes
+All results were obtained in 20 minutes on a single-core personal computer
+% subwavelength? all use only 1-4 square vacuum wavelengths
+% high performance
+
+% Special mention (arbitrariness)
+% breaking symmetry for figs 2, and 3
+% fig 3 is not even index guided
+
+% Starting point given just by e = 9
+% Mention thresholding efficiencies.
+
 % Coupling efficiency
@@
 % Frequency
-\begin{figure}[htbp]
+\begin{figure}[h]
     \centering
-    \includegraphics[width=\textwidth]{fig/fiber} 
-    \caption{Waveguide coupler for a wide, low-index waveguide. 
+    \includegraphics[width=\textwidth]{quickfig/fiber} 
+    \caption{Waveguide coupler for a wide, low-index 
+        ($\epsilon=2.25$) waveguide. 
         The dielectric structure of the coupler and surrounding input and
@@
 \end{figure}
-\begin{figure}[htbp]
+\begin{figure}[h]
     \centering
-    \includegraphics[width=\textwidth]{fig/mode-conv} 
+    \includegraphics[width=\textwidth]{quickfig/mode-conv} 
     \caption{Coupler that converts the fundamental waveguide mode to the
@@
         which achieves a coupling efficiency of $95.5\%$. 
-        Computation time was extended to 50 minutes to improve efficiency.
+        Computation time was 20 minutes on a personal computer. (movie?)
         }
@@
     \end{figure}
-\begin{figure}[htbp]
+\begin{figure}[h]
     \centering
-    \includegraphics[width=\textwidth]{fig/air-core}
+    \includegraphics[width=\textwidth]{quickfig/air-core}
     \caption{Coupler to an air-core mode.
@@
         while the device footprint is still $36 \times 66$ grid points.
-        Computation time was 20 minutes.
+        Computation time was 20 minutes on a personal computer.
         }

### 2011-10-07 presentations/ob1_wg_paper/paper.tex
First draft done.

@@
 \usepackage{graphicx}
-% \usepackage{osameet2}
+\usepackage{osameet2}
 \usepackage{amsmath,amssymb}
@@
 \author{Jesse Lu and Jelena Vu\v{c}kovi\'{c}}
-% \address{Stanford University, Stanford, California, USA.}
-% \email{jesselu@stanford.edu}
+\address{Stanford University, Stanford, California, USA.}
+\email{jesselu@stanford.edu}
 
@@
 \begin{abstract}
-We demonstrate a design algorithm which automatically generates 
-    wavelength-scale coupling devices between arbitrary waveguide modes 
-    with high efficiency.
-Our algorithm is computationally fast, 
-    can be extended to multiple dimensions,
-    and requires no trial-and-error.
+We introduce an ``objective-first'' approach to the design of
+    nanophotonic waveguide couplers.
+We show that our method is
+    computationally fast (20 minutes), 
+    requires no trial-and-error,
+    does not require a good starting design,
+    can be applied to arbitrary waveguide modes,
+    and generates devices with high coupling efficiencies (typically 95\%)
+    and small footprints (1-4 square vacuum wavelengths).
 \end{abstract}
@@
             or energy-focusing devices\cite{}.
-    \item Coupling between different materials.
-       This is to couple between passive, active\cite{}, 
-        and non-linear\cite{} materials. 
+    \item Coupling between different materials such as
+       passive, active\cite{}, and non-linear\cite{} materials. 
     \end{enumerate}
+Although efficient waveguide coupling is essential in any nanophotonic system,
+    practical methods to design couplers have not yet been developed.
 
 % Why are current solutions insufficient?
-\subsection{Common approaches to designing waveguide couplers}
+\subsection{Approaches to designing waveguide couplers}
 % Brute force
-Brute-force parameter search is the most popular nanophotonic design strategy 
+Of the design strategies currently available,
+    brute-force parameter search is the most often employed 
     to-date because of its sheer simplicity\cite{}.
@@
 % Adiabatic mode conversion (large devices, symmetry breaking)
-Adiabtic mode conversion strategies have been succesful
+Adiabatic mode conversion strategies have been succesful
     for certain fiber-waveguide\cite{} and waveguide-waveguide\cite{} couplers,
-    although resulting devices are quite large.
-However, adiabatic strategy cannot be used in many important cases such as
-    coupling from ridge to some photonic crystal waveguides,
-    coupling in the out-of-plane direction, and
+    even if the resulting devices require large footprints.
+However, adiabatic approaches cannot be used in many important cases 
+    where the mode structure is more complex, such as
+    coupling from ridge to some photonic crystal waveguides\cite{},
+    or where the geometry of the problem is non-trivial, such as
+    coupling in the out-of-plane direction, or
     coupling between modes of opposite symmetry.
@@
 % Local optimization
-Optimization methods based on local derivatives seem very promising\cite{},
+On the other hand, optimization methods based on local topological derivatives 
+    seem very promising\cite{}
     in that they are both much faster than brute-force methods and
     more adaptable than adiabatic strategies.
-However, these methods still require that every updated design be simulated
-    at least once,
-    and for the user to supply an initial design.
+However, these methods still carry a significant computational burden 
+    in that every updated design must be simulated at least once.
+Also, there is a significant burden for the user from whom
+    a good initial design is usually required.
 
 % How does your algorithm solve this problem?
-\subsection{Advantages of objective-first design}
-We present an ``objective-first'' approach to nanophotonic design, 
-    and apply it to the problem of high-efficiency waveguide couplers.
-The resulting algorithm
+% \subsection{Advantages of objective-first design}
+In contrast, our method
 \begin{itemize}
@@
 \end{itemize}
+We outline the general design strategy,
+    as well as how it is applied to nanophotonic design, in the section below.
 
@@
 
-The differences between Eqs.~\ref{eq:adj} and \ref{eq:ob1} are
+The differences between Eqs.~\ref{eq:adj} and \ref{eq:ob1} are:
 \begin{enumerate}
@@
 In Eq.~\ref{eq:adj}, the constraint that physics must be satisfied, $g(x,p)=0$, 
-    essentially forces $x$ to be dependent on $p$,
+    essentially forces $x$ to be a dependentent variable,
     since the choice of $p$ implicitly determines the value of $x$
@@
 
-Together, these implications result in a method
+In conclusion, an objective-first approach results in a method 
     that is computationally fast (since it does not require simulation), and
@@
 \subsection{Objective-first approach to waveguide coupler design}
-We apply an objective-first approach to the problem of designing 
+We now apply an objective-first approach to the problem of designing 
     two-dimensional nanophotonic waveguide couplers.
@@
     variable is considered separately Eq.~\ref{eq:act} has only one minimum
-    (it is convex), and can be easily solved using standard methods.
+    (it is convex), and can be easily solved using standard methods
+    such as employed in our previous work\cite{}.
 We employ such an alternating directions strategy,
@@
     as shown in Figs.~\ref{fig:fiber}, \ref{fig:mode} and \ref{fig:aircore}.
+These results demonstrate that our method
+    \begin{itemize}
+    \item is computationally fast, 
+        requiring only 20 minutes on a single-core personal computer;
+    \item generates compact devices with footprints of only
+        1-4 square vacuum wavelengths;
+    \item generates highly efficient devices with  
+        typical coupling efficiencies of $95\%$;
+    \item can be applied to arbitrary input and output modes,
+        as seen from the diverse selection of desired output waveguide modes;
+    \item does not require a good initial design.
+        The initial design was simply $\epsilon = 9$ everywhere
+            (a somewhat arbitrary guess, other values work as well),
+            which in the case of Figs.~\ref{fig:mode} and \ref{fig:aircore}
+            produces an initially non-functional device 
+            (coupling efficiency of $0\%$).
 
-% For all designs mention
-% fast - 20 minutes
-All results were obtained in 20 minutes on a single-core personal computer
-% subwavelength? all use only 1-4 square vacuum wavelengths
-% high performance
+    \end{itemize}
 
-% Special mention (arbitrariness)
-% breaking symmetry for figs 2, and 3
-% fig 3 is not even index guided
+Lastly, note that the couplers in Figs.~\ref{fig:mode} and \ref{fig:aircore}
+    must convert between modes of opposing symmetry,
+    in which case adiabatic approaches cannot be applied.
+Note also that the output waveguide in Fig.~\ref{fig:aircore}
+    even operates on a completely different principle 
+    (distributed reflection instead of index-guiding).
 
-% Starting point given just by e = 9
-% Mention thresholding efficiencies.
-
-% Coupling efficiency
-% Design time
-% Size of the device
-% Frequency
 \begin{figure}[h]
@@
 
+% \section{Conclusion}
+% We introduce an objective-first approach to structure design,
+%     and apply it to the design of nanophotonic waveguide couplers.
+% We show that our method is
+%     computationally fast,
+%     generates high-efficiency devices with compact footprints,
+%     does not require a good starting design, and
+%     can be applied to arbitrary waveguide modes.
+% 
+%
+
 This work has been supported in part by the 

### 2011-10-10 presentations/ob1_wg_paper/paper.tex
Copy of draft sent to Jelena.

@@
 \begin{document}
-\title{Automated Design of Nanophotonic Waveguide Couplers}
+\title{Objective-First Design of Nanophotonic Waveguide Couplers}
 \author{Jesse Lu and Jelena Vu\v{c}kovi\'{c}}
@@
     nanophotonic waveguide couplers.
-We show that our method is
+Our method is
     computationally fast (20 minutes), 
@@
 \end{abstract}
-% \ocis{230.7370, 130.3990.}
+\ocis{230.7370, 130.3990.}
 
-% \begin{thebibliography}{99}
-% \bibitem{lipson} Almeida et al, Optics Letters \textbf{28}, 1302-1304 (2003).
-% \end{thebibliography}
-% Importance of problem.
+\begin{thebibliography}{99}
+\bibitem{fibergrating} Y. Tang, Z. Wang, L. Wosinski, U. Westergren, and S. He,
+    ``Highly efficient nonuniform grating coupler for silicon-on-insulator 
+    nanophotonic circuits,''
+    Opt. Lett. \textbf{35}, 1290-1292 (2010)
+\bibitem{ridge}  K. K. Lee, D. R. Lim, L.C. Kimerling, J. Shin, and F. Cerrina, 
+    ``Fabrication of ultralow-loss Si/SiO2 waveguides by roughness reduction,''
+    Opt. Lett. \textbf{26}, 1888-1890 (2001)
+\bibitem{pcslow} Y. A. Vlasov, M. O'Boyle, H. F. Hamann, and S. J. McNab,
+    ``Active control of slow light on a chip with photonic crystal waveguides,''
+    Nature \textbf{438}, 65-69 (2005)
+\bibitem{slotfocus} M. Lipson, 
+    ``Guiding, Modulating, and Emitting Light on 
+    Silicon-Challenges and Opportunities,'' 
+    J. Lightwave Technol. \textbf{23}, 4222-4238 (2005) 
+\bibitem{active} J. Van Campenhout, P. Rojo Romeo, P. Regreny, C. Seassal, 
+    D. Van Thourhout, S. Verstuyft, L. Di Cioccio, J.-M. Fedeli, 
+    C. Lagahe, and R. Baets, 
+    ``Electrically pumped InP-based microdisk lasers integrated with a 
+    nanophotonic silicon-on-insulator waveguide circuit,'' 
+    Opt. Express \textbf{15}, 6744-6749 (2007) 
+\bibitem{metallic} L. Tang, S. E. Kocabas, S. Latif, A. K. Okyay, 
+    D. S. Ly-Gagnon, K. C. Saraswat and D. A. B. Miller, 
+    ``Nanometre-Scale Germanium Photodetector Enhanced by a 
+    Near-Infrared Dipole Antenna,'' 
+    Nature Photonics \textbf{2}, 226 – 229 (2008) 
+\bibitem{fwadia} V. R. Almeida, R. R. Panepucci, and M. Lipson, 
+    ``Nanotaper for compact mode conversion,'' 
+    Opt. Lett. \textbf{28}, 1302-1304 (2003) 
+\bibitem{wwadia} S. G. Johnson, P. Bienstman,  M. A. Skorobogatiy, 
+    M. Ibanescu1, E. Lidorikis, and J. D. Joannopoulos,
+    ``Adiabatic theorem and continuous coupled-mode theory for 
+    efficient taper transitions in photonic crystals,''
+    Phys. Rev. E \textbf{66}, 066608 (2002)
+\bibitem{deriv} F. Wang, J. S. Jensen, O. Sigmund, 
+    ``Robust topology optimization of photonic crystal waveguides with 
+    tailored dispersion properties.'' 
+    J. Opt. Soc. Am. B \textbf{28}, 387-397 (2011)
+\bibitem{boydbook} S. Boyd, and L. Vandenberghe, 
+    \emph{Convex Optimization} 
+    (Cambridge University Press, 2004)
+\bibitem{prevwork} J. Lu, S. Boyd, and J. Vuckovic, 
+    ``Inverse design of a three-dimensional nanophotonic resonator,''
+    Opt. Express \textbf{19}, 10563-10570 (2011) 
+\bibitem{code} \url{www.github.com/JesseLu/objective-first}
+\end{thebibliography}
 
@@
     \begin{enumerate}
-        \item Coupling to and from optical fiber\cite{}, 
+        \item Coupling to and from optical fiber\cite{fibergrating}, 
         to communicate with the outside world.
@@
         since different waveguides are best suited for different applications.
-        For example, ridge waveguides seem ideal for low-loss transport\cite{},
+        For example, ridge waveguides seem ideal for 
+            low-loss transport\cite{ridge},
             but other waveguides, 
             such as photonic crystal waveguides or slot waveguides,
-            may be better suited for slow-light\cite{} 
-            or energy-focusing devices\cite{}.
-    \item Coupling between different materials such as
-       passive, active\cite{}, and non-linear\cite{} materials. 
+            may be better suited for slow-light\cite{pcslow} 
+            or energy-focusing devices\cite{slotfocus}.
+    \item Coupling between different materials systems such as
+       passive, active\cite{active}, and metallic\cite{metallic} devices. 
     \end{enumerate}
@@
     brute-force parameter search is the most often employed 
-    to-date because of its sheer simplicity\cite{}.
-Although it may be suitable for tuning existing designs\cite{},
+    because of its sheer simplicity.
+Although it may be suitable for tuning existing designs,
     the parameter space for most practical devices is simply too large
@@
 Adiabatic mode conversion strategies have been succesful
-    for certain fiber-waveguide\cite{} and waveguide-waveguide\cite{} couplers,
-    even if the resulting devices require large footprints.
+    for certain fiber-waveguide\cite{fwadia} and 
+    waveguide-waveguide\cite{wwadia} couplers,
+    even if the resulting devices often require large footprints.
 However, adiabatic approaches cannot be used in many important cases 
-    where the mode structure is more complex, such as
-    coupling from ridge to some photonic crystal waveguides\cite{},
-    or where the geometry of the problem is non-trivial, such as
-    coupling in the out-of-plane direction, or
+    such as coupling in the out-of-plane direction, or
     coupling between modes of opposite symmetry.
@@
 On the other hand, optimization methods based on local topological derivatives 
-    seem very promising\cite{}
+    seem very promising\cite{deriv}
     in that they are both much faster than brute-force methods and
@@
     \item generates couplers between seemingly arbitrary waveguide modes, and
-    \item can generate these couplers in a very small footprint. 
+    \item can generate these couplers within a very small footprint. 
 \end{itemize}
 We outline the general design strategy,
-    as well as how it is applied to nanophotonic design, in the section below.
+    as well as how it is applied to coupler design, in the section below.
 
@@
 \begin{enumerate}
-    \item in Eq.~\ref{eq:adj}, we attempt to decrease the design objective 
-            (Eq.~\ref{eq:adj:obj}), 
-        while in Eq.~\ref{eq:ob1}, the design objective is kept at zero 
-            (Eq.~\ref{eq:ob1:con}); 
-    \item in Eq.~\ref{eq:adj}, we always satisfy the underlying physics 
-            (Eq.~\ref{eq:adj:con}),
-        while in Eq.~\ref{eq:ob1}, physics is not satisfied,
-            since the physics residual is generally non-zero
-            (Eq.~\ref{eq:ob1:obj}).
+    \item in Eq.~\ref{eq:adj:obj}, we attempt to decrease the design objective,
+        while in Eq.~\ref{eq:ob1:con}, the design objective is kept at zero;
+    \item in Eq.~\ref{eq:adj:con}, we always satisfy the underlying physics,
+        while in Eq.~\ref{eq:ob1:obj}, physics is not satisfied,
+            since the physics residual is generally non-zero.
 \end{enumerate}
@@
     both $x$ and $p$.
-In Eq.~\ref{eq:adj}, the constraint that physics must be satisfied, $g(x,p)=0$, 
+This occurs because in Eq.~\ref{eq:adj}, 
+    the constraint that physics must be satisfied, $g(x,p)=0$, 
     essentially forces $x$ to be a dependentent variable,
@@
 In contrast, the constraint $f(x)=0$ in Eq.~\ref{eq:ob1} 
-    can often be enforced so quickly (as shown below) that 
-    future implementations may even produce designs in the same amount of time
-    as required to simulate them!
+    can often be enforced with a trivial amount of computation (as shown below).
 
@@
     a non-zero amount of power to the desired output mode).
-In constrast, methods based on Eq.~\ref{eq:ob1} perform just as well
+In constrast, out method, based on Eq.~\ref{eq:ob1}, performs just as well
     when started from a completely non-functional design 
@@
 
-In conclusion, an objective-first approach results in a method 
-    that is computationally fast (since it does not require simulation), and
-    that can be applied to non-intuitive problems 
-    where a functional starting design is not readily available.
-
 % How is it applied to waveguide coupler design?
 \subsection{Objective-first approach to waveguide coupler design}
-We now apply an objective-first approach to the problem of designing 
+We now apply the objective-first approach to the problem of designing 
     two-dimensional nanophotonic waveguide couplers.
@@
     which only couples $E_x$, $E_y$, and $H_z$ ($E_z, H_x, H_y = 0$),
-    since it is most relevant for on-chip devices\cite{}.
+    since it is most relevant for on-chip devices.
 We choose to use $H_z$ as the field variable, 
@@
 
-Finally, in any objective-first approach,
-    the physics residual is never guaranteed to decrease to zero.
+Finally, as in any method vase on an objective-first approach,
+    the physics residual is not guaranteed to decrease to zero.
 Thus, it is entirely possible to never achieve 
@@
     \text{subject to} & \quad 
-        \left. H_z - H_z^\text{perfect} \right| _\text{boundary} = 0 
-        \label{eq:act:con1} \\
-        & \quad 
-        \left. \frac{\partial H_z}{\partial n} - 
-        \frac{\partial H_z^\text{perfect}}{\partial n} \right|_\text{boundary}
-            = 0. \label{eq:act:con2}
+        \begin{bmatrix}
+        H_z - H_z^\text{perfect} \\
+        \frac{\partial H_z}{\partial n} - 
+            \frac{\partial H_z^\text{perfect}}{\partial n}
+        \end{bmatrix}_\text{boundary}
+        = 0.
     \end{align}
@@
 
-This problem contains many local minima (it is non-convex\cite{});
+This problem contains many local minima (it is non-convex\cite{boydbook});
     however, when either the field ($H_z$) or the structure ($\epsilon^{-1}$)
@@
     (it is convex), and can be easily solved using standard methods
-    such as employed in our previous work\cite{}.
+    such as employed in our previous work\cite{prevwork}.
 We employ such an alternating directions strategy,
@@
     but is employed because the underlying numerical methods
-    do not require any tuning.
+    do not need to be tuned by the user.
 We expect considerable improvements in computational efficiency
@@
     \caption{Coupler that converts the fundamental waveguide mode to the
-        second-order waveguide mode.
+        second-order waveguide mode
+        (a movie of the design progress is included as a
+        supplementary material).
         This problem is quite difficult since the two modes are of 
@@
         (which has the same dimensions and vacuum wavelength as Fig. 1) 
-        which achieves a coupling efficiency of $95.5\%$. 
-        Computation time was 20 minutes on a personal computer. (movie?)
+        with a coupling efficiency of $95.5\%$. 
+        Computation time was 20 minutes on a personal computer.
         }
@@
         but the output waveguide operates on a fundamentally different
-        principle (guided by Bragg reflection) than the input waveguide 
+        principle (distributed reflection) than the input waveguide 
         (index guided).
@@
 
-% \section{Conclusion}
-% We introduce an objective-first approach to structure design,
-%     and apply it to the design of nanophotonic waveguide couplers.
-% We show that our method is
-%     computationally fast,
-%     generates high-efficiency devices with compact footprints,
-%     does not require a good starting design, and
-%     can be applied to arbitrary waveguide modes.
-% 
-%
-
 This work has been supported in part by the 
@@
     (Dr. Gernot Pomrenke), grant number FA9550-09-1-0704.
+The Matlab code used is available online\cite{code}.
 

### 2011-10-14 presentations/ob1_wg_paper/paper.tex
Updated with Jelena's edits.

@@
 Our method is
-    computationally fast (20 minutes), 
+    computationally fast (20 minutes on a single-core personal computer), 
     requires no trial-and-error,
-    does not require a good starting design,
+    does not require guessing a good starting design,
     can be applied to arbitrary waveguide modes,
@@
             may be better suited for slow-light\cite{pcslow} 
-            or energy-focusing devices\cite{slotfocus}.
+            or nonlinear optical devices based on 
+            localized field intensities\cite{slotfocus}.
     \item Coupling between different materials systems such as
@@
     \item in Eq.~\ref{eq:adj:obj}, we attempt to decrease the design objective,
-        while in Eq.~\ref{eq:ob1:con}, the design objective is kept at zero;
+        while in Eq.~\ref{eq:ob1:con}, the design objective is kept at zero
+        (i.e. we force the optimization to satisfy the design objective);
     \item in Eq.~\ref{eq:adj:con}, we always satisfy the underlying physics,
-        while in Eq.~\ref{eq:ob1:obj}, physics is not satisfied,
-            since the physics residual is generally non-zero.
+        while in Eq.~\ref{eq:ob1:obj}, physics is not necessarily satisfied,
+            since the physics residual is generally non-zero
+            (although the optimization is directed at minimizing this residual).
 \end{enumerate}
@@
     we forcibly impose the desired performance on the device at the expense of
-    breaking the physics which govern its operation.
+    not perfectly satisfying the physical equation which governs its operation.
 
@@
     the constraint that physics must be satisfied, $g(x,p)=0$, 
-    essentially forces $x$ to be a dependentent variable,
+    essentially forces $x$ to be a dependent variable,
     since the choice of $p$ implicitly determines the value of $x$
@@
 Secondly, the amount of computation needed to enforce the constraint is
-    drastically reduced in the objective-first approach.
+    drastically reduced in our objective-first approach.
 This is because Eq.~\ref{eq:adj} requires a full solution of $g(x,p)=0$
@@
     since it is most relevant for on-chip devices.
-We choose to use $H_z$ as the field variable, 
+We choose to use $H_z$ as the field variable ($x$ in Eq.~\ref{eq:ob1}), 
     and $\epsilon^{-1}$ (inverse of the permittivity) 
-    as the structure variable.
+    as the structure variable $p$.
 This results in the following representation of the physics residual, 
@@
     \|g(H_z, \epsilon^{-1})\|^2 = 
-    \| \nabla \times \epsilon^{-1} \nabla \times H_z - \mu \omega^2 H_z \|^2,
+    \| \nabla \times \epsilon^{-1} \nabla \times H_z - \mu_0 \omega^2 H_z \|^2,
     \end{equation}
     where $\omega$ is the angular frequency,
-    and $\mu$ is the permeability of free-space.
+    and $\mu_0$ is the permeability of free-space.
 
-For the design objective, we choose a boundary element formulation
+For the design objective, we choose a boundary-value formulation
     based on $H_z^\text{perfect}$,
     where $H_z^\text{perfect}$ is constructed 
-    of the exact input and output waveguide modes at the input and output ports,
-    repectively, and of zero-amplitude fields at the unused ports.
-The actual form of the design objective is simply, 
+    of the exact input and output waveguide modes at the input and output ports
+    of the optimization region (where the coupler will be placed),
+    repectively, and of zero-amplitude fields at the unused ports,
+    as illustrated in Fig.~\ref{fig:intro}.
+
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width=\textwidth]{quickfig/intro} 
+    \caption{Boundary-value formulation of the design objective.
+        The values of $H_z^\text{perfect}$, 
+            defined along the dashed box surrounding the design area
+            (coupling structure), 
+            are shown in orange (color online).
+        The values of $H_z^\text{perfect}$ along the top and bottom edges
+            of the dashed box are set to zero.
+        In this schematic, the fundamental and second-order waveguide modes
+            have been chosen as the input and output modes respectively.}
+    \label{fig:intro}
+\end{figure}
+
+The mathematical form of the design objective is simply, 
     \begin{equation}
@@
 
-Finally, as in any method vase on an objective-first approach,
+Finally, as in any method based on an objective-first approach,
     the physics residual is not guaranteed to decrease to zero.
@@
     \text{decrease} & \quad  
-        \| \nabla \times \epsilon^{-1} \nabla \times H_z - \mu \omega^2 H_z \|^2
-        \label{eq:act:obj} \\ 
+        \| \nabla \times \epsilon^{-1} \nabla \times H_z - 
+            \mu_0 \omega^2 H_z \|^2 \label{eq:act:obj} \\ 
     \text{subject to} & \quad 
@@
     however, when either the field ($H_z$) or the structure ($\epsilon^{-1}$)
-    variable is considered separately Eq.~\ref{eq:act} has only one minimum
+    variable is considered separately, Eq.~\ref{eq:act} has only one minimum
     (it is convex), and can be easily solved using standard methods
@@
 \section{Results}
-The method described above is applied to 
-    the design of three different waveguide couplers
-    as shown in Figs.~\ref{fig:fiber}, \ref{fig:mode} and \ref{fig:aircore}.
+We apply our method to three practically interesting problems 
+    that are hard to solve using other available methods: 
+    \begin{enumerate}
+    \item a coupler between waveguides of different refractive index and width,
+    \item a coupler between waveguide modes of different order and symmetry, and
+    \item a coupler between waveguides that confine light 
+        using different principles 
+        (index guided vs. distributed Bragg reflection guided), 
+        i.e., between a slab waveguide and a photonic crystal fiber. 
+    \end{enumerate}
+
+The corresponding designs as well as the boundary values which make up the
+    respective design objectives ($H_z^\text{perfect}$) 
+    are shown in Figs.~\ref{fig:fiber}, \ref{fig:mode} and \ref{fig:aircore}.
+As initial designs, we uniformly choose $\epsilon = 9$ throughout 
+    the whole computational region.
 These results demonstrate that our method
@@
 
-Lastly, note that the couplers in Figs.~\ref{fig:mode} and \ref{fig:aircore}
-    must convert between modes of opposing symmetry,
-    in which case adiabatic approaches cannot be applied.
-Note also that the output waveguide in Fig.~\ref{fig:aircore}
-    even operates on a completely different principle 
-    (distributed reflection instead of index-guiding).
-
-\begin{figure}[h]
+\begin{figure}[htbp]
     \centering
     \includegraphics[width=\textwidth]{quickfig/fiber} 
-    \caption{Waveguide coupler for a wide, low-index 
-        ($\epsilon=2.25$) waveguide. 
-        The dielectric structure of the coupler and surrounding input and
-        output waveguides is shown on the left, while the simulation
-        validating our results is shown on the right.
+    \caption{Coupler from a narrow, high-index ($\epsilon=12.25$) waveguide to
+        a wide, low-index ($\epsilon=2.25$) waveguide. 
+        On the left, the dielectric structure of the coupler 
+        and surrounding input and output waveguides are shown.
+        The $H_z^\text{perfect}$ boundary values used as 
+        the design objective are plotted on the left as well
+        (top and bottom boundary values were set to zero).
+        On the right, we show the simulation results used
+        to compute the performance of the device.
         The coupler converts $96.3\%$ of the input power to the
         designated output mode.
-        The device is extremely compact, 
+        The device is also extremely compact, 
         convering only $36 \times 66$ grid points,
@@
 \end{figure}
-\begin{figure}[h]
+\begin{figure}[htbp]
     \centering
@@
     \end{figure}
-\begin{figure}[h]
+\begin{figure}[htbp]
     \centering
     \includegraphics[width=\textwidth]{quickfig/air-core}
-    \caption{Coupler to an air-core mode.
+    \caption{Coupler between a dielectric slab waveguide to 
+        an air-core waveguide.
         Here, not only are the modes of opposite symmetry,
@@
 
+\section{Conclusion}
+We develop a fundamentally new approach to designing physical structures,
+    which we term ``objective-first'', 
+    in that we choose to satisfy the design objective 
+    even above satisfying the physical equation which governs its operation.
+We show that such an approach drastically reduces the
+    amount of computation required per iteration, and 
+    performs well even with a non-functional initial design.
+
+We then apply an objective-first approach to the design of 
+    three practical nanophotonic waveguide couplers which are difficult, 
+    at best, to solve with existing methods. 
+We show that our method produces
+    high-efficiency designs ($\sim 95\%$ efficiency) 
+    in small footprints ($\sim 1$ square vacuum wavelength),
+    is computationally fast (20 minutes on a single-core personal computer), and
+    does not require trial-and-error, or even 
+    a good starting design.\\
+
 This work has been supported in part by the 

### 2011-10-14 bible/1Peter1:17-19.tex
Added questions for Bible Study.

\documentclass[12pt]{article}
\begin{document}

\section{The Father's judgement (v.~17a)}
This verse begins with, ``And if\ldots'',
    which means that it is the following truth that
    demands obedience to the command in the second half of the verse.
Peter is saying, ``if $A$ is true, then you must do $B$''.
\begin{enumerate}
\item In this verse, who is being judged, Christians or unbelievers? 
    How do we know this?
\item This verse says that God's judgement is ``according to each man's work'',
    what is meant by one's ``work''?
\item Since God judges ``without partiality'', 
    how does God's standard of judgement vary from one person to the other, 
    if at all?
\end{enumerate}

\section{Conduct yourselves in fear (v.~17b)}
\begin{enumerate}
\item As believers, what are we \emph{not} to be afraid of?
\item What are we to fear?
\end{enumerate}

\section{The precious blood of Christ (v.~18-19)}
This verse begins with ``knowing\ldots'' which means
    that Peter is giving a reason why we are to obey the command in v.~17b.
Peter is arguing, ``Do $B$ because $C$ is true''.
\begin{enumerate}
\item In what way is the life was the life we were redeemed from 
    aimless and futile?
\item In what way is the life we were redeemed to purposeful and valuable?
\item What is so precious about Christ's blood, the perfect Lamb of God?
\end{enumerate}

\end{document}

### 2011-10-14 presentations/ob1_wg_paper/opex_submission/paper.tex
Version that was submitted to OpEx.

--- 2011-10-14 presentations/ob1_wg_paper/paper.tex
@@
     of the optimization region (where the coupler will be placed),
-    repectively, and of zero-amplitude fields at the unused ports,
-    as illustrated in Fig.~\ref{fig:intro}.
+    repectively, and of zero-amplitude fields at the unused ports.
 
-\begin{figure}[htbp]
-    \centering
-    \includegraphics[width=\textwidth]{quickfig/intro} 
-    \caption{Boundary-value formulation of the design objective.
-        The values of $H_z^\text{perfect}$, 
-            defined along the dashed box surrounding the design area
-            (coupling structure), 
-            are shown in orange (color online).
-        The values of $H_z^\text{perfect}$ along the top and bottom edges
-            of the dashed box are set to zero.
-        In this schematic, the fundamental and second-order waveguide modes
-            have been chosen as the input and output modes respectively.}
-    \label{fig:intro}
-\end{figure}
+% \begin{figure}[htbp]
+%     \centering
+%     \includegraphics[width=\textwidth]{intro} 
+%     \caption{Boundary-value formulation of the design objective.
+%         The values of $H_z^\text{perfect}$, 
+%             defined along the dashed box surrounding the design area
+%             (coupling structure), 
+%             are shown in orange (color online).
+%         The values of $H_z^\text{perfect}$ along the top and bottom edges
+%             of the dashed box are set to zero.
+%         In this schematic, the fundamental and second-order waveguide modes
+%             have been chosen as the input and output modes respectively.}
+%     \label{fig:intro}
+% \end{figure}
 
@@
     \centering
-    \includegraphics[width=\textwidth]{quickfig/fiber} 
+    \includegraphics[width=\textwidth]{fiber} 
     \caption{Coupler from a narrow, high-index ($\epsilon=12.25$) waveguide to
@@
     \centering
-    \includegraphics[width=\textwidth]{quickfig/mode-conv} 
+    \includegraphics[width=\textwidth]{mode-conv} 
     \caption{Coupler that converts the fundamental waveguide mode to the
@@
     \centering
-    \includegraphics[width=\textwidth]{quickfig/air-core}
+    \includegraphics[width=\textwidth]{air-core}
     \caption{Coupler between a dielectric slab waveguide to 

### 2011-10-14 presentations/cleo_2012/abstract/abstract.tex
CLEO 2012 abstract added.

--- 2011-10-03 presentations/fios_2011/abstract/abstract.tex
@@
 \end{abstract}
-\ocis{000.0000.}
+\ocis{230.7370, 130.3990.}
 
@@
 Notably, neither trial-and-error nor the modeling of device subcomponents 
-are utilized.
+is needed.
 
@@
 The algorithm operates by calculating the boundary electromagnetic fields
-needed for perfect operation (100\% conversion), and then varying the 
-interior fields and permittivities to reproduce the boundary fields.  
+needed for perfect operation (100\% coupling efficiency), and then varying the 
+interior fields and permittivities to reproduce those boundary fields.  
 Numerically, we fix $H({border}) = H_\text{perfect}$,
@@
 
-Lastly, we validate our designs in simulation (finite-difference 
-frequency-domain) by exciting the input waveguide mode and then calculating
-the transmitted power in the desired output waveguide mode.
+Lastly, we validate our designs in simulation 
+(finite-difference frequency-domain, 2D tranverse electric mode) 
+by exciting the input waveguide mode and then calculating the transmitted power
+in the desired output waveguide mode.
 
@@
 of nanophotonic waveguide couplers in two dimensions.  
+All devices are extremely compact, and yet exhibit high coupling efficiency; 
+even in spite of significant differences in mode size and mode symmetry.
 
-Note that we allow $\epsilon$ to vary continuously between the
-permittivity of air and silicon, even though discrete values are more
+Lastly, for numerical reasons, we allow values of $\epsilon$ to vary 
+continuously between $\epsilon_\text{air} = 1$ and 
+$\epsilon_\text{silicon} = 12.25$, even though discrete values are more
 amenable to fabrication. 
+Forcing discreteness in $\epsilon$ will be investigated in future work.
+
+This work has been supported in part by the 
+AFOSR MURI for Complex and Robust On-chip Nanophotonics (Dr. Gernot Pomrenke),
+grant number FA9550-09-1-0704.
+% \begin{thebibliography}{99}
+% \bibitem{lipson} Almeida et al, Optics Letters \textbf{28}, 1302-1304 (2003).
+% \end{thebibliography}
+
+% Coupling efficiency
+% Design time
+% Size of the device
+% Frequency
 \begin{figure}[htbp]
-    \includegraphics[width=\textwidth]{fig/fiber.jpg}
-    \caption{caption test}
+    \centering
+    \includegraphics[width=0.9\textwidth]{fig/fiber.jpg}
+    \caption{Waveguide coupler for a wide, low-index waveguide. 
+        The dielectric structure of the coupler and surrounding input and
+        output waveguides is shown on the left, while the simulation
+        validating our results is shown on the right.
+        The coupler converts $96.3\%$ of the input power to the
+        designated output mode.
+        The device is extremely compact, 
+        convering only $36 \times 66$ grid points,
+        where the vacuum wavelength is 42 grid points.
+        Computation time was 20 minutes on a personal computer.}
 \end{figure}
-% \includegraphics[width=\textwidth]{fig/mode-conv.jpg}
-% \includegraphics[width=\textwidth]{fig/air-core.jpg}
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width=0.9\textwidth]{fig/mode-conv.jpg}
+    \caption{Coupler that converts the fundamental waveguide mode to the
+        second-order waveguide mode.
+        This problem is quite difficult since the two modes are of 
+        opposite symmetry.
+        For example, adiabatic approaches cannot be applied to this case.
+        However, our method produces a device 
+        (which has the same dimensions and vacuum wavelength as Fig. 1) 
+        which achieves a coupling efficiency of $95.5\%$. 
+        Computation time was extended to 50 minutes to improve efficiency.
+        }
+\end{figure}
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width=0.9\textwidth]{fig/air-core.jpg}
+    \caption{Coupler to an air-core mode.
+        Here, not only are the modes of opposite symmetry,
+        but the output waveguide operates on a fundamentally different
+        principle (guided by Bragg reflection) than the input waveguide 
+        (index guided).
+        The device still achieves an efficiency of $83.3\%$, demonstrating the
+        versatility of our method.
+        The vacuum wavelength is 25 grid points, 
+        while the device footprint is still $36 \times 66$ grid points.
+        Computation time was 20 minutes.
+        }
+\end{figure}
 \end{document}

### 2011-10-16 bible/Luke12:13-48.tex
Added materials for church Bible study.

\documentclass[12pt]{article}
\begin{document}
\title{Luke 12:13-48, True Riches}
\author{Providence Bible Church Sunday School}
\maketitle
\section*{v.~15, Jesus' warning}
From v.~15, what is the relationship between 
    fullness of life and one's posessions?
\section*{v.~16-21, Parable of the rich fool}
From v.~20-21, what do we lose and what do we gain at our death?
\section*{v.~22-28, Inappropriateness of Christian worry}
From v.~28, what heart attitude produces worry over food and clothing?
\section*{v.~29-34, Seek the kingdom of God}
How does v.~33 inform us of what it means to seek the kingdom of God?
\section*{v.~29-34, Be ready}
Why is Christ's return the most important future event for the believer?
\section*{v.~41-48, God's judgement}
From v.~42-43 and v.~48, what are the two main criteria for God's
    judgement?

\section*{Supplementary: God's judgement of believers}
\begin{enumerate}
\item Based on 2 Corinthians 5:10, 
    what will God judgement toward believers be based on?
\item Based on Ephesians 2:10, how is the work of every believer determined?
\item Based on Matthew 25:14-15, where does the believer obtain the resources
    needed to accomplish his work?
\item How does Matthew 25:20-23 inform us on how God will judge believers?
\item How does 1 Corinthians 3:11-15 inform us of God's judging of believers?
\end{enumerate}
\end{document}

### 2011-10-26 presentations/ob1_wg_paper/paper.tex
Added materials for church Bible study.
Revised draft of wg coupler paper (OpEx).

@@
 Our method is
-    computationally fast (20 minutes on a single-core personal computer), 
+    computationally fast (15 minutes on a single-core personal computer), 
     requires no trial-and-error,
@@
     \centering
-    \includegraphics[width=\textwidth]{quickfig/intro} 
+    \includegraphics[width=\textwidth]{intro} 
     \caption{Boundary-value formulation of the design objective.
@@
 \section{Results}
-We apply our method to three practically interesting problems 
+We apply our method to five practically interesting problems 
     that are hard to solve using other available methods: 
@@
     \item a coupler between waveguides of different refractive index and width,
-    \item a coupler between waveguide modes of different order and symmetry, and
+    \item a coupler between waveguide modes of different order and symmetry,
     \item a coupler between waveguides that confine light 
@@
         i.e., between a slab waveguide and a photonic crystal fiber. 
+    \item a coupler from a dielectric to a plasmonic metal-insulator-metal 
+        waveguide, and
+    \item a coupler from a dielectric waveguide to a (plasmonic) metal wire.
     \end{enumerate}
@@
     \item is computationally fast, 
-        requiring only 20 minutes on a single-core personal computer;
+        requiring only 15 minutes on a single-core personal computer;
     \item generates compact devices with footprints of only
@@
     \centering
-    \includegraphics[width=\textwidth]{quickfig/fiber} 
+    \includegraphics[width=\textwidth]{1} 
     \caption{Coupler from a narrow, high-index ($\epsilon=12.25$) waveguide to
             a wide, low-index ($\epsilon=2.25$) waveguide. 
-        On the left, the dielectric structure of the coupler 
-        and surrounding input and output waveguides are shown.
         The $H_z^\text{perfect}$ boundary values used as 
-        the design objective are plotted on the left as well
-        (top and bottom boundary values were set to zero).
-        On the right, we show the simulation results used
-        to compute the performance of the device.
-        The coupler converts $96.3\%$ of the input power to the
-        designated output mode.
-        The device is also extremely compact, 
+            the design objective are plotted in the upper-left quadrant, 
+            the generated structure is shown in the upper-right quadrant, and
+            the simulated $H_z$ fields of the device are shown 
+            in the bottom two plots.
+        The computed efficiency of the coupler is high, $98.2\%$, and
+            the device is also extremely compact, 
             convering only $36 \times 66$ grid points,
             where the vacuum wavelength is 42 grid points.
-        Computation time was 20 minutes on a personal computer.}
+        Computation time was 15 minutes on a personal computer.}
     \label{fig:fiber}
@@
     \centering
-    \includegraphics[width=\textwidth]{quickfig/mode-conv} 
+    \includegraphics[width=\textwidth]{2} 
     \caption{Coupler that converts the fundamental waveguide mode to the
@@
         However, our method produces a device 
-        (which has the same dimensions and vacuum wavelength as Fig. 1) 
-        with a coupling efficiency of $95.5\%$. 
-        Computation time was 20 minutes on a personal computer.
+            (which has the same dimensions and vacuum wavelength as 
+            Fig.~\ref{fig:fiber})  
+            with a coupling efficiency of $97.0\%$. 
+        Computation time was 15 minutes on a personal computer.
         }
@@
     \centering
-    \includegraphics[width=\textwidth]{quickfig/air-core}
+    \includegraphics[width=\textwidth]{3}
     \caption{Coupler between a dielectric slab waveguide to 
@@
             (index guided).
-        The device still achieves an efficiency of $83.3\%$, demonstrating the
+        The device still achieves an efficiency of $85.1\%$, demonstrating the
             versatility of our method.
@@
             while the device footprint is still $36 \times 66$ grid points.
-        Computation time was 20 minutes on a personal computer.
+        Computation time was 15 minutes on a personal computer.
         }
         \label{fig:aircore}
+\end{figure}
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width=\textwidth]{4}
+    \caption{Coupler between a dielectric slab waveguide to 
+            a plasmonic metal-insulator-metal waveguide.
+        The efficiency of the device is $92.9\%$ and 
+            has the same wavelength and footprint as the device in
+            Fig.~\ref{fig:aircore}.
+        Computation time was 15 minutes on a personal computer.
+        }
+        \label{fig:mim}
+\end{figure}
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width=\textwidth]{5}
+    \caption{Coupler between a dielectric slab waveguide to 
+            a plasmonic wire waveguide.
+        The efficiency of the device is $93.2\%$ and 
+            has the same wavelength and footprint as the device in
+            Fig.~\ref{fig:aircore}.
+        Computation time was 15 minutes on a personal computer.
+        }
+        \label{fig:wire}
 \end{figure}
@@
 We then apply an objective-first approach to the design of 
-    three practical nanophotonic waveguide couplers which are difficult, 
+    five practical nanophotonic waveguide couplers which are difficult, 
     at best, to solve with existing methods. 
@@
     in small footprints ($\sim 1$ square vacuum wavelength),
-    is computationally fast (20 minutes on a single-core personal computer), and
+    is computationally fast (15 minutes on a single-core personal computer), and
     does not require trial-and-error, or even 

### 2011-11-11 bible/1Peter1:20-21.tex
Added 1 Peter 1:20-21 Bible study notes.

\documentclass[12pt]{article}
\begin{document}
\part*{1 Peter 1:20-21}
\section*{v.~18-19 (review), The high value of Jesus' blood}
\begin{enumerate}
    \item What is it that makes Jesus' blood so precious?
\end{enumerate}

\section*{v.~20, The preparation and presentation of the Lamb}
\begin{enumerate}
    \item How does the foreordained nature of Jesus' sacrifice
        exalt the preciousness of His blood?
    \item How does the withholding of Jesus' full manifestation
        exalt the preciousness of His blood?
\end{enumerate}

\section*{v.~21a, Belief in God through Jesus Christ}
This verse tells us that it was Jesus who 
    not only paid for our sins by His blood,
    but who also caused us to believe in God.
\begin{enumerate}
    \item How, specifically, does Jesus initiate faith in believers?
    \item How did this happen in your life?
\end{enumerate}

\section*{v.~21b, The result of redemption by Jesus' blood}
This verse presents the effect of Jesus' work of 
    redeeming us and causing us to believe in God, 
    which is in stark contrast to our previous aimless life (v.~18).
\begin{enumerate}
    \item What are the \emph{specific} promises of God
        that a believer puts his/her faith and hope in?
\end{enumerate}
\end{document}

### 2011-12-09 presentations/inv_dev_plan_dec-2011/paper.tex
Added theory for inverse design.

\documentclass{article}
\title{Theory for inverse design}
\author{Jesse Lu}
\begin{document}
\maketitle
\tableofcontents
\section{Introduction}
\subsection{Problem statement}
\subsection{Key insights/assumptions}
\section{Adjoint method}
\subsection{Computational cost}
\subsection{Multi-mode formulation}
\section{Alternating directions method of multipliers (ADMM)}
\subsection{Computational cost of ADMM}
\subsection{Multi-mode ADMM}
\end{document}

### 2011-12-12 presentations/inv_dev_plan_dec-2011/paper.tex
Partially documented adjoint method theory.

@@
 \documentclass{article}
-\title{Theory for inverse design}
+\usepackage{graphicx}
+\usepackage{amsmath}
+\usepackage{hyperref}
+
+\title{Nanophotonic Inverse Design}
 \author{Jesse Lu}
@@
 \tableofcontents
+
 \section{Introduction}
+Our goal is to produce
+    a software package capable of designing virtually any nanophotonic device.
+The software must produce designs
+    \begin{itemize}
+    \item with exceptional device performance,
+    \item which are easily manufacturable, and
+    \item with computational efficiency.
+    \end{itemize}
+
+Such a software package would be extremely useful 
+    in designing the components needed to guide light on a computer chip
+    such as couplers, filters, absorbers, and multiplexors.
+
+However, the scale of the problem as well as 
+    the difficulty of inverting the underlying wave equation
+    have been major obstacles in producing successful design algorithms.
+
 \subsection{Problem statement}
-\subsection{Key insights/assumptions}
+We formulate the design problem in the following way,
+    \begin{subequations}\begin{align}
+    \text{minimize} \quad   & f(x) + g(p) \\
+    \text{subject to} \quad & r(x, p) = 0
+    \end{align}\label{prob_stat}\end{subequations}
+    where
+    \begin{itemize}
+    \item $x$ is the field variable,
+    \item $p$ is the structure variable,
+    \item $f(x)$ is the performance objective,
+    \item $g(p)$ is the manufacturability objective,
+    \item $f(x) + g(p)$ is generally referred to as the design objective, and
+    \item $r(x,p)$ is the physics residual for which we use 
+            the time-harmonic electromagnetic wave equation,
+            \begin{equation}
+            r(x,p) = 
+                (\nabla \times \epsilon^{-1} \nabla \times - \mu \omega^2) H
+                - \text{sources}.
+            \end{equation}
+    \end{itemize}
+
+\subsection{Key insights}
+Generic nonlinear optimization routines are usually unable
+    to solve \eqref{prob_stat},
+    because there are an extremely large (millions) of variables, 
+    and because $r(x,p)$ often results in ill-conditioned matrices.
+For this reason, we need to take advantage of key features of the problem.
+\begin{itemize}
+\item $r(x,p)$ is separably affine (bi-affine) in $x$ and $p$,
+    \begin{equation}
+    r(x,p) = A(p)x - b(p) = B(x) p - d(x),
+    \end{equation}
+        this allows us to form two simpler sub-problems.
+\item Simulators which compute $A(p)^{-1} z$ are available,
+        where $z$ is an arbitrary vector, 
+        even for very large systems (millions of variables).
+\item Solving $B(x) p - d(x) = 0$ is possible with generic software, 
+        because manufacturing processes severely limit
+        the degrees of freedom of $p$ 
+        (decreasing $p$ to thousands of variables).
+\end{itemize}
+
 \section{Adjoint method}
+The adjoint method is a steepest-descent method
+    on the space $r(x,p) = 0$,
+    and relies upon the following linear approximations
+    of the design objective and the physics residual,
+    \begin{subequations}\begin{align}
+    (f(x + \Delta x) + g(p + \Delta p)) - (f(x) + g(p)) &\approx
+        \nabla f^T \Delta x + \nabla g^T \Delta p \label{d lin} \\ 
+    r(x + \Delta x, p + \Delta p) - r(x, p) &\approx
+        \nabla_x r^T \Delta x + \nabla_p r^T \Delta p. \label{r lin}
+    \end{align}\end{subequations}
+
+Assuming a starting point already satisfying $r(x,p) = 0$,
+    we note that \eqref{r lin} must equal zero,
+    in order to keep the physics residual at zero.
+This allows us to form the following relationship between
+    $\Delta x$ and $\Delta p$,
+    \begin{subequations}\begin{align}
+        A(p) \Delta x + B(x) \Delta p &= A \Delta x + B \Delta p = 0 \\
+        \Delta x &= - A^{-1} B \Delta p,
+    \end{align}\end{subequations}
+    which allows us to write \eqref{d lin} only in terms of $\Delta p$,
+    \begin{equation}
+    \nabla f^T \Delta x + \nabla g^T \Delta p =
+        - (\nabla f^T A^{-1} B - \nabla g) \Delta p.
+    \end{equation}
+Thus, we see that the steepest-descent direction is
+    \begin{equation}
+    \Delta p = B^T A^{-T} \nabla f - \nabla g.
+    \end{equation}
 \subsection{Computational cost}
@@
 \subsection{Multi-mode ADMM}
+\begin{appendix}
+\section{Constructing the relevant matrices and vectors}
+\section{Solving the matrices}
+\end{appendix}
 \end{document}

### 2011-12-12 presentations/inv_dev_plan_dec-2011/paper.tex
Started to write up theory for ADMM.

@@
 \usepackage{hyperref}
+\input defs.tex
 
@@
     \text{subject to} \quad & r(x, p) = 0
-    \end{align}\label{prob_stat}\end{subequations}
+    \end{align}\label{prob stat}\end{subequations}
     where
@@
 
-\subsection{Key insights}
+\subsubsection{Multimode formulation}
+We often desire a single device to perform multiple functions,
+    in this case we can modify \eqref{prob stat} in the following way,
+    \begin{subequations}\begin{align}
+    \text{minimize} \quad   & \sum_i f_i(x_i) + g(p) \\
+    \text{subject to} \quad & r_i(x_i, p) = 0.
+    \end{align}\label{multi stat}\end{subequations}
+
+\subsection{Key insights}\label{key insights}
 Generic nonlinear optimization routines are usually unable
-    to solve \eqref{prob_stat},
+    to solve \eqref{prob stat},
     because there are an extremely large (millions) of variables, 
@@
     \begin{equation}
-    r(x,p) = A(p)x - b(p) = B(x) p - d(x),
+    r(x,p) = A(p)x - b(p) = B(x) p - d(x), \label{bi-affine}
     \end{equation}
@@
     r(x + \Delta x, p + \Delta p) - r(x, p) &\approx
-        \nabla_x r^T \Delta x + \nabla_p r^T \Delta p. \label{r lin}
+        A(p) \Delta x + B(x) \Delta p. \label{r lin}
     \end{align}\end{subequations}
@@
     \end{equation}
+
 \subsection{Computational cost}
+The adjoint method proceeds by iteratively
+    \begin{enumerate}
+    \item updating $p$ along $\Delta p$, and then \label{adj p step}
+    \item updating $x$ by solving $r(x,p)$ for fixed $p$. \label{adj x step}
+    \end{enumerate}
+
+Computationally, step \ref{adj p step} requires an $A^{-T}$ solve,
+    and step \ref{adj x step} requires an $A^{-1}$ solve.
+The strength of the adjoint method resides in the fact that 
+    each of these operations corresponds to a \emph{single simulation},
+    and so the entire iteration costs only two simulations.
+
 \subsection{Multi-mode formulation}
+If one wishes to design a multi-functional device,
+    the adjoint method can also be applied to \eqref{multi stat}.
+In this case,
+    \begin{equation}
+    \Delta p = \sum_i B_i^T A_i^{-T} \nabla f_i - \nabla g,
+    \end{equation}
+    and each iterations costs $2N$ simulations,
+    where $N$ is the number of modes considered.
+Note that the $2N$ simulations can be spread over
+    $N$ different computational nodes,
+    so that the total running time of the optimization is   
+    virtually identical to the single-mode case.
+
+\section{Alternating directions method}
+An alternative optimization method is to iteratively solve
+    \begin{subequations}\begin{align}
+    \mathop{\rm minimize}_x \quad   & f(x) + \frac{\rho}{2} \| r(x,p) \|^2 \\
+    \mathop{\rm minimize}_p \quad   & g(p) + \frac{\rho}{2} \| r(x,p) \|^2,
+    \end{align}\end{subequations}
+    where the coefficient $\rho$ can be 
+    gradually increased in order to drive $r(x,p) \to 0$.
+
+The alternating directions method allows a non-physical starting point,
+    and takes advantage of bi-affine $r(x,p)$ in the sense that 
+    the subproblems can be re-written as
+    \begin{subequations}\begin{align}
+    \mathop{\rm minimize}_x \quad   & f(x) + 
+        \frac{\rho}{2} \| A(p)x - b(p) \|^2 \\
+    \mathop{\rm minimize}_p \quad   & g(p) + 
+        \frac{\rho}{2} \| B(x)p - d(x) \|^2,
+    \end{align}\end{subequations}
+    since each of these subproblems may be readily 
+    solved by generic optimization tools,
+    especially if both $f(x)$ and $g(p)$ are convex.
+
 \section{Alternating directions method of multipliers (ADMM)}
+The inclusion of a dual variable ($y$) allows 
+    us to form an \emph{augmented Lagrangian},
+    \begin{equation}
+    \mathcal{L}(x, p, y) = f(x) + g(p) + 
+        \frac{\rho}{2} \| r(x,p) \|^2 + y^T r(x,p).
+    \end{equation}
+This leads to the 
+    alternating directions method of multipliers (ADMM) \cite{ADMM},
+    which proceeds in the following way,
+    \begin{subequations}\begin{align}
+    x &:= \argmin_x \mathcal{L}(x,p,y) \\
+    p &:= \argmin_p \mathcal{L}(x,p,y) \\
+    y &:= y + \rho r(x,p).
+    \end{align}\end{subequations}
+Similarily to alternating directions, 
+    ADMM allows for an infeasible starting point, $r(x,p) \neq 0$.
+However, ADMM allows the coefficient $\rho$ to remain fixed,
+    and generally demonstrates faster convergence.
+
 \subsection{Computational cost of ADMM}
+We infer that the majority of computational resources 
+    will be used in updating $x$ since
+    the $y$ update is trivial, and
+    the $p$ update involves far fewer variables 
+    (see section \ref{key insights}).
+
+In this vein, we examine the computational work, for various choices of $f(x)$,
+    required in efficiently solving
+    \begin{equation}
+    \argmin_x \mathcal{L}(x,p,y) = 
+        \argmin_x f(x) + \frac{\rho}{2}\|Ax - b\|^2 + y^T(Ax - b)
+    \end{equation}
+    via Newton's method; that is, updating $x$ along $\Delta x$ given by
+    \begin{equation}
+    \Delta x = (\nabla_{xx}^2 \mathcal{L})^{-1} \nabla_x \mathcal{L}.
+    \end{equation}
+
+Furthermore, we limit our analysis to choices of $f(x)$ for which 
+    $\mathcal{L}(x,p,y)$ is quadratic,
+    since the optimum is simply $x + \Delta x$ and
+    requires only one calculation of $\Delta x$.
+Newton's method, of course, is very capable of minimizing nonlinear functions,
+    and adapting our analysis to nonlinear choices of $f(x)$ 
+    simply requires multiple steps ($\Delta x$) to be computed.
+
+\subsubsection{Linear $f(x)$}
+We investigate the choice $f(x) = c^T x$, 
+    where $c \in \reals^{n \times 1}$
+    and $x \in \reals^{n \times 1}$.
+
+\subsubsection{Low-rank quadratic $f(x)$}
+We investigate the case where $f(x) = \|C_1^T x - d_1\|$,
+    where $C_1 \in \reals^{n \times p}$
+    and $d_1 \in \reals^{p \times 1}$.
+
+\subsubsection{$f(x)$ composed of linear equality constraints}
+We investigate the situation where $f(x)$ involves
+    satisfying the equality constraint $C_2^T x = d_2$,
+    where $C_2 \in \reals^{n \times p}$
+    and $d_2 \in \reals^{p \times 1}$.
+
+\subsubsection{Combined problem}
 \subsection{Multi-mode ADMM}
@@
 \end{appendix}
+\begin{thebibliography}{99}
+\bibitem{ADMM} Boyd group ADMM paper
+\end{thebibliography}
 \end{document}

### 2011-12-12 presentations/inv_dev_plan_dec-2011/paper.tex
Added more to ADMM theory section.

@@
 \input defs.tex
+\newcommand{\inv}[1]{\frac{1}{#1}}
+\newcommand{\tC}{\tilde{C}}
 
@@
     will be used in updating $x$ since
-    the $y$ update is trivial, and
-    the $p$ update involves far fewer variables 
+    the $y$-update is trivial, and
+    the $p$-update involves far fewer variables 
     (see section \ref{key insights}).
@@
     \begin{equation}
-    \Delta x = (\nabla_{xx}^2 \mathcal{L})^{-1} \nabla_x \mathcal{L}.
+    \Delta x = (\nabla_{xx}^2 \mathcal{L})^{-1} \nabla_x \mathcal{L},
     \end{equation}
+    where
+    \begin{subequations}\begin{align}
+    \nabla_x \mathcal{L} &= \nabla f(x) + \rho A^T (A x - b + \inv{\rho}y) \\
+    \nabla_{xx}^2 \mathcal{L} &= \nabla^2 f(x) + \rho A^T A.
+    \end{align}\end{subequations}
 
@@
     and $x \in \reals^{n \times 1}$.
+Here,
+    \begin{subequations}\begin{align}
+    \nabla f(x) &= c \\
+    \nabla^2 f(x) &= 0
+    \end{align}\end{subequations}
+    which results in
+    \begin{subequations}\begin{align}
+    \nabla_x \mathcal{L} &= c + \rho A^T (A x - b + \inv{\rho} y) 
+        = \rho A^T (Ax - b + \inv{\rho}(y + \tilde{c})) \\
+    \nabla_{xx}^2 \mathcal{L} &= \rho A^T A,
+    \end{align}\end{subequations}
+    where $\tilde{c} = A^{-T} c$.
+A single Newton step is
+    \begin{equation}\begin{split}
+    \Delta x &= (\nabla_{xx}^2 \mathcal{L})^{-1} \nabla_x \mathcal{L} \\
+        &= (\rho^{-1} A^{-1} A^{-T}) 
+            A^T (A x - b + \inv{\rho}(y + \tilde c)) \\
+        &= A^{-1}(A x - b + \inv{\rho}(y + \tilde c)).
+    \end{split}\end{equation}
+
+From this analysis we see that 
+    the computation cost of a linear performance objective, $f(x)$, 
+    for the $x$-update is two simulations.
+That is, in a very similar fashion to the adjoint method,
+    an $A^{-T}$ solve is required to compute $\tilde{c}$,
+    and an additional $A^{-1}$ solve is needed to compute $\Delta x$.
 
@@
 We investigate the case where $f(x) = \|C_1^T x - d_1\|$,
-    where $C_1 \in \reals^{n \times p}$
-    and $d_1 \in \reals^{p \times 1}$.
+    where $C_1 \in \reals^{n \times p_1}$
+    and $d_1 \in \reals^{p_1 \times 1}$, for $p_1 \ll n$.
+Here,
+    \begin{subequations}\begin{align}
+    \nabla f(x) &= C_1 (C_1^T x - d_1) \\
+    \nabla^2 f(x) &= C_1 C_1^T
+    \end{align}\end{subequations}
+    which results in
+    \begin{subequations}\begin{align}
+    \nabla_x \mathcal{L} &= \rho A^T ((I + \inv{\rho}\tC_1\tC_1^T)Ax
+        - b + \inv{\rho}(y - \tC_1 d)) \\
+    \nabla_{xx}^2 \mathcal{L} &= \tC_1\tC_1^T + \rho A^T A,
+    \end{align}\end{subequations}
+    where $\tC_1 = A^{-T}C_1$.
+
+We then apply the matrix inversion lemma (see appendix \ref{inv lemma})
+    \begin{equation}\begin{split}
+    (\nabla_{xx}^2 \mathcal{L})^{-1} &= (\tC_1\tC_1^T + \rho A^T A)^{-1} \\
+        &= \inv{\rho} A^{-1} 
+            (I - \tC_1(\rho I + \tC_1^T\tC_1)^{-1}\tC_1^T) A^{-T} \\
+        &= \inv{\rho} A^{-1} M A^{-T}
+    \end{split}\end{equation}
+    where $M = I - \tC_1(\rho I + \tC_1^T\tC_1)^{-1}\tC_1^T$.
+Note that computing $M$ is computationally inexpensive
+    since the matrix which must be inverted, $\rho I + \tC_1^T\tC_1$,
+    is $p_1 \times p_1$ ($p_1 \ll n$).
+
+The Newton step is given by
+    \begin{equation}
+    \Delta x = A^{-1}M ((I + \inv{\rho}\tC_1\tC_1^T)Ax
+        - b + \inv{\rho}(y - \tC_1 d)),
+    \end{equation}
+    and requires $p_1$ solutions of $A^{-T}$ to compute $\tC_1$, 
+    and then 1 solution of $A^{-1}$ to compute $\Delta x$.
+
+\subsubsection{Concave, low-rank quadratic $f(x)$}
 
@@
     satisfying the equality constraint $C_2^T x = d_2$,
-    where $C_2 \in \reals^{n \times p}$
-    and $d_2 \in \reals^{p \times 1}$.
+    where $C_2 \in \reals^{n \times p_2}$
+    and $d_2 \in \reals^{p_2 \times 1}$.
+Once again, we assume that $p_2 \ll n$.
 
+Newton's method for a linearly-constrained quadratic function is
+    \begin{equation}
+    \begin{bmatrix} \nabla_{xx}^2 \mathcal{L} & C_2 \\ C_2^T & 0 \end{bmatrix} 
+    \begin{bmatrix} \Delta x \\ v \end{bmatrix} = 
+    \begin{bmatrix} -\nabla_x\mathcal{L} \\ C_2 x - d_2 \end{bmatrix}.
+    \end{equation}
+We assume that 
+    \begin{subequations}\begin{align}
+    (\nabla_{xx}^2 \mathcal{L})^{-1} &= A^{-1} M A^{-T} \\
+    \nabla_x \mathcal{L} &= A^T z
+    \end{align}\end{subequations}
+    and solve for $\Delta x$ 
+    using block elimination (see appendix \ref{block elim}),
+    \begin{subequations}\begin{align}
+    v &= -(\tC_2^T M^{-1} \tC_2)^{-1}(\tC_2^T Ax - d_2 + \tC_2^T Mz) \\
+    \Delta x &= -A^{-1} M (z + \tC_2 v),
+    \end{align}\end{subequations}
+    where $\tC_2 = A^{-T} C_2$.
+
+Once again, $p_2 + 1$ simulations are required, 
+    because computing $\tC_2$ requires $p_2$ solves of $A^{-T}$ and
+    computing $\Delta x$ requires 1 solve of $A^{-1}$.
+
+\subsubsection{Linearly constrained $f(x)$ with arbitrary phase}
 \subsubsection{Combined problem}
@@
 \section{Solving the matrices}
+\section{Linear algebra definitions}
+\subsection{Gradient and Hessian calculations}
+\subsection{Matrix inversion lemma}\label{inv lemma}
+\begin{equation}
+(A + UCV)^{-1} = A^{-1} - A^{-1}U (C^{-1} + V A^{-1} U)^{-1} V A^{-1}
+\end{equation}
+\subsection{Block elimination of a matrix}\label{block elim}
+\begin{equation}
+\begin{bmatrix} A_{11} & A_{12} \\ A_{21} & A_{22} \end{bmatrix} 
+\begin{bmatrix} x_1 \\ x_2 \end{bmatrix} = 
+\begin{bmatrix} b_1 \\ b_2 \end{bmatrix}
+\end{equation}
+\begin{subequations}\begin{align}
+A_{11} x_1 + A_{12} x_2 &= b_1 \\
+x_1 &= A_{11}^{-1} (b_1 - A_{12} x_2)
+\end{align}\end{subequations}
+\begin{subequations}\begin{align}
+A_{21} x_1 + A_{22} x_2 &= b_2 \\
+A_{21} A_{11}^{-1} (b_1 - A_{12} x_2) + A_{22} x_2 &= b_2 \\
+(A_{22} - A_{21} A_{11}^{-1} A_{12}) x_2 &= b_2 - A_{21} A_{11}^{-1} b_1
+\end{align}\end{subequations}
+Typically, one computes $A_{11}^{-1} A_{12}$ and $A_{11}^{-1} b_1$, 
+    and then solves for the rest of the system.
 \end{appendix}

### 2011-12-13 presentations/inv_dev_plan_dec-2011/paper.tex
Draft, excluding appendix, completed.

@@
 \subsubsection{Low-rank quadratic $f(x)$}
-We investigate the case where $f(x) = \|C_1^T x - d_1\|$,
+We investigate the case where $f(x) = \frac{1}{2}\|C_1^T x - d_1\|^2$,
     where $C_1 \in \reals^{n \times p_1}$
@@
     \Delta x = A^{-1}M ((I + \inv{\rho}\tC_1\tC_1^T)Ax
-        - b + \inv{\rho}(y - \tC_1 d)),
+        - b + \inv{\rho}(y - \tC_1 d_1)),
     \end{equation}
@@
     and then 1 solution of $A^{-1}$ to compute $\Delta x$.
-
-\subsubsection{Concave, low-rank quadratic $f(x)$}
 
@@
     \begin{subequations}\begin{align}
-    v &= -(\tC_2^T M^{-1} \tC_2)^{-1}(\tC_2^T Ax - d_2 + \tC_2^T Mz) \\
+    v &= -(\tC_2^T M \tC_2)^{-1}(\tC_2^T Ax - d_2 + \tC_2^T Mz) \\
     \Delta x &= -A^{-1} M (z + \tC_2 v),
@@
     where $\tC_2 = A^{-T} C_2$.
+    If we condense the block elimination procedure to a single step,
+    we obtain
+    \begin{equation}
+    \Delta x = -A^{-1} M (z - 
+        \tC_2 (\tC_2^T M \tC_2)^{-1}(\tC_2^T Ax - d_2 + \tC_2^T Mz)).
+    \end{equation}
 
@@
 
+\subsubsection{Combined performance objective}
+As can be seen from the previous examples,
+    efficiently computing $\Delta x$ involves transforming $Ax \to z$,
+    and then converting back, $A^{-1}z \to x$.
+It should be no surprise then, 
+    that we can also include all three performance objectives 
+    in a single $f(x)$.
+
+This results in computing
+    \begin{equation}
+    \Delta x = -A^{-1} M (z - 
+        \tC_2 (\tC_2^T M \tC_2)^{-1}(\tC_2^T Ax - d_2 + \tC_2^T Mz)),
+    \end{equation}
+    where 
+    \begin{subequations}\begin{align}
+    M &= I - \tC_1(\rho I + \tC_1^T\tC_1)^{-1}\tC_1^T \\
+    \begin{split}
+    z &= A^{-T} \nabla_x \mathcal{L} \\
+      &= \rho((I + \inv{\rho}\tC_1\tC_1^T)Ax
+        - b + \inv{\rho}(y +\tilde{c} - \tC_1 d_1))
+    \end{split} \\
+    \tilde{c} &= A^{-1} c \\
+    \tC_1 &= A^{-1} C_1 \\
+    \tC_2 &= A^{-1} C_2. 
+    \end{align}\end{subequations}
+
+As expected, the first transformation costs $1 + p_1 + p_2$ solves of $A^{-T}$,
+    and the second transformation costs 1 solve of $A^{-1}$.
+
+\subsubsection{Concave, low-rank quadratic $f(x)$}
+As a special case, we now consider the choice of 
+    $f(x) = - \frac{1}{2}\|C_1^T x \|^2$,
+    which is a quadratic, but concave, performance objective.
+We consider the case where $f(x)$ is low-rank, that is,
+    $C_1 \in \reals^{n \times p_1}$ where $p_1 \ll n$.
+
+To deal with the concavity of $f(x)$ we would like to use
+    a truncated Newton method,
+    \begin{equation}
+    \hat{\mathcal{L}}(x,p,y) = \mathcal{L}(x,p,y) + \frac{\eta}{2} \|x - x_0\|^2
+    \end{equation}
+    or even
+    \begin{equation}
+    \Delta x = -(\nabla_{xx}^2 \mathcal{L} + \eta I)^{-1}
+        \nabla_x \mathcal{L},
+    \end{equation}
+    where the coefficient $\eta$ is increased in order to 
+    ensure that the augmented Hessian is positive definite 
+    (so that $(\nabla_x\mathcal{L})^T\Delta x > 0$).
+However, this generally makes inverting the Hessian intractable.
+
+A computationally efficient alternative would be to augment $\mathcal{L}(x,p,y)$
+    in the following way,
+    \begin{equation}
+    \hat{\mathcal{L}}(x,p,y) = \mathcal{L}(x,p,y) + 
+        \frac{\eta}{2} \|A(x - x_0)\|^2
+    \end{equation}
+    so that
+    \begin{equation}
+    (\nabla_{xx}^2 \hat{\mathcal{L}})^{-1} = 
+        A^{-1} (\rho I + \eta I - \tC_1 \tC_1^T)^{-1} A^{-T}
+    \end{equation}
+    where $\tC_1 = A^{-T} C_1$ and $\nabla_{xx}^2 \mathcal{L} = \rho A^T A$.
+
+For the case $p_1 = 1$, positive definiteness can be ensured by choosing
+    $\eta = \| \tC_1 \|^2$.
+Generally, for $p_1 > 1$, $\eta$ can be set to the extremal eigenvalue of
+    $\tC_1 \tC_1^T$ in order to ensure positive definiteness.
+Efficient computation of such an eigenvalue can be performed
+    via a $QR$ factorization of $\tC_1$.
+
+The computational cost of using a truncated Newton method is that 
+    multiple steps are needed, and so $\Delta x$ must be computed many times.
+Fortunately, $\tC = A^{-T} C$ needs only to be computed once,
+    bringing the total number of solves to $n_{tn} + p_1$, 
+    where $n_{tn}$ is the number of steps needed 
+    for the truncated Newton method.
+
 \subsubsection{Linearly constrained $f(x)$ with arbitrary phase}
-\subsubsection{Combined problem}
+We now investigate another special case of $f(x)$, 
+    namely, when $f(x)$ implements the equality constraint 
+    $C_2^T x = e^{i \phi}d_2$,
+    where $C_2 \in \reals^{n \times p_2}$ and $p_2 \ll n$.
+This situation corresponds to
+    the addition of an arbitrary phase $e^{i\phi}$
+    to a linear equality constraint.
+
+We simply note that this case can be handled by computing
+    \begin{equation}
+    \Delta x = -A^{-1} M (z - 
+        \tC_2 (\tC_2^T M \tC_2)^{-1}(\tC_2^T Ax - e^{i\phi}d_2 + \tC_2^T Mz)).
+    \end{equation}
+    for different choices of $\phi$.
+The total computational cost is then simply $n_\phi + p_2$ solves,
+    where $n_\phi$ is the number of values of $\phi$ which are tried.
+
 \subsection{Multi-mode ADMM}
+Since ADMM explicitly separates updating the field and structure variables,
+    handling multiple fields is very naturally included in the formulation.
+Namely, multiple fields ($x_i$) are updated simultaneously, in parallel,
+    and then care ``connected'' by updating a single $p$ 
+    which takes all the $x_i$ into account.
+
 \begin{appendix}

### 2011-12-13 presentations/inv_dev_plan_dec-2011/paper.tex
Working on apendix still.

@@
         &= (\rho^{-1} A^{-1} A^{-T}) 
-            A^T (A x - b + \inv{\rho}(y + \tilde c)) \\
+            \rho A^T (A x - b + \inv{\rho}(y + \tilde c)) \\
         &= A^{-1}(A x - b + \inv{\rho}(y + \tilde c)).
@@
     \begin{bmatrix} \Delta x \\ v \end{bmatrix} = 
-    \begin{bmatrix} -\nabla_x\mathcal{L} \\ C_2 x - d_2 \end{bmatrix}.
+    \begin{bmatrix} -\nabla_x\mathcal{L} \\ C_2^T x - d_2 \end{bmatrix}.
     \end{equation}
@@
 
-To deal with the concavity of $f(x)$ we would like to use
-    a truncated Newton method,
+To deal with the concavity of $f(x)$ we can use a truncated Newton method,
     \begin{equation}
@@
     namely, when $f(x)$ implements the equality constraint 
-    $C_2^T x = e^{i \phi}d_2$,
+    $C_2^T x = e^{i \theta}d_2$,
     where $C_2 \in \reals^{n \times p_2}$ and $p_2 \ll n$.
 This situation corresponds to
-    the addition of an arbitrary phase $e^{i\phi}$
+    the addition of an arbitrary phase $e^{i\theta}$
     to a linear equality constraint.
@@
     \Delta x = -A^{-1} M (z - 
-        \tC_2 (\tC_2^T M \tC_2)^{-1}(\tC_2^T Ax - e^{i\phi}d_2 + \tC_2^T Mz)).
+        \tC_2 (\tC_2^T M \tC_2)^{-1}(\tC_2^T Ax - e^{i\theta}d_2 + \tC_2^T Mz)).
     \end{equation}
-    for different choices of $\phi$.
-The total computational cost is then simply $n_\phi + p_2$ solves,
-    where $n_\phi$ is the number of values of $\phi$ which are tried.
+    for different choices of $\theta$.
+The total computational cost is then simply $n_\theta + p_2$ solves,
+    where $n_\theta$ is the number of values of $\theta$ which are tried.
 
@@
 Namely, multiple fields ($x_i$) are updated simultaneously, in parallel,
-    and then care ``connected'' by updating a single $p$ 
+    and then are ``connected'' by updating a single $p$ 
     which takes all the $x_i$ into account.
@@
 \section{Constructing the relevant matrices and vectors}
+The physics residual is based on the electromagnetic wave equation, 
+    \begin{equation}
+    \nabla \times \epsilon^{-1} \nabla \times H - \mu \omega^2 H - 
+        \nabla \times \epsilon^{-1} J - i \omega M = 0,
+    \end{equation}
+    which can be written as
+    \begin{equation}
+    r(x,p) = A(p) x - b(x) = B(x) p - d(x).
+    \end{equation}
+
+\subsection{Defining the curl operators}
+Specifically, the curl operations are defined as
+    \begin{equation}
+    \nabla^\pm \times u = \begin{bmatrix}
+        D_y^\pm u_z - D_z^\pm u_y \\
+        D_z^\pm u_x - D_x^\pm u_z \\
+        D_x^\pm u_y - D_y^\pm u_x
+        \end{bmatrix}
+    \end{equation}
+    where
+    \begin{subequations}\begin{align}
+    D_x^- v &= \frac{v(i,j,k) - v(i-1,j,k)}{\phi_x(i-\frac{1}{2})} \\
+    D_x^+ v &= \frac{v(i+1,j,k) - v(i,j,k)}{\phi_x(i+\frac{1}{2})},
+    \end{align}\end{subequations}
+    and likewise for the numerical derivatives in the $y$ and $z$ directions.
+Note that we assume that $\Delta x, \Delta y, \Delta z = 1$, and so omit them
+    from the denominators of $D$.
+
+Lastly, the $\phi$ functions are used to construct 
+    absorbing boundary conditions.
+Specifically, we use stretched-coordinate perfectly matched layers\cite{scpml}
+    for which $\phi$ is defined as
+    \begin{equation}
+    \phi_x(x) = \begin{cases}
+        1 + \frac{i\sigma}{\omega} x^m & x < t_\text{PML}, \\ 
+        1 + \frac{i\sigma}{\omega} (x_\text{max} -x)^m
+            & x > x_\text{max} - t_\text{PML}, \\ 
+        1 & \text{otherwise,}
+        \end{cases}
+    \end{equation}
+    where $\sigma$ is the strength of the absorbing layer, 
+    and $m$ controls the profile of the layer.
+Typical values for $\sigma$ and $m$ are $1$ and $2.5$ respectively.
+
+\subsection{Forming the field subproblem}
+$A(p)$ and $b(p)$ are constructed as follows,
+    \begin{subequations}\begin{align}
+    A(p) &= A_1 \diag(\epsilon(p)^{-1}) A_2 - \mu \omega^2 I \\
+    b(p) &= A_1 \diag(\epsilon(p)^{-1}) b_j + i \omega b_m \\
+    A_1 &= \nabla^- \times \\
+    A_2 &= \nabla^+ \times \\
+    b_j &= J \\
+    b_m &= M,
+    \end{align}\end{subequations}
+    where $\nabla^+$ and $\nabla^-$ refer to forward- and backward-differencing
+    respectively.
+
+\subsection{Forming the structure subproblem}
+We now show how to form $r(x,p) = B(x)p - d(x)$.
+
 \section{Solving the matrices}
@@
 \subsection{Gradient and Hessian calculations}
+Mention something about complex values.
 \subsection{Matrix inversion lemma}\label{inv lemma}
@@
 \bibitem{ADMM} Boyd group ADMM paper
+\bibitem{scpml} \url{http://math.mit.edu/~stevenj/18.369/pml.pdf}
 \end{thebibliography}

### 2011-12-14 presentations/inv_dev_plan_dec-2011/paper.tex
Draft of theory notes for admm finished.

@@
     \nabla \times \epsilon^{-1} \nabla \times H - \mu \omega^2 H - 
-        \nabla \times \epsilon^{-1} J - i \omega M = 0,
+        \nabla \times \epsilon^{-1} J - i \omega M = 0, \label{em wave}
     \end{equation}
@@
 \subsection{Defining the curl operators}
-Specifically, the curl operations are defined as
-    \begin{equation}
-    \nabla^\pm \times u = \begin{bmatrix}
-        D_y^\pm u_z - D_z^\pm u_y \\
-        D_z^\pm u_x - D_x^\pm u_z \\
-        D_x^\pm u_y - D_y^\pm u_x
+The various curl operators in \eqref{em wave} do not all
+    correspond to the same matrix.
+We use both forward-differencing $(\nabla^+)$
+    and backward-differencing $(\nabla^-)$ curl operators.
+These are defined as
+    \begin{subequations}\begin{align}
+    \nabla^\pm \times u &= \begin{bmatrix}
+        0 & -S_z^\pm D_z^\pm & S_y^\pm D_y^\pm \\
+        S_z^\pm D_z^\pm & 0 & -S_x^\pm D_x^\pm \\
+        -S_y^\pm D_y^\pm & S_x^\pm D_x^\pm & 0 \end{bmatrix}
+        \begin{bmatrix} u_x \\ u_y \\ u_z \end{bmatrix}
+    \\
+    &= \begin{bmatrix}
+        S_y^\pm D_y^\pm u_z - S_z^\pm D_z^\pm u_y \\
+        S_z^\pm D_z^\pm u_x - S_x^\pm D_x^\pm u_z \\
+        S_x^\pm D_x^\pm u_y - S_y^\pm D_y^\pm u_x
         \end{bmatrix}
-    \end{equation}
-    where
+    \end{align}\end{subequations}
+    where the $D\pm$ matrices perform either forward- or backward-differencing,
+    and the $S^\pm$ matrices implement the stretched-coordinate 
+    absorbing boundary conditions\cite{scpml}.
+
+These matrices are defined as follows,
     \begin{subequations}\begin{align}
-    D_x^- v &= \frac{v(i,j,k) - v(i-1,j,k)}{\phi_x(i-\frac{1}{2})} \\
-    D_x^+ v &= \frac{v(i+1,j,k) - v(i,j,k)}{\phi_x(i+\frac{1}{2})},
+    D_x^+ u_w &= \frac{u_w(i+1,j,k) - u_w(i,j,k)}{\Delta x} \\
+    D_x^- u_w &= \frac{u_w(i,j,k) - u_w(i-1,j,k)}{\Delta x} \\
+    S_x^+ v &= \frac{v(i,j,k)}{\phi_x(i+\frac{1}{2})} \\
+    S_x^- v &= \frac{v(i,j,k)}{\phi_x(i)}, 
     \end{align}\end{subequations}
-    and likewise for the numerical derivatives in the $y$ and $z$ directions.
-Note that we assume that $\Delta x, \Delta y, \Delta z = 1$, and so omit them
-    from the denominators of $D$.
-
-Lastly, the $\phi$ functions are used to construct 
-    absorbing boundary conditions.
-Specifically, we use stretched-coordinate perfectly matched layers\cite{scpml}
-    for which $\phi$ is defined as
+    and likewise for the $y$ and $z$ directions.
+Here, the $w$ subscript signifies either $x$, $y$, or $z$,
+    while $v$ is just a placeholder vector.
+Also, the $\phi$ functions are defined according to \cite{scpml} as
     \begin{equation}
@@
     \end{equation}
-    where $\sigma$ is the strength of the absorbing layer, 
-    and $m$ controls the profile of the layer.
-Typical values for $\sigma$ and $m$ are $1$ and $2.5$ respectively.
+    where $\sigma$ is the strength of the perfectly-matched layer (PML), 
+    $m$ controls the profile of the PML,
+    and $t_\text{PML}$ is the thickness of the PML.
+Typical values for $\sigma$, $m$, and $t_\text{PML}$ are 
+    $1.0$, $2.5$, and $10$ respectively.
+
+Lastly, the $D$ matrices impose periodic (wrap-around) boundary conditions
+    for cells adjacent to the boundary.
+Also, note that the assymetry in the definition of the $S^\pm$ matrices
+    is due to the structure of the Yee cell\cite{yee cell}.
 
@@
     A(p) &= A_1 \diag(\epsilon(p)^{-1}) A_2 - \mu \omega^2 I \\
-    b(p) &= A_1 \diag(\epsilon(p)^{-1}) b_j + i \omega b_m \\
-    A_1 &= \nabla^- \times \\
-    A_2 &= \nabla^+ \times \\
+    b(p) &= A_1 \diag(\epsilon(p)^{-1}) b_j + i \omega b_m, \\
+    \end{align}\end{subequations}
+    where
+    \begin{subequations}\begin{align}
+    A_1 &= \nabla^+ \times \\
+    A_2 &= \nabla^- \times \\
     b_j &= J \\
-    b_m &= M,
+    b_m &= M.
     \end{align}\end{subequations}
-    where $\nabla^+$ and $\nabla^-$ refer to forward- and backward-differencing
-    respectively.
 
@@
 We now show how to form $r(x,p) = B(x)p - d(x)$.
+    \begin{subequations}\begin{align}
+    r(x,p) &= A(p)x - b(p) \\
+        &= (A_1 \diag(\epsilon(p)^{-1}) A_2 - \mu \omega^2 I) x - 
+            (A_1 \diag(\epsilon(p)^{-1}) b_j + i \omega b_m) \\ 
+        &= A_1 \diag(\epsilon(p)^{-1}) (A_2 x - b_j) - 
+            (\mu \omega^2 x + i \omega b_m) \\ 
+        &= A_1 \diag(A_2 x - b_j) \epsilon(p)^{-1} - 
+            (\mu \omega^2 x + i \omega b_m),
+    \end{align}\end{subequations}
+    and choosing $\epsilon(p)^{-1} = A_3 p + p_0$, we obtain
+    \begin{subequations}\begin{align}
+    r(x,p) &= A_1 \diag(A_2 x - b_j) (A_3 p + p_0) - 
+            (\mu \omega^2 x + i \omega b_m) \\
+        &= B(x) p - d(x),
+    \end{align}\end{subequations}
+    where
+    \begin{subequations}\begin{align}
+    B(x) &= A_1 \diag(A_2 x - b_j) A_3\\
+    d(x) &= \mu \omega^2 x + i \omega b_m - A_1 \diag(A_2 x - b_j) p_0.
+    \end{align}\end{subequations}
 
@@
 \subsection{Gradient and Hessian calculations}
-Mention something about complex values.
+The following convention is assumed throughout these notes.
+Given $f(x) \in \reals^n \to \reals$,
+    \begin{equation}
+    \nabla f(x) = \begin{bmatrix}
+        \frac{df}{dx_1} \\
+        \frac{df}{dx_2} \\
+        \vdots
+        \end{bmatrix}
+    \end{equation}
+    and
+    \begin{equation}
+    \nabla^2 f(x) = \begin{bmatrix}
+        \frac{d^2f}{dx_1^2} & \frac{d^2f}{dx_1 dx_2} & \cdots \\
+        \frac{d^2f}{dx_2 dx_1} & \frac{d^2f}{dx_2^2} & \cdots \\
+        \vdots & \vdots & \ddots
+        \end{bmatrix}.
+    \end{equation}
+
+\subsection{Handling complex values}
+
 \subsection{Matrix inversion lemma}\label{inv lemma}
+The matrix inversion simply states that
 \begin{equation}
-(A + UCV)^{-1} = A^{-1} - A^{-1}U (C^{-1} + V A^{-1} U)^{-1} V A^{-1}
+(A + UCV)^{-1} = A^{-1} - A^{-1}U (C^{-1} + V A^{-1} U)^{-1} V A^{-1}.
 \end{equation}
-\subsection{Block elimination of a matrix}\label{block elim}
+
+\subsection{Block-elimination of a matrix}\label{block elim}
+Solving $Ax=b$ via block-elimination involves first splitting the problem up as
     \begin{equation}
@@
     \begin{bmatrix} x_1 \\ x_2 \end{bmatrix} = 
-\begin{bmatrix} b_1 \\ b_2 \end{bmatrix}
+    \begin{bmatrix} b_1 \\ b_2 \end{bmatrix},
     \end{equation}
+    solving for $x_1$ in terms of $x_2$, 
     \begin{subequations}\begin{align}
     A_{11} x_1 + A_{12} x_2 &= b_1 \\
-x_1 &= A_{11}^{-1} (b_1 - A_{12} x_2)
+    x_1 &= A_{11}^{-1} (b_1 - A_{12} x_2), \label{x1 solve}
     \end{align}\end{subequations}
+    substituting in order to solve for $x_2$,
     \begin{subequations}\begin{align}
@@
     \end{align}\end{subequations}
-Typically, one computes $A_{11}^{-1} A_{12}$ and $A_{11}^{-1} b_1$, 
+    and then plugging the solution in to \eqref{x1 solve} to back out $x_1$.
+Typically, one pre-computes $A_{11}^{-1} A_{12}$ and $A_{11}^{-1} b_1$, 
     and then solves for the rest of the system.
+
+Additionally, if we are only concerned about the value of $x_1$,
+    we can simply use the formula
+    \begin{equation}
+    x_1 = A_{11}^{-1} (b_1 - A_{12} 
+        (A_{22} - A_{21} A_{11}^{-1} A_{12})^{-1}
+        (b_2 - A_{21} A_{11}^{-1} b_1)).
+    \end{equation}
 \end{appendix}

### 2011-12-15 presentations/ob1_wg_paper/paper.tex
Made changes to ob1 wg paper.

@@
 \begin{document}
-\title{Objective-First Design of Nanophotonic Waveguide Couplers}
+\title{High-Efficiency, Small-Footprint Couplers Between 
+    Arbitrary Nanophotonic Waveguide Modes in Two Dimensions}
 \author{Jesse Lu and Jelena Vu\v{c}kovi\'{c}}
@@
 \begin{abstract}
-We introduce an ``objective-first'' approach to the design of
-    nanophotonic waveguide couplers.
-Our method is
+We develop a design algorithm which can design 
+    high efficiency ($\sim$95\%), 
+    small-footprint (1-4 square vacuum wavelengths)
+    couplers between arbitrary nanophotonic waveguide modes.
+Such a capability is extremely useful since it fundamentally allows for the
+    design of all linear optical devices.
+Our ``objective-first'' method is
     computationally fast (15 minutes on a single-core personal computer), 
-    requires no trial-and-error,
-    does not require guessing a good starting design,
-    can be applied to arbitrary waveguide modes,
-    and generates devices with high coupling efficiencies (typically 95\%)
-    and small footprints (1-4 square vacuum wavelengths).
+    requires no trial-and-error, and
+    does not require guessing a good starting design.
 \end{abstract}
@@
     is a fundamental requirement in nanophotonics.
-Efficient conversion between waveguides modes
-    is critical in the many cases, including:
+In fact, the problem of converting between nanophotonic modes is essentially
+    the function of \emph{all} linear nanophotonic devices.
+For instance, efficient conversion between waveguides modes
+    is useful for:
     \begin{enumerate}
@@
 \section{Results}
-We apply our method to five practically interesting problems 
-    that are hard to solve using other available methods: 
+We now present evidence that the method outlined above 
+    is indeed able to design coupling structures between essentially
+    any two nanophotonic waveguide modes.
+To do so, we apply our method to the following five problems:
     \begin{enumerate}
-    \item a coupler between waveguides of different refractive index and width,
-    \item a coupler between waveguide modes of different order and symmetry,
-    \item a coupler between waveguides that confine light 
+    \item coupling between waveguides of different refractive index and width,
+    \item coupling between waveguide modes of different order and symmetry,
+    \item coupling between waveguides that confine light 
         using different principles 
@@
         i.e., between a slab waveguide and a photonic crystal fiber. 
-    \item a coupler from a dielectric to a plasmonic metal-insulator-metal 
+    \item coupling from a dielectric to a plasmonic metal-insulator-metal 
         waveguide, and
-    \item a coupler from a dielectric waveguide to a (plasmonic) metal wire.
+    \item coupling from a dielectric waveguide to a (plasmonic) metal wire,
     \end{enumerate}
-
-The corresponding designs as well as the boundary values which make up the
-    respective design objectives ($H_z^\text{perfect}$) 
-    are shown in Figs.~\ref{fig:fiber}, \ref{fig:mode} and \ref{fig:aircore}.
-As initial designs, we uniformly choose $\epsilon = 9$ throughout 
-    the whole computational region.
-These results demonstrate that our method
-    \begin{itemize}
-    \item is computationally fast, 
-        requiring only 15 minutes on a single-core personal computer;
-    \item generates compact devices with footprints of only
-        1-4 square vacuum wavelengths;
-    \item generates highly efficient devices with  
-        typical coupling efficiencies of $95\%$;
-    \item can be applied to arbitrary input and output modes,
-        as seen from the diverse selection of desired output waveguide modes;
-    \item does not require a good initial design.
-        The initial design was simply $\epsilon = 9$ everywhere
-            (a somewhat arbitrary guess, other values work as well),
-            which in the case of Figs.~\ref{fig:mode} and \ref{fig:aircore}
-            produces an initially non-functional device 
-            (coupling efficiency of $0\%$).
-
-    \end{itemize}
-
+    the results of which are shown in Figs.~\ref{fig:fiber}-\ref{fig:wire}.
 \begin{figure}[htbp]
     \centering
-    \includegraphics[width=\textwidth]{1} 
+    \includegraphics[width=0.8\textwidth]{1} 
     \caption{Coupler from a narrow, high-index ($\epsilon=12.25$) waveguide to
@@
     \centering
-    \includegraphics[width=\textwidth]{2} 
+    \includegraphics[width=0.8\textwidth]{2} 
     \caption{Coupler that converts the fundamental waveguide mode to the
@@
     \centering
-    \includegraphics[width=\textwidth]{3}
+    \includegraphics[width=0.8\textwidth]{3}
     \caption{Coupler between a dielectric slab waveguide to 
@@
     \centering
-    \includegraphics[width=\textwidth]{4}
+    \includegraphics[width=0.8\textwidth]{4}
     \caption{Coupler between a dielectric slab waveguide to 
@@
     \centering
-    \includegraphics[width=\textwidth]{5}
+    \includegraphics[width=0.8\textwidth]{5}
     \caption{Coupler between a dielectric slab waveguide to 
@@
 \end{figure}
+
+These results clearly demonstrate that our method
+    \begin{itemize}
+    \item can be applied to arbitrary input and output modes,
+        as seen from the diverse selection of desired output waveguide modes;
+    \item generates highly efficient devices with  
+        typical coupling efficiencies of $95\%$;
+    \item generates compact devices with footprints of only
+        1-4 square vacuum wavelengths;
+    \item does not require a good initial design.
+        The initial design was simply $\epsilon = 9$ everywhere
+            (a somewhat arbitrary guess, other values work as well),
+            which in almost every case
+            produces an initially non-functional device 
+            (coupling efficiency of $0\%$);
+    \item is computationally fast, 
+        requiring only 15 minutes on a single-core personal computer.
+    \end{itemize}
+
+Critically, these results form a key advancement in our understanding of 
+    nanophotonic design; namely, 
+    that it is indeed possible to efficiently design
+    virtually any linear optical device using an objective-first approach.
 
@@
     high-efficiency designs ($\sim 95\%$ efficiency) 
-    in small footprints ($\sim 1$ square vacuum wavelength),
+    in small footprints ($\sim 1$ square vacuum wavelength)
+    between arbitrary waveguide modes.
+Furthermore, out method
     is computationally fast (15 minutes on a single-core personal computer), and

### 2012-01-04 presentations/ob1_wg_paper/paper.tex
Half done editing ob1 paper

@@
 \title{High-Efficiency, Small-Footprint Couplers Between 
-    Arbitrary Nanophotonic Waveguide Modes in Two Dimensions}
+    Arbitrary Nanophotonic Waveguide Modes}
 \author{Jesse Lu and Jelena Vu\v{c}kovi\'{c}}
@@
 \begin{abstract}
-We develop a design algorithm which can design 
+We develop an algorithm for designing
     high efficiency ($\sim$95\%), 
     small-footprint (1-4 square vacuum wavelengths)
-    couplers between arbitrary nanophotonic waveguide modes.
-Such a capability is extremely useful since it fundamentally allows for the
-    design of all linear optical devices.
+    couplers between arbitrary nanophotonic waveguide modes
+    in two dimensions.
 Our ``objective-first'' method is
@@
     does not require guessing a good starting design.
+We demonstrate designs for various coupling problems which suggest 
+    that our method allows for the design of any linear optical device.
 \end{abstract}
@@
 % Why is waveguide mode conversion important?
-\subsection{The importance of waveguide mode conversion}
 Optical mode conversion, 
@@
     is a fundamental requirement in nanophotonics.
-In fact, the problem of converting between nanophotonic modes is essentially
-    the function of \emph{all} linear nanophotonic devices.
 For instance, efficient conversion between waveguides modes
-    is useful for:
-    \begin{enumerate}
+    is essential for:
+    \begin{itemize}
         \item Coupling to and from optical fiber\cite{fibergrating}, 
@@
        passive, active\cite{active}, and metallic\cite{metallic} devices. 
-    \end{enumerate}
-Although efficient waveguide coupling is essential in any nanophotonic system,
-    practical methods to design couplers have not yet been developed.
+    \end{itemize}
+In fact, the problem of converting between nanophotonic modes is essentially
+    the function of all linear nanophotonic devices, since
+    any linear device is completely characterized by its input and output modes.
 
-% Why are current solutions insufficient?
-\subsection{Approaches to designing waveguide couplers}
-% Brute force
-Of the design strategies currently available,
-    brute-force parameter search is the most often employed 
-    because of its sheer simplicity.
-Although it may be suitable for tuning existing designs,
-    the parameter space for most practical devices is simply too large
-    for such a strategy to be tractable.
+In this paper, we propose a design algorithm which, 
+    we believe, solves this problem.
+Namely, we outline a method capable of designing nanophotonic devices
+    to efficiently transfer photons between 
+    arbitrary input and output modes,
+    and we demonstrate this method by designing various nanophotonic couplers
+    between different waveguides.
 
-% Adiabatic mode conversion (large devices, symmetry breaking)
-Adiabatic mode conversion strategies have been succesful
-    for certain fiber-waveguide\cite{fwadia} and 
-    waveguide-waveguide\cite{wwadia} couplers,
-    even if the resulting devices often require large footprints.
-However, adiabatic approaches cannot be used in many important cases 
-    such as coupling in the out-of-plane direction, or
-    coupling between modes of opposite symmetry.
-
-% Local optimization
-On the other hand, optimization methods based on local topological derivatives 
-    seem very promising\cite{deriv}
-    in that they are both much faster than brute-force methods and
-    more adaptable than adiabatic strategies.
-However, these methods still carry a significant computational burden 
-    in that every updated design must be simulated at least once.
-Also, there is a significant burden for the user from whom
-    a good initial design is usually required.
+Furthermore, we show that our method 
+     does not employ brute-force parameter searches;
+     does not require a good initial design;
+     is computationally fast (no simulations required);
+     and can generate high efficiency couplers within a very small footprint. 
+% 
+% 
+% % Why are current solutions insufficient?
+% % Brute force
+% Of the design strategies currently available,
+%     brute-force parameter search is the most often employed 
+%     because of its sheer simplicity.
+% Although it may be suitable for tuning existing designs,
+%     the parameter space for most practical devices is simply too large
+%     for such a strategy to be tractable.
+% 
+% % Adiabatic mode conversion (large devices, symmetry breaking)
+% Adiabatic mode conversion strategies have been succesful
+%     for certain fiber-waveguide\cite{fwadia} and 
+%     waveguide-waveguide\cite{wwadia} couplers,
+%     even if the resulting devices often require large footprints.
+% However, adiabatic approaches cannot be used in many important cases 
+%     such as coupling in the out-of-plane direction, or
+%     coupling between modes of opposite symmetry.
 
@@
 % \subsection{Advantages of objective-first design}
-In contrast, our method
-\begin{itemize}
-    \item does not employ brute-force parameter searches,
-    \item does not require a good initial design,
-    \item is computationally fast (no simulations required),
-    \item generates couplers between seemingly arbitrary waveguide modes, and
-    \item can generate these couplers within a very small footprint. 
-\end{itemize}
-We outline the general design strategy,
-    as well as how it is applied to coupler design, in the section below.
-
-\section{Methods}
+\section{Objective-first formulation}
 % What is objective-first optimization?
-\subsection{Objective-first optimization}
 The typical approach to designing physical structures can be formulated 
-    in the following way, 
-    where $x$ is the field variable and $p$ is the structure variable,
+    in the following way:
     \begin{subequations}\label{eq:adj}
@@
     \text{decrease} & \quad f(x) \label{eq:adj:obj} \\ 
-    \text{subject to} & \quad g(x,p) = 0. \label{eq:adj:con}
+    \text{subject to} & \quad g(x,p) = 0, \label{eq:adj:con}
     \end{align}
     \end{subequations}
+    where $x$ is the field variable and $p$ is the structure variable.
 Here, $f(x)$, the \emph{design objective}, 
@@
     specifically, we force our design to always exhibit the desired performance
-    ($f(x) = 0$).
+    ($f(x) = 0$), even at the expense of
+    not perfectly satisfying the underlying physics which governs its operation.
 
-The differences between Eqs.~\ref{eq:adj} and \ref{eq:ob1} are:
-\begin{enumerate}
-    \item in Eq.~\ref{eq:adj:obj}, we attempt to decrease the design objective,
-        while in Eq.~\ref{eq:ob1:con}, the design objective is kept at zero
-        (i.e. we force the optimization to satisfy the design objective);
-    \item in Eq.~\ref{eq:adj:con}, we always satisfy the underlying physics,
-        while in Eq.~\ref{eq:ob1:obj}, physics is not necessarily satisfied,
-            since the physics residual is generally non-zero
-            (although the optimization is directed at minimizing this residual).
-\end{enumerate}
-
-Thus, the fundamental innovation in the objective-first approach
-    is simply this:
-    we forcibly impose the desired performance on the device at the expense of
-    not perfectly satisfying the physical equation which governs its operation.
-
-% What are the implications of the objective-first approach?
-\subsection{Numerical implications of the objective-first approach}
-
-While the differences between the design strategies presented in 
-    Eqs.~\ref{eq:adj} and \ref{eq:ob1} are straightforward,
-    the numerical implications are more subtle.
-
-The first practical implication of the objective-first approach 
-    is that the number of independent variables is increased to include
-    both $x$ and $p$.
-This occurs because in Eq.~\ref{eq:adj}, 
-    the constraint that physics must be satisfied, $g(x,p)=0$, 
-    essentially forces $x$ to be a dependent variable,
-    since the choice of $p$ implicitly determines the value of $x$
-    (there is generally a one-to-one mapping from $p$ to $x$).
-In contrast, Eq.~\ref{eq:ob1} allows both $x$ and $p$ to vary independently,
-    because the constraint, $f(x)=0$, is only a function of $x$.
-
-Secondly, the amount of computation needed to enforce the constraint is
-    drastically reduced in our objective-first approach.
-This is because Eq.~\ref{eq:adj} requires a full solution of $g(x,p)=0$
-    (i.e. a full simulation of the structure, $p$) to compute $x$.
-In contrast, the constraint $f(x)=0$ in Eq.~\ref{eq:ob1} 
-    can often be enforced with a trivial amount of computation (as shown below).
-
-Lastly, the objective-first approach eliminates the need for even a reasonable
-    initial design.
-Generally, methods based on Eq.~\ref{eq:adj} require an initial design which
-    already provides some limited functionality
-    (e.g. a coupler which already transfers 
-    a non-zero amount of power to the desired output mode).
-In constrast, out method, based on Eq.~\ref{eq:ob1}, performs just as well
-    when started from a completely non-functional design 
-    (e.g. a coupler which transfers no power into the desired output mode).
+The motivation behind this formulation is two-fold.
+First, to arrive at a locally-optimal design rapidly 
+    by allowing $x$ and $p$ to vary independently, 
+    as opposed to Eq.~\ref{eq:adj}
+    where the value of $x$ is completely dependent on $p$.
+Second, to increase the likelihood of arriving at a high efficiency design
+    by forcibly imposing $f(x) = 0$,
+    and thereby circumventing any local optima consisting of
+    low-performance devices.
 
 % How is it applied to waveguide coupler design?
-\subsection{Objective-first approach to waveguide coupler design}
-We now apply the objective-first approach to the problem of designing 
-    two-dimensional nanophotonic waveguide couplers.
-
-We choose to work in the two-dimensional transverse electric mode,
-    which only couples $E_x$, $E_y$, and $H_z$ ($E_z, H_x, H_y = 0$),
-    since it is most relevant for on-chip devices.
-We choose to use $H_z$ as the field variable ($x$ in Eq.~\ref{eq:ob1}), 
-    and $\epsilon^{-1}$ (inverse of the permittivity) 
+\section{Objective-first design of arbitrary waveguide couplers}
+We demonstrate the objective-first approach
+    by designing waveguide couplers in two-dimensions.
+Specifically, we work in the two-dimensional transverse electric mode,
+    and choose $H_z$ as the field variable $x$,
+    and $\epsilon^{-1}$ (the inverse of the permittivity) 
     as the structure variable $p$.
-This results in the following representation of the physics residual, 
-    based on the time-harmonic electromagnetic wave equation without sources;
+This results in the following form of the physics residual,
     \begin{equation}
+    \|g(x,p)\|^2 = 
     \|g(H_z, \epsilon^{-1})\|^2 = 
@@
             (coupling structure), 
-            are shown in orange (color online).
+            are shown in orange. 
         The values of $H_z^\text{perfect}$ along the top and bottom edges
@@
     requiring only that we overwrite boundary field values.
-Although there is ambiguity in the relative phases of 
-    the input and output boundary fields,
-    our experience suggests that successful designs are possible for 
-    arbitrary choice of relative phase.
+Our experience suggests that successful designs are possible for 
+    arbitrary choice of relative phase between the input and output fields.
 
@@
 
-\subsection{Numerical methods used to solve the objective-first design problem}
 The design problem is now
@@
 
-\section{Results}
+\subsection{Coupler designs}
 We now present evidence that the method outlined above 
@@
     \begin{enumerate}
-    \item coupling between waveguides of different refractive index and width,
-    \item coupling between waveguide modes of different order and symmetry,
+    \item coupling between waveguides of different refractive index and width
+        (Fig.~\ref{fig:fiber});
+    \item coupling between waveguide modes of different order and symmetry
+        (Fig.~\ref{fig:mode});
     \item coupling between waveguides that confine light 
@@
         (index guided vs. distributed Bragg reflection guided), 
-        i.e., between a slab waveguide and a photonic crystal fiber. 
+        i.e., between a slab waveguide and a photonic crystal fiber
+        (Fig.~\ref{fig:aircore})
     \item coupling from a dielectric to a plasmonic metal-insulator-metal 
-        waveguide, and
-    \item coupling from a dielectric waveguide to a (plasmonic) metal wire,
+        waveguide (Fig.~\ref{fig:mim}); and
+    \item coupling from a dielectric waveguide to a (plasmonic) metal wire
+        (Fig.~\ref{fig:wire}).
     \end{enumerate}
-    the results of which are shown in Figs.~\ref{fig:fiber}-\ref{fig:wire}.
 \begin{figure}[htbp]
@@
 
-These results clearly demonstrate that our method
-    \begin{itemize}
-    \item can be applied to arbitrary input and output modes,
-        as seen from the diverse selection of desired output waveguide modes;
-    \item generates highly efficient devices with  
-        typical coupling efficiencies of $95\%$;
-    \item generates compact devices with footprints of only
-        1-4 square vacuum wavelengths;
-    \item does not require a good initial design.
-        The initial design was simply $\epsilon = 9$ everywhere
-            (a somewhat arbitrary guess, other values work as well),
-            which in almost every case
-            produces an initially non-functional device 
-            (coupling efficiency of $0\%$);
-    \item is computationally fast, 
+These results clearly demonstrate that our method can
+    be applied to arbitrary input and output modes,
+    as seen from the diverse selection of desired output waveguide modes.
+Moreover, it produces highly efficient devices with  
+    typical coupling efficiencies of $95\%$,
+    which are at the same time compact 
+    (with footprints of only 1-4 square vacuum wavelengths).
+In addition, the method does not require a good initial guess for the design.
+In our case the initial design was simply $\epsilon = 9$ everywhere
+        (a somewhat arbitrary guess, other values work as well).
+Finally, the method is computationally fast, 
     requiring only 15 minutes on a single-core personal computer.
-    \end{itemize}
 
-Critically, these results form a key advancement in our understanding of 
+These results form a key advancement in our understanding of 
     nanophotonic design; namely, 
@@
 We then apply an objective-first approach to the design of 
-    five practical nanophotonic waveguide couplers which are difficult, 
-    at best, to solve with existing methods. 
+    five practical nanophotonic waveguide couplers which are difficult
+    to solve with existing methods. 
 We show that our method produces
@@
 
-This work has been supported in part by the 
+This work has been supported by the 
     AFOSR MURI for Complex and Robust On-chip Nanophotonics 

### 2012-01-05 presentations/ob1_wg_paper/paper.tex
Finished bulk of editing on the ob-1 paper.

@@
     Nature Photonics \textbf{2}, 226 – 229 (2008) 
-\bibitem{fwadia} V. R. Almeida, R. R. Panepucci, and M. Lipson, 
-    ``Nanotaper for compact mode conversion,'' 
-    Opt. Lett. \textbf{28}, 1302-1304 (2003) 
-\bibitem{wwadia} S. G. Johnson, P. Bienstman,  M. A. Skorobogatiy, 
-    M. Ibanescu1, E. Lidorikis, and J. D. Joannopoulos,
-    ``Adiabatic theorem and continuous coupled-mode theory for 
-    efficient taper transitions in photonic crystals,''
-    Phys. Rev. E \textbf{66}, 066608 (2002)
-\bibitem{deriv} F. Wang, J. S. Jensen, O. Sigmund, 
-    ``Robust topology optimization of photonic crystal waveguides with 
-    tailored dispersion properties.'' 
-    J. Opt. Soc. Am. B \textbf{28}, 387-397 (2011)
-\bibitem{boydbook} S. Boyd, and L. Vandenberghe, 
-    \emph{Convex Optimization} 
-    (Cambridge University Press, 2004)
+% \bibitem{fwadia} V. R. Almeida, R. R. Panepucci, and M. Lipson, 
+%     ``Nanotaper for compact mode conversion,'' 
+%     Opt. Lett. \textbf{28}, 1302-1304 (2003) 
+% \bibitem{wwadia} S. G. Johnson, P. Bienstman,  M. A. Skorobogatiy, 
+%     M. Ibanescu1, E. Lidorikis, and J. D. Joannopoulos,
+%     ``Adiabatic theorem and continuous coupled-mode theory for 
+%     efficient taper transitions in photonic crystals,''
+%     Phys. Rev. E \textbf{66}, 066608 (2002)
+% \bibitem{deriv} F. Wang, J. S. Jensen, O. Sigmund, 
+%     ``Robust topology optimization of photonic crystal waveguides with 
+%     tailored dispersion properties.'' 
+%     J. Opt. Soc. Am. B \textbf{28}, 387-397 (2011)
+% \bibitem{boydbook} S. Boyd, and L. Vandenberghe, 
+%     \emph{Convex Optimization} 
+%     (Cambridge University Press, 2004)
 \bibitem{prevwork} J. Lu, S. Boyd, and J. Vuckovic, 
@@
     the function of all linear nanophotonic devices, since
-    any linear device is completely characterized by its input and output modes.
+    any linear device is completely characterized by its input and output modes
+    and the coupling coefficients between them.
 
-In this paper, we propose a design algorithm which, 
-    we believe, solves this problem.
-Namely, we outline a method capable of designing nanophotonic devices
-    to efficiently transfer photons between 
-    arbitrary input and output modes,
-    and we demonstrate this method by designing various nanophotonic couplers
-    between different waveguides.
-
+In this paper, we present a method to solve the problem 
+    of designing linear nanophotonic devices.
+We then demonstrate this method by designing coupling structures 
+    between various nanophotonic waveguides.
 Furthermore, we show that our method 
-     does not employ brute-force parameter searches;
-     does not require a good initial design;
-     is computationally fast (no simulations required);
+     does not require a good initial design,
+     is computationally fast,
      and can generate high efficiency couplers within a very small footprint. 
@@
 % \subsection{Advantages of objective-first design}
-\section{Objective-first formulation}
+\section{Objective-first approach}
 % What is objective-first optimization?
-The typical approach to designing physical structures can be formulated 
-    in the following way:
+Physical structures are typically designed by solving the following problem:
     \begin{subequations}\label{eq:adj}
@@
     calculates the performance of the device 
-    (e.g. amount of power not coupled to output mode); 
+    (e.g. amount of power lost); 
     while $g(x,p)$ is the underlying physical equation for the system
@@
 
-In contrast, the objective-first formulation is
+In contrast, the objective-first approach solves 
     \begin{subequations}\label{eq:ob1}
@@
 % How is it applied to waveguide coupler design?
-\section{Objective-first design of arbitrary waveguide couplers}
-We demonstrate the objective-first approach
+\section{Objective-first design of waveguide couplers}
+We now demonstrate the objective-first approach
     by designing waveguide couplers in two-dimensions.
 Specifically, we work in the two-dimensional transverse electric mode,
-    and choose $H_z$ as the field variable $x$,
+    choosing $H_z$ as the field variable $x$,
     and $\epsilon^{-1}$ (the inverse of the permittivity) 
@@
 
-For the design objective, we choose a boundary-value formulation
-    based on $H_z^\text{perfect}$,
-    where $H_z^\text{perfect}$ is constructed 
-    of the exact input and output waveguide modes at the input and output ports
-    of the optimization region (where the coupler will be placed),
-    repectively, and of zero-amplitude fields at the unused ports, 
-    as illustrated in Fig.~\ref{fig:intro}.
+In order to produce a method applicable 
+    to the design of any linear nanophotonic device,
+    we note that its performance
+    will be completely characterized by the fields along its boundary,
+    and therefore, 
+    we choose a boundary-value formulation for the design objective.
+Namely, we first compute the boundary fields needed to obtain
+    perfect performance, $H_z^\text{perfect}$,
+    and then form the design objective as
+    \begin{equation}
+    f(x) = f(H_z) = \begin{bmatrix}
+        H_z - H_z^\text{perfect} \\
+        \frac{\partial H_z}{\partial n} - 
+            \frac{\partial H_z^\text{perfect}}{\partial n}
+        \end{bmatrix}_\text{boundary}
+        = 0,
+    \end{equation}
+    where $\partial H_z / \partial n$ 
+    denotes the spatial derivative in the direction normal to the boundary.
 
@@
 
-The mathematical form of the design objective is simply, 
-    \begin{equation}
-    f(H_z) = \begin{bmatrix}
-        H_z - H_z^\text{perfect} \\
-        \frac{\partial H_z}{\partial n} - 
-            \frac{\partial H_z^\text{perfect}}{\partial n}
-        \end{bmatrix}_\text{boundary}
-        = 0.
-    \end{equation}
-That is to say,
-    the values of $H_z$ and $\partial H_z / \partial n$
-    (spatial derivative along normal direction)
-    along the device boundary are forced to be 
-    those of a device with perfect performance 
-    (100\% coupling efficiency).
+Such a design objective is both extremely simple and widely adaptable 
+    to the design of any linear nanophotonic device.
+Additionally, it is trivial to enforce,
+    often requiring only that we overwrite boundary field values.
+On the other hand, such a formulation often prohibits the physics residual 
+    from disappearing completely; 
+    however, we find that very good device performance is still obtained
+    as long as the physics residual is sufficiently small.
 
-Such a design objective is both extremely simple and widely adaptable 
-    to the design of nearly every kind of nanophotonic device.
-Most importantly, it is trivial to enforce,
-    requiring only that we overwrite boundary field values.
-Our experience suggests that successful designs are possible for 
-    arbitrary choice of relative phase between the input and output fields.
-
-Finally, as in any method based on an objective-first approach,
-    the physics residual is not guaranteed to decrease to zero.
-Thus, it is entirely possible to never achieve 
-    a physically realizable field, $H_z$.
-In such cases, which are the norm rather than the exception,
-    we find that a relatively small residual usually leads to
-    fairly good, although imperfect, device performance.
-
-The design problem is now
-    \begin{subequations}\label{eq:act}
-    \begin{align} 
-    \text{decrease} & \quad  
-        \| \nabla \times \epsilon^{-1} \nabla \times H_z - 
-            \mu_0 \omega^2 H_z \|^2 \label{eq:act:obj} \\ 
-    \text{subject to} & \quad 
-        \begin{bmatrix}
-        H_z - H_z^\text{perfect} \\
-        \frac{\partial H_z}{\partial n} - 
-            \frac{\partial H_z^\text{perfect}}{\partial n}
-        \end{bmatrix}_\text{boundary}
-        = 0.
-    \end{align}
-    \end{subequations}
-
-This problem contains many local minima (it is non-convex\cite{boydbook});
-    however, when either the field ($H_z$) or the structure ($\epsilon^{-1}$)
-    variable is considered separately, Eq.~\ref{eq:act} has only one minimum
-    (it is convex), and can be easily solved using standard methods
-    such as employed in our previous work\cite{prevwork}.
-We employ such an alternating directions strategy,
-    where both $H_z$ and $\epsilon^{-1}$ are solved independently.
-This process is extremely inefficient,
-    but is employed because the underlying numerical methods
-    do not need to be tuned by the user.
-We expect considerable improvements in computational efficiency
-    when more sophisticated algorithms are applied,
-    especially those which can update $H_z$ and $\epsilon^{-1}$ independently.
-
-Lastly, we limit the allowable values of $\epsilon$ to be between
+Lastly, we employ an alternating directions strategy,
+    where both $x$ and $p$ are solved iteratively\cite{prevwork}
+    and limit the allowable values of $\epsilon$ to be between
     the permittivity of vacuum and of silicon,
@@
     \end{equation}
-A completely binary structure would be preferred,
-    $\epsilon = \{\epsilon_0, \epsilon_\text{silicon}\}$,
-    and will be pursued in a future work.
+Note that a completely binary structure,
+    where $\epsilon = \{\epsilon_0, \epsilon_\text{silicon}\}$,
+    is needed for manufacturing purposes; this will be pursued in a future work.
 That said, the final designs presented here 
@@
 \subsection{Coupler designs}
-We now present evidence that the method outlined above 
-    is indeed able to design coupling structures between essentially
-    any two nanophotonic waveguide modes.
-To do so, we apply our method to the following five problems:
+We now present five results which suggest our method
+    is indeed able to design arbitrary linear nanophotonic devices.
+These results comprise of couplers between 
+    the following nanophotonic waveguides:
     \begin{enumerate}
@@
     \end{enumerate}
+All the designs presented are both highly efficient 
+    ($\sim 95\%$ coupling efficiency)
+    and extremely compact 
+    (with footprints of only 1-4 square vacuum wavelengths).
+In addition, good starting points were not required; 
+    all initial designs were simply $\epsilon = 9$ everywhere
+    (a somewhat arbitrary guess, other values work as well).
+Finally, only 15 minutes on a single-core personal computer
+    were needed to obtain each design.
+
 \begin{figure}[htbp]
@@
         The $H_z^\text{perfect}$ boundary values used as 
-            the design objective are plotted in the upper-left quadrant, 
-            the generated structure is shown in the upper-right quadrant, and
+            the design objective are shown in the upper-left plots, 
+            the generated structure is shown in the upper-right plot, and
             the simulated $H_z$ fields of the device are shown 
@@
 
-These results clearly demonstrate that our method can
-    be applied to arbitrary input and output modes,
-    as seen from the diverse selection of desired output waveguide modes.
-Moreover, it produces highly efficient devices with  
-    typical coupling efficiencies of $95\%$,
-    which are at the same time compact 
-    (with footprints of only 1-4 square vacuum wavelengths).
-In addition, the method does not require a good initial guess for the design.
-In our case the initial design was simply $\epsilon = 9$ everywhere
-        (a somewhat arbitrary guess, other values work as well).
-Finally, the method is computationally fast, 
-    requiring only 15 minutes on a single-core personal computer.
-
-These results form a key advancement in our understanding of 
-    nanophotonic design; namely, 
-    that it is indeed possible to efficiently design
-    virtually any linear optical device using an objective-first approach.
-
 \section{Conclusion}
@@
     even above satisfying the physical equation which governs its operation.
-We show that such an approach drastically reduces the
-    amount of computation required per iteration, and 
-    performs well even with a non-functional initial design.
-
-We then apply an objective-first approach to the design of 
-    five practical nanophotonic waveguide couplers which are difficult
-    to solve with existing methods. 
-We show that our method produces
+We then apply this approach to the design of 
+    various nanophotonic waveguide couplers,
+    and show that our method produces
     high-efficiency designs ($\sim 95\%$ efficiency) 
-    in small footprints ($\sim 1$ square vacuum wavelength)
-    between arbitrary waveguide modes.
-Furthermore, out method
-    is computationally fast (15 minutes on a single-core personal computer), and
-    does not require trial-and-error, or even 
-    a good starting design.\\
+    in small footprints (1-4 square vacuum wavelengths)
+    without needing a good starting point.
+Furthermore, we suggest that such a methodology may be applicable
+    to the design of any linear nanophotonic device.\\
 

### 2012-01-09 presentations/ob1_wg_paper/paper.tex
Second submission of the paper (draft to Jelena).

@@
     high efficiency ($\sim$95\%), 
-    small-footprint (1-4 square vacuum wavelengths)
+    small-footprint (1.5-4 square vacuum wavelengths)
     couplers between arbitrary nanophotonic waveguide modes
@@
 We demonstrate designs for various coupling problems which suggest 
-    that our method allows for the design of any linear optical device.
+    that our method allows for the design of any 
+    single-mode, linear optical device.
 \end{abstract}
-\ocis{230.7370, 130.3990.}
+\ocis{230.75370, 130.3990.}
 
@@
     nanophotonic silicon-on-insulator waveguide circuit,'' 
-    Opt. Express \textbf{15}, 6744-6749 (2007) 
+    Opt. Express \textbf{15}, 6744-6749 (20.75) 
 \bibitem{metallic} L. Tang, S. E. Kocabas, S. Latif, A. K. Okyay, 
@@
     ``Inverse design of a three-dimensional nanophotonic resonator,''
-    Opt. Express \textbf{19}, 10563-10570 (2011) 
+    Opt. Express \textbf{19}, 10563-10.750 (2011) 
 \bibitem{code} \url{www.github.com/JesseLu/objective-first}
@@
 In this paper, we present a method to solve the problem 
-    of designing linear nanophotonic devices.
+    of designing single-mode, linear nanophotonic devices.
 We then demonstrate this method by designing coupling structures 
@@
 
-\begin{figure}[htbp]
+\begin{figure}[htb]
     \centering
@@
 Such a design objective is both extremely simple and widely adaptable 
-    to the design of any linear nanophotonic device.
+    to the design of linear nanophotonic devices in general.
 Additionally, it is trivial to enforce,
@@
 We now present five results which suggest our method
-    is indeed able to design arbitrary linear nanophotonic devices.
+    is indeed able to design arbitrary single-mode, linear nanophotonic devices.
 These results comprise of couplers between 
@@
 All the designs presented are both highly efficient 
-    ($\sim 95\%$ coupling efficiency)
+    ($\sim 98\%$ coupling efficiency)
     and extremely compact 
-    (with footprints of only 1-4 square vacuum wavelengths).
+    (with footprints of only 1.5-4 square vacuum wavelengths).
 In addition, good starting points were not required; 
@@
             in the bottom two plots.
-        The computed efficiency of the coupler is high, $98.2\%$, and
+        The computed efficiency of the coupler is high, $99.8\%$, and
             the device is also extremely compact, 
-            convering only $36 \times 66$ grid points,
-            where the vacuum wavelength is 42 grid points.
+            convering only $36 \times 76$ grid points,
+            where the vacuum wavelength is 42 grid points
+            (footprint of $1.55$ square vacuum wavelengths).
         Computation time was 15 minutes on a personal computer.}
@@
 \end{figure}
-\begin{figure}[htbp]
+\begin{figure}[htb]
     \centering
@@
             Fig.~\ref{fig:fiber})  
-            with a coupling efficiency of $97.0\%$. 
+            with a coupling efficiency of $98.0\%$. 
         Computation time was 15 minutes on a personal computer.
@@
             (index guided).
-        The device still achieves an efficiency of $85.1\%$, demonstrating the
+        The device still achieves an efficiency of $98.9\%$, demonstrating the
             versatility of our method.
         The vacuum wavelength is 25 grid points, 
-            while the device footprint is still $36 \times 66$ grid points.
+            while the device footprint is still $36 \times 76$ grid points
+            (footprint of 4.38 square vacuum wavelengths).
         Computation time was 15 minutes on a personal computer.
@@
             a plasmonic metal-insulator-metal waveguide.
-        The efficiency of the device is $92.9\%$ and 
+        The efficiency of the device is $97.5\%$ and 
             has the same wavelength and footprint as the device in
@@
             a plasmonic wire waveguide.
-        The efficiency of the device is $93.2\%$ and 
+        The efficiency of the device is $99.1\%$ and 
             has the same wavelength and footprint as the device in
@@
     and show that our method produces
-    high-efficiency designs ($\sim 95\%$ efficiency) 
-    in small footprints (1-4 square vacuum wavelengths)
+    high-efficiency designs ($\sim 98\%$ efficiency) 
+    in small footprints (1.5-4 square vacuum wavelengths)
     without needing a good starting point.
 Furthermore, we suggest that such a methodology may be applicable
-    to the design of any linear nanophotonic device.\\
+    to the design of any single-mode, linear nanophotonic device.\\
 
@@
 The Matlab code used is available online\cite{code}.
+\clearpage
+\begin{appendix}
+\section{Additional mode coupler designs}
+In this section, we present additional mode coupler designs.
+A wide, high-index waveguide is used at both the input and output ports,
+    and all permutations of couplers are fabricated among
+    the first four propagating modes.
+\begin{figure}[htb]
+    \centering
+    \includegraphics[width=0.75\textwidth]{6}
+    \caption{
+        Efficiency: $99.3\%$,
+        footprint: $1.55$ square vacuum wavelengths.
+        }
+        % \label{fig:wire}
+\end{figure}
 
+\begin{figure}[htb]
+    \centering
+    \includegraphics[width=0.75\textwidth]{7}
+    \caption{
+        Efficiency: $98.3\%$,
+        footprint: $1.55$ square vacuum wavelengths.
+        }
+        % \label{fig:wire}
+\end{figure}
+
+\begin{figure}[htb]
+    \centering
+    \includegraphics[width=0.75\textwidth]{8}
+    \caption{
+        Efficiency: $90.6\%$,
+        footprint: $1.55$ square vacuum wavelengths.
+        }
+        % \label{fig:wire}
+\end{figure}
+
+\begin{figure}[htb]
+    \centering
+    \includegraphics[width=0.75\textwidth]{9}
+    \caption{
+        Efficiency: $96.8\%$,
+        footprint: $1.55$ square vacuum wavelengths.
+        }
+        % \label{fig:wire}
+\end{figure}
+
+\begin{figure}[htb]
+    \centering
+    \includegraphics[width=0.75\textwidth]{10}
+    \caption{
+        Efficiency: $86.3\%$,
+        footprint: $1.55$ square vacuum wavelengths.
+        }
+        % \label{fig:wire}
+\end{figure}
+
+\begin{figure}[htb]
+    \centering
+    \includegraphics[width=0.75\textwidth]{11}
+    \caption{
+        Efficiency: $80.1\%$,
+        footprint: $1.55$ square vacuum wavelengths.
+        }
+        % \label{fig:wire}
+\end{figure}
+\clearpage
+\section{Additional designs with wide, low-index input waveguide}
+\begin{figure}[htb]
+    \centering
+    \includegraphics[width=0.75\textwidth]{12}
+    \caption{
+        Efficiency: $96.9\%$,
+        footprint: $1.55$ square vacuum wavelengths.
+        }
+        % \label{fig:wire}
+\end{figure}
+
+\begin{figure}[htb]
+    \centering
+    \includegraphics[width=0.75\textwidth]{13}
+    \caption{
+        Efficiency: $99.0\%$,
+        footprint: $4.38$ square vacuum wavelengths.
+        }
+        % \label{fig:wire}
+\end{figure}
+
+\begin{figure}[htb]
+    \centering
+    \includegraphics[width=0.75\textwidth]{14}
+    \caption{
+        Efficiency: $96.7\%$,
+        footprint: $4.38$ square vacuum wavelengths.
+        }
+        % \label{fig:wire}
+\end{figure}
+
+\begin{figure}[htb]
+    \centering
+    \includegraphics[width=0.75\textwidth]{15}
+    \caption{
+        Efficiency: $99.7\%$,
+        footprint: $4.38$ square vacuum wavelengths.
+        }
+        % \label{fig:wire}
+\end{figure}
+\clearpage
+
+\section{Additional designs with multiple output plasmonic waveguides}
+\begin{figure}[htb]
+    \centering
+    \includegraphics[width=0.75\textwidth]{16}
+    \caption{
+        Efficiency: $94.0\%$,
+        footprint: $4.38$ square vacuum wavelengths.
+        }
+        % \label{fig:wire}
+\end{figure}
+
+\begin{figure}[htb]
+    \centering
+    \includegraphics[width=0.75\textwidth]{17}
+    \caption{
+        Efficiency: $97.3\%$,
+        footprint: $4.38$ square vacuum wavelengths.
+        }
+        % \label{fig:wire}
+\end{figure}
+
+\begin{figure}[htb]
+    \centering
+    \includegraphics[width=0.75\textwidth]{18}
+    \caption{
+        Efficiency: $98.5\%$,
+        footprint: $4.38$ square vacuum wavelengths.
+        }
+        % \label{fig:wire}
+\end{figure}
+
+\begin{figure}[htb]
+    \centering
+    \includegraphics[width=0.75\textwidth]{19}
+    \caption{
+        Efficiency: $97.7\%$,
+        footprint: $4.38$ square vacuum wavelengths.
+        }
+        % \label{fig:wire}
+\end{figure}
+
+\begin{figure}[htb]
+    \centering
+    \includegraphics[width=0.75\textwidth]{20}
+    \caption{
+        Efficiency: $95.6\%$,
+        footprint: $4.38$ square vacuum wavelengths.
+        }
+        % \label{fig:wire}
+\end{figure}
+
+\begin{figure}[htb]
+    \centering
+    \includegraphics[width=0.75\textwidth]{21}
+    \caption{
+        Efficiency: $87.5\%$,
+        footprint: $4.38$ square vacuum wavelengths.
+        }
+        % \label{fig:wire}
+\end{figure}
+\clearpage
+\end{appendix}
 \end{document}

### 2012-01-10 presentations/ob1_wg_paper/paper.tex
Another update on ob1 paper.

@@
 We develop an algorithm for designing
-    high efficiency ($\sim$95\%), 
+    high efficiency ($\sim$98\%), 
     small-footprint (1.5-4 square vacuum wavelengths)
@@
 \end{figure}
+\clearpage
 \begin{figure}[htb]
@@
     the first four propagating modes.
-\begin{figure}[htb]
+\begin{figure}[h!]
     \centering
-    \includegraphics[width=0.75\textwidth]{6}
+    \includegraphics[width=0.8\textwidth]{6}
     \caption{
+        Coupler from the first-order to the second-order mode 
+            of a wide dielectric waveguide.
         Efficiency: $99.3\%$,
@@
 \end{figure}
-
-\begin{figure}[htb]
+\begin{figure}[h!]
     \centering
-    \includegraphics[width=0.75\textwidth]{7}
+    \includegraphics[width=0.8\textwidth]{7}
     \caption{
+        Coupler from the first-order to the third-order mode 
+            of a wide dielectric waveguide.
         Efficiency: $98.3\%$,
@@
 \end{figure}
-
-\begin{figure}[htb]
+\begin{figure}[h!]
     \centering
-    \includegraphics[width=0.75\textwidth]{8}
+    \includegraphics[width=0.8\textwidth]{8}
     \caption{
+        Coupler from the first-order to the fourth-order mode 
+            of a wide dielectric waveguide.
         Efficiency: $90.6\%$,
@@
 \end{figure}
-
-\begin{figure}[htb]
+\begin{figure}[h!]
     \centering
-    \includegraphics[width=0.75\textwidth]{9}
+    \includegraphics[width=0.8\textwidth]{9}
     \caption{
+        Coupler from the second-order to the third-order mode 
+            of a wide dielectric waveguide.
         Efficiency: $96.8\%$,
@@
 \end{figure}
-
-\begin{figure}[htb]
+\begin{figure}[h!]
     \centering
-    \includegraphics[width=0.75\textwidth]{10}
+    \includegraphics[width=0.8\textwidth]{10}
     \caption{
+        Coupler from the second-order to the fourth-order mode 
+            of a wide dielectric waveguide.
         Efficiency: $86.3\%$,
@@
 \end{figure}
-
-\begin{figure}[htb]
+\begin{figure}[h!]
     \centering
-    \includegraphics[width=0.75\textwidth]{11}
+    \includegraphics[width=0.8\textwidth]{11}
     \caption{
+        Coupler from the third-order to the fourth-order mode 
+            of a wide dielectric waveguide.
         Efficiency: $80.1\%$,
@@
 \section{Additional designs with wide, low-index input waveguide}
-\begin{figure}[htb]
+We now reproduce Figs~\ref{fig:mode}-\ref{fig:wire}
+    but instead use a wide, low-index waveguide as the input.
+Once again, this is to demonstrate the generality of our method;
+    namely, that it can be applied to the design of nearly any
+    single-mode, linear nanophotonic device.
+\begin{figure}[h!]
     \centering
-    \includegraphics[width=0.75\textwidth]{12}
+    \includegraphics[width=0.8\textwidth]{12}
     \caption{
+        Coupler from a wide, low-index waveguide to the
+            second-order mode of a narrow, high-index waveguide.
         Efficiency: $96.9\%$,
@@
 \end{figure}
-
-\begin{figure}[htb]
+\begin{figure}[h!]
     \centering
-    \includegraphics[width=0.75\textwidth]{13}
+    \includegraphics[width=0.8\textwidth]{13}
     \caption{
+        Coupler from a wide, low-index waveguide to an 
+            ``air-core'' waveguide mode.
         Efficiency: $99.0\%$,
@@
 \end{figure}
-
-\begin{figure}[htb]
+\begin{figure}[h!]
     \centering
-    \includegraphics[width=0.75\textwidth]{14}
+    \includegraphics[width=0.8\textwidth]{14}
     \caption{
+        Coupler from a wide, low-index waveguide to a
+            metal-insulator-metal plasmonic waveguide mode.
         Efficiency: $96.7\%$,
@@
 \end{figure}
-
-\begin{figure}[htb]
+\begin{figure}[h!]
     \centering
-    \includegraphics[width=0.75\textwidth]{15}
+    \includegraphics[width=0.8\textwidth]{15}
     \caption{
+        Coupler from a wide, low-index waveguide to a
+            plasmonic wire waveguide mode.
         Efficiency: $99.7\%$,
@@
 \section{Additional designs with multiple output plasmonic waveguides}
-\begin{figure}[htb]
+We also present ``selector'' designs where photons are coupled to 
+    only one of five possible plasmonic output waveguides.
+We demonstrate these selector designs for both metal-insulator-metal and
+    metal-wire plasmonic waveguides.
+\begin{figure}[h!]
     \centering
-    \includegraphics[width=0.75\textwidth]{16}
+    \includegraphics[width=0.8\textwidth]{16}
     \caption{
+        Coupler from a dielectric waveguide to the 
+            lowest branch of a set of five plasmonic wire waveguides.
         Efficiency: $94.0\%$,
@@
 \end{figure}
-
-\begin{figure}[htb]
+\begin{figure}[h!]
     \centering
-    \includegraphics[width=0.75\textwidth]{17}
+    \includegraphics[width=0.8\textwidth]{17}
     \caption{
+        Coupler from a dielectric waveguide to the 
+            second branch of a set of five plasmonic wire waveguides.
         Efficiency: $97.3\%$,
@@
 \end{figure}
-
-\begin{figure}[htb]
+\begin{figure}[h!]
     \centering
-    \includegraphics[width=0.75\textwidth]{18}
+    \includegraphics[width=0.8\textwidth]{18}
     \caption{
+        Coupler from a dielectric waveguide to the 
+            middle branch of a set of five plasmonic wire waveguides.
         Efficiency: $98.5\%$,
@@
 \end{figure}
-
-\begin{figure}[htb]
+\begin{figure}[h!]
     \centering
-    \includegraphics[width=0.75\textwidth]{19}
+    \includegraphics[width=0.8\textwidth]{19}
     \caption{
+        Coupler from a dielectric waveguide to the 
+            middle branch of a set of five plasmonic 
+            metal-insulator-metal waveguides.
         Efficiency: $97.7\%$,
@@
 \end{figure}
-
-\begin{figure}[htb]
+\begin{figure}[h!]
     \centering
-    \includegraphics[width=0.75\textwidth]{20}
+    \includegraphics[width=0.8\textwidth]{20}
     \caption{
+        Coupler from a dielectric waveguide to the 
+            fourth branch of a set of five plasmonic 
+            metal-insulator-metal waveguides.
         Efficiency: $95.6\%$,
@@
 \end{figure}
-
-\begin{figure}[htb]
+\begin{figure}[h!]
     \centering
-    \includegraphics[width=0.75\textwidth]{21}
+    \includegraphics[width=0.8\textwidth]{21}
     \caption{
+        Coupler from a dielectric waveguide to the 
+            uppermost branch of a set of five plasmonic 
+            metal-insulator-metal waveguides.
         Efficiency: $87.5\%$,

### 2012-01-10 presentations/ob1_wg_paper/paper.tex
Submitted to opex for the second time.

@@
 \begin{document}
-\title{High-Efficiency, Small-Footprint Couplers Between 
+\title{Objective-First Design of 
+    High-Efficiency, Small-Footprint Couplers Between 
     Arbitrary Nanophotonic Waveguide Modes}
@@
 \begin{abstract}
-We develop an algorithm for designing
+We present an algorithm for designing
     high efficiency ($\sim$98\%), 
@@
 The motivation behind this formulation is two-fold.
-First, to arrive at a locally-optimal design rapidly 
+First, this approach allows is to arrive at a locally-optimal design rapidly 
     by allowing $x$ and $p$ to vary independently, 
@@
     where the value of $x$ is completely dependent on $p$.
-Second, to increase the likelihood of arriving at a high efficiency design
+Second, it enables an increase in the likelihood of 
+    arriving at a high efficiency design
     by forcibly imposing $f(x) = 0$,
-    and thereby circumventing any local optima consisting of
+    and thereby circumvents any local optima consisting of
     low-performance devices.
@@
     were needed to obtain each design.
+
+In the appendix, we further demonstrate the generality of our method
+    by presenting several additional examples including
+    \begin{enumerate}
+    \item coupling between all four modes of a wide dielectric waveguide;
+    \item coupling from a wide, low-index waveguide to the output waveguides in 
+        Figs~\ref{fig:mode}-\ref{fig:wire}; and
+    \item coupling to selected channels of a set of five plasmonic waveguides.
+    \end{enumerate}
 

### 2012-01-14 bible/1Peter2:4-10.tex
Added Bible study of 1 Peter 2:4-10.

\documentclass[12pt]{article}
\begin{document}
\part*{1 Peter 2:4-10}
% Instructions:
% Answer the questions below based on
\begin{enumerate}
\section*{The analogy (4-5)}
\item How do verses 4-5 describe the following relationships?
    \begin{enumerate}
    \item Jesus and God the Father
    \item Jesus and unbelievers
    \item Jesus and believers
    \end{enumerate}
\item Chief cornerstone: In the ancient Middle-Eastern world,
    the cornerstone was the first stone laid in the building process,
    determining the position and alignment of the rest of the structure.
    \begin{enumerate}
    \item What is the spiritual house, for which Jesus is the chief cornerstone?
        See also Ephesians 2:19-22.
    \item What is the purpose of this house?
        What is the earthly house that is analogous to this spiritual house?
    \item In what ways does Jesus serve as chief cornerstone 
        to this spiritual house?
        Read Colossians 1:15-18, Ephesians 4:15-16, and Revelation 2:12-20
        as well.
    \end{enumerate}
\item How does Jesus' relationship with unbelievers determine
    how we live in the world?
\section*{The testimony of Scripture (6-8)}
\item What does it mean, as quoted in verse 6, that 
        believers will not ``be put to shame''?
    What effect does meditating on this truth have on the believer,
        as described in verse 7?
\item Evaluate the value you place on knowing and obeying Jesus Christ,
        compared to that placed on other objects and pursuits in your life.
    How must you change, in order to rightly live
        in light of what God has done for you in Jesus Christ?
\item Verse 8 describes Jesus as a source of stumbing and offense
    to unbelievers.
    \begin{enumerate}
    \item How did Jesus cause of stumbling and offense 
            for both the Jews and the Greeks of that time?
        See 1 Corinthians 1:23.
    \item In what ways is Jesus an offense and stumbling block to our culture?
    \end{enumerate}
\section*{The appointments (8-10)}
\end{enumerate}
\end{document}

### 2012-01-16 bible/1Peter2:4-10.tex
Finished 1 Peter2:4-10 questions.

@@
 \documentclass[12pt]{article}
+\newcommand{\answerbox}{\vspace{1cm}}
 \begin{document}
 \part*{1 Peter 2:4-10}
-% Instructions:
-% Answer the questions below based on
+Please answer the following questions.
+We will discuss them at Bible Study.
 \begin{enumerate}
-\section*{The analogy (4-5)}
+\section*{The analogy (4-6)}
 \item How do verses 4-5 describe the following relationships?
@@
     \item Jesus and God the Father
+        \answerbox
     \item Jesus and unbelievers
+        \answerbox
     \item Jesus and believers
+        \answerbox
     \end{enumerate}
-\item Chief cornerstone: In the ancient Middle-Eastern world,
+\item Chief cornerstone, read also verse 6: In the ancient Middle-Eastern world,
     the cornerstone was the first stone laid in the building process,
@@
         See also Ephesians 2:19-22.
+        \answerbox
     \item What is the purpose of this house?
         What is the earthly house that is analogous to this spiritual house?
+        \answerbox
     \item In what ways does Jesus serve as chief cornerstone 
@@
         as well.
+        \answerbox
     \end{enumerate}
 \item How does Jesus' relationship with unbelievers determine
-    how we live in the world?
+        our relationship with the world?
+    How does this affect how we live in the world?
+        \answerbox
+
 \section*{The testimony of Scripture (6-8)}
@@
         as described in verse 7?
+        \answerbox
 \item Evaluate the value you place on knowing and obeying Jesus Christ,
@@
         in light of what God has done for you in Jesus Christ?
+        \answerbox
 \item Verse 8 describes Jesus as a source of stumbing and offense
@@
     \begin{enumerate}
-    \item How did Jesus cause of stumbling and offense 
+    \item How was Jesus a cause of stumbling and offense 
             for both the Jews and the Greeks of that time?
-        See 1 Corinthians 1:23.
+        See also 1 Corinthians 1:23.
+        \answerbox
     \item In what ways is Jesus an offense and stumbling block to our culture?
+        \answerbox
     \end{enumerate}
 \section*{The appointments (8-10)}
+\item What is the ultimate reason why unbelievers stumble
+        on the rock that is Jesus Christ?
+    See also Romans 9:14-24.
+        \answerbox
+\item In contrast, according to verses 9 and 10, 
+        to what end have believers been called to?
+        \answerbox
+\item Define the following terms found in verse 9.
+    In what way has God made us to be these things?
+    Give a supporting verse for each.
+   \begin{enumerate}
+   \item a chosen generation
+        \answerbox
+   \item a royal priesthood
+        \answerbox
+   \item a holy nation
+        \answerbox
+   \item His own special people
+        \answerbox
+   \end{enumerate}
+\item How must our day-to-day living be determined by
+        who God has made us in Jesus Christ, 
+        as seen in the previous question?
+        \answerbox
+\item Relate this study (verses 4-10) back to the theme of this section
+        of 1 Peter, which is holiness.
+    Specifically, how do these verses fit in with the command 
+        given in 1 Peter 1:14-16?
+        \answerbox
 \end{enumerate}

### 2012-01-20 bible/1Peter1:14-2:12.tex
Added bible study.

\documentclass[12pt]{article}
\newcommand{\BE}{\begin{enumerate}}
\newcommand{\EE}{\end{enumerate}}
\newcommand{\I}{\item}
\begin{document}
\part*{1 Peter 1:14-2:12}
This study is designed to be a review of this section of Scripture,
    where Peter's focus is holy living.
Please take multiple days to gradually study, meditate, and apply
    the truths and commands found in this section.
Be prepared to share, encourage, and strengthen others 
    as we discuss these questions in our Friday night Bible study.

\BE
\section*{1 Peter 1:14-16}
\I  What does Peter command us \emph{not to} do,
        and what does Peter command us \emph{to} do in these verses?
\I  What is the fundamental reason why we are to obey this command?
    How does this relate to being his obedient children (v. 14)?
    See also Leviticus 11:44-45, 19:2, 20:7.
\I  Application:
    \BE
    \I  Identify the area of your life which continues most to be conformed
            to a past pattern of sin.
    \I  What is the root desire (i.e. lust) that drives you to sin in this way?
    \I  Consider Jesus, who was tempted in the same way (Hebrews 4:15).
        Search the Scripture and find how He overcame such temptation, 
            give verses.
    \I  What is the one change in your life 
            with which you can most effectively overcome this temptation?
        Consider Jesus' example from your previous answer.
    \I  Write down one Scripture that you will memorize and use to 
            fight temptation when tempted in this area.
    \EE
\section*{1 Peter 1:17-21}
\I  What is the command that we are given in these verses?
    Explain what it means, and write down the command using your own words.
\I  What are the two motivations Peter gives us, to help us to obey the command?
\I  Why is Jesus' blood so precious? Give verses.
\I  Read 1 Corinthians 3:11-15, which speaks of God's judging of believers.
    \BE
    \I  Prayerfully evaluate your Christian life up to this point.
        In what areas have you built with gold, silver, and precious stones?
        In what areas have you built with wood, hay, and straw?
    \I  Choose an area that you feel would be burned up in the fires of testing.
        Write down a verse to remember that teaches what God's will for you is
            in this area of your life.
    \EE

\section*{1 Peter 1:22-25}
\section*{1 Peter 2:1-10}
\section*{1 Peter 2:11-12}
\EE
\end{document}

### 2012-01-20 bible/1Peter1:14-2:12.tex
Finished questions.

@@
-\documentclass[12pt]{article}
+\documentclass{article}
+\usepackage{fullpage}
+\newcommand{\answerbox}{\vspace{1.5cm}}
 \newcommand{\BE}{\begin{enumerate}}
@@
         and what does Peter command us \emph{to} do in these verses?
+    \answerbox
 \I  What is the fundamental reason why we are to obey this command?
@@
     See also Leviticus 11:44-45, 19:2, 20:7.
+    \answerbox
 \I  Application:
@@
             to a past pattern of sin.
+    \answerbox
     \I  What is the root desire (i.e. lust) that drives you to sin in this way?
-    \I  Consider Jesus, who was tempted in the same way (Hebrews 4:15).
-        Search the Scripture and find how He overcame such temptation, 
-            give verses.
+    \answerbox
+    \I  Consider Jesus, who was tempted in the same way, yet without sin 
+            (Hebrews 4:15).
+        Search the Scripture and find how He overcame such temptation.
+        Give verses.
+    \answerbox
     \I  What is the one change in your life 
@@
         Consider Jesus' example from your previous answer.
+    \answerbox
     \I  Write down one Scripture that you will memorize and use to 
             fight temptation when tempted in this area.
+    \answerbox
     \EE
@@
     Explain what it means, and write down the command using your own words.
-\I  What are the two motivations Peter gives us, to help us to obey the command?
+    \answerbox
+\I  What are the two motivations Peter gives us, to help us in obeying the command?
+    \answerbox
 \I  Why is Jesus' blood so precious? Give verses.
+    \answerbox
 \I  Read 1 Corinthians 3:11-15, which speaks of God's judging of believers.
@@
         In what areas have you built with wood, hay, and straw?
-    \I  Choose an area that you feel would be burned up in the fires of testing.
+    \answerbox
+    \I  Choose an area that you feel would be ``burned up'' 
+            if tested at this moment.
         Write down a verse to remember that teaches what God's will for you is
             in this area of your life.
+        How can you start building with gold, silver, and precious stones 
+            in this area?
+    \answerbox
     \EE
-
 \section*{1 Peter 1:22-25}
+\I  What are we commanded to do in these verses?
+    How is holiness related to this command?
+    \answerbox
+\I  From these verses, how do we prepare ourselves to obey this command?
+    Also, how has God prepared us to obey this command?
+    \answerbox
+\I  What do these verse tell us about the work that God's word 
+        has accomplished in our lives?
+    Read Psalm 19:7-11, in what other ways does the Word transform a believer?
+    \answerbox
+\I  Application:
+    \BE
+    \I  What impurity in your own life most prevents you from 
+            fervently loving others?
+    \answerbox
+    \I  In what ways would your love for the brethren be enhanced or increased
+            if this impurity was no longer present in your life?
+    \answerbox
+    \I  How can others pray for you to this end?
+        Share this prayer request with a brother or sister,
+            and ask them to pray for you in this regard.
+    \answerbox
+    \EE
 \section*{1 Peter 2:1-10}
+\I  What pair of commands are we given in these verses?
+    How are these commands related to one another?
+    \answerbox
+\I  In your own words, explain what Peter means when he says
+        that we are to desire the Word as newborn babes.
+    What is the purpose that this is to accomplish in our lives?
+    \answerbox
+\I  What do we learn about our growth from these verses?
+    Specifically, what are we growing into,
+        what is the end purpose of this growth, and
+        what has God accomplished on our behalf in order to make this possible?
+    \answerbox
+\I  What reason does 1 Peter 2:3 give us to obey the commands presented 
+        in this section? 
+    How have you personally experienced this in a deep and profound way 
+        in your lifetime?
+    See also Psalm 34:8.
+    \answerbox
 \section*{1 Peter 2:11-12}
+\I  What pair of commands are we given in these verses?
+    \answerbox
+\I  What are fleshly lusts, and what specific tactics do they use 
+        to attack our own souls?
+    See also James 4:1.
+    \answerbox
+\I  How will our good deeds cause unbelievers to glorify God
+        in the day of visitation?
+    See also 1 Peter 1:6-7.
+    \answerbox
+\I  Define the term ``sojourners and pilgrims''.
+    \answerbox
+    \BE
+    \I  In what ways are we spiritual pilgrims in this world? Give verses.
+    \answerbox
+    \I  What are the objectives that a sojourner is to pursue, and 
+            how are they different from the objective that 
+            someone who dwells in the land pursues?
+        How does this relate to the war that fleshly lusts wage
+            against the soul of the sojourner?
+    \answerbox
+    \I  Evaluate how you use your time and resources.
+        What have you put your hope in?
+        Are you living as one who is passing through this world,
+            or one who is trying to settle down in this world?
+    \answerbox
+    \I  Choose one area of our life where you are not living as a 
+            spiritual pilgrim.
+        Find and write down a Scripture that speaks either of
+            the futility of this pursuit as one who dwells in the world, or
+            the great reward of submitting to God's will in this area,
+            as a spiritual pilgrim.
+    \answerbox
+    \EE
 \EE

### 2012-01-21 sermons/Revelation1:1-3.tex
Started Rev1:1-3 sermon.

\documentclass{article}
\newcommand{\BI}{\begin{itemize}}
\newcommand{\EI}{\end{itemize}}
\newcommand{\I}{\item}
\begin{document}
\part*{Revelation 1:1-3 --- The Revelation of Jesus Christ}
\BI
\section*{Notes}
\I  The point of this sermon is:
        \begin{quote} 
        You need to know and obey the Revelation of Jesus Christ.
        \end{quote}

This Scripture prepares us to read and obey the rest of the book.
It does so by telling us what Revelation is about
    and what we must do with it.

In this light, the goal of this sermon is to place a burden on the hearers 
    to know and become familiar with the contents of this book, 
    and to heed the commands given in it.

\section*{Introduction}
\section{The Nature of the Revelation of Jesus Christ}
\subsection{What is it about?}
\I The subject of Revelation is Jesus Christ.
\subsection{Who is it from?}
\subsection{What is its purpose?}
\subsection{Who is it for?}
\subsection{What is its focus?}

\section{The Authority of the Revelation of Jesus Christ}
\subsection{The word of God}
\subsection{The testimony of Jesus Christ}
\subsection{All things that he saw}

\section{The Blessing of the Revelation of Jesus Christ}
\EI
\end{document}

### 2012-01-27 sermons/Revelation1:1-3.tex
Updated Rev 1:1-3 sermon.

@@
 \newcommand{\I}{\item}
+\newcommand{\Q}[1]{\begin{quote} #1 \end{quote}}
 \begin{document}
 \part*{Revelation 1:1-3 --- The Revelation of Jesus Christ}
+\tableofcontents
 \BI
@@
 \section{The Nature of the Revelation of Jesus Christ}
-\subsection{What is it about?}
-\I The subject of Revelation is Jesus Christ.
+\subsection{Who does it reveal?}
+\I The book of Revelation reveals Jesus Christ.
+\subsubsection{He is God}
+\I Rev 1:11 \Q{``I am the Alpha and the Omega, the First and the Last.''}
+\I Rev 1:17 \Q{``Do not be afraid, I am the First and the Last.''}
+\I Rev 22:13 \Q{``I am the Alpha and the Omega, the Beginning and the End, 
+                the First and the Last.''}
+\I Rev 1:13 \Q{\ldots and in the midst of the seven lampstands One 
+                like the Son of Man, \ldots}
+\I Rev 3:1, 5:6
+            \Q{``These things says He who has the seven Spirits of God 
+                and the seven stars: \ldots''}    
+            \Q{And I looked, and behold, in the midst of the throne 
+                and of the four living creatures, 
+                and in the midst of the elders, 
+                stood a Lamb as though it had been slain, 
+                having seven horns and seven eyes, 
+                which are the seven Spirits of God sent out into all the earth.}
+\I Rev 3:14 \Q{``These things says the Amen, the Faithful and True Witness,
+                the Beginning of the creation of God; \ldots}
+\I Rev 22:16 \Q{``I, Jesus, have sent My angel to testify to you these things 
+                in the churches, I am the Root and the Offspring of David, 
+                the Bright and Morning Star.''}
+\I Rev 1:16 \Q{\dots and His countenance was like the sun shining 
+                in its strength.}
+
+\subsubsection{He is the Savior}
+\I Rev 1:5 \Q{To Him who loved us and washed us from our sins 
+                in His own blood, \ldots}
+\I Rev 1:18 \Q{I am He who lives, and was dead, and behold, 
+                I am alive forevermore.}
+\I Rev 5:6 \Q{And I looked, and behold, in the midst of the throne
+                and of the four living creatures, and in the midst of the
+                elders, stood a Lamb as though it had been slain, \ldots}
+\I Rev 13:8 \Q{All who dwell on the earth will worship him [the beast], 
+                whose names have not been written in the Book of Life
+                of the Lamb who was slain from the foundation of the world.}
+\I Rev 5:9 \Q{``You are worthy to take the scroll, \\
+                And to open its seals; \\
+                For You were slain, \\
+                And have redeemed us to God by Your blood \\
+                Out of every tribe and tongue and people and nation, \ldots''}
+\I Rev 5:12 \Q{``Worthy is the Lamb who was slain \\
+                To receive power and riches and wisdom, \\
+                And strength and honor and glory and blessing!''}
+\I Rev 5:13 \Q{``Blessing and honor and glory and power \\
+                Be to Him who sits on the throne, \\
+                And to the Lamb, forever and ever!''}
+\I Rev 5:5 \Q{``Do not weep. Behold, the Lion of the tribe of Judah,
+                the Root of David, has prevailed to open the scroll 
+                and to loose its seven seals.''}
+\I Rev 3:7 \Q{``He who has the key of David, He who opens and no one shuts, 
+                and shuts and no one opens.''}
+\I Rev 1:18 \Q{``And I have the keys of Hades and of Death.''}
+\I Rev 19:7 \Q{``Let us be glad and rejoive and give Him glory,
+                for the marriage of the Lamb has come,
+                and His wife has made herself ready.''}
+\I Rev 7:17 \Q{``for the Lamb who is in the midst of the throne 
+                will shepherd them and lead them to living fountains of waters.
+                And God will wipe away every tear from their eyes.''}
+\I Rev 21:22-23 \Q{But I saw no temple in it, for the Lord God Almighty 
+                and the Lamb are its temple. The city had no need 
+                of the sun or of the moon to shine in it, 
+                for the glory of God illuminated it. The Lamb is its light.}
+\I Rev 22:1-2 \Q{And he showed me a pure river of water of life, 
+                clear as crystal, proceeding from the throne of God 
+                and of the Lamb. In the middle of its street, and on either
+                of the river, was the tree of life, which bore twelve fruits,
+                each tree yielding its fruit every month. 
+                The leaves of the tree were for the healing of the nations.}
+\I Rev 22:3-4 \Q{And there shall be no more curse, but the throne of God
+                and of the Lamb shall be in it, and His servants shall 
+                serve Him. They shall see His face, and His name shall be on
+                their foreheads.}
+
+\subsubsection{He is King}
 \subsection{Who is it from?}
 \subsection{What is its purpose?}
-\subsection{Who is it for?}
+\subsection{Who is it to?}
 \subsection{What is its focus?}

### 2012-02-02 sermons/Revelation1:1-3.tex
Updated sermon.

@@
 
-\subsubsection{He is King}
+\subsubsection{He is the conquering King}
+\I Rev 1:7 \Q{Behold, He is coming with clouds, and every eye will see Him, 
+                even they who pierced Him. And all the tribes of the earth
+                will mourn because of Him. Even so, Amen.}
+\I Rev 1:14-16 \Q{His head and hair were white like wool, as white as snow,
+                and His eyes like a flame of fire; His feet were like brass, 
+                as if refined in a furnace, and His voice as the sound of 
+                many waters; He had in his right hand seven stars, 
+                out of His mouth went a sharp two-edged sword, 
+                and His countenance was like the sun shining in its strength.}
+\I Rev 6:16-17 \Q{\ldots and said to the mountains and rocks, 
+                ``Fall on us and hide us from the face of Him who sits on the
+                throne and from the wrath of the Lamb! For the great day of His
+                wrath has come, and who is able to stand?''}
+\I Rev 14:14 \Q{Then I looked, and behold, a white cloud, and on the cloud
+                sat One like the Son of Man, having on His head a golden crown, 
+                and in His hand a sharp sickle.}
+\I Rev 17:14 \Q{``These [ten kings and the beast] will make war with the Lamb, 
+                and the Lamb will overcome them, for He is Lord of lords and
+                King of kings; and those who are with Him are called, 
+                chosen, and faithful.''}
+\I Rev 19:11-16 \Q{Now I saw heaven opened, and behold, a white horse.
+                And He who sat on Him was called Faithful and True,
+                and in righteousness He judges and makes war.
+                His eyes were like a flame of fire, and on His head were
+                many crowns. He had a name written that no one knew except
+                Himself. He was clothed with a robe dipped with blood,
+                and His name is called The Word of God.
+                And the armies of heaven, clothed in fine linen, white and
+                clean, followed Him on white horses.
+                Now out of His mouth goes a sharp sword, that with it He 
+                should strike the nations. And He Himself will rule them 
+                with a rod of iron. He Himself treads the winepress of the
+                fierceness and wrath of Almighty God. And He has on His robe 
+                and on His thigh a name written:
+                \Q{KING OF KINGS \\ AND LORD OF LORDS.}}
+
+\I Rev 20:15 \Q{And anyone not found written in the Book of Life was cast 
+                into the lake of fire.}
+            Note: we know this is the Lamb's Book of Life from Rev 13:8.
+
 \subsection{Who is it from?}

### 2012-02-02 sermons/Revelation1:1-3.tex
Sermon updated.

@@
-\documentclass{article}
+\documentclass[12pt]{article}
 \newcommand{\BI}{\begin{itemize}}
@@
 \section*{Introduction}
-\section{The Nature of the Revelation of Jesus Christ}
-\subsection{Who does it reveal?}
+\section{The Subject of the Revelation of Jesus Christ}
 \I The book of Revelation reveals Jesus Christ.
-\subsubsection{He is God}
+\subsection{He is God}
 \I Rev 1:11 \Q{``I am the Alpha and the Omega, the First and the Last.''}
@@
 
-\subsubsection{He is the Savior}
+\subsection{He is the Savior}
 \I Rev 1:5 \Q{To Him who loved us and washed us from our sins 
@@
 
-\subsubsection{He is the conquering King}
+\subsection{He is the conquering King}
 \I Rev 1:7 \Q{Behold, He is coming with clouds, and every eye will see Him, 
@@
 
-\subsection{Who is it from?}
-\subsection{What is its purpose?}
-\subsection{Who is it to?}
-\subsection{What is its focus?}
+\section{The Purpose of the Revelation of Jesus Christ}
+\subsection{To show}
+\I Definition: to expose to the eyes; to explain, to reveal, and to inform.
+\I Matthew 16:21 \Q{From that time Jesus began to show to His disciples
+                    that He must go to Jerusalem, and suffer many things from
+                    the elders and chief priests and scribes, and be killed,
+                    and be raised on the third day.}
+\I John 20:20 \Q{When He had said this, He showed them His hands and His side.
+                Then the disciples were glad when they saw the Lord.}
+\I The purpose of Revelation is \emph{communication}, not \emph{confusion}.
+\subsubsection{Understanding is expected}
+\I Rev 2:7, 11, 17, 29; 3:6, 13, 22 -- the repeated exhortation to the churches
+    \Q{He who has an ear, let him hear what the Spirit says to the churches.}
+\I Rev 1:3, 22:7 -- we are expected to hear \emph{with understanding} in order
+    to obey
+    \Q{Blessed is he who reads and those who hear the words of this prophecy,
+    and keep those things which are written in it; for the time is near.}
+    \Q{Behold, I am coming quickly! Blessed is he who keeps the words 
+    of the prophecy of this book.}
+\subsubsection{Understanding has been enabled}
+\I Some will say that they are not able to understand. This is \emph{not}
+    a valid excuse.
+\I Has He not given you the Holy Spirit?
+\BI \I Was it not the washing of regeneration and renewing of the Holy Spirit
+        that saved you? (Titus 3:5)
+    \I Were you not born of water and the Spirit? (John 3:5)
+    \I Do you not live by the Spirit (thereby putting to death 
+        the deeds of the flesh)? (Romans 8:13)
+    \I How then can we say that we are unable to hear, and understand,
+        what the Spirit says to the churches? \EI
+\I Maybe if you were those who had hearts of stone,
+    but you have been given a heart of flesh (Ezekiel 36:26).
+\I Maybe if you were still futile in your thoughts (Romans 1:21), 
+    but you have been given the mind of Christ (1 Corinthians 2:16).
+\I In Jesus Christ you have been blessed with every spiritual blessing 
+    in the heavenly places in Jesus Christ (Eph 1:3), 
+\BI \I including knowing the mystery of His will (Eph 1:9), 
+    \I and the dispensation of the fullness of the times (Eph 1:10), \EI
+\I so that you can understand, and that you are without excuse.
 
+\subsubsection{Why understanding is not achieved}
+\I Why do we still have such trouble understanding?
+\I Yes, Revelation is, without a doubt, the most
+    controversial, misinterpreted, and misused book of the Bible.
+\I The problem is the hardness of our hearts, not the clarity of God's Word.
+\I Consider Jesus' disciples,
+\BI \I with the Lord 24/7 for 3 years,
+    \I Jesus personally taught them that He must be crucified and then 
+        rise again,
+    \I but the Jesus' death caught them by surprise,
+        and they initially didn't believe that He had risen!
+    \I How did Jesus characterize two of them, on the Emmaus road?
+        \Q{``O foolish ones, and slow of heart to believe in all that the 
+            prophets have spoken!''} (Luke 24:25)
+    \I And He basically preached the entire Old Testament to them,
+        in order that they might finally understand God's plan of redemption. 
+    \EI
+\I In the same way, we do not understand only because we are either
+\BI \I lovers of the world, 
+    \I ensnared by sin, 
+    \I foolish,
+    \I slow of heart to believe, or because 
+    \I we have not diligently searched and studied the Scriptures 
+        that we might understand God's full plan of redemption. \EI
+
+\subsection{His servants}
+\subsection{Things which must shortly take place}
 \section{The Authority of the Revelation of Jesus Christ}

### 2012-02-03 scribblings/symmA.tex
Draft of symmA.

\documentclass{article}
\usepackage{amsmath}
\newcommand{\BE}{\begin{equation}}
\newcommand{\EE}{\end{equation}}
\newcommand{\D}{\Delta}
\begin{document}
\BE (AD)^T = DA^T \EE
\BE (AD)_{ij} = A_{ij} d_j \EE
\BE (DA^T)_{ij} = d_i (A^T)_{ij} = A_{ji} d_i \EE
Find $d$ such that $AD$ is symmetric where 
\BE A = \nabla \times \nabla \times \EE
for a non-regular cartesian grid.
In other words, find $d$ such that
\BE A_{ij} d_j = A_{ji} d_i, \quad \text{for all $i, j$.} \EE
\begin{quote} FIGURE HERE \end{quote}
For the figure above,
\BE A_{ba} = -\frac{1}{\D x_b \D y_b} \EE
\BE A_{ab} = -\frac{1}{\D x_a \D y_a} \EE
\BE d_i \propto \frac{1}{\D x_i \D y_i} \EE
Also, we will have
\BE A_{ca} = -\frac{1}{\D x_b \D z_b} \EE
\BE A_{ac} = -\frac{1}{\D x_a \D z_a} \EE
\BE d_i \propto \frac{1}{\D x_i \D z_i} \EE
Lastly, we already have $A_{aa'} = A_{a'a}$ 
    for $a$ and $a'$ in the same direction.

The conclusion, then, is
\BE d_i = \frac{1}{\D x_i \D y_i \D z_i} \EE

\end{document}

### 2012-02-04 scribblings/symmA.tex
First part of symmA done.

@@
 \usepackage{amsmath}
+\usepackage{pstricks}
 \newcommand{\BE}{\begin{equation}}
@@
 \newcommand{\D}{\Delta}
+\title{Notes on symmetrizing the FDFD matrix with stretched-coordinate PML.}
+\author{Jesse Lu, Wonseok Shin}
 \begin{document}
+\maketitle
+We want to find a diagonal matrix 
+    \BE D = \text{diag}(d) \EE
+    such that
+    \BE (AD)^T = AD, \EE
+    where $A = \nabla \times \nabla \times$ is the system matrix
+    for the finite-difference frequency-domain problem
+    for Maxwell's equations.
+
+In fact, if we use an equally-spaced Cartesian grid 
+    (constant $\D x$, $\D y$, and $\D z$),
+    $A$ is already symmetric.
+However, when applying a stretched-coordinate perfectly-matched layer (SC-PML)
+    this no longer holds true,
+    and one requires a diagonal preconditioning matrix $D$
+    in order to restore the symmetry of $A$.
+Note that we assume that both $A$ and $D$ are complex-valued,
+    and that our goal is to make $A$ symmetric, not Hermitian.
+
+First we note that,
     \BE (AD)^T = DA^T \EE
     \BE (AD)_{ij} = A_{ij} d_j \EE
-\BE (DA^T)_{ij} = d_i (A^T)_{ij} = A_{ji} d_i \EE
-Find $d$ such that $AD$ is symmetric where 
-\BE A = \nabla \times \nabla \times \EE
-for a non-regular cartesian grid.
-In other words, find $d$ such that
+    \BE (DA^T)_{ij} = d_i (A^T)_{ij} = A_{ji} d_i, \EE
+    and so state our problem as finding $d$ such that
 \BE A_{ij} d_j = A_{ji} d_i, \quad \text{for all $i, j$.} \EE
-\begin{quote} FIGURE HERE \end{quote}
-For the figure above,
+
+\begin{figure}[h]\begin{center}
+\psset{gridcolor=green, subgridcolor=yellow}
+\begin{pspicture}(5,5)
+    \let\psgrid\relax
+    \psline[linestyle=dotted](2,1)(4,1)
+    \psline[linestyle=dotted](2,3)(4,3)
+    \psline[linestyle=dotted](4,1)(4,3)
+    \psline[linestyle=dotted](2,1)(2,3)
+    \psline{->}(2.6,2)(3.4,2)
+    \rput[t](3,1.9){$a$}
+    \psline{|-|}(2,0.8)(4,0.8)
+    \rput[t](3,0.7){$\D x_a$}
+    \psline{|-|}(4.2,1)(4.2,3)
+    \rput[l](4.3,2){$\D y_a$}
+
+    \psline[linestyle=dotted](1,2)(1,4)
+    \psline[linestyle=dotted](3,2)(3,4)
+    \psline[linestyle=dotted](1,4)(3,4)
+    \psline[linestyle=dotted](1,2)(3,2)
+    \psline{->}(2,2.6)(2,3.4)
+    \rput[r](1.9,3){$b$}
+    \psline{|-|}(0.8,2)(0.8,4)
+    \rput[r](0.7,3){$\D y_b$}
+    \psline{|-|}(1,4.2)(3,4.2)
+    \rput[b](2,4.3){$\D x_b$}
+\end{pspicture}
+\caption{Schematic used to find the values of $A_{ab}$ and $A_{ba}$,
+            where $a$ is a vector component in the $x$-direction
+            and $b$ is a vector component in the $y$-direction.
+        A similar schematic can be used to determine
+            the values for the $A_{ac}$ and $A_{ca}$,
+            where $c$ is a vector component in the $z$-direction,
+            by replacing $b \to c$ and $\D y_{a,b} \to \D z_{a,c}$.}
+            \label{fig1}
+\end{center} \end{figure}
+
+To do so, we observe that from figure~\ref{fig1} we can deduce that the
+    $\nabla \times \nabla \times$ operation will result in
     \BE A_{ba} = -\frac{1}{\D x_b \D y_b} \EE
-\BE A_{ab} = -\frac{1}{\D x_a \D y_a} \EE
-\BE d_i \propto \frac{1}{\D x_i \D y_i} \EE
-Also, we will have
+    \BE A_{ab} = -\frac{1}{\D x_a \D y_a}, \EE
+    from which we conclude that
+    \BE d_i \propto \frac{1}{\D x_i \D y_i}. \EE
+
+Similarly, if we replace $b \to c$ and $\D y_{a,b} \to \D z_{a,c}$ 
+    in the figure, then we have
     \BE A_{ca} = -\frac{1}{\D x_b \D z_b} \EE
-\BE A_{ac} = -\frac{1}{\D x_a \D z_a} \EE
-\BE d_i \propto \frac{1}{\D x_i \D z_i} \EE
-Lastly, we already have $A_{aa'} = A_{a'a}$ 
-    for $a$ and $a'$ in the same direction.
+    \BE A_{ac} = -\frac{1}{\D x_a \D z_a}, \EE
+    which leads to
+    \BE d_i \propto \frac{1}{\D x_i \D z_i}. \EE
 
-The conclusion, then, is
+We then conclude that the choice of 
     \BE d_i = \frac{1}{\D x_i \D y_i \D z_i} \EE
+    will lead to symmetric $AD$.
+Note that none of the $A_{aa'}$ terms need to be included,
+    where $a$ and $a'$ point in the same direction,
+    since $A_{aa'} = A_{a'a}$ will hold both with or without the preconditioner.
 

### 2012-02-04 sermons/Revelation1:1-3.tex
Sermon update.

@@
 \I Rev 1:18 \Q{``And I have the keys of Hades and of Death.''}
-\I Rev 19:7 \Q{``Let us be glad and rejoive and give Him glory,
+\I Rev 19:7 \Q{``Let us be glad and rejoice and give Him glory,
                 for the marriage of the Lamb has come,
@@
 \subsection{His servants}
+\I If you are a Christian, then you are the target audience of Revelation.
+    This highlights our need, as His servants, to know His Revelation.
+\BI \I Not for the world, but for His saints.
+    \I Not primarily for evangelism, but for the edification of the Church.
+    \I Not for repentance in the unbeliever, but in the life of the Christian.
+\EI
+\I This need is further deepened when we consider that 
+    ``servant'' is more accurately translated ``slave''.
+\BI \I We are the property of Jesus Christ,
+    \I owned by Him,
+    \I fully subject to His will.
+    \I Jesus has the full and complete rights to your life. \EI
+\I This means that knowing Revelation 
+\BI \I Is not a matter of leisure, or a hobby -- 
+        it is a matter of necessity and duty, as Christ's slave.
+    \I It is not about enriching yourself, 
+        or simply becoming more knowledgeable about the Bible -- 
+        it's about being faithful, and obedient.\EI
+\I Revelation is \emph{literally} Master Jesus' final instructions 
+    to His slaves before His return.
+\I And we cannot be the
+\BI \I faithful and wise servant (Matt 24:45) who is found faithfully
+        carrying out his Master's instructions, or
+    \I the servant (Matt 25) who has faithfully used the 2 or 5
+        talents entrusted to him by his Master \EI
+    apart from knowing and obeying the Revelation of Jesus Christ.
+
 \subsection{Things which must shortly take place}
+\I \emph{Transition:} We must make Revelation an urgent, \#1 priority,
+    because it informs us of the imminent.
+\I If imminent back then, how much more so now!
+\I Revelation has \emph{not} been fulfilled:
+\BI \I We are not in the new heaven and the new earth.
+    \I Death and Hades have not been thrown into the lake of fire.
+    \I Sin has not been abolished.
+    \I There still remains the final battle against Satan and the world.
+    \I The final judgement of sinners and the righteous.
+    \I Christ's evaluation of believers. \EI
+\I These things are future, but not far off, they are future imminent.
+\BI \I The Lord is not slow, He is merciful (2 Peter 3:19)
+    \I Nothing is hard for Him, 
+        but His judgement would have been far too much for you to bear! \EI
+\I The Second Coming is unheralded, it comes without warning.
+\BI \I Rev 22:7, 12 \Q{``Behold! I am coming quickly!''}
+    \I Rev 16:15 \Q{``Behold! I am coming as a thief''} \EI
+\I We must learn from the flood of Noah's time (Matt 24:38-39).
+    \Q{``For as in the days before the flood, they were eating and drinking,
+    marrying and giving in marriage, until the day that Noah entered
+    the ark, and did not know until the flood came and took them all away,
+    so also will the coming of the Son of Man be.''} 
+\I We must be those who are prepared for His return 
+    (Matt 25, parable of the virgins).
+\I And we can start on this by reading, understanding, and obeying
+    the Revelation of Jesus Christ.
+
 \section{The Authority of the Revelation of Jesus Christ}

### 2012-02-05 sermons/Revelation1:1.tex
Sermon on Rev 1:1 done.

--- 2012-02-04 sermons/Revelation1:1-3.tex
@@
 \begin{document}
-\part*{Revelation 1:1-3 --- The Revelation of Jesus Christ}
+\part*{Revelation 1:1 --- 
+        The Person and Purpose of the Revelation of Jesus Christ}
 \tableofcontents
 \BI
-\section*{Notes}
+\section{Introduction}
 \I  The point of this sermon is:
@@
     and to heed the commands given in it.
+That they would be convinced that Revelation is critical to living a 
+    victorious life in Christ Jesus.
 
-\section*{Introduction}
-\section{The Subject of the Revelation of Jesus Christ}
+Even beyond this, the goal is to show Jesus Christ and to call people 
+    to faith and obedience in Him.
+
+\I Envelope analogy
+
+\section{The Person of the Revelation of Jesus Christ}
 \I The book of Revelation reveals Jesus Christ.
+\BI \I That is is His revelation (given to Him by God).
+    \I That it is about Him (The disclosure, or unveiling, of Jesus Christ).
+    \I He is who John saw.
+    \I He is the One speaking to the Churches.
+    \I He is the One who will end the world. \EI
+\I  Reveltation gives us an exalted, and often unique, 
+    understanding of who Jesus is.
+\I Specifically, Revelation shows us that Jesus is God, the Savior, and
+    the conquering King.
+
 \subsection{He is God}
-\I Rev 1:11 \Q{``I am the Alpha and the Omega, the First and the Last.''}
+\I He is eternal, unchanging, and infinitely above all creation.
+\BI \I Rev 1:11 \Q{``I am the Alpha and the Omega, the First and the Last.''}
     \I Rev 1:17 \Q{``Do not be afraid, I am the First and the Last.''}
     \I Rev 22:13 \Q{``I am the Alpha and the Omega, the Beginning and the End, 
-                the First and the Last.''}
-\I Rev 1:13 \Q{\ldots and in the midst of the seven lampstands One 
-                like the Son of Man, \ldots}
-\I Rev 3:1, 5:6
+                    the First and the Last.''} \EI
+\I He directs and controls the Holy Spirit.
+\BI \I Rev 3:1, 5:6
             \Q{``These things says He who has the seven Spirits of God 
@@
                 which are the seven Spirits of God sent out into all the earth.}
-\I Rev 3:14 \Q{``These things says the Amen, the Faithful and True Witness,
-                the Beginning of the creation of God; \ldots}
-\I Rev 22:16 \Q{``I, Jesus, have sent My angel to testify to you these things 
-                in the churches, I am the Root and the Offspring of David, 
-                the Bright and Morning Star.''}
+\EI
+\I He is the Creator.
+\BI \I Rev 3:14 \Q{``These things says the Amen, the Faithful and True Witness,
+                    the Beginning of the creation of God; \ldots} \EI
+\I He is the Light.
+\BI \I Rev 22:16 \Q{``I, Jesus, have sent My angel to testify to you these 
+                things in the churches, I am the Root and the Offspring of 
+                David, the Bright and Morning Star.''}
     \I Rev 1:16 \Q{\dots and His countenance was like the sun shining 
-                in its strength.}
+                    in its strength.} \EI
 
 \subsection{He is the Savior}
-\I Rev 1:5 \Q{To Him who loved us and washed us from our sins 
-                in His own blood, \ldots}
-\I Rev 1:18 \Q{I am He who lives, and was dead, and behold, 
+\I The One who loved us and cleansed us.
+\BI \I Rev 1:5 \Q{To Him who loved us and washed us from our sins 
+                in His own blood, \ldots} \EI
+\I The Crucified and Risen Savior.
+\BI \I Rev 1:18 \Q{I am He who lives, and was dead, and behold, 
                     I am alive forevermore.} 
@@
                     of the Lamb who was slain from the foundation of the world.}
-\I Rev 5:9 \Q{``You are worthy to take the scroll, \\
+                    \EI
+\I Worthy of worship.
+\BI \I Rev 5:9 \Q{``You are worthy to take the scroll, \\
                     And to open its seals; \\
@@
                     Be to Him who sits on the throne, \\
-                And to the Lamb, forever and ever!''}
-\I Rev 5:5 \Q{``Do not weep. Behold, the Lion of the tribe of Judah,
+                    And to the Lamb, forever and ever!''} \EI
+\I Promised Messiah from the line of David.
+\BI \I Rev 5:5 \Q{``Do not weep. Behold, the Lion of the tribe of Judah,
                     the Root of David, has prevailed to open the scroll 
@@
                     and shuts and no one opens.''}
-\I Rev 1:18 \Q{``And I have the keys of Hades and of Death.''}
-\I Rev 19:7 \Q{``Let us be glad and rejoice and give Him glory,
+    \I Rev 1:18 \Q{``And I have the keys of Hades and of Death.''} \EI
+\I Final Salvation.
+\BI \I Rev 19:7 \Q{``Let us be glad and rejoice and give Him glory,
                     for the marriage of the Lamb has come,
@@
                     serve Him. They shall see His face, and His name shall be on
-                their foreheads.}
+                    their foreheads.} \EI
 
 \subsection{He is the conquering King}
-\I Rev 1:7 \Q{Behold, He is coming with clouds, and every eye will see Him, 
+\I No longer clothed in humility, but He comes with power to avenge.
+\BI \I Rev 1:7 \Q{Behold, He is coming with clouds, and every eye will see Him, 
                 even they who pierced Him. And all the tribes of the earth
@@
                 and His countenance was like the sun shining in its strength.}
-\I Rev 6:16-17 \Q{\ldots and said to the mountains and rocks, 
+                \EI
+\I He comes with great wrath.
+\BI \I Rev 6:16-17 \Q{\ldots and said to the mountains and rocks, 
                 ``Fall on us and hide us from the face of Him who sits on the
@@
                 sat One like the Son of Man, having on His head a golden crown, 
-                and in His hand a sharp sickle.}
-\I Rev 17:14 \Q{``These [ten kings and the beast] will make war with the Lamb, 
+                and in His hand a sharp sickle.} \EI
+\I He will be victorious.
+\BI \I Rev 17:14 \Q{``These [ten kings and the beast] will make war with 
+                the Lamb, 
                 and the Lamb will overcome them, for He is Lord of lords and
@@
                 and on His thigh a name written:
-                \Q{KING OF KINGS \\ AND LORD OF LORDS.}}
+                \Q{KING OF KINGS \\ AND LORD OF LORDS.}} \EI
 
-\I Rev 20:15 \Q{And anyone not found written in the Book of Life was cast 
+\I He is the final Judge.
+\BI \I Rev 20:15 \Q{And anyone not found written in the Book of Life was cast 
                 into the lake of fire.}
-            Note: we know this is the Lamb's Book of Life from Rev 13:8.
+            Note: we know this is the Lamb's Book of Life from Rev 13:8. \EI
+
+\subsection{Application}
+\I We need to know who Jesus is.
+\BI \I Knowing His sovereignty will give us peace.
+    \I Knowing His salvation will produce love and devotion to Him.
+    \I Knowing His eternal reward will keep us from pursuing the things of
+        the world.
+    \I Knowing His victory will give us courage unto obedience. \EI
 
@@
     the Revelation of Jesus Christ.
-
-\section{The Authority of the Revelation of Jesus Christ}
-\subsection{The word of God}
-\subsection{The testimony of Jesus Christ}
-\subsection{All things that he saw}
-
-\section{The Blessing of the Revelation of Jesus Christ}
 \EI

### 2012-02-06 scribblings/symmA.tex
Minor edit.
Updated symm A.

@@
 \title{Notes on symmetrizing the FDFD matrix with stretched-coordinate PML.}
-\author{Jesse Lu, Wonseok Shin}
+\author{Jesse Lu}
 \begin{document}
@@
     such that
-    \BE (AD)^T = AD, \EE
+    \BE (DA)^T = DA, \EE
     where $A = \nabla \times \nabla \times$ is the system matrix
@@
 First we note that,
-    \BE (AD)^T = DA^T \EE
-    \BE (AD)_{ij} = A_{ij} d_j \EE
-    \BE (DA^T)_{ij} = d_i (A^T)_{ij} = A_{ji} d_i, \EE
+    \BE (DA)^T = A^T D \EE
+    \BE (DA)_{ij} = A_{ij} d_i \EE
+    \BE (A^T D)_{ij} = (A^T)_{ij} d_j = A_{ji} d_j, \EE
     and so state our problem as finding $d$ such that
-\BE A_{ij} d_j = A_{ji} d_i, \quad \text{for all $i, j$.} \EE
+\BE A_{ij} d_i = A_{ji} d_j, \quad \text{for all $i, j$.} \EE
 
@@
     from which we conclude that
-    \BE d_i \propto \frac{1}{\D x_i \D y_i}. \EE
+    \BE d_i \propto \D x_i \D y_i. \EE
 
@@
     which leads to
-    \BE d_i \propto \frac{1}{\D x_i \D z_i}. \EE
+    \BE d_i \propto \D x_i \D z_i. \EE
 
 We then conclude that the choice of 
-    \BE d_i = \frac{1}{\D x_i \D y_i \D z_i} \EE
-    will lead to symmetric $AD$.
+    \BE d_i = \D x_i \D y_i \D z_i \EE
+    will lead to symmetric $DA$.
 Note that none of the $A_{aa'}$ terms need to be included,

### 2012-02-22 presentations/ob1_wg_paper/response.tex
Updated paper with response.

\documentclass{article}
\newcommand{\I}{\item}
\newcommand{\Q}[1]{\begin{quote} #1 \end{quote}}
\begin{document}
\section*{Response to Reviewer 1}
We appreciate the reviewer's detailed analysis and critique of the submitted
    publication.
A short response to the reviewer's remarks follows.
\begin{itemize}
\item Reviewer comments: 
    \Q{The method use only waveguides with the same direction of propagation and it is not
    possible to use this method for 2 tilt beams as in the case occurring in the grating
    coupler. first reference of the paper is not really appropriate.}

    The purpose of the first paper is appropriate because it is an example of
    solving the mode conversion for nanophotonics

\item Reviewer comments: 
    \Q{The method uses a 2.5 D approximation that it is not able to calculate accurately the
diffraction losses in the 3rd direction. In the paper, there are no validations of the
design by an accurate 3D method of modeling like FDTD for example.}

    The paper actually does not use a 2.5D approximation. 
    All simulations are in 2D. 
    3D devices will be investigated in a future publication.

\item Reviewer comments:
    \Q{The problem of realization of such coupler is not address. The size of the grid points
use for the modeling is closed to 10 nm and Iam not sure that it is compatible with the
resolution of standard or best lithographic tools. The authors must be added some
comments and if it possible to adapt her design with some rules that consider the
limitations induce by the fabrication.}

    According to the captions of Figs. 2 and following, the highest resolution 
    structures that are even possible are $\lambda_0/42$, where $\lambda_0$
    is the vacuum wavelength of light. 
    Therefore, for the case of $\lambda_0 = 1550 nm$ a \emph{single} pixel is 
    still 37nm $\times$ 37nm in size, from which we infer that the
    characteristic features of all the devices presented are well within
    the resolution of the current lithographic tools.

\item Reviewer comments:
    \Q{The problem of the wavelength tolerance and the alignment tolerances is not address.}

    The goal of this publication is simply to present the objective-first
    algorithm. 
    Robustness considerations are left to subsequent investigations.

\item Reviewer comments:
    \Q{In this paper, there are no comparison with other solution of coupling structure
describe in the literature. So, it is difficult to evaluate if this new method can be bring
realistic solutions of waveguide couplers.}

    The reviewer's point is valid.
    However, the reason why comparable solutions are not evaluated is largely
    because no competing methods for designing arbitrary mode couplers exist.
\end{itemize}

\section*{Response to Reviewer 2}
We appreciate the reviewer's encouraging remarks and suggestions.

The reviewer suggested that
\Q{ However, the use of the permittivity of a large range makes the example impractical and limit the method to theoretical analysis. I suggest the authors give at least one example (e.g. 1x2 coupler) to show its capability for the binary structure. }

This suggestion is very useful, however, we would like to defer the design of
    completely binary structures to a later publication.
\end{document}

### 2012-02-22 presentations/ob1_wg_paper/paper.tex
Updated paper with response.

@@
 \begin{document}
-\title{Objective-First Design of 
-    High-Efficiency, Small-Footprint Couplers Between 
-    Arbitrary Nanophotonic Waveguide Modes}
-\author{Jesse Lu and Jelena Vu\v{c}kovi\'{c}}
+\title{Objective-first design of 
+    high-efficiency, small-footprint couplers between 
+    arbitrary nanophotonic waveguide modes}
+\author{Jesse Lu$^\ast$ and Jelena Vu\v{c}kovi\'{c}}
 \address{Stanford University, Stanford, California, USA.}
-\email{jesselu@stanford.edu}
+\email{\url{jesselu@stanford.edu}}
 
@@
     nanophotonic circuits,''
-    Opt. Lett. \textbf{35}, 1290-1292 (2010)
+    Opt. Lett. \textbf{35}, 1290-1292 (2010).
 \bibitem{ridge}  K. K. Lee, D. R. Lim, L.C. Kimerling, J. Shin, and F. Cerrina, 
     ``Fabrication of ultralow-loss Si/SiO2 waveguides by roughness reduction,''
-    Opt. Lett. \textbf{26}, 1888-1890 (2001)
+    Opt. Lett. \textbf{26}, 1888-1890 (2001).
 \bibitem{pcslow} Y. A. Vlasov, M. O'Boyle, H. F. Hamann, and S. J. McNab,
     ``Active control of slow light on a chip with photonic crystal waveguides,''
-    Nature \textbf{438}, 65-69 (2005)
+    Nature \textbf{438}, 65-69 (2005).
 \bibitem{slotfocus} M. Lipson, 
-    ``Guiding, Modulating, and Emitting Light on 
-    Silicon-Challenges and Opportunities,'' 
-    J. Lightwave Technol. \textbf{23}, 4222-4238 (2005) 
+    ``Guiding, modulating, and emitting light on 
+    silicon-challenges and opportunities,'' 
+    J. Lightwave Technol. \textbf{23}, 4222-4238 (2005).
 \bibitem{active} J. Van Campenhout, P. Rojo Romeo, P. Regreny, C. Seassal, 
@@
     nanophotonic silicon-on-insulator waveguide circuit,'' 
-    Opt. Express \textbf{15}, 6744-6749 (20.75) 
+    Opt. Express \textbf{15}, 6744-6749 (2007).
 \bibitem{metallic} L. Tang, S. E. Kocabas, S. Latif, A. K. Okyay, 
-    D. S. Ly-Gagnon, K. C. Saraswat and D. A. B. Miller, 
-    ``Nanometre-Scale Germanium Photodetector Enhanced by a 
-    Near-Infrared Dipole Antenna,'' 
-    Nature Photonics \textbf{2}, 226 – 229 (2008) 
+    D. S. Ly-Gagnon, K. C. Saraswat, and D. A. B. Miller, 
+    ``Nanometre-scale germanium photodetector enhanced by a 
+    near-infrared dipole antenna,'' 
+    Nature Photonics \textbf{2}, 226 – 229 (2008).
 % \bibitem{fwadia} V. R. Almeida, R. R. Panepucci, and M. Lipson, 
@@
     ``Inverse design of a three-dimensional nanophotonic resonator,''
-    Opt. Express \textbf{19}, 10563-10.750 (2011) 
+    Opt. Express \textbf{19}, 10563-10.750 (2011). 
 \bibitem{code} \url{www.github.com/JesseLu/objective-first}
@@
 The motivation behind this formulation is two-fold.
-First, this approach allows is to arrive at a locally-optimal design rapidly 
+First, this approach allows one to arrive at a locally-optimal design rapidly 
     by allowing $x$ and $p$ to vary independently, 
@@
     and therefore, 
-    we choose a boundary-value formulation for the design objective.
+    we choose a boundary-value formulation for the design objective 
+    as shown in Fig.~\ref{fig:intro}.
 Namely, we first compute the boundary fields needed to obtain

### 2012-02-27 bible/1Peter2:13-17.tex
Added a bible study.

\documentclass{article}
\usepackage{fullpage}
\newcommand{\answerbox}{\vspace{1.5cm}}
\newcommand{\BE}{\begin{enumerate}}
\newcommand{\EE}{\end{enumerate}}
\newcommand{\I}{\item}
\begin{document}
\part*{1 Peter 2:13-17}

\BE
\section*{The command}
\I  What is the command given to us in verse 13? \answerbox
\I  In your own words, define ``submit'' (verse 13). 
    How is submission different than mere obedience? \answerbox
\I  How does verse 17 describe our duty to civil authorities?
    How does this differ from our relationship with fellow believers and God?
        \answerbox
\I  According to verses 13 and 14, in what cases does Peter's command apply?
    Are there exceptional cases where it does not apply? Give verses. 
        \answerbox
\I  According to verse 13, why are we to obey the command, and how does it 
        connect to verses 11 and 12, as seen by the word, ``Therefore''? 
        \answerbox
\I  What are some of the ordinances we must submit to today? 
    In what ways does our obedience to these ordinances bring glory to God? 
        \answerbox

\section*{The principle}
\I  What is God's plan for our lives, according to verse 15? \answerbox
\I  What are foolish men ignorant of, and how does our doing good silence
        their accusations? \answerbox
\I  In what way is the Christian free, as described in verse 16? \answerbox
\I  How can a carnal Christian use his freedom as a ``cloak for vice''?
        \answerbox
\I  How are obedient Christians to use their freedom in Christ as 
        ``bondservants of God''? 
    Consider especially the example of Paul in 1 Corinthians 9:19-23 and
        10:23-24. \answerbox
\I  What freedoms has God called you to renounce in order to serve Him more
        fully? \answerbox
\EE
\end{document}

### 2012-02-28 presentations/lightlabsFDS_mar-2012/pres.tex
Started group presentation.

\documentclass[landscape]{foils}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage[pdf]{pstricks}
\input defs.tex
\raggedright
\special{! TeXDict begin /landplus90{true}store end }
\renewcommand{\oursection}[1]{
\foilhead[-1.0cm]{#1}
}

\title{An introduction to lightlabsFDS}
\author{}
\MyLogo{}
\date{}

\begin{document}
\setlength{\parskip}{0cm}
\maketitle

\BIT \itemsep -1pt
\I  The lightlabsFDS mission
\I  Solver
\I  Interface
\I  Hardware
\I  End it
\EIT

\vfill

\oursection{The lightlabsFDS mission}
\textbf{To enable engineers and scientists to characterize optical structures 
        quickly, simply, and cost-effectively.}
\vspace{10 mm}

Innovate on three fronts to make this a reality:
\BIT
\I  Solve for electromagnetic fields in the frequency domain,
\I  Run simulations from pre-installed scientific software (Matlab), 
\I  Offload computation to centralized custom-tuned hardware.
\EIT

\oursection{Solving electromagnetics in the frequency domain}
\BIT
\I  lightlabsFDS: Frequency-Domain Solver
\I  Solves 
    \BEQ \nabla \times \mu^{-1} \nabla \times E - \omega^2 \epsilon E 
            = -i \omega J. \EEQ
    \BIT
    \I  Inputs: frequency $(\omega)$, structure $(\mu, \epsilon)$, 
            and excitation $(J)$.
    \I  Outputs: electromagnetic fields $(E, H, D, B)$.
    \EIT
\I  \emph{Many} practical advantages over existing time-domain solvers.
\EIT
\newpage

\oursection{Example: time-domain solver}

\psset{unit=1.5cm}
\psset{gridcolor=green, subgridcolor=yellow}
\begin{center}
\begin{pspicture}(8,5)
    \let\psgrid\relax

    \psframe*[linecolor=gray, fillcolor=gray, fillstyle=solid] (1,2.2)(4,2.8)
    \psframe*[linecolor=gray, fillcolor=gray, fillstyle=solid] (3,1)(5,4)
    \psframe*[linecolor=gray, fillcolor=gray, fillstyle=solid] (4,1.4)(7,2)
    \psframe*[linecolor=gray, fillcolor=gray, fillstyle=solid] (4,3.0)(7,3.6)
    \rput[B](4,4.1){Device}
    \psline[linestyle=dashed](1.6,0.6)(1.6,4.0)
    \rput[B](1.6,4.1){in}
    \psline[linestyle=dashed](6.4,0.6)(6.4,4.0)
    \rput[B](6.4,4.1){out}
\end{pspicture}
\end{center}
Time-domain issues include
\BIT
\I  Input: clean excitation at input requires an auxiliary simulation
\I  Device: approximations required for material dispersion
\I  Output: overlap integrals must be repeatedly calculated 
        \emph{during} the simulation
\EIT
\newpage

\begin{center}
\begin{pspicture}(8,5)
    \psgrid

    \psframe*[linecolor=gray, fillcolor=gray, fillstyle=solid] (1,2.2)(4,2.8)
    \psframe*[linecolor=gray, fillcolor=gray, fillstyle=solid] (3,1)(5,4)
    \psframe*[linecolor=gray, fillcolor=gray, fillstyle=solid] (4,1.4)(7,2)
    \psframe*[linecolor=gray, fillcolor=gray, fillstyle=solid] (4,3.0)(7,3.6)
    \rput[B](4,4.1){Device}
    \psline[linestyle=dashed](1.6,0.6)(1.6,4.0)
    \rput[B](1.6,4.1){in}
    \psline[linestyle=dashed](6.4,0.6)(6.4,4.0)
    \rput[B](6.4,4.1){out}
\end{pspicture}
\end{center}
\end{document}

### 2012-02-29 presentations/lightlabsFDS_mar-2012/pres.tex
Updated presentation a little.

@@
 \usepackage{amsmath}
-\usepackage[pdf]{pstricks}
+% \usepackage[pdf]{pstricks}
 \input defs.tex
@@
 
-\oursection{Example: time-domain solver}
+\oursection{Example}
 
-\psset{unit=1.5cm}
-\psset{gridcolor=green, subgridcolor=yellow}
-\begin{center}
-\begin{pspicture}(8,5)
-    \let\psgrid\relax
-
-    \psframe*[linecolor=gray, fillcolor=gray, fillstyle=solid] (1,2.2)(4,2.8)
-    \psframe*[linecolor=gray, fillcolor=gray, fillstyle=solid] (3,1)(5,4)
-    \psframe*[linecolor=gray, fillcolor=gray, fillstyle=solid] (4,1.4)(7,2)
-    \psframe*[linecolor=gray, fillcolor=gray, fillstyle=solid] (4,3.0)(7,3.6)
-    \rput[B](4,4.1){Device}
-    \psline[linestyle=dashed](1.6,0.6)(1.6,4.0)
-    \rput[B](1.6,4.1){in}
-    \psline[linestyle=dashed](6.4,0.6)(6.4,4.0)
-    \rput[B](6.4,4.1){out}
-\end{pspicture}
-\end{center}
+% \psset{unit=1.5cm}
+% \psset{gridcolor=green, subgridcolor=yellow}
+% \begin{center}
+% \begin{pspicture}(8,5)
+%     \let\psgrid\relax
+% 
+%     \psframe*[linecolor=gray, fillcolor=gray, fillstyle=solid] (1,2.2)(4,2.8)
+%     \psframe*[linecolor=gray, fillcolor=gray, fillstyle=solid] (3,1)(5,4)
+%     \psframe*[linecolor=gray, fillcolor=gray, fillstyle=solid] (4,1.4)(7,2)
+%     \psframe*[linecolor=gray, fillcolor=gray, fillstyle=solid] (4,3.0)(7,3.6)
+%     \rput[B](4,4.1){Device}
+%     \psline[linestyle=dashed](1.6,0.6)(1.6,4.0)
+%     \rput[B](1.6,4.1){in}
+%     \psline[linestyle=dashed](6.4,0.6)(6.4,4.0)
+%     \rput[B](6.4,4.1){out}
+% \end{pspicture}
+% \end{center}
 Time-domain issues include
@@
 
-\begin{center}
-\begin{pspicture}(8,5)
-    \psgrid
+% \begin{center}
+% \begin{pspicture}(8,5)
+%     \psgrid
+% 
+%     \psframe*[linecolor=gray, fillcolor=gray, fillstyle=solid] (1,2.2)(4,2.8)
+%     \psframe*[linecolor=gray, fillcolor=gray, fillstyle=solid] (3,1)(5,4)
+%     \psframe*[linecolor=gray, fillcolor=gray, fillstyle=solid] (4,1.4)(7,2)
+%     \psframe*[linecolor=gray, fillcolor=gray, fillstyle=solid] (4,3.0)(7,3.6)
+%     \rput[B](4,4.1){Device}
+%     \psline[linestyle=dashed](1.6,0.6)(1.6,4.0)
+%     \rput[B](1.6,4.1){in}
+%     \psline[linestyle=dashed](6.4,0.6)(6.4,4.0)
+%     \rput[B](6.4,4.1){out}
+% \end{pspicture}
+% \end{center}
+\BIT
+\I  Fundamental problem: trying to use a time-domain solver as a 
+        frequency-domain solver.
+\I  Additionally, no method to measure simulation error!
+\EIT
+\newpage
 
-    \psframe*[linecolor=gray, fillcolor=gray, fillstyle=solid] (1,2.2)(4,2.8)
-    \psframe*[linecolor=gray, fillcolor=gray, fillstyle=solid] (3,1)(5,4)
-    \psframe*[linecolor=gray, fillcolor=gray, fillstyle=solid] (4,1.4)(7,2)
-    \psframe*[linecolor=gray, fillcolor=gray, fillstyle=solid] (4,3.0)(7,3.6)
-    \rput[B](4,4.1){Device}
-    \psline[linestyle=dashed](1.6,0.6)(1.6,4.0)
-    \rput[B](1.6,4.1){in}
-    \psline[linestyle=dashed](6.4,0.6)(6.4,4.0)
-    \rput[B](6.4,4.1){out}
-\end{pspicture}
-\end{center}
+\BIT
+\I  Allow direct access to frequency-domain data.
+\I  Take care of input and output fields outside of the simulation.
+\I  Material dispersion explicitly defined.
+\I  Simulation error well defined.
+\EIT
+\newpage
+
+\BIT
+\I  Frequency-domain solver made possible by correct choice of PML and 
+        linear algebra algorithm.
+\I  See: Wonseok Shin, Shanhui Fan, 
+            ``Choice of the perfectly matched layer boundary condition for 
+            frequency-domain Maxwell's equations solvers'',
+            Journal of Computational Physics (January 2012).
+\EIT
+
+\oursection{Interface}
+\BIT
+\I  No installation required.
+\begin{verbatim}
+>>> [E, H] = fds(omega, epsilon, J); % Run FDS.
+\end{verbatim}
+\EIT
 \end{document}

### 2012-02-29 presentations/lightlabsFDS_mar-2012/pres.tex
Updated presentation.

@@
 
+Picture from paper here.
 \BIT
@@
 \oursection{Interface}
+\textbf{We want engineers and scientists to absolutely love using FDS
+        and, at the same time, to forget about it because it just works.}
 \BIT
-\I  No installation required.
+\I  No installation, just start up Matlab and
 \begin{verbatim}
->>> [E, H] = fds(omega, epsilon, J); % Run FDS.
+>>> [E, H] = fds(omega, epsilon, J); % Done.
 \end{verbatim}
+\I  Helper functions to
+    \BIT
+    \I  construct the optical structures $(\epsilon, \mu)$,
+    \I  define the input excitations $(J)$, and
+    \I  analyze and visualize the output fields $(E,H,D,B)$
+    \EIT
+    are all included and open-sourced.
+\I  Additionally, lots of examples and tutorials.
+\EIT
+
+\oursection{Hardware}
+Hub and spokes picture here.
+\BIT
+\I  Centralized, shared, custom-tuned server able to deliver the performance
+        of a large cluster
+\I  Performance achieved via heavily optimized GPU code
+\I  Multiple servers can be clustered with nearly $100\%$ computational
+        efficiency.
+\EIT
+
+\oursection{Current status}
+\BIT
+\I  Algorithm: Implemented on GPUs, still optimizing (Jesse)
+\I  Interface: (Wonseok)
+\I  Hardware: Prototype ordered and being built (Jesse)
 \EIT

### 2012-02-29 presentations/lightlabsFDS_mar-2012/pres.tex
Group meetin presentation draft done.

@@
 \usepackage{amsmath}
-% \usepackage[pdf]{pstricks}
+\usepackage[pdf]{pstricks}
 \input defs.tex
@@
 
-% \psset{unit=1.5cm}
-% \psset{gridcolor=green, subgridcolor=yellow}
-% \begin{center}
-% \begin{pspicture}(8,5)
-%     \let\psgrid\relax
-% 
-%     \psframe*[linecolor=gray, fillcolor=gray, fillstyle=solid] (1,2.2)(4,2.8)
-%     \psframe*[linecolor=gray, fillcolor=gray, fillstyle=solid] (3,1)(5,4)
-%     \psframe*[linecolor=gray, fillcolor=gray, fillstyle=solid] (4,1.4)(7,2)
-%     \psframe*[linecolor=gray, fillcolor=gray, fillstyle=solid] (4,3.0)(7,3.6)
-%     \rput[B](4,4.1){Device}
-%     \psline[linestyle=dashed](1.6,0.6)(1.6,4.0)
-%     \rput[B](1.6,4.1){in}
-%     \psline[linestyle=dashed](6.4,0.6)(6.4,4.0)
-%     \rput[B](6.4,4.1){out}
-% \end{pspicture}
-% \end{center}
+\psset{unit=1.5cm}
+\psset{gridcolor=green, subgridcolor=yellow}
+\begin{center}
+\begin{pspicture}(8,5)
+    \let\psgrid\relax
+
+    \psframe*[linecolor=lightgray,fillcolor=lightgray,fillstyle=solid]
+        (1,2.2)(4,2.8)
+    \psframe*[linecolor=lightgray,fillcolor=lightgray,fillstyle=solid]
+        (3,1)(5,4)
+    \psframe*[linecolor=lightgray,fillcolor=lightgray,fillstyle=solid]
+        (4,1.4)(7,2)
+    \psframe*[linecolor=lightgray,fillcolor=lightgray,fillstyle=solid]
+        (4,3.0)(7,3.6)
+    \rput[B](4,4.2){\textrm{Device}}
+    \psline[linestyle=dashed](1.6,0.6)(1.6,4.0)
+    \rput[B](1.6,4.2){\textrm{in}}
+    \psline[linestyle=dashed](6.4,0.6)(6.4,4.0)
+    \rput[B](6.4,4.2){\textrm{out}}
+\end{pspicture}
+\end{center}
 Time-domain issues include
@@
 % \begin{center}
-% \begin{pspicture}(8,5)
-%     \psgrid
-% 
-%     \psframe*[linecolor=gray, fillcolor=gray, fillstyle=solid] (1,2.2)(4,2.8)
-%     \psframe*[linecolor=gray, fillcolor=gray, fillstyle=solid] (3,1)(5,4)
-%     \psframe*[linecolor=gray, fillcolor=gray, fillstyle=solid] (4,1.4)(7,2)
-%     \psframe*[linecolor=gray, fillcolor=gray, fillstyle=solid] (4,3.0)(7,3.6)
-%     \rput[B](4,4.1){Device}
-%     \psline[linestyle=dashed](1.6,0.6)(1.6,4.0)
-%     \rput[B](1.6,4.1){in}
-%     \psline[linestyle=dashed](6.4,0.6)(6.4,4.0)
-%     \rput[B](6.4,4.1){out}
-% \end{pspicture}
+\begin{pspicture}(6,5)(-6,0)
+    \psgrid
+
+    \psframe[fillstyle=none](-1,2)(1,3)
+    \rput(0,2.5){\textrm{TDS}}
+
+    \psline(-2.4,2.5)(-1,2.5)
+    \rput[B](-1.6,2.7){$x(t)$}
+
+    \pspolygon[fillcolor=lightgray,fillstyle=solid]
+        (-2.4,4)(-2.4,1)(-3.2,0.5)(-3.2,4.5)
+    \psline(-4,4)(-3.2,4) \rput(-4.8,4){$X(\omega_1)$}
+    \psline(-4,3)(-3.2,3) \rput(-4.8,3){$X(\omega_2)$}
+    \psline(-4,2)(-3.2,2) \rput(-4.8,2){$\vdots$}
+    \psline(-4,1)(-3.2,1) \rput(-4.8,1){$X(\omega_n)$}
+
+    \psline(2.4,2.5)(1,2.5)
+    \rput[B](1.6,2.7){$y(t)$}
+
+    \pspolygon[fillcolor=lightgray,fillstyle=solid]
+        (2.4,4)(2.4,1)(3.2,0.5)(3.2,4.5)
+    \psline(4,4)(3.2,4) \rput(4.8,4){$Y(\omega_1)$}
+    \psline(4,3)(3.2,3) \rput(4.8,3){$Y(\omega_2)$}
+    \psline(4,2)(3.2,2) \rput(4.8,2){$\vdots$}
+    \psline(4,1)(3.2,1) \rput(4.8,1){$Y(\omega_n)$}
+\end{pspicture}
 % \end{center}
@@
 
+\begin{center}
+\begin{pspicture}(6,4)(-6,-2)
+    \psgrid
+
+    \psframe[fillstyle=none](-1,2)(1,3)
+    \rput(0,2.5){\textrm{FDS}}
+    \psline(-2.4,2.5)(-1,2.5)
+    \rput(-3.2,2.5){$X(\omega_1)$}
+    \psline(2.4,2.5)(1,2.5)
+    \rput(3.2,2.5){$Y(\omega_1)$}
+
+    \psframe[fillstyle=none](-1,0.6)(1,1.6)
+    \rput(0,1.1){\textrm{FDS}}
+    \psline(-2.4,1.1)(-1,1.1)
+    \rput(-3.2,1.1){$X(\omega_2)$}
+    \psline(2.4,1.1)(1,1.1)
+    \rput(3.2,1.1){$Y(\omega_2)$}
+
+    \rput(0,0.2){$\vdots$}
+
+    \psframe[fillstyle=none](-1,-0.4)(1,-1.4)
+    \rput(0,-0.9){\textrm{FDS}}
+    \psline(-2.4,-0.9)(-1,-0.9)
+    \rput(-3.2,-0.9){$X(\omega_n)$}
+    \psline(2.4,-0.9)(1,-0.9)
+    \rput(3.2,-0.9){$Y(\omega_n)$}
+\end{pspicture}
+\end{center}
 \BIT
@@
 
-Picture from paper here.
+\begin{center}
+% \includegraphics[width=\textwidth]{pml_cutout}
+\end{center}
 \BIT
@@
 \oursection{Hardware}
-Hub and spokes picture here.
+\begin{center}
+\begin{pspicture}(6,3)(-6,-3)
+    \psgrid
+    \rput(0,0){\parbox{5cm}{\begin{center}\textrm{lightlabsFDS\\server}
+                            \end{center}}}
+    \psline{<->}(-1.2,0.8)(-2.8,1.4) \rput(-3.5,1.5){\textrm{user1}}
+    \psline{<->}(-3.2,0)(-1.6,0) \rput(-4,0){\textrm{user2}}
+    \psline{<->}(-1.2,-0.8)(-2.8,-1.4) \rput(-3.5,-1.5){\textrm{user3}}
+    \psline{<->}(1.2,0.8)(2.8,1.4) \rput(3.5,1.5){\textrm{user4}}
+    \psline{<->}(3.2,0)(1.6,0) \rput(4,0){$\vdots$}
+    \psline{<->}(1.2,-0.8)(2.8,-1.4) \rput(3.5,-1.5){\textrm{userN}}
+\end{pspicture}
+\end{center}
 \BIT

### 2012-03-01 presentations/lightlabsFDS_mar-2012/pres.tex
Final presentation (group meeting).

@@
 \I  Hardware
-\I  End it
+\I  Current status 
 \EIT
@@
 
-% \begin{center}
+\begin{center}
 \begin{pspicture}(6,5)(-6,0)
-    \psgrid
+    \let\psgrid\relax
 
@@
 \end{pspicture}
-% \end{center}
+\end{center}
 \BIT
@@
 \begin{pspicture}(6,4)(-6,-2)
-    \psgrid
+    \let\psgrid\relax
 
@@
 \end{center}
+In contrast, a frequency-domain solver allows
 \BIT
-\I  Allow direct access to frequency-domain data.
-\I  Take care of input and output fields outside of the simulation.
-\I  Material dispersion explicitly defined.
-\I  Simulation error well defined.
+\I  Direct access to frequency-domain data,
+\I  External processing of input and output fields,
+\I  Explicit definition of material dispersion, and
+\I  Explicit measurement of simulation error.
 \EIT
@@
 \begin{center}
-% \includegraphics[width=\textwidth]{pml_cutout}
+\includegraphics[width=0.8\textwidth]{pml_cutout}
 \end{center}
@@
 \begin{pspicture}(6,3)(-6,-3)
-    \psgrid
+    \let\psgrid\relax
     \rput(0,0){\parbox{5cm}{\begin{center}\textrm{lightlabsFDS\\server}

### 2012-03-06 presentations/ob1_wg_paper/paper.tex
Final submission to Opec, with response to reviewers.
Updated bicg theory.

@@
     near-infrared dipole antenna,'' 
-    Nature Photonics \textbf{2}, 226 – 229 (2008).
+    Nature Photonics \textbf{2}, 226-229 (2008).
 % \bibitem{fwadia} V. R. Almeida, R. R. Panepucci, and M. Lipson, 
@@
     ``Inverse design of a three-dimensional nanophotonic resonator,''
-    Opt. Express \textbf{19}, 10563-10.750 (2011). 
+    Opt. Express \textbf{19}, 10563-10750 (2011). 
+\bibitem{veronis} G. Veronis, and S. Fan, 
+    ``Theoretical investigations of compact couplers between dielectric slab 
+    waveguides and two-dimensional metal-dielectric-metal plasmonic waveguides,'' 
+    Opt. Express \textbf{15}, 1211-1221 (2007).
+\bibitem{yang} R. Yang, R. A. Wahsheh, Z. Lu, and M. A. G. Abushagur, 
+    ``Efficient light coupling between dielectric slot waveguide and plasmonic
+    slot waveguide,'' Opt. Lett. \textbf{35}, 649-651 (2010).
 \bibitem{code} \url{www.github.com/JesseLu/objective-first}
@@
     by designing waveguide couplers in two-dimensions.
+As such, we do not analyze effects which are only present in full 
+    three-dimensional systems, such as out-of-plane losses.
 Specifically, we work in the two-dimensional transverse electric mode,
@@
     where $\epsilon = \{\epsilon_0, \epsilon_\text{silicon}\}$,
-    is needed for manufacturing purposes; this will be pursued in a future work.
+    is needed for manufacturing purposes; this will be pursued in a future work
+    along with an analysis of robustness to fabrication imperfections.
 That said, the final designs presented here 
@@
 All the designs presented are both highly efficient 
-    ($\sim 98\%$ coupling efficiency)
+    ($\sim 98\%$ coupling efficiency, in contrast to previous designs
+    which achieve only $\sim 70\%$ coupling efficiency\cite{veronis,yang})
     and extremely compact 
     (with footprints of only 1.5-4 square vacuum wavelengths).
+
+Note, however, that the small footprint of the designs presented does not 
+    imply small, unresolvable feature sizes.
+On the other hand, assuming a vacuum wavelength of 1550 nm,
+    the smallest possible feature in any of the examples presented is still
+    37 nm $\times$ 37 nm (see Fig.~\ref{fig:fiber}, for example),
+    as given by the size of a single grid point;
+    placing virtually all designs within reach of current-generation lithographic
+    systems.
+
 In addition, good starting points were not required; 
@@
     \caption{Coupler that converts the fundamental waveguide mode to the
-            second-order waveguide mode
-            (a movie of the design progress is included as a
-            supplementary material).
+            second-order waveguide mode.
         This problem is quite difficult since the two modes are of 
@@
 \end{figure}
-\clearpage
 \begin{figure}[htb]
@@
 \end{figure}
+\clearpage
 
@@
 The Matlab code used is available online\cite{code}.
-\clearpage
+% \clearpage
 \begin{appendix}

### 2012-03-08 sandbox/pb_template/pbt.tex
Added prayer bulletin template (latex).

\documentclass[12pt,twocolumn]{article}
\usepackage[landscape]{geometry}
\pagestyle{empty}
\newcommand{\B}{\begin{description}}
\newcommand{\I}[1]{\item[#1]}
\newcommand{\E}{\end{description}}
\begin{document}
\subsection*{Notes}
\pagebreak
\section*{Providence Bible Church Prayer Bulletin}
\begin{quote}
    Our Father in Heaven, \\
    Hallowed be Your name. \\
    Your kingdom come. \\
    Your will be done \\
    On earth as it is in heaven.
\end{quote}
\B
\I{Easter} Pray for our ministry oportunity with Lakewood elementary.
\E
\begin{quote}
    Give us this day our daily bread, \\
    And forgive us our debts, \\
    As we forgive our debtors. \\
    And do not lead us into temptation, \\
    But deliver us from the evil one.
\end{quote}
\B
\I{Needs} the other section...
\E

\begin{quote}
    For Yours is the kingdom and the power and the glory forever. Amen.
\end{quote}
\end{document}

### 2012-03-10 sandbox/pb_template/pbt.tex
Got prayer bulletin template to work.

@@
 \usepackage[landscape]{geometry}
+\usepackage{fullpage}
 \pagestyle{empty}
@@
 \newcommand{\E}{\end{description}}
+\newcommand{\Q}[1]{\parbox{\columnwidth}{\begin{quote} #1 \end{quote}}}
+\addtolength{\columnsep}{2cm}
+% \setlength{\oddsidemargin}{0cm}
+% \setlength{\evensidemargin}{0cm}
 \begin{document}
@@
 \section*{Providence Bible Church Prayer Bulletin}
-\begin{quote}
-    Our Father in Heaven, \\
+\Q{ Our Father in Heaven, \\
     Hallowed be Your name. \\
@@
     Your will be done \\
-    On earth as it is in heaven.
-\end{quote}
+    On earth as it is in heaven.} 
 \B
-\I{Easter} Pray for our ministry oportunity with Lakewood elementary.
+\input{cat1.tex} % Insert first category of requests here.
 \E
-\begin{quote}
-    Give us this day our daily bread, \\
+
+\Q{ Give us this day our daily bread, \\
     And forgive us our debts, \\
@@
     And do not lead us into temptation, \\
-    But deliver us from the evil one.
-\end{quote}
+    But deliver us from the evil one.}
 \B
-\I{Needs} the other section...
+% Insert second category of requests here.
+\input{cat2.tex}%% 2
 \E
 
-\begin{quote}
-    For Yours is the kingdom and the power and the glory forever. Amen.
-\end{quote}
+\Q{ For Yours is the kingdom and the power and the glory forever. Amen.}
 \end{document}

### 2012-03-13 bible/1Peter2:18-25.tex
Added Peter Bible study.

\documentclass{article}
\usepackage{fullpage}
\newcommand{\answerbox}{\vspace{1.5cm}}
\newcommand{\BE}{\begin{enumerate}}
\newcommand{\EE}{\end{enumerate}}
\newcommand{\I}{\item}
\begin{document}
\part*{1 Peter 2:18-25}

\BE
\I  What command are servants given and why are they to obey it? \answerbox
\I  Describe the circumstances of the submissive servant that Peter is exhorting
    his readers to be. What has be done? Why did he do it? And why is his master
    punishing him? \answerbox
\I  Name people from the Bible who patiently endured unjust suffering. 
    In what way were these commendable to God? \answerbox
\I  Who is ultimately responsible for the unjust suffering of Christians?
    \answerbox
\I  How can it be right for a holy and just God to give undeserved punishment?
    \answerbox
\I  From Jesus' example, what are you to do when suffering unjustly? \answerbox
\I  How do verses 24 and 25 describe who we were before Christ and then what
    Christ has done for us? \answerbox
\I  What perspective does this give us in undeserved suffering? \answerbox
\EE
\end{document}

### 2012-04-12 bible/1Peter3:1-7.tex
Added Peter Bible study.

\documentclass{article}
\usepackage{fullpage}
\newcommand{\answerbox}{\vspace{1.5cm}}
\newcommand{\BE}{\begin{enumerate}}
\newcommand{\EE}{\end{enumerate}}
\newcommand{\I}{\item}
\begin{document}
\part*{1 Peter 3:1-7}

\BE
\section*{Wives, v.1-6}
\I  According to the passage, why are wives to be submissive to their own
    husbands? Compare with Ephesians 5:22-24 and Colossians 3:18. \answerbox
\I  Define the following terms from verses 2 and 4: 
    chaste, fear, gentle, quiet. \answerbox
\I  What were some of the specific ways in which Sarah obeyed Abraham?
    See Genesis 12-23. \answerbox
\section*{Husbands, v.7}
\I  What principles undergird \emph{both} v.1-6 and v.7, as evident by the word 
    ``likewise'' (v.7)? \answerbox
\I  In what ways is a husband to dwell with understanding, and give honor
    to his wife? \answerbox
\I  What does the warning tell us about the importance of the command?
    In what other circumstances are a believer's prayers hindered? \answerbox
\EE
\end{document}

### 2012-04-23 sermons/Revelation1:1b-3.tex
Started on new sermon.

--- 2012-02-02 sermons/Revelation1:1-3.tex
@@
 \begin{document}
-\part*{Revelation 1:1-3 --- The Revelation of Jesus Christ}
+\part*{Revelation 1:1b-3 --- The Power and Promise of the Revelation of Jesus Christ}
 \tableofcontents
@@
         \end{quote}
-
-This Scripture prepares us to read and obey the rest of the book.
-It does so by telling us what Revelation is about
-    and what we must do with it.
-
-In this light, the goal of this sermon is to place a burden on the hearers 
-    to know and become familiar with the contents of this book, 
-    and to heed the commands given in it.
+\I  Remember that with every subsection, your job is to answer three questions:
+    \begin{enumerate}
+    \I  What does it mean?
+    \I  Why does it matter?
+    \I  How does it change my life?
+    \end{enumerate}
 
 \section*{Introduction}
-\section{The Nature of the Revelation of Jesus Christ}
-\subsection{Who does it reveal?}
-\I The book of Revelation reveals Jesus Christ.
-\subsubsection{He is God}
-\I Rev 1:11 \Q{``I am the Alpha and the Omega, the First and the Last.''}
-\I Rev 1:17 \Q{``Do not be afraid, I am the First and the Last.''}
-\I Rev 22:13 \Q{``I am the Alpha and the Omega, the Beginning and the End, 
-                the First and the Last.''}
-\I Rev 1:13 \Q{\ldots and in the midst of the seven lampstands One 
-                like the Son of Man, \ldots}
-\I Rev 3:1, 5:6
-            \Q{``These things says He who has the seven Spirits of God 
-                and the seven stars: \ldots''}    
-            \Q{And I looked, and behold, in the midst of the throne 
-                and of the four living creatures, 
-                and in the midst of the elders, 
-                stood a Lamb as though it had been slain, 
-                having seven horns and seven eyes, 
-                which are the seven Spirits of God sent out into all the earth.}
-\I Rev 3:14 \Q{``These things says the Amen, the Faithful and True Witness,
-                the Beginning of the creation of God; \ldots}
-\I Rev 22:16 \Q{``I, Jesus, have sent My angel to testify to you these things 
-                in the churches, I am the Root and the Offspring of David, 
-                the Bright and Morning Star.''}
-\I Rev 1:16 \Q{\dots and His countenance was like the sun shining 
-                in its strength.}
+\I  John's prologue underscores the gravity and urgency of Revelation.
+\I  The Person of Revelation.
+\I  The Purpose of Revelation.
 
-\subsubsection{He is the Savior}
-\I Rev 1:5 \Q{To Him who loved us and washed us from our sins 
-                in His own blood, \ldots}
-\I Rev 1:18 \Q{I am He who lives, and was dead, and behold, 
-                I am alive forevermore.}
-\I Rev 5:6 \Q{And I looked, and behold, in the midst of the throne
-                and of the four living creatures, and in the midst of the
-                elders, stood a Lamb as though it had been slain, \ldots}
-\I Rev 13:8 \Q{All who dwell on the earth will worship him [the beast], 
-                whose names have not been written in the Book of Life
-                of the Lamb who was slain from the foundation of the world.}
-\I Rev 5:9 \Q{``You are worthy to take the scroll, \\
-                And to open its seals; \\
-                For You were slain, \\
-                And have redeemed us to God by Your blood \\
-                Out of every tribe and tongue and people and nation, \ldots''}
-\I Rev 5:12 \Q{``Worthy is the Lamb who was slain \\
-                To receive power and riches and wisdom, \\
-                And strength and honor and glory and blessing!''}
-\I Rev 5:13 \Q{``Blessing and honor and glory and power \\
-                Be to Him who sits on the throne, \\
-                And to the Lamb, forever and ever!''}
-\I Rev 5:5 \Q{``Do not weep. Behold, the Lion of the tribe of Judah,
-                the Root of David, has prevailed to open the scroll 
-                and to loose its seven seals.''}
-\I Rev 3:7 \Q{``He who has the key of David, He who opens and no one shuts, 
-                and shuts and no one opens.''}
-\I Rev 1:18 \Q{``And I have the keys of Hades and of Death.''}
-\I Rev 19:7 \Q{``Let us be glad and rejoive and give Him glory,
-                for the marriage of the Lamb has come,
-                and His wife has made herself ready.''}
-\I Rev 7:17 \Q{``for the Lamb who is in the midst of the throne 
-                will shepherd them and lead them to living fountains of waters.
-                And God will wipe away every tear from their eyes.''}
-\I Rev 21:22-23 \Q{But I saw no temple in it, for the Lord God Almighty 
-                and the Lamb are its temple. The city had no need 
-                of the sun or of the moon to shine in it, 
-                for the glory of God illuminated it. The Lamb is its light.}
-\I Rev 22:1-2 \Q{And he showed me a pure river of water of life, 
-                clear as crystal, proceeding from the throne of God 
-                and of the Lamb. In the middle of its street, and on either
-                of the river, was the tree of life, which bore twelve fruits,
-                each tree yielding its fruit every month. 
-                The leaves of the tree were for the healing of the nations.}
-\I Rev 22:3-4 \Q{And there shall be no more curse, but the throne of God
-                and of the Lamb shall be in it, and His servants shall 
-                serve Him. They shall see His face, and His name shall be on
-                their foreheads.}
-
-\subsubsection{He is the conquering King}
-\I Rev 1:7 \Q{Behold, He is coming with clouds, and every eye will see Him, 
-                even they who pierced Him. And all the tribes of the earth
-                will mourn because of Him. Even so, Amen.}
-\I Rev 1:14-16 \Q{His head and hair were white like wool, as white as snow,
-                and His eyes like a flame of fire; His feet were like brass, 
-                as if refined in a furnace, and His voice as the sound of 
-                many waters; He had in his right hand seven stars, 
-                out of His mouth went a sharp two-edged sword, 
-                and His countenance was like the sun shining in its strength.}
-\I Rev 6:16-17 \Q{\ldots and said to the mountains and rocks, 
-                ``Fall on us and hide us from the face of Him who sits on the
-                throne and from the wrath of the Lamb! For the great day of His
-                wrath has come, and who is able to stand?''}
-\I Rev 14:14 \Q{Then I looked, and behold, a white cloud, and on the cloud
-                sat One like the Son of Man, having on His head a golden crown, 
-                and in His hand a sharp sickle.}
-\I Rev 17:14 \Q{``These [ten kings and the beast] will make war with the Lamb, 
-                and the Lamb will overcome them, for He is Lord of lords and
-                King of kings; and those who are with Him are called, 
-                chosen, and faithful.''}
-\I Rev 19:11-16 \Q{Now I saw heaven opened, and behold, a white horse.
-                And He who sat on Him was called Faithful and True,
-                and in righteousness He judges and makes war.
-                His eyes were like a flame of fire, and on His head were
-                many crowns. He had a name written that no one knew except
-                Himself. He was clothed with a robe dipped with blood,
-                and His name is called The Word of God.
-                And the armies of heaven, clothed in fine linen, white and
-                clean, followed Him on white horses.
-                Now out of His mouth goes a sharp sword, that with it He 
-                should strike the nations. And He Himself will rule them 
-                with a rod of iron. He Himself treads the winepress of the
-                fierceness and wrath of Almighty God. And He has on His robe 
-                and on His thigh a name written:
-                \Q{KING OF KINGS \\ AND LORD OF LORDS.}}
-
-\I Rev 20:15 \Q{And anyone not found written in the Book of Life was cast 
-                into the lake of fire.}
-            Note: we know this is the Lamb's Book of Life from Rev 13:8.
-
-\subsection{Who is it from?}
-\subsection{What is its purpose?}
-\subsection{Who is it to?}
-\subsection{What is its focus?}
-
-\section{The Authority of the Revelation of Jesus Christ}
+\section{The Power of Revelation}
 \subsection{The word of God}
 \subsection{The testimony of Jesus Christ}
-\subsection{All things that he saw}
+\subsection{A personal eyewitness account}
 
-\section{The Blessing of the Revelation of Jesus Christ}
+\section{The Promise of Revelation}
+\subsection{What is the blessing?}
+\subsection{Who is the blessing for?}
+\subsection{What does the blessing mean?}
+
 \EI

### 2012-04-24 sermons/Revelation1:1b-3.tex
Updated sermon.

@@
 \section*{Introduction}
-\I  John's prologue underscores the gravity and urgency of Revelation.
+\I  The purpose of John's prologue is to prepare us to read, understand, and 
+    obey the rest of the book.
 \I  The Person of Revelation.
@@
 \section{The Power of Revelation}
-\subsection{The word of God}
-\subsection{The testimony of Jesus Christ}
-\subsection{A personal eyewitness account}
+\I  Lead: There is a reason why verse 2 doesn't simply say, ``who wrote it down.''
+\I  John wants to emphasize the power of what follows, and he does so by describing it in three ways.
+
+\subsection{Eternal: the word of God}
+\I  Lead: Isn't it obvious that Revelation is the word of God?
+\BI \I It should be to us, but not necessarily to the original recipients. \EI
+\I  That Revelation is the word of God means that it is both eternal and living.
+    Eternal in that 
+\BI \I  it does not decay (Isaiah 40:8),
+    \I  is complete, with no part missing or ommitted (22:18-19),
+    \I  is perfect, and nothing can be added to it (Psalm 19:7);
+\EI
+    and living in that it
+\BI \I  transforms, converting the soul (Psalm 19:7),
+    \I  purifies, cleansing from sin (Psalm 119:9-10), and
+    \I  strengthens, producing endurance for trials (Matthew 7:24-27).
+\EI
+\I  And so Revelation does not merely point to the truth, it \emph{is} the truth.
+
+\subsection{Essential: the testimony of Jesus Christ}
+\I  Lead: The next issue, is Revelation essential?
+\BI \I Foundational or secondary?
+    \I Part of the Christian's core curriculum, or an optional specialty?
+\EI
+\I  Holding to the testimony of Jesus Christ is the essence of what a Christian is. It was 
+\BI \I  the reason for John's exile on Patmos (1:9), and
+    \I  the reason why the saints were killed (6:9) and beheaded (20:4).
+    \I  Believers are described as those who have the testimony of Jesus Christ (12:17),
+    \I  and they overcome Satan by clinging to it, even to death (12:11).
+\EI
+\I  Testimony means a legally-binding witness as submitted to a judge.
+\BI \I  As if Jesus is on the witness stand of a courtroom, and outlines 
+        who He is, what He has done, and what He will do. \EI
+\I  That Revelation is the testimony of Jesus Christ means that it is the essential truth of Jesus 
+    (who He is, what He has done, and what He will do)
+    that every Christian must cling to.
+
+\subsection{Eyewitness: all things that he saw}
+\I  John emphasizes that Revelation is a personal eyewitness account,
+\BI \I  Not something he thought up or figured out. \EI
+\I  Highlights the divine origin of the letter.
+\BI \I  Revelation does not depend at all on Jon's ability to pastor, preach, interpret, or organize.
+    \I  John only needs to see/hear and copy it down.
+    \I  He is effectively Jesus' scribe/typist.
+\EI
+\I  Allows us to step into John's shoes and see what he saw.
 

### 2012-04-26 sermons/Revelation1:1b-3.tex
Updated sermon.

@@
     obey the rest of the book.
-\I  The Person of Revelation.
-\I  The Purpose of Revelation.
+\I  John does so by telling us (from last time)
+\BI \I  the Person of Revelation, and
+    \I  the purpose of Revelation. \EI
 
@@
 \I  Highlights the divine origin of the letter.
-\BI \I  Revelation does not depend at all on Jon's ability to pastor, preach, interpret, or organize.
+\BI \I  Revelation does not depend at all on John's ability to pastor, preach, interpret, or organize.
     \I  John only needs to see/hear and copy it down.
@@
 \subsection{What is the blessing?}
+\I  New life in Christ, or to have Christ wholly:
+\BI \I  Jesus confesses you before the Father,
+    \I  not hurt by the second death,
+    \I  clothed in white garments, 
+    \I  to eat from the tree of life,
+    \I  to be given hidden manna to eat, and
+    \I  given the morning star. \EI
+\I  New identity in Christ, or to be Christ's wholly:
+\BI \I  given a white stone with a new name no one else knows,
+    \I  inscribed with the names of the Father, the Son, and the new Jerusalem,
+    \I  to be a pillar in the temple of God and never leave,
+    \I  to have power over the nations like Jesus, and
+    \I  to sit with Christ on His throne. \EI
+
 \subsection{Who is the blessing for?}
-\subsection{What does the blessing mean?}
+\I  Lead: Is it for select believers, or for the Church universal?
+\I  The blessing is for those who overcome.
+\BI \I All true believers overcome the world (1 John 5:5). \EI
+\I  The blessing, essentially salvation in Jesus Christ, shows that it is for
+    all Christians.
+
+\subsection{How does the blessing matter?}
+\I  Lead: Casts the Christian life in an entirely new light; it shows us 
+\BI \I  what we are fighting for,
+    \I  who we are fighting against,
+    \I  how we must be victorious. \EI
+\I  Christ's commands are not optional.
+\I  The blessing gices us he power and motivation to overcome.
 

### 2012-04-26 sermons/Revelation1:1b-3.tex
Updated sermon.

@@
 \section*{Introduction}
+\I  Spiritual telescope to see
+\BI \I  Jesus in heaven,
+    \I  what He is doing, and
+    \I  what He wants us to do, \EI
+    it would (I hope!) have a profound affect on how we live.
+    Revelation is that spiritual telescope.
+\I  Of course, the whole Bible does this for us in some measure, but Revelation is special\ldots 
+\I  Revelation is a paradigm-shifting book for the Christian in that it shows us
+    what our lives are about. 
+    Especially in the fog of battle (the distractions and confusions in our lives),
+    Revelation gives us understanding and direction.
+\BI \I  Who Jesus Christ is,
+    \I  what He is doing and will do; and in light of this,
+    \I  who He has made us,
+    \I  and what He would have us do. \EI
 \I  The purpose of John's prologue is to prepare us to read, understand, and 

### 2012-04-27 sermons/Revelation1:1b-3.tex
Updated sermon.

--- 2012-04-26 sermons/Revelation1:1b-3.tex
@@
 \section{The Promise of Revelation}
+\I  Revelation is unique in that it promises and emphasizes blessing from the very beginning.
+\BI \I  ``he who reads and those who hear'', the proclaimer and the hearer,
+    \I  ``and keep those things which are written in it'', above all, the doer,
+    \I  ``for the time is near.'', there is an urgency to know and obey. \EI
+\I  The blessings are concentrated in the 7 letters to the churches in Asia Minor.
+\BI \I  Evaluation, ``I know your works'',
+    \I  Command, repent and hold fast,
+    \I  Blessing, ``to him who overcomes''. \EI
+
 \subsection{What is the blessing?}
-\I  New life in Christ, or to have Christ wholly:
+\I  Lead: We need to answer three questions regarding the blessing\ldots
+\I  New life in Christ, that you have Christ fully: 
 \BI \I  Jesus confesses you before the Father,
@@
     \I  given the morning star. \EI
-\I  New identity in Christ, or to be Christ's wholly:
+\I  New identity in Christ, that Christ has you fully:
 \BI \I  given a white stone with a new name no one else knows,
@@
     \I  to sit with Christ on His throne. \EI
+\I  Note: The blessing is attractive to the extent that we are attracted to Jesus.
+\BI \I  Which is why seeing Him in all His glory (as Revelation reveals Him to us)
+        is so critical to living a victorious Christian life. \EI
 
@@
 \I  Lead: Is it for select believers, or for the Church universal?
-\I  The blessing is for those who overcome.
-\BI \I All true believers overcome the world (1 John 5:5). \EI
 \I  The blessing, essentially salvation in Jesus Christ, shows that it is for
     all Christians.
+\I  At the same time, the blessing is for those who overcome.
+\BI \I This is confirmed by 1 John 5:4-5, 
+        which tells us that all true believers overcome the world (1 John 5:5). \EI
+\I  This means that there is no such thing as a 
+    perpetually disobedient or continually defeated Christian.
+\BI \I  Not that a believer does not sin, but that he repents when he sins.
+    \I  The two repeated commands in chapters 2 and 3 are to repent of the wrong,
+        and to hold fast to the good. \EI
 
 \subsection{How does the blessing matter?}
-\I  Lead: Casts the Christian life in an entirely new light; it shows us 
+\I  Lead: Casts the Christian life in an entirely different light from what we often consider; 
+        it shows us 
 \BI \I  what we are fighting for,

### 2012-04-29 sermons/Revelation1:1b-3.tex
Sermon done.

--- 2012-04-27 sermons/Revelation1:1b-3.tex
@@
 \BI
-\section*{Notes}
-\I  The point of this sermon is:
-        \begin{quote} 
-        You need to know and obey the Revelation of Jesus Christ.
-        \end{quote}
-\I  Remember that with every subsection, your job is to answer three questions:
-    \begin{enumerate}
-    \I  What does it mean?
-    \I  Why does it matter?
-    \I  How does it change my life?
-    \end{enumerate}
+% \section*{Notes}
+% \I  The point of this sermon is:
+%         \begin{quote} 
+%         You need to know and obey the Revelation of Jesus Christ.
+%         \end{quote}
+% \I  Remember that with every subsection, your job is to answer three questions:
+%     \begin{enumerate}
+%     \I  What does it mean?
+%     \I  Why does it matter?
+%     \I  How does it change my life?
+%     \end{enumerate}
+%
 
 \section*{Introduction}
-\I  The purpose of John's prologue is to prepare us to read, understand, and 
-    obey the rest of the book.
-\I  John does so by telling us (from last time)
-\BI \I  the Person of Revelation, and
-    \I  the purpose of Revelation. \EI
+\I  Revelation is a paradigm-shifting book for the Christian.
+\BI \I  Literally an unveiling of present and future realities.
+    \I  Identifies what is eternal and what is not.
+    \I  Identifies who is in God's army and who is in Satan's.
+    \I  Jesus Christ's personal evaluation of His Church. \EI
+
+\section*{Review}
+\I  In the first three verses, John gets us ready for the rest of the book.
+    He gives us four preparations for the book of Revelation.
+\I  The Person of Revelation
+\BI \I  Jesus Christ is the focus of Revelation.
+    \I  All about who Jesus Christ is and what He will do. 
+    \I  Not so much about how the world will end, as how Jesus Christ will end the world.
+    \I  We are first and foremost learning about Jesus; not about seals, trumpets, bowls, beasts\ldots \EI
+\I  The Purpose of Revelation
 
@@
 \I  Lead: There is a reason why verse 2 doesn't simply say, ``who wrote it down.''
-\I  John wants to emphasize the power of what follows, and he does so by describing it in three ways.
+\BI \I  John wants us to have the correct attitude in approaching Revelation.
+    \I  He wants us to be aware of the nature of what we are reading. \EI
 
@@
 \I  And so Revelation does not merely point to the truth, it \emph{is} the truth.
+\I  Side-note: What's so special about Revelation? 
+    Isn't the rest of the Bible the word of God too?
+\BI \I  Yes, Revelation \emph{actually is} part of the Bible.
+    \I  Furthermore, Revelation is especially important to us, the post-apostolic Church. \EI
+\I  Where do you go when you are wrestling with sin, discouraged, worn out, or without hope?
+\BI \I  Go to Revelation, you will leave changed, transformed, and steadfast. 
+    \I  Because you will behold the glory of the Word of God, Jesus Christ,
+        and you will be transformed into the same image from glory to glory (2 Corinthians 3:18) \EI
 
@@
 \EI
+\I  Testimony means a legally-binding witness as submitted to a judge.
+\BI \I  As if Jesus is on the witness stand of a courtroom, and outlines 
+        who He is, what He has done, and what He will do. \EI
 \I  Holding to the testimony of Jesus Christ is the essence of what a Christian is. It was 
@@
     \I  the reason why the saints were killed (6:9) and beheaded (20:4).
-    \I  Believers are described as those who have the testimony of Jesus Christ (12:17),
+    \I  Believers are described (defined) as those who have the testimony of Jesus Christ (12:17),
     \I  and they overcome Satan by clinging to it, even to death (12:11).
 \EI
-\I  Testimony means a legally-binding witness as submitted to a judge.
-\BI \I  As if Jesus is on the witness stand of a courtroom, and outlines 
-        who He is, what He has done, and what He will do. \EI
+\I  Connection: John calls Revelation \emph{is} the testimony of Jesus Christ.
 \I  That Revelation is the testimony of Jesus Christ means that it is the essential truth of Jesus 
@@
 \EI
-\I  Allows us to step into John's shoes and see what he saw.
+\I  Revelation is very direct, there is hardly a mediator between us and Jesus.
 
@@
     \I  given the morning star. \EI
+    In other words, to have eternal life, which is knowing Jesus Christ, and to be unhindered in experiencing Him.
 \I  New identity in Christ, that Christ has you fully:
@@
     \I  to sit with Christ on His throne. \EI
+    To be completely owned by Christ, to have Him take every aspect of who you are and make you fully His.
+\I  These blessings are the hope, goal, and anticipation of the Christian.
+\BI \I  These form the motivation for our obedience to Christ. \EI
 \I  Note: The blessing is attractive to the extent that we are attracted to Jesus.
@@
 \I  Lead: Is it for select believers, or for the Church universal?
-\I  The blessing, essentially salvation in Jesus Christ, shows that it is for
+\BI \I  The blessing, essentially salvation in Jesus Christ, shows that it is for
         all Christians.
-\I  At the same time, the blessing is for those who overcome.
-\BI \I This is confirmed by 1 John 5:4-5, 
-        which tells us that all true believers overcome the world (1 John 5:5). \EI
-\I  This means that there is no such thing as a 
-    perpetually disobedient or continually defeated Christian.
-\BI \I  Not that a believer does not sin, but that he repents when he sins.
-    \I  The two repeated commands in chapters 2 and 3 are to repent of the wrong,
-        and to hold fast to the good. \EI
+    \I  At the same time, there is a condition on the blessing: it is for those who overcome. \EI
 
-\subsection{How does the blessing matter?}
-\I  Lead: Casts the Christian life in an entirely different light from what we often consider; 
-        it shows us 
-\BI \I  what we are fighting for,
-    \I  who we are fighting against,
-    \I  how we must be victorious. \EI
-\I  Christ's commands are not optional.
-\I  The blessing gices us he power and motivation to overcome.
+\I  The inevitable conclusion is that all true believers must and do overcome the world. 
+\BI \I This is confirmed by 1 John 5:4-5. \EI
+
+\I  In other words, there is no way to get to God except to persevere through the fires of this world.
+\BI \I  We are saved by grace through faith and that not of ourselves, but know also that the genuineness of our faith will be tested in the furnace of trial (1 Peter 1:6-7). \EI
+
+\I  Every Christian will be tempted and tried.  
+    Satan and the world will not choose to pass over any single believer.
+\BI \I  In God's sovereignty, not every believer is tried in the same way nor to the same extent.
+    \I  However, every believer is tried, including American believers. \EI
+
+\I  Now, many of us may not experience this reality. There are really only two explanations for this.
+\BI \I  Either our faith is not genuine (just intellectual assent, a set of morals, showing up at church on Sundays),
+    \I  or we are not being obedient (avoiding confrontation with the world by choosing to disobey God). 
+        Too scared to evangelize, too busy to edify, too comfortable for sanctification\ldots\EI
+\I  We overcome by repenting of our sin, and holding fast to the good.
+\BI \I  The one who overcomes does not always obey, but he does always repent.
+    \I  He may stumble but he cannot continue in sin, in the end, he values the prize of Jesus Christ more than the things of this world. 
+    \I  As we will see, the call to the 7 churches is to overcome by holding fast to the good, and by repenting of the bad.
+    \I  This repentance is not easy, and it will lead to a life of adversity with the world;
+        but also an incalculable blessing in the life to come. \EI
 

### 2012-05-29 presentations/invdes_paper1/idp1.tex
Added older inverse design papers.

\documentclass[10pt,letterpaper]{article}
\usepackage{opex3}
\usepackage{graphicx}
\usepackage{amsmath}
\DeclareMathOperator*{\minimize}{minimize}
\begin{document}

\title{Inverse design of nanophotonic structures using complementary convex optimization}
\author{Jesse Lu and Jelena Vu\v{c}kovi\'{c}}
\address{E.~L.~Ginzton Laboratory, Stanford University, Stanford, CA 94305-4085, U.~S.~A.}
\email{jesselu@stanford.edu}

\begin{abstract}
A computationally-fast inverse design method for nanophotonic structures is presented. The method is based on two complementary convex optimization problems which modify the dielectric structure and resonant field respectively. The design of one- and two-dimensional nanophotonic resonators is demonstrated and is shown to require minimal computational resources.
\end{abstract}

\ocis{350.4238 Nanophotonics and photonic crystals, 230.5750 Resonators, 230.5298 Photonic crystals, 220.0220 Optical design and fabrication}

\begin{thebibliography}{99}
\bibitem{Yee66} K. Yee, ``Numerical solution of initial boundary value problems involving Maxwell’s equations in isotropic media,'' IEEE Trans. Antennas Propag. Mag. \textbf{14}, 302-307 (1966).
\bibitem{AB74} M.~Albani and P.~Bernardi, ``A Numerical Method Based on the Discretization of Maxwell Equations in Integral Form,'' IEEE Trans.~Microwave Theory Tech. \textbf{22}, 446-450 (1974).
\bibitem{GA79} J.~M.~Gerardy and M.~Ausloos, ``Absorption spectrum of clusters of spheres from the general solution of Maxwell's equations. The long-wavelength limit,'' Phys.~Rev.~B \textbf{22}, 4950-4959 (1979).
\bibitem{Lon09} P. Deotare, M. McCutcheon, I. Frank, M. Khan, M. Loncar, ``High quality factor photonic crystal nanobeam cavities,'' Appl. Phys. Lett. \textbf{94}, 121106 (2009).
\bibitem{Sch02} J. Vuckovic, M. Loncar, H. Mabuchi, A. Scherer, ``Design of photonic crystal microcavities for cavity QED,'' Phys. Rev. E \textbf{65}, 1-11 (2002).
\bibitem{Nod05} Y.~Akahane, T.~Asano, B.~Song, S.~Noda, ``Fine-tuned high-Q photonic-crystal nanocavity,'' Opt. Express \textbf{13}, 1202-1214 (2005).
\bibitem{Lip08} A. Gondarenko, M. Lipson, ``Low modal volume dipole-like dielectric slab resonator,'' Opt. Express \textbf{16}, 17689-17694 (2008).
\bibitem{SD05} A. Hakansson, J. Sanchez-Dehesa, ``Inverse designed photonic crystal de-multiplex waveguide coupler,'' Opt. Express \textbf{13}, 5440-5449 (2005).
\bibitem{Sig04} P. Borel, A. Harpøth, L. Frandsen, M. Kristensen, P. Shi, J. Jensen, and O. Sigmund, ``Topology optimization and fabrication of photonic crystal structures,'' Opt. Express \textbf{12}, 1996-2001 (2004).
\bibitem{Vuc05} D. Englund, I. Fushman, and J. Vuckovic. ``General Recipe for Designing Photonic Crystal Cavities,'' Opt. Express \textbf{12}, 5961–5975 (2005).
\bibitem{cholmod} \emph{CHOLMOD} software package, accessed via \emph{Matlab}.
\bibitem{mycomp} Intel Core 2 Quad $2.5$GHz, 8Gb RAM.
\bibitem{JJ99} S.~G.~Johnson, J.~D.~Joannopoulos, ``Block-iterative frequency-domain methods for Maxwell’s equations in a planewave basis,'' Opt.~Express \textbf{8}, 967-970 (1999).
\bibitem{BV04} S. Boyd, L. Vandenberghe, \emph{Convex Optimization} (Cambridge University Press, 2004).
\bibitem{CVX} M. Grant and S. Boyd, \emph{CVX: Matlab software for disciplined convex programming}, \texttt{http://stanford.edu/$\sim$boyd/cvx}, June 2009.
\bibitem{Hen06} K. Hennessy, C.~Högerle, E.~Hu, A. Badolato, A. Imamoğlu, ``Tuning photonic nanocavities by atomic force microscope nano-oxidation,'' Appl.~Phys.~Lett.~\textbf{89}, 041118 (2006).
\bibitem{Aka05} B.~-S.~Song, S.~Noda, T.~Asano, Y.~Akahane, ``Ultra-high-Q photonic double-heterostructure nanocavity,'' Nat. Mater. \textbf{4}, 207-210 (2005).
\bibitem{Riv09} K.~Rivoire, Z.~Lin, F.~Hatami, W.~Ted Masselink, and J.~Vuckovic, ``Second harmonic generation in gallium phosphide photonic crystal nanocavities with ultralow continuous wave pump power,'' Optics Express \textbf{17}, 22609-22615 (2009).
\end{thebibliography}

\section{Introduction}
Numerous numerical methods have been devised to solve Maxwell's equations in both time\cite{Yee66} and frequency\cite{AB74,GA79} domains. We refer to these schemes as direct solvers, since they compute the electric and magnetic fields based on current sources, charge distributions and surrounding dielectric and/or metallic structures. While extremely useful in simulating optical components, using direct methods to design optical components, especially in two or three dimensions,  typically requires an extremely time-consuming direct search in a large parameter space\cite{Lon09,Sch02,Nod05,Lip08,SD05}.

On the other hand, an inverse solver would be much more adept in such design and optimization problems\cite{Sig04,Vuc05}. In this work, we define the inverse problem as that where the electromagnetic field is known, but the surrounding structure is not known. The goal in the inverse problem is, then, to find a dielectric structure that will produce that specific electromagnetic field profile.

We show that one can design nanophotonic resonators by specifying the electromagnetic field and its desirable characteristics (such as cavity quality (Q) factor and/or mode volume) and then using an inverse solver to find the corresponding dielectric structure. We show that the inverse method used is not only computationally-fast, but is also able to optimize for multiple device characteristics and produce multiple resonances, both of which are very difficult using direct methods.

\section{Numerical Setup}
We start from the time-harmonic eigenvalue equation 
\begin{equation}
\nabla \times \epsilon^{-1} \nabla \times H = \left(\frac{\omega}{c}\right)^2 H
\label{trad ev}\end{equation}
where $H$, $\epsilon$, $\omega$ and $c$ are the magnetic field, relative permittivity, resonance frequency and speed of light respectively. To solve the problem numerically, $H$ and $\epsilon$ are discretized in space using the standard Yee cell used in finite difference methods\cite{Yee66}. Also, the curl operators, since they are linear, are represented by the matrix $A$. Eq.~\eqref{trad ev} can now be written as 
\begin{equation}
A Y A x = \xi x
\label{lin ev}\end{equation}
where
\begin{align*}
&A \text{ is the discretized curl operator,} \\
&Y = \text{diag}(\epsilon^{-1}) \text{ is the diagonal matrix representing the dielectric structure,} \\
&x \text{ is a vector representing $H$, and} \\
&\xi =  \left(\frac{\omega}{c}\right)^2. 
\end{align*}
In this form, given $Y$, we can solve the direct problem by computing $x$ using an eigenvalue solver\cite{JJ99}. However, we note that eq.~\eqref{lin ev} is also linear in $Y$, which allows us, if $x$ is held constant, to solve the inverse problem by expressing eq.~\eqref{trad ev} as
\begin{equation}
By = d
\label{inv ls}\end{equation}
where
\begin{align*}
&B = A \cdot \text{diag}(Ax), \\
&d = \xi x\text{, and} \\
&y = 
\begin{bmatrix}
\epsilon_1^{-1} \\ \epsilon_2^{-1} \\ \vdots
\end{bmatrix} \text{ the variable for which we solve.}
\end{align*}
Here, $\text{diag}(Ax)$ is the matrix with the values of $Ax$ along the main diagonal and zeros elsewhere.

\section{Least-Squares Method in 1D}
\subsection{Least-Squares}
\begin{figure}[htbp]\centering
\includegraphics[width=\textwidth]{leastsquares}
\caption{Inverse design of a one-dimensional structure using the unmodified least-squares method. The target field is a sinusoid within a Gaussian envelope. The computed dielectric structure (green area) supports a field (red circles) that exactly matches the target field (blue line). The entire design process is also extremely fast and takes less than $1$ second to complete on a generic desktop computer~\cite{mycomp}. The periodic singularities in the dielectric structure are non-physical and will be addressed later in the article.}
\label{ls pic}\end{figure}
The result of applying this method to a simple one-dimensional problem is shown in Fig.~\ref{ls pic}. A generic least-squares solver~\cite{cholmod} was used to find the dielectric structure, $y$ (green region), that exactly produces the target field, $x$ (blue line), using eq.~\eqref{lin ev}. Using a generic desktop computer, the solution was obtained in less than a second. Then a finite-difference time-domain (FDTD) solver was used to obtain the actual field (red circles) produced by the structure and to verify the accuracy of $y$.

As expected, Fig.~\ref{ls pic} shows that the target field is reproduced exactly by the dielectric structure. However, the resulting structure is full of undesireable singularities. The rest of the section focuses on producing a well-behaved dielectric structure that still reproduces the target field accurately.

\subsection{Regularized Least-Squares}
The simplest way to produce a well-behaved dielectric structure is to add a regularization term to our least-squares problem, 
% \begin{equation}
% \begin{bmatrix} B \\ \sqrt{\eta} I \end{bmatrix} y = \begin{bmatrix} d \\ \sqrt{\eta}y_0 \end{bmatrix}
% \label{regls}\end{equation}
which is equivalent to solving the following optimization problem
\begin{equation}
\minimize_{y}\quad \|By-d\|^2 + \eta\|y-y_0\|^2.
\label{regls alt} \end{equation}
Here $y_0$ represents some initial guess for the dielectric structure, which we want the values of $y$ to stay close to, and $\eta>0$ is a parameter used to trade off fit, i.e. $\|By-d\|^2$, and deviation from $y_0$, i.e. $\|y-y_0\|^2$.

We chose to constrain $\epsilon$ around a constant value of $\epsilon_0 = 10$ and solved the least-squares system for $\eta=10^{-8}$, $10^{-6}$, and $10^{-4}$. The results, each still obtained in under a second, are shown in Fig.~\ref{regls pic} and illustrate the trade-off between constraining $\epsilon$ and accurately reproducing $H$.

\begin{figure}[htbp]\centering
\includegraphics[width=\textwidth]{regularized}
\caption{Inverse design of one-dimensional structures using the regularized least-squares method. The same target field is used as in Fig.~\ref{ls pic}, and the computation time remains below $1$ second. As the regularization parameter, $\eta$, is increased, $\epsilon$ is increasingly constrained to a chosen constant value of $10$. At the same time, the mismatch between target and actual fields increases markedly. This illustrates the apparent trade-off between producing reasonable structures and accurately reproducing a fixed target field.}
\label{regls pic}
\end{figure}

\section{Complementary Optimization in 1D}
\subsection{Motivation for a Complementary Optimization Strategy}
The fundamental problem in the previous examples is actually not in the methods themselves, but in the improper selection of a target field. In fact, it is very difficult to select a suitable target resonant field because not every resonant mode even has a corresponding dielectric structure that is able to reproduce it. Furthermore, it is nearly impossible to select a multi-dimensional field which corresponds to a well-behaved, isotropic and discretely-valued $\epsilon$, as would be needed for practical structures.

For this reason, a successful method must be allowed to either modify the target field, or specify it completely, in which case the user would only determine certain characteristics (e.g. mode-volume, Q-factor) that the target field should have. The former strategy is developed in both one and two dimensions, while the latter strategy is implemented in Section \ref{sec:2Dbounded} in order to design two-dimensional resonators with discrete values of $\epsilon$.

\subsection{Complementary Optimization}\label{sec:comp}
We start with the same target field as in the previous examples but we now formulate a method that allows for it to be modified during the design process. The formulation chosen is a complementary optimization routine, where we continually alternate between modifying $\epsilon$ to better fit the field, and then modifying the field to better fit $\epsilon$. Here, we use the term ``fit'' to mean that either $\epsilon$ or $H$ is solved so that the residual error from eq.~\eqref{trad ev} is minimized. Additionally, both iterations are regularized in order to stably approach a solution. This algorithm can be summarized as follows, 
\begin{align}
&\text{choose $x_0$ and $y_0$} \nonumber \\
&\text{for } i = 1, 2, \ldots \nonumber \\
&\quad\minimize_{y_i}\quad \|B_{i-1} y_i-d_{i-1}\|^2 + \eta_1\|y_i-y_{i-1}\|^2 \label{comp1}\\
&\quad\minimize_{x_i}\quad \|A Y_i A x_i - \xi x_{i-1}\|^2 + \eta_2\|x_i-x_{i-1}\|^2 \label{comp2}
\end{align}
where $Y_i = \text{diag}(y_i)$, $B_i = A \cdot \text{diag}(A x_i)$ and $d_i = \xi x_i$. $\|A Y_i A x_i - \xi x_{i-1}\|^2$ is used instead of $\|A Y_i A x_i - \xi x_{i}\|^2$ to avoid the trivial $x_i = 0$ solution and does not affect the overall accuracy since $x$ changes very slowly.

\begin{figure}[htbp]\centering
\includegraphics[width=\textwidth]{complementary}
\caption{Inverse design of a one-dimensional structure using the complementary optimization method. The target field in Figs \ref{ls pic} and \ref{regls pic} is used as the initial target field. The rates of change for both $\epsilon$ and $H$ are controlled by regularization parameters $\eta_1=10^{-4}$ and $\eta_2=10^{-3}$ respectively. The $400$ iterations used to achieve this result took $60$ seconds to compute. This method results in a well-behaved $\epsilon$ that actually produces a field very similar to the original target field. Interestingly, the formation of a ``steady-state'' periodic structure toward the sides of the structure has emerged.}
\label{comp pic}
\end{figure}

Fig.~\ref{comp pic} shows that the complementary optimization algorithm, after $400$ iterations and with the correct choice of regularization parameters $\eta_1$ and $\eta_2$, results in a well-behaved structure that is able to closely reproduce the modified target field. Numerically, the least-squares problem must now be solved numerous times, which increases the computational time needed to around $60$ seconds.

\subsection{Complementary Optimization with Bounded $\epsilon$}
In order to achieve a more practical, discretely-valued dielectric structure, we can impose strict upper- and lower-bounds on $\epsilon$. To this end, we modify our algorithm as such,
\begin{align}
&\text{choose $x_0$ and $y_0$} \nonumber \\
&\text{for } i = 1, 2, \ldots \nonumber \\
&\quad\minimize_{y_i}\quad \|B_{i-1} y_i-d_{i-1}\|^2 \nonumber \\
&\quad\text{subject to}\quad \epsilon_\text{max}^{-1} \leq y_i \leq \epsilon_\text{min}^{-1} \label{bc1} \\
\nonumber \\
&\quad\minimize_{x_i}\quad \|A Y_i A x_i - \xi x_{i-1}\|^2 + \eta_2\|x_i-x_{i-1}\|^2. \label{bc2}
\end{align}
In this algorithm, eq.~\eqref{bc1} is a convex optimization problem\cite{BV04}. This allows us to impose hard constraints on $\epsilon$, which in turn allows us to remove the regularization term present in eq.~\eqref{comp1}. The \emph{CVX} package\cite{CVX}, a Matlab-based modeling system for convex optimization, is used to solve eq.~\eqref{bc1}, with each iteration of the algorithm now requiring roughly $1$ second of computation time.
\begin{figure}[htbp]\centering
\includegraphics[width=\textwidth]{bounded}
\caption{Inverse design of a one-dimensional structure using the complementary optimization method with bounded $\epsilon$. The parameters are identical to those used to produce Fig.~\ref{comp pic} with the exception that only one regularization term is now needed ($\eta_2=10^{-3}$). The algorithm was run for $100$ iterations, which took $100$ seconds. The structure turns out to be almost completely binary-valued and looks like a periodic structure with tapered duty cycle. It produces an actual field which very closely matches the final target field.}
\label{bounded comp pic}
\end{figure}

A nearly binary-valued dielectric structure is obtained in Fig.~\ref{bounded comp pic}, which accurately produces the final target field. This is very useful for the design of practical structures, since they usually consist of two or three different materials at most. Interestingly, although the directly discreteness of $\epsilon$ was not enforced (since that would make the problem non-convex), a discrete, binary-valued structure has still arisen.

\section{Complementary Optimization in 2D}
\subsection{``S'' Resonator}
We now demonstrate that the complementary optimization method is versatile and can be scaled to multiple dimensions. To ensure that $\epsilon$ is well-behaved we use a point-spread function which does not allow $\epsilon$ to change at a certain point in space without affecting the values surrounding it.

In order to show that our method can produce complex designs, we choose an S-shaped target field which is non-trivial to reproduce. The optimization results, using the complementary optimization method from Section \ref{sec:comp}, are shown in Fig.~\ref{S pic}. The resulting dielectric structure is continuous, unbounded and contains some singularities (white dots), but the final target and actual fields match up well. Also, the computational cost remains quite reasonable; the $50$ iterations needed required only $5$ minutes of computation time. The resulting structure is completely unintuitive, and illustrates the kind of new capabilities offered by the inverse design strategy. Specifically, that a complex, intricate structure can be designed just by specifying the shape and frequency of a rather simple electromagnetic mode.
\begin{figure}\centering
\includegraphics[width=\textwidth]{S}
\caption{Inverse design of an ``S'' resonator using the complementary optimization method without bounds on $\epsilon$. The design was initialized by specifying an initial dielectric structure ($\epsilon=1$ everywhere) and a resonant field in the shape of an ``S''. The final dielectric structure was produced after $50$ iterations which took $90$ seconds to complete in total. The grid size was $80\times 120$. The final dielectric structure is quite unintuive, and yet reproduces the target field surprisingly well. This example demonstrates the versatility of the complementary optimization method in producing designs, from very simple specifications, which otherwise could be attained only with considerable difficulty.}
\label{S pic}
\end{figure}

\subsection{Multi-Mode Inverse Design}
The complementary optimization method can also be extended to produce dielectric structures with multiple resonances. To do so, multiple initial target fields are specified. The dielectric structure is first modified to simultaneously fit all target fields using a multi-objective least-squares method. Then each target field is individually modified to fit the structure; and we continue alternating between optimizing $\epsilon$ and $H^{(j)}$ in this way. A benefit of this scheme is that only the $\epsilon$ optimization increases in size, so the design process remains computationally tractable, even for several resonant fields. This algorithm can be summarized as follows,
\begin{align}
&\text{choose $y_0$, $x^{(1)}_0$, $x^{(2)}_0$, \ldots} \nonumber \\
&\text{for } i = 1, 2, \ldots \nonumber \\
&\quad\minimize_{y_i}\quad \eta_1\|y_i-y_{i-1}\|^2 + \sum_j \|B^{(j)}_{i-1} y_i-d^{(j)}_{i-1}\|^2  \label{mm1}\\
&\quad\text{for } j = 1, 2, \ldots \nonumber \\
&\quad\quad\minimize_{x^{(j)}_i}\quad \|A Y_i A x^{(j)}_i - \xi x^{(j)}_{i-1}\|^2 + \eta_2\|x^{(j)}_i-x^{(j)}_{i-1}\|^2. \label{mm2}
\end{align}
The design of an ``X'' resonator with two perpendicular, degenerate modes is shown in Fig.~\ref{X pic}. The added complexity increases the total computation time to $5$ minutes for $40$ iterations of the algorithm. 
\begin{figure}\centering
\includegraphics[width=\textwidth]{X}
\caption{Inverse design of a doubly-resonant, degenerate ``X'' resonator produced by the complementary optimization method with unbounded $\epsilon$. As in Fig.~\ref{S pic} the initial value of $\epsilon$ was $1$ everywhere. The two initial target fields used are only slightly perturbed and are very similar to the two final actual target fields. Computationally, this design took $5$ minutes to complete on a $120\times 120$ grid and required $40$ iterations. This example shows that the complementary optimization strategy can be extended to produce dielectric structures with multiple resonances. Such an ``X'' resonator is useful for polarization-entangled single-photon sources for example\cite{Hen06}.}
\label{X pic}
\end{figure}

\subsection{Design of Waveguiding Devices}
The multi-mode inverse design method can also be applied to the design of waveguiding devices such as multiplexers/demultiplexers, waveguide couplers, crossbars and dispersion-tailored waveguides. This can be accomplished by treating a waveguiding device as a doubly-degenerate resonator at its operational frequencies and then enforcing opposite symmetries (even/odd or cosine/sine) in the degenerate modes. A single-to-dual beam waveguide coupler designed based on Eq.~\eqref{mm1} and \eqref{mm2} is shown in Fig.~\ref{wg pic}, and motivates how one might design other waveguiding devices such as channel-drop filters. 
\begin{figure}[htbp]\centering
\includegraphics[width=\textwidth]{wg}
\caption{Inverse design of a single-to-dual beam waveguide coupler using the complementary optimization method without bounds on $\epsilon$. Two degenerate modes with opposite symmetry (sine and cosine) are used as target fields. Only $4$ iterations ($14$ seconds) are needed to achieve this solution on a $240\times 55$ grid. This is a simple demonstration showing that the complementary optimization method can also be extended to design waveguiding devices.}
\label{wg pic}
\end{figure}
In addition to macroscopic waveguiding devices, one should also be able to create novel periodic waveguiding structures. For instance, by controlling the frequency of a particular waveguiding mode at each of its $k$-vectors, one could create a waveguide with a customized dispersion characteristic, which would be useful in the design of slow-light waveguides.

\section{Complementary Optimization with Bounded $\epsilon$ in 2D}\label{sec:2Dbounded}
\subsection{Numerical Method}\label{sec:2Dnum}
We now use the complementary optimization method to design resonators with discrete, binary $\epsilon$ in two dimensions. At the same time, the algorithm is modified so that we no longer specify an initial target field; instead, only an initial dielectric structure and the maximum desired mode volume (i.e. mode area in 2D) are specified. In addition, the optimization process attempts to maximize the Q-factor. Such an algorithm now consists of iteratively solving two convex optimization problems,
\begin{align}
&\text{choose $y_0$} \nonumber \\
&\text{for } i = 1, 2, \ldots \nonumber \\
&\quad\minimize_{x_i}\quad \|A Y_{i-1} A x_i - \xi x_{i}\|^2 +   \eta \|F x_i\|^2\nonumber \\
&\quad\text{subject to}\quad (A x_i)^T Y_{i-1} (A x_i) \leq A_\text{mode} \label{be1} \\
\nonumber \\
&\quad\minimize_{y_i}\quad \|B_i y_i-d_i\|^2 \nonumber \\
&\quad\text{subject to}\quad \epsilon_\text{max}^{-1} \leq y_i \leq \epsilon_\text{min}^{-1}. \label{be2} 
\end{align}
In this algorithm, the field optimization, Eq.~\eqref{be1}, differs significantly from Eq.~\eqref{bc2}. First, the eigenvalue equation term $\|A Y_{i-1} A x_i - \xi x_{i}\|^2$ no longer utilizes $x_{i-1}$. Also, a new ``Fourier-minimizing'' term $\|F x_i\|^2$ has been added. Here, the row vectors of $F$ consist of the field Fourier components that we do not want incorporated in the final solution. The motivation for adding this term is to design high-Q resonators using planar structures, where the Q-factor is limited by out-of-plane losses, and can thus be improved by eliminating field Fourier components that are not localized by total internal reflection (components inside the light cone)~\cite{Vuc05}. Lastly, the $(A x_i)^T Y_{i-1} (A x_i)$ term allows us to specify the mode area (mode volume in three dimensions), that we desire for our resonant field. This works because the two minimization objectives in Eq.~\eqref{be1} will generally cause the mode area to be as large as possible, which means we always end up with $(A_1 x_i)^T Y_{i-1} (A_1 x_i) = A_\text{mode}$.

The addition of the two new terms in Eq.~\eqref{be1} signifies that the field iteration in our algorithm attempts to do more than to just satisfy Maxwell's equations. Rather than only trying to fit the dielectric structure, the resonant field now also minimizes some of its Fourier components while working with a limited mode area.

In contrast with the field optimization given by Eq.~\eqref{be1}, the structure optimization given by Eq.~\eqref{be2} remains identical to the equation in the one-dimensional case, Eq.~\eqref{bc1}, and contains no terms related to notions of Fourier components or mode area. In fact, the only objective in the $\epsilon$ optimization is to better fit the field generated from the field optimization. This means that in this scheme, the field iteration is leading the structure iteration. In other words, Eq.~\eqref{be1} ``looks ahead'' and gradually adapts itself to become a more desirable field, while Eq.~\eqref{be2} just ``follows along''. For this reason, this algorithm is unique from the other complementary optimization algorithms previously presented in the article, since in those algorithms both iterations follow one another and eventually ``meet in the middle''.

Finally, in this scheme, we chose to limit the degrees of freedom of both $x_i$ and $y_i$. Some components of $x_i$ were fixed at non-zero values and were not allowed to be modified simply to avoid the $x_i = 0$ situation. To enhance the aesthetics of the resulting dielectric structure, some components of $y_i$ were frozen as well, which is useful in cases where one would only like to modify the dielectric structure within a waveguide only, for example.

\subsection{Circular Grating Resonator}
\begin{figure}[htbp]\centering
\includegraphics[width=\textwidth]{circle}
\caption{Inverse design of a two-dimensional resonator using the complementary optimization method with strict bounds on $\epsilon$. The initial specification is very simple and consists an initial dielectric structure ($\epsilon=12.25$ everywhere), the frequency and mode-volume of the resonance field as well as a weighting factor, $\eta$, to avoid leaky field Fourier components. Additionally, the values of $\epsilon$ are only allowed to be modified within a central circular region and must be kept between $1$ and $12.25$. After $40$ iterations on a $160 \times 160$ grid, which took $7$ minutes to complete, a discrete structure emerged with excellent match between the predicted ($x_{40}$) and actual fields. The structure resembles a circular grating with a bowtie-like central structure for focusing the resonant energy to a single point.} 
\label{circle pic}
\end{figure}
Fig.~\ref{circle pic} shows the design of a circular grating resonator using the method from Section \ref{sec:2Dnum}. The dielectric structure emerged from a very simple choice of initial structure, namely a constant $\epsilon=12.25$ everywhere. The range of $\epsilon$ was limited to be from $1$ to $12.25$, the mode area was set to $5$ and $\eta= 10^{-3}$. Central components of $x_i$ were held constant to ensure that an electric dipole in the y-direction was produced in the center of the structure. Additionally, the components of $\epsilon$ outside a specified circle were held at a constant $\epsilon=12.25$ for the duration of the design process. The entire algorithm was run for $40$ iterations and took $7$ minutes.

After $40$ iterations, we see that a strong binary-valued structure has formed. Interestingly, the central bowtie-like structure has emerged from previous geneetic optimization methods as well\cite{Lip08}. Note also the extremely small amount of information needed to produce this result: only the frequency and mode area of the resonant field desired, and a trivial intial $\epsilon$. The ability to produce a rather advanced design from such a simple problem specification highlights the potential usefulness of inverse methods in the design of novel nanophotonic devices.

\subsection{Beam Resonator}
The same approach was used to design a beam resonator as shown in Fig.~\ref{line pic}. The parameters used in this design are identical to those used for the circular resonator, with the exception that the initial dielectric structure now consists of an unbroken waveguide, and the region where $\epsilon$ can be modified is now confined to the center of the waveguide.
\begin{figure}[htbp]\centering
\includegraphics[width=\textwidth]{beam}
\caption{Inverse design of a beam resonator in two dimensions using the complementary optimization method with bounded $\epsilon$. The initial conditions are identical to those for Fig.~\ref{circle pic}, except that the initial dielectric structure is an unbroken waveguide, and $\epsilon$ can only be modified within that waveguide. The structure emerged after $40$ iterations on a $320\times 40$ grid, which took $5$ minutes of computation. The bowtie-like structure has reappeared in the center. Interestingly, the effect of the Fourier term in Eq.~\eqref{be1}, is seen in the outward tapering of the holes.}
\label{line pic}
\end{figure}

These two, simple modifications produce a vastly different result as is plainly seen from Fig.~\ref{line pic}. Some characteristics remain, such as the two closely spaced holes in the center of the structures which focus the electromagnetic energy to a central point. Other features are unique to the beam resonator, such as a gradual outward tapering of hole diameters and size ending in a periodic ``steady-state'' structure, in similar fashion to Fig.~\ref{comp pic}. This tapering is a direct result of the Fourier term in Eq.~\eqref{be1} as it leads to a smooth field profile variation and minimization of the components in the light cone that lead to out-of-plane losses\cite{Vuc05,Aka05}.

\section{Conclusions and Outlook}
In summary, we have introduced and demonstrated a complementary optimization method for the inverse design of nanophotonic resonators as well as waveguiding structures. We have demonstrated that, in two dimensions, this method can be used to design non-trivial as well as multi-resonant structures. Furthermore, we have shown that by constraining the range of available dielectric constants, the same underlying method can produce binary-valued, discrete dielectric structures.

The methods presented here can readily be extended into three dimensions. In essence, the only hurdle is the size of the convex optimization problem for the field optimization. Since a full three-dimensional grid often consists of tens of millions of variables, solving the field optimization problem, Eq.~\eqref{be1}, using methods such as LU factorization is no longer computationally tractable. Instead, iterative methods such as truncated Newton methods must be employed. As it turns out, such iterative methods are especially well suited to this complementary optimization scheme, since they can take advantage of the information in $x_{i-1}$ in order to solve $x_i$ very quickly. This is very applicable to our algorithm since the field changes very little from one iteration to the next.

Although solving the field optimization problem is numerically challenging in three dimensions, solving the structure optimization problem, Eq.~\eqref{be2}, in three dimensions is much simpler. This is because only structural variations in-plane need to be accounted for planar nanophotonic devices. The number of variables in Eq.~\eqref{be2} for both two- and three-dimensional problems is then effectively the same, and the same numerical techniques can be employed to solve both.

A full three-dimensional inverse design method based on complementary optimization would enable the design of novel nanophotonic resonators. For instance, a resonator for efficient wavelength-conversion could be designed by creating a structure with multiple well-placed resonant frequencies~\cite{Riv09}. Furthermore, effects such as mode overlap and the use of frequency-dependent refractive index materials could be taken into account with such a method.

\subsection*{Acknowledgements}
This work has been supported in part by the AFOSR MURI for Compex and Robust On-chip Nanophotonics (Dr. Gernot Pomrenke).
We thank Prof. Stephen Boyd for many fruitful discussions regarding convex optimization.

\end{document}

### 2012-05-29 presentations/invdes_paper2/paper1.tex
Added older inverse design papers.

\documentclass[10pt,letterpaper]{article}
\usepackage{opex3}
\usepackage{amsmath}
\usepackage{graphicx}

\begin{document}
\title{Inverse design of a three-dimensional nanophotonic resonator}
\author{Jesse Lu, Stephen Boyd, and Jelena Vu\v{c}kovi\'{c}}
\address{Stanford University, \\ Stanford, C.A., 94305}
\email{jesselu@stanford.edu}

\begin{abstract} 
The inverse design of a three-dimensional nanophotonic resonator is presented. The design methodology is computationally fast (10 minutes on a standard desktop workstation) and utilizes a 2.5-dimensional approximation of the full three-dimensional structure. As an example, we employ the proposed method to design a resonator which exhibits a mode volume of $0.32(\lambda/n)^3$ and a quality factor of $7063$. % 8808 35648
\end{abstract}

\ocis{(230.5750) Resonators.} % REPLACE WITH CORRECT OCIS CODES FOR YOUR ARTICLE

%%%%%%%%%%%%%%%%%%%%%%% References %%%%%%%%%%%%%%%%%%%%%%%%%
\begin{thebibliography}{99}
\bibitem{miller} D. A. B. Miller, ``Rationale and challenges for optical interconnects to electronic chips,'' Proc. of the IEEE \textbf{88}, 728-749 (2000).
\bibitem{prevwork} J. Lu and J. Vuckovic, ``Inverse design of nanophotonic structures using complementary convex optimization,'' Opt. Express \textbf{18}, 3793-3804 (2010).
\bibitem{inan} U. Inan, A. Inan, \emph{Electromagnetic Waves} (Prentice Hall, 2000), page 296.
\bibitem{yee} K. Yee, ``Numerical solution of initial boundary value problems involving maxwell's equations in isotropic media,'' IEEE Trans. Antennas Propag. Mag. \textbf{14}, 302-307 (1966).
\bibitem{boydbook} S. Boyd and L. Vandenberghe, \emph{Convex Optimization} (Cambridge University Press, 2004).
\bibitem{altdir} S. Boyd, N. Parikh, E. Chu, B. Peleato, and J. Eckstein are preparing a manuscript to be called, ``Distributed Optimization and Statistical Learning via the Alternating Direction Method of Multipliers,'' \verb+http://www.stanford.edu/~boyd/papers/distr_opt_stat_learning_admm.html+. 
\bibitem{cholmod} Y. Chen, T. A. Davis, W. W. Hager, and S. Rajamanickam, ``Algorithm 887: CHOLMOD, supernodal sparse Cholesky factorization and update/downdate,'' ACM Trans. Math. Software \textbf{35}, No. 3, 2009.
\bibitem{cvx} M. Grant and S. Boyd, \emph{CVX: Matlab software for disciplined convex programming}, version 1.21. \verb+http://cvxr.com/cvx+, January 2011.
\bibitem{digitize} D. Englund, I. Fushman, and J. Vuckovic, ``General recipe for designing photonic crystal cavities,'' Opt. Express \textbf{13}, 5961-5975 (2005).
\end{thebibliography}

%%%%%%%%%%%%%%%%%%%%%%%%%%  body  %%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Motivation}
To date, the design of nanophotonic devices has generally involved a lengthy (days, weeks) process in which one perturbs, by trial-and-error, canonical structures such as photonic crystals or waveguide-coupled rings to achieve the desired performance for the device.

Instead, an inverse design method in which the user only specifies the desired electromagnetic field, or characteristics thereof, and then leaves the computer to find a dielectric structure satisfying these requirements, would be a much more intuitive and computationally efficient design strategy. Furthermore, such a method may even be the only feasible option available for the design of more complex multi-wavelength and multi-functional nanophotonic devices needed for on-chip integration\cite{miller}.

\section{2.5-dimensional approximation}
Previously, we demonstrated the inverse design of various nanophotonic devices in two dimensions\cite{prevwork}.
Unfortunately, to directly extend our previous method to full three-dimensional space requires solving for a very large ($\sim 10^7 \times 10^7$) and ill-conditioned matrix, namely that given by the time-harmonic Maxwell's equation in three dimensions, which for the electric ($E$) field is
\begin{align}
\nabla\times\nabla\times E - \mu\omega^2\epsilon E &= 0,\quad\text{where}\label{wave} \\
E &= E(x,y,z).
\end{align}

Therefore, to make our problem more tractable, we formulate a 2.5-dimensional approximation of the electromagnetic fields of a planar three-dimensional nanophotonic device. As shown in Fig.~\ref{approx}a, this involves treating a planar three-dimensional nanophotonic device as a truncated holey fiber with identical dielectric structure. We take advantage of the planar nature of most nanophotonic devices in this way to produce a tractable, computationally-fast method. The $E$-field inside such a holey fiber is expressed as
\begin{equation}
E = E(x,y)e^{-i\beta z},
\end{equation}
where $\beta$ is the wave-vector along the fiber axis. Solving for Eq.~\ref{wave} now requires solving for a much smaller ($\sim 10^5 \times 10^5$) matrix, which can be accomplished using standard linear algebra packages. This simulation technique is thus very similar to a two-dimensional finite-difference frequency-domain solve.

As an example, in Fig.~\ref{approx}b, we compare the 2.5-dimensional electric field against the three-dimensional simulated electric field (at the central plane of the slab), given by a standard finite-difference time-domain (FDTD) software package, for an L3 photonic crystal resonator. We see that with the appropriate choice of $\beta$, which we obtain by fitting a sinusoid to the out-of-plane decay in the three-dimensional FDTD solution, our approximation captures most of the characteristics of the three-dimensional field at the center plane of the slab. 
\begin{figure}[hbt]
\centering\includegraphics[width=\textwidth]{approx.eps}
\caption{(a) For computational feasibility, the resonant fields of a planar nanophotonic device are approximated as those of a truncated holey fiber with identical dielectric structure. (b) An example of our approximation using an L3 photonic crystal resonator. Most of the characteristics of the full three-dimensional field at the center of the slab appear in the approximate solution.}\label{approx}
\end{figure}

In this approximation, converting from a 2.5-dimensional structure to a full three-dimensional structure only requires the correct choice of slab thickness, $t$, since the in-plane values of $\epsilon$ remain the same. To estimate $t$ for the full three-dimensional device, we treat the resonant mode as a guided mode in a slab waveguide surrounded by a cladding of $n=1$. The expression for $t$ is then the thickness of the slab for the lowest-order TE mode of a slab waveguide with effective refractive index $n_\text{eff}$\cite{inan}:
\begin{align}
t &= \frac{2}{\beta}\tan^{-1}\frac{\alpha}{\beta},\label{t} \quad\text{where} \\
\alpha &= \sqrt{k_x^2 - \left(\frac{\omega}{c}\right)^2}, \quad\text{and} \\
k_x &= \sqrt{\left(\frac{n_\text{eff}\omega}{c}\right)^2 - \beta^2}.
\end{align}
Here, $\alpha$ is the wave-vector which determines the evanescent decay of the slab waveguide mode into air, while $k_x$ is an approximated in-plane k-vector. To determine $n_\text{eff}$, the effective refractive index, we use the following approximation,
\begin{equation}
n_\text{eff} = \sqrt{\frac{\|\epsilon E^2\|}{\|E^2\|}}.
\end{equation}
In the above formulation and for the remainder of the manuscript, the norm ($\|\cdot\|$) refers to the 2-norm over the entire grid and is equivalent to the spatial integral $(\int | \cdot |^2 dr)^{1/2}$.

\section{Inverse design method}
\subsection{Original formulation}
In our inverse design method, one proceeds by specifying either the resulting field or its characteristics and then computing a structure which will produce such a field. In this work, we chose to specify the desired field characteristics, namely, small mode-volume and large quality factor. The inverse design problem can then be formulated as,
\begin{align}
\text{minimize} \quad& \frac{\|\epsilon E^2\|}{\text{max}\{\epsilon E^2\}} \label{a1}\\ 
\text{subject to} \quad 
    & \nabla\times\nabla\times E - \mu\omega^2\epsilon E = 0 \label{a2}\\
    & \nabla\cdot\epsilon E = 0 \label{adiv}\\
    & \text{FT}_\text{lightcone}\{E\} = 0, \label{a3} \\
    & \epsilon = \{\epsilon_\text{air}, \epsilon_\text{silicon}\} \label{a4}
\end{align}
where $\epsilon$ and $E$ are the permittivity and electric vector field respectively, defined within the 2.5-dimensional approximation and discretized along a standard Yee grid\cite{yee} with periodic boundary conditions. $\epsilon$ was constrained to be isotropic by only varying $\epsilon_z$ in each cell, and then determining $\epsilon_x$ and $\epsilon_y$ via spatial interpolation. $\text{FT}$ is the two-dimensional Fourier transform.

In this formulation, the minimization objective (Eq.~\ref{a1}) is the mode volume, which we desire to be as small as possible. Similarily, Eq.~\ref{a3} is a constraint on the electric field to produce a large quality factor by forbidding the existence of any Fourier components within the light cone. Eqs.~\ref{a2} and \ref{adiv} are physical constraints that $\epsilon$ and $E$ must satisfy, that is, the wave equation for the 2.5-dimensional fiber mode and the transversality condition. Lastly, Eq.~\ref{a4} is a binary constraint on epsilon, denoting that we only want the structure to be composed of air or silicon.

Although our 2.5-dimensional approximation has reduced the size and complexity of the matrices found in the above formulation, the form of the problem in Eq.~\ref{a1}-\ref{a4} is actually incredibly difficult to solve, if for no other reason that Eq.~\ref{a1}, \ref{a2}, and \ref{a4} are non-convex\cite{boydbook} for joint minimization on both $\epsilon$ and $E$. To make matters worse, the binary constraint in Eq.~\ref{a4} generally results in a problem which is NP-hard\cite{boydbook}. For these reasons, our strategy is to employ an alternating directions scheme\cite{altdir}, in which we break Eq.~\ref{a1}-\ref{a4} into two separate, tractable sub-problems which we then solve iteratively.

\subsection{Alternating directions: field optimization sub-problem}
The first sub-problem in the alternating directions scheme involves optimizing $E$ while holding $\epsilon$ constant,
\begin{align}
\underset{E}{\text{minimize}} \quad& \|\nabla\times\nabla\times E - \mu\omega^2\epsilon E\|
    + \eta \|\epsilon E^2\| \label{b1}\\ 
\text{subject to} \quad 
    & E_\text{center} = 1 \label{bcenter} \\
    & \nabla\cdot\epsilon E = 0 \label{bdiv}\\
    & \text{FT}_\text{lightcone}\{E\} = 0, \label{bQ}
\end{align}
which is a quadratic problem with linear equality constraints, and is easily solved using a standard factor-solve method for sparse matrices\cite{cholmod}.

In this sub-problem, the most significant modification to the original formulation in Eq.~\ref{a1}-\ref{a4} is that the constraint in Eq.~\ref{a2} has been relaxed and moved into the minimization objective (Eq.~\ref{b1}). We will denote this term ($\|\nabla\times\nabla\times E - \mu\omega^2\epsilon E\|$) as the \emph{physics residual}.

At the same time, the term for the mode volume from Eq.~\ref{a1} has also been modified in Eq.~\ref{b1}. We denote this term ($\|\epsilon E^2\|$) as the \emph{design objective}. Note that although the denominator in the original formulation has been removed in order to make the term convex, the present formulation is still equivalent because we fix the $E$-field in the center of the structure (Eq.~\ref{bcenter}), where we want the maximum to occur. Also note that the constraint in Eq.~\ref{bcenter} is crucial in order to avoid the trivial solution $E=0$.

Lastly, the $\eta$ coefficient in Eq.~\ref{b1} allows us to trade-off between the physics residual and the design objective. Thus, in order to achieve a small mode volume, the initial value of $\eta$ is large and is subsequently exponentially reduced once per iteration at all points in the grid in order to bring the physics residual to 0. Furthermore, $\eta$ can also be given a spatial weighting in order to reduce in-plane losses; this strategy was implemented in the results presented here.

\subsection{Alternating directions: structure optimization sub-problem}
The second sub-problem in the alternating directions scheme involves optimizing $\epsilon$ while holding $E$ constant,
\begin{align}
\underset{\epsilon}{\text{minimize}} \quad& \|\nabla\times\nabla\times E - \mu\omega^2\epsilon E\| \label{c1} \\
\text{subject to} \quad 
    & \epsilon_\text{air} \le \epsilon \le \epsilon_\text{silicon}, \label{clim}
\end{align}
which is a quadratic problem with linear inequality constraints and is solved using CVX\cite{cvx}, a convex optimization package for Matlab.

As in the field optimization sub-problem, the physics residual has been relaxed and placed in the minimization objective (Eq.~\ref{c1}). However, we have chosen not to include the design objective term (mode volume). This modification was implemented as a heurestic that seemed to improve the aesthetic quality of the resulting structure.

The second major modification from the original formulation is found in the constraint in Eq.~\ref{clim}. Since the combinatorial problem given by the original constraint in Eq.~\ref{a3} proved to be intractable, the constraint on the values of $\epsilon$ is relaxed to allow for any value in the range from $\epsilon_\text{air}$ to $\epsilon_\text{silicon}$. The sub-problem is now relatively straightforward to solve, although it is very unlikely that one obtains a completely binary structure. In practice various digitization schemes can be implemented\cite{digitize}; however, such schemes were not needed here since a nearly binary structure was produced fortuitously.

\section{Result}
Using the formulations for the field optimization and structure optimization sub-problems presented above, along with our 2.5-dimensional approximation, the inverse design of a planar three-dimensional nanophotonic device is performed.

In order to do so, the frequency, $\omega = 0.16 c/\Delta x$, and the out-of-plane wave vector, $\beta = 0.24 (\Delta x)^{-1}$, are chosen by the user. Here, $\Delta x$ is the grid spacing and $c$ is the speed of light in vacuum. Lastly, an initial dielectric structure consisting entirely of silion, $\epsilon = \epsilon_\text{silicon}$ everywhere on a $160 \times 160$ grid, is used as a starting point---although other initial structures (e.~g.~ air everywhere or random $\epsilon$) yield nearly identical structures in this case.

Having already determined the desired characteristics of our resonator (small mode-volume and large quality factor) in the formulation of the two sub-problems, the inverse design proceeds by alternately solving the field optimization and then the structure optimization sub-problems. That is to say, in every iteration of the algorithm, $E$ is updated to be the solution of Eq.~\ref{b1}-\ref{bQ} and is then plugged into Eq.~\ref{c1}-\ref{clim}, the solution of which becomes the updated value of $\epsilon$. The subsequent iteration then uses the updated $\epsilon$ variable to re-optimize $E$ once again. And the algorithm continues to proceed in this way until the physics residual ($\|\nabla\times\nabla\times E - \mu\omega^2\epsilon E\|$) is reduced to an acceptable value.

\begin{figure}[hbt]
\centering\includegraphics[width=\textwidth]{target.eps}
\caption{The (a) dielectric structure, $\epsilon$, and (b) target field, $E$ ($E_y$ shown only), produced after 75 iterations (10 minutes) on a $160\times 160$ grid. The resulting $\epsilon$ is almost completely binary, and relatively smooth.}\label{target}
\end{figure}
Figs.~\ref{target}a and \ref{target}b are the resulting values of $\epsilon$ and $E$ ($E_y$ shown only), respectively, after 75 iterations of our inverse design method. The entire inverse design process takes only 10 minutes on a standard desktop computer for the $160 \times 160$ grid. An animation of the values of $\epsilon$ and $E_y$ at each iteration of the algorithm is included in the supplementary material.

The values of the physics residual and the design objective (mode volume) at each iteration are shown in Fig.~\ref{progress}. Most importantly, we see that the physics residual seems to converge linearly, indicating that the algorithm is reasonably efficient. The primary factor in determining this rate of convergence is the exponential decrease in $\eta$ (Eq.~\ref{b1}), since as $\eta$ decreases, increasing emphasis is placed on minimizing the physics residual in the field sub-problem.

\begin{figure}[hbt]
\centering\includegraphics[width=\textwidth]{the_prog.eps}
\caption{Value of the physics residual (blue) and design objective, or mode volume, (red) at each iteration. The physics residual seems to exhibit linear convergence, while the mode volume quickly saturates after roughly 25 iterations.}\label{progress}
\end{figure}

\section{Verification} % Find better section name
\subsection{Accuracy}
To evaluate the accuracy of the inverse design method, we compared the field resulting from the iterations (target field) with the actual field of the resulting structure solved by the 2.5-dimensional approximation (2.5D fiber mode) as well as the field of a full three-dimensional FDTD simulation of the resulting structure (full 3D field), as shown in Figs.~\ref{comp} and \ref{xsec}.

As detailed above, the thickness of the corresponding three-dimensional structure is determined by Eq.~\ref{t}, which yielded a value of $8.16 \Delta x$. However, a small sampling of thicknesses in that vicinity resulted in a more accurate thickness of $8.5\Delta x$, which matched the resonant frequency of the target field and 2.5-dimensional fiber mode.
\begin{figure}[hbt]
\centering\includegraphics[width=\textwidth]{compare.eps}
\caption{Comparison ($E_y$) of (a) the target field from the inverse design method (from Fig.~\ref{target}), (b) the actual 2.5-dimensional fiber mode, and (c) the field from the full three-dimensional FDTD simulation. The target field matches well with the full three-dimensional field.}\label{comp}
\end{figure}

\begin{figure}[hbt]
\centering\includegraphics[width=\textwidth]{the_xsec.eps}
\caption{Comparison of the cross sections of the $E_y$ field along the x-axis from the target field (blue), the actual 2.5-dimensional fiber mode (green), and the field from the full three-dimensional FDTD simulation (red). There is some discrepancy between the target field and the full three-dimensional field, but even that is confined to the edges and is only on the order of $\sim 1\%$ of the maximum field amplitude.}\label{xsec}
\end{figure}
Fig.~\ref{comp} plots the $E_y$ component of the target field, 2.5-dimensional fiber mode and the full three-dimensional FDTD field side-by-side. Fig.~\ref{xsec} plots the horizontal cross sections of the magnitudes of the fields on a logarithmic scale. We see that the target field and fiber mode match very well, while there is significantly more discrepancy between the target field and the full three-dimensional field. This is expected with the use of our approximation; however, the error is still relatively small (below 1\% of the maximum field strength) and confined mostly to the edges of the structure.

\subsection{Performance}
The fields from the full three-dimensional FDTD simulation were used to evaluate the performance of the device. The resulting mode volume was $0.32 (\frac{\lambda}{n})^3$ and the total quality factor was 7063. The radiative (out-of-plane) quality factor was 8808 and the in-plane quality factor was 35648.

Fig.~\ref{qcomp} shows the Fourier transforms of the target, fiber and three-dimensional $E_y$ fields taken at the center of the slab. Although there are virtually no field components in the light cone in the case of the target and fiber fields, additional components are present in the full three-dimensional case. This explains why even when leaky radiative components were strictly disallowed in the field optimization sub-problem, the error in the 2.5-dimensional approximation unavoidably introduces some leaky components in the case of the actual three-dimensional structure.

\begin{figure}[hbt]
\centering\includegraphics[width=\textwidth]{qcomp.eps}
\caption{Comparison of the Fourier transforms of the $E_y$ fields of the (a) the target field from the inverse design method, (b) the actual 2.5-dimensional fiber mode, and (c) the field from the full three-dimensional FDTD simulation. The error in our approximation introduces some small additional Fourier components into the light cone.}\label{qcomp}
\end{figure}

\section{Conclusion}
In summary, by using a 2.5-dimension approximation, we demonstrate the inverse design of a three-dimensional nanophotonic resonator. Further development of our method includes applying our inverse method to design three-dimensional devices which support multiple fields at different frequencies. This includes resonant devices such as a multi-wavelength cavity, as well as waveguiding devices such as $N$-port couplers, multiplexers, and grating couplers.\\

This work has been supported in part by the AFOSR MURI for Complex and Robust On-chip Nanophotonics (Dr. Gernot Pomrenke), grant number FA9550-09-1-0704.
\end{document}

### 2012-05-29 presentations/meta_book/1d.tex
Added progress on meta book chapter.

\section{1D resonator design}
We now build up to the objective-first formulation by example. 
And from a different perspective.

We're going to take a step back and start with the most naive inverse design strategy possible.
Then we'll end with objective first.
This motivates the need for the alternating directions and objective-first strategy.

\subsection{Direct solve of structure}
This is the simplest thing you can do. Basically, set $x$ and solve for $p$.
Also, take out the relaxed constraint on $p$.
\BA \minimize{p} \| B(x) p - d(x) \|^2 \EA
\myfig{1d/leastsquares}{test}
We perfectly satisfy the field but...

\subsection{Regularized solve of structure}
We add a term to try to control $p$
\BA \minimize{p} \| B(x) p - d(x) \|^2 + \eta \|p - p_0\|^2 \EA
\myfig{1d/regularized}{test}
Better, but a trade-off between field accuracy and structure variation.

\subsection{Alternating directions solve}
Now we actually do both fields.
\BA \minimize{p} \| B(x) p - d(x) \|^2 + \eta_1 \|p - p_\text{prev}\|^2 \EA

\BA \minimize{x} \| A(p) x - b(p) \|^2 + \eta_2 \|x - x_\text{prev}\|^2 \EA
\myfig{1d/complementary}{test}

\subsection{Alternating directions solve with bounded $p$}
\BA \minimize{p} \| B(x) p - d(x) \|^2 \\
    \subto 0 \le p \le 1 \EA

\BA \minimize{x} \| A(p) x - b(p) \|^2 + \eta_2 \|x - x_\text{prev}\|^2 \EA
\myfig{1d/bounded}{test}

### 2012-05-29 presentations/meta_book/my_chapter.tex
Added progress on meta book chapter.

% Some custom commands.
\newcommand{\BE}{\begin{equation}}
\newcommand{\EE}{\end{equation}}
\newcommand{\BA}{\begin{eqnarray}}
\newcommand{\EA}{\end{eqnarray}}
\newcommand{\curl}{\nabla\times}
\newcommand{\minimize}[1]{\JLUminimize_{#1}\;&}
\newcommand{\subto}{\text{subject to}\;&}
\newcommand{\myfig}[2]{\begin{figure}[!h]\includegraphics[width=\textwidth]{fig/#1}\caption{#2}\label{#1}\end{figure}}

\chapter{Objective-First Nanophotonic Design}
\label{intro}

\abstract{The abstract for the book.}

Introductory paragraph.

\input{wave_eq}
\input{ob1}
\input{1d}
\input{res}
\input{wg}

\section{Metamaterials design}
\subsection{Modification of the design objective}
\subsection{Cloak devices}
\subsection{Mimic devices}

\section{Extending the method}
\subsection{3D}
\subsection{Multi-mode}
\subsection{Robustness}

\section{Appendix}
\subsection{Full 3D curl}
\subsection{1D}
\subsection{2D}
\subsection{2.5D}

### 2012-05-29 presentations/meta_book/ob1.tex
Added progress on meta book chapter.

\section{The objective-first design problem}
intro

\subsection{Design objectives}
Talk about $f(x)$ and that we are interested in convex ones.

\subsection{Convexity}
Convex optimization quick intro.

\subsection{Typical design formulation}
Typically,
\BA \minimize{x,p} f(x) \\
    \subto g(x, p) = 0 \\
        & p \in {0,1} \EA

\subsection{Objective-first design formulation}
Objective-first does 
\BA \minimize{x,p} \|g(x,p)\|^2 \\
    \subto f(x) = f_\text{ideal} \\
        & 0 \le p \le 1 \EA

This is a bi-convex problem, which we solve using an alternating directions method.

\subsection{Field sub-problem}
\BA \minimize{x} \| A(p) x - b(p) \|^2 \\
    \subto f(x) = f_\text{ideal} \EA

\subsection{Structure sub-problem}
\BA \minimize{p} \| B(x) p - d(x) \|^2 \\
    \subto 0 \le p \le 1 \EA

### 2012-05-29 presentations/meta_book/res.tex
Added progress on meta book chapter.

\section{Resonator design}
Now that we see the usefulness of objective-first design strategy for a 1D resonator,
    we extend to 2D and approximate 3D as well.

We also transition design objectives:
    field everywhere,
    to certain field characteristics.

We continue to fill-out our understanding of objective-first,
    and we get a fuller flavor of what it can do.

\subsection{``S'' resonator}
We construct an ``S''-shaped field and create a resonator to make that field.
This uses the previous equation...
\myfig{res/S}{caption}

\subsection{2D}
Now we design for minimal mode-volume and maximal Q.
Although $Q^{-1}$ minimization should be a constraint we only do this in the next section.
\BA \minimize{x} \| A(p) x - b(p) \|^2 + \eta \| F x \|^2 \\
    \subto \| \text{diag}(\sqrt{p}) A_\text{curl} x \|^2 \le a_\text{mode} \EA
\BA \minimize{p} \| B(x) p - d(x) \|^2 \\
    \subto 0 \le p \le 1 \EA
\myfig{res/beam}{caption}
\myfig{res/circle}{caption}

\subsection{2.5D}
Although solving for the relevant matrices in 3D is really hard, we can make an approximation.

Here we make 
\BA \minimize{x} \| A(p) x - b(p) \|^2 + \eta \|\text{diag}(\sqrt{p}) A_\text{curl} x\|^2 \\
    \subto Fx = 0  \EA
\BA \minimize{p} \| B(x) p - d(x) \|^2 \\
    \subto 0 \le p \le 1 \EA

\myfig{res/target}{Add the actual field here!}

### 2012-05-29 presentations/meta_book/wave_eq.tex
Added progress on meta book chapter.

\section{The electromagnetic wave equation}
\subsection{Physics formulation}
Let's talk about the electromagnetic wave equation from a physics standpoint.
Let's start from Maxwell's equations without currents.
\BA \curl E = - \mu_0 \frac{\partial H}{\partial t} \\
    \curl H = J + \epsilon \frac{\partial E}{\partial t} \EA

\BA \curl E = - i \mu_0 \omega H \\
    \curl H = J + i \epsilon \omega E \EA

\BE \curl \epsilon^{-1} \curl H - \mu_0 \omega^2 H = \curl \epsilon^{-1} J \EE

Talk about reduced dimensions here. Refer reader to appendix.

\subsection{Numerical formulation}
Now let's talk about the electromagnetic wave equation from a computational perspective.

To solve the wave equation on a computer we need to use the Yee grid.

To make things easier we will use weird units.

We also need to take care of boundary conditions.

\subsection{Solving for $H$}
The wave equation from a mathematical perspective.

\BE (\curl \epsilon^{-1} \curl - \mu_0 \omega^2) H = \curl \epsilon^{-1} J \EE

Becomes, with a change of variables.

\BE A(p)x = b(p) \EE

This can be solved directly in 1D and 2D. 
Special methods needed in 3D. 
We just do 1D and 2D.

\subsection{Solving for $\epsilon^{-1}$}
The wave equation from a optimization perspective.

Because scalar multiplication is transitive 
    ($\epsilon^{-1} (\curl H) = (\curl H) \epsilon^{-1}$ and
    $\epsilon^{-1} J = J \epsilon^{-1}$)
\BE \curl (\curl H) \epsilon^{-1} - \curl J \epsilon^{-1}  = \mu_0 \omega^2 H  \EE

which we write as

\BE B(x)p = d(x) \EE

Special constraints... (binary)

\subsection{Insight}
Basically, we see that the electromagnetic wave equation is separably linear in $H$ and $\epsilon^{-1}$

This means that...

### 2012-05-29 presentations/meta_book/wg.tex
Added progress on meta book chapter.

\section{Waveguide coupler design}
Finally, we now implement 
    the full objective-first design strategy
    by doing an alternating directions solve.

\subsection{Choice of design objective}
We choose, for generality,

\BE f(x) = \begin{cases}
        x & \text{at boundary}, \\
        0 & \text{elsewhere}.
        \end{cases} \EE

    where the boundary denotes the two outermost layers of the design space.
This means

\BE f_\text{ideal} = \begin{cases}
        x_\text{perfect} & \text{at boundary}, \\
        0 & \text{elsewhere}.
        \end{cases} \EE

We then do

\BA \minimize{x} \| A(p) x - b(p) \|^2 \\
    \subto f(x) = f_\text{ideal} \EA

\BA \minimize{p} \| B(x) p - d(x) \|^2 \\
    \subto 0 \le p \le 1 \EA

\subsection{Coupling between dielectric waveguide modes}
\myfig{wg/1}{test}
\myfig{wg/2}{test}
\myfig{wg/3}{test}

\subsection{Coupling to plasmonic waveguide modes}
\myfig{wg/4}{test}
\myfig{wg/5}{test}

### 2012-05-31 presentations/meta_book/my_chapter.tex
Getting started on text.

@@
 \newcommand{\myfig}[2]{\begin{figure}[!h]\includegraphics[width=\textwidth]{fig/#1}\caption{#2}\label{#1}\end{figure}}
-
+\newcommand{\BI}{\begin{itemize}\item}
+\renewcommand{\I}{\item}
+\newcommand{\EI}{\end{itemize}}
+\newcommand{\ER}[1]{\eqref{eq:#1}}
 \chapter{Objective-First Nanophotonic Design}
@@
 
-Introductory paragraph.
+In this chapter, we introduce an ``objective-first'' strategy 
+    for designing nanophotonic devices.
+
+General description:
+\BI Only uses desired fields.
+\I  Can attempt to design any linear device.
+\I  Allows for non-physical fields. \EI
+
+This strategy is unique in that it
+    asks the user only for what electromagnetic field
+    the device should produce,
+    and then attempts to generate the design
+    without further user intervention.
 
@@
 \input{ob1}
-\input{1d}
-\input{res}
-\input{wg}
+% \input{1d}
+% \input{res}
+% \input{wg}
 

### 2012-05-31 presentations/meta_book/ob1.tex
Getting started on text.

@@
 \section{The objective-first design problem}
-intro
+We now build off of the field-solver and the structure-solver,
+    as previously outlined,
+    by formulating the design problem
+    and outlining the objective-first strategy.
 
 \subsection{Design objectives}
-Talk about $f(x)$ and that we are interested in convex ones.
+A design objective, $f(x)$, is simply defined as
+    a function we wish to be minimal 
+    for the design to be produced.
+
+For instance, in the design of a device
+    which must transmit efficiently into a particular mode,
+    we could choose $f(x)$ to be the negative power into that mode.
+Or, if the device was to be a low-loss resonator,
+    we could choose $f(x)$ to be the amount of power leaking 
+    out of the device.
 

### 2012-05-31 presentations/meta_book/wave_eq.tex
Getting started on text.

@@
 \section{The electromagnetic wave equation}
+
+We start by understanding the underlying physical equation.
+We extend it beyond its usual use in simulation, 
+    and use it for design.
+
 \subsection{Physics formulation}
-Let's talk about the electromagnetic wave equation from a physics standpoint.
-Let's start from Maxwell's equations without currents.
+First, let's derive our wave equation,
+    starting with the differential form of Maxwell's equations, 
 \BA \curl E = - \mu_0 \frac{\partial H}{\partial t} \\
-    \curl H = J + \epsilon \frac{\partial E}{\partial t} \EA
+    \curl H = J + \epsilon \frac{\partial E}{\partial t}, \EA
+    where $E$, $H$, and $J$ are 
+    the electric, magnetic and electric current % TODO: Check this.
+    vector fields, respectively,
+    $\epsilon$ is the permittivity
+    and $\mu_0$ is the permeability, which we assume to be 
+    that of vacuum everywhere.
 
+For time dependence $\exp(-i \omega t)$, 
+    where $\omega$ is the angular frequency,
+    these become
 \BA \curl E = - i \mu_0 \omega H \\
-    \curl H = J + i \epsilon \omega E \EA
-
-\BE \curl \epsilon^{-1} \curl H - \mu_0 \omega^2 H = \curl \epsilon^{-1} J \EE
-
-Talk about reduced dimensions here. Refer reader to appendix.
+    \curl H = J + i \epsilon \omega E, \label{eq:H2E} \EA
+    which we can combine to form our wave equation,
+\BE \curl \epsilon^{-1} \curl H - \mu_0 \omega^2 H = \curl \epsilon^{-1} J. 
+    \label{eq:wave} \EE
+For further information,
+    as well as simplifications to the wave equation in reduced dimensions,
+    please see the Appendix. % TODO: Use reference.
 
 \subsection{Numerical formulation}
-Now let's talk about the electromagnetic wave equation from a computational perspective.
+Now, on top of the analytical formulation of the wave equation \ER{wave}
+    we will now add a numerical, or discretized, formulation.
+This will be needed in order to solve for arbitrary structures.
 
-To solve the wave equation on a computer we need to use the Yee grid.
+First, we discretize our computational space 
+    according to the Yee grid, % TODO: Reference!
+    which allows us to easily define the curl $(\curl)$
+    operators in \ER{wave} as described in the Appendix. % TODO: ref.
+This allows us, with a change of variables to formulate \ER{wave} as
+\BE A(p)x = b(p), \label{eq:Ab} \EE 
+    where $H \to x$, $\epsilon^{-1} \to p$; 
+    and where
+\BE A(p) = \curl \epsilon^{-1} \curl - \mu_0 \omega^2 \EE 
+    and
+\BE b(p) = \curl \epsilon^{-1} J. \EE
+Note that our use of $A(p)$ and $b(p)$ instead of $A$ and $b$
+    simply serves to clarify the dependence
+    of both $A$ and $b$ to $p$.
 
-To make things easier we will use weird units.
-
-We also need to take care of boundary conditions.
+Additionally,  we use periodic boundary conditions
+    with stretched-coordinate % TODO: ref.
+    perfectly matched layers where necessary for our examples.
 
 \subsection{Solving for $H$}
-The wave equation from a mathematical perspective.
+With our numerical formulation, we can now solve for the $H$-field
+    (the $E$-field can be computed from the $H$-field using \ER{H2E})
+    by using general linear algebra solvers.
+Doing so is also simply known as a time-harmonic or 
+    a finite-difference frequency-domain (FDFD) simulation.
 
-\BE (\curl \epsilon^{-1} \curl - \mu_0 \omega^2) H = \curl \epsilon^{-1} J \EE
-
-Becomes, with a change of variables.
-
-\BE A(p)x = b(p) \EE
-
-This can be solved directly in 1D and 2D. 
-Special methods needed in 3D. 
-We just do 1D and 2D.
+Now, while a full three-dimensional problem
+    is computationally quite taxing;
+    in one- and two-dimensions, 
+    \ER{Ab} is easily solved using the standard sparse solver
+    included in Matlab,
+    and this technique is regularly employed 
+    in the examples which follow.
 
 \subsection{Solving for $\epsilon^{-1}$}
-The wave equation from a optimization perspective.
+The next step,
+    after having built a field-solver or simulator
+    (finds $x$ given $p$) for our wave equation,
+    is to build a structure-solver for it.
+In other words, we need to be able to solve for $p$ given $x$.
 
-Because scalar multiplication is transitive 
-    ($\epsilon^{-1} (\curl H) = (\curl H) \epsilon^{-1}$ and
-    $\epsilon^{-1} J = J \epsilon^{-1}$)
+To do so, we return to \ER{wave}
+    and remark that 
+    $\epsilon^{-1} (\curl H) = (\curl H) \epsilon^{-1}$ and
+    $\epsilon^{-1} J = J \epsilon^{-1}$ 
+    since scalar multiplication is communicative.
+This allows us to rearrange \ER{wave} as
 \BE \curl (\curl H) \epsilon^{-1} - \curl J \epsilon^{-1}  = \mu_0 \omega^2 H  \EE
+which we now write as 
+\BE B(x)p = d(x), \label{eq:Bd} \EE 
+    where
+\BE B(x) = \curl (\curl H) - \curl J\EE
+    and 
+\BE d(x)  = \mu_0 \omega^2 H.  \EE
 
-which we write as
+Solving this system would now seem to allow us
+    to choose an electromagnetic field
+    and then find the structure to produce it;
+    which strongly suggests that it will be useful in
+    the design of nanophotonic devices.
 
-\BE B(x)p = d(x) \EE
+In terms of computational complexity, as with \ER{Ab}, 
+    \ER{Bd} in its current form can be solved using standard tools.
 
-Special constraints... (binary)
+\subsection{Bi-linearity of the wave equation}
+Although additional mathematical machinery must still be added
+    in order to get a useful design tool,
+    we have really shown so far is that the wave equation is 
+    separately linear or \emph{bi-linear} in $x$ and $p$.
+Namely that,
+\BE A(p)x-b(p) = B(x)p - d(x). \EE
+In other words, fixing $p$ makes solving the wave equation for $x$
+    a linear problem, and vice versa.
+Note that the joint problem,
+    where both $x$ and $p$ are allowed to vary,
+    is not linear.
 
-\subsection{Insight}
-Basically, we see that the electromagnetic wave equation is separably linear in $H$ and $\epsilon^{-1}$
-
-This means that...
+The bi-linearity of the wave equation
+    is fundamental in our objective-first strategy
+    which relies on the fact
+    that we already know how to solve linear systems well,
+    and is the reason why we chose $\epsilon^{-1} \to p$
+    instead of the more natual $\epsilon \to p$.
+Indeed, this property forms a natural division of labor
+    in the objective-first scheme, which we outline below.

### 2012-05-31 presentations/meta_book/ob1.tex
More work on book.

@@
     which must transmit efficiently into a particular mode,
-    we could choose $f(x)$ to be the negative power into that mode.
+    we could choose $f(x)$ to be the negative power transmitted into that mode.
 Or, if the device was to be a low-loss resonator,
@@
 
+In general, there are multiple choices of $f(x)$
+    which can be used to describe the same objective.
+For example, $f(x)$ for a transmissive device 
+    may not only be the negative power transmitted into the desired output mode,
+    but it could also be the amount of power lost to other modes,
+    or even the error in the field values at the output port
+    relative to the field values needed for perfect transmission.
+These design objectives are equivalent in the sense that, if minimized, 
+    all would produce structures with good performance.
+At the same time, we must consider that the computational cost and complexity
+    of using one $f(x)$ over another may indeed vary greatly.
+
 \subsection{Convexity}
-Convex optimization quick intro.
+Before formulating the design problem,
+    we would like to inject a note regarding the complexity of various 
+    optimization problems.
+
+Specifically, we want to introduce the notion of \emph{convexity} %TODO: ref.
+    and to simply note the difference between problems that
+    are convex and those which are not.
+The difference is simply this:
+    convex problems have a single optimum point
+    (only one local optimum, which is therefore the global optimum)
+    which we can reliably find using existing numerical software,
+    whereas non-convex problems typically have multiple optima 
+    and are thus much more difficult to reliably solve.
+
+That a convex problem can be reliably solved, in this case, 
+    means that regardless of the starting guess,
+    convex optimization software will 
+    always arrive at the globally optimal solution
+    and will be able to numerically prove global optimality as well.
+Thus, formulating a design problem in terms of convex optimization problems
+    virtually eliminates any ideas of chance or randomness.
+
+For the examples presented in this chapter,
+    we use CVX, a convex optimization software written for Matlab. % Ref.
 
 \subsection{Typical design formulation}
-Typically,
+The typical, and most straightforward formulation
+    of the design problem is
 \BA \minimize{x,p} f(x) \\
-    \subto g(x, p) = 0 \\
-        & p \in {0,1} \EA
+    \subto A(p)x - b(p) = 0, \label{eq:typ:eqcon} \EA
+    which states that we would like to vary $x$ and $p$ simultaneously
+    in order to decrease $f(x)$
+    while always satisfying physics (the electromagnetic wave equation).
+
+Such a formulation, if solved using a steepest-descent method,
+    is the well-known adjoint optimization method. % Ref.
 
 \subsection{Objective-first design formulation}
-Objective-first does 
-\BA \minimize{x,p} \|g(x,p)\|^2 \\
-    \subto f(x) = f_\text{ideal} \\
-        & 0 \le p \le 1 \EA
+In contrast, the objective-first formulation is 
+\BA \minimize{x,p} \| A(p) x - b(p) \|^2 \\
+    \subto f(x) = f_\text{ideal}, \EA
+    where the roles of the wave equation and the design objective are switched.
 

### 2012-05-31 presentations/meta_book/wave_eq.tex
Small commit.

--- 2012-05-29 presentations/meta_book/wave_eq.tex
@@
 \section{The electromagnetic wave equation}
+
 \subsection{Physics formulation}
-Let's talk about the electromagnetic wave equation from a physics standpoint.
-Let's start from Maxwell's equations without currents.
+We will start by reviewing 
+    the fundamental physical equation governing nanophotonics, 
+    the electromagnetic wave equation.
+
+We first derive the wave equation by starting with Maxwell's equations:
+
 \BA \curl E = - \mu_0 \frac{\partial H}{\partial t} \\

### 2012-05-31 presentations/meta_book/ob1.tex
New pictures added.

@@
     while always satisfying physics (the electromagnetic wave equation).
-
 Such a formulation, if solved using a steepest-descent method,
@@
 \subsection{Objective-first design formulation}
-In contrast, the objective-first formulation is 
-\BA \minimize{x,p} \| A(p) x - b(p) \|^2 \\
-    \subto f(x) = f_\text{ideal}, \EA
-    where the roles of the wave equation and the design objective are switched.
+In contrast, the objective-first formulation switches
+    the roles of the wave equation and the design objective
+    with one another,
+\BA \minimize{x,p} \| A(p) x - b(p) \|^2 \label{eq:ob1:1} \\
+    \subto f(x) = f_\text{ideal}. \label{eq:ob1:2} \EA
 
-This is a bi-convex problem, which we solve using an alternating directions method.
+This first means that, as seen from \ER{ob1:1},
+    we allow for non-zero residual in the electromagnetic wave equation.
+This literally means that we allow for \emph{non-physical} $x$ and $p$,
+    since $A(p) x - b(p) \ne 0$ is now allowed.
+For this reason, we denote $A(p) x - b(p)$ the \emph{physics residual}.
+
+Secondly, we see from \ER{ob1:2} that we always force the device
+    to exhibit ideal performance,
+    even if doing so means breaking the laws of physics.
+As such, our strategy will be to vary $x$ and $p$
+    in order to decrease the physics residual \ER{ob1:1} to zero,
+    while always maintaining ideal performance.
+
+Our initial motivation for doing this 
+    was that it allowed us to solve for $x$ and $p$ separately,
+    as will be outlined below,
+    and that always forcing ideal performance
+    might provide a mechanism to ``override'' local optima 
+    in the optimization process.
+
+To this end we have found that such a strategy
+    actually allows us to design very unintuitive devices
+    which exhibit very good performance,
+    even when starting from completely non-functional initial guesses.
+Furthermore, we have found this to be true
+    even true when the physics residual is never brought to exactly zero.
+
+From a numerical standpoint, 
+    although the objective-first formulation is still non-convex 
+    in its original form,
+    the bi-linearity of the physics residual term allows us to 
+    naturally break the original problem into two sub-problems
+    which we outline below.
+
+Lastly, we add an additional constraint to the original formulation,
+    which is to set hard-limits on the allowable values of $p$,
+    namely $p_0 \le p \le p_1$.
+This is actually a relaxation of the ideal constraint,
+    which would be to allow $p$ to only have discrete values,
+    $p \in p_0, p_1$,
+    but such a constraint would be essentially force us to only
+    be able to perform brute force trial-and-error.
+
+Our objective-first formulation is thus,
+\BA \minimize{x,p} \| A(p) x - b(p) \|^2 \notag \\
+    \subto f(x) = f_\text{ideal} \label{eq:ob1} \\
+        & p_0 \le p \le p_1. \notag \EA
 
 \subsection{Field sub-problem}
-\BA \minimize{x} \| A(p) x - b(p) \|^2 \\
-    \subto f(x) = f_\text{ideal} \EA
+Since the objective-first problem in its original form is still non-convex,
+    we break it down into two convex sub-problems.
+The first of these is the field sub-problem, 
+    which simply involves fixing $p$ and independently optimizing $x$,
+\BA \minimize{x} \| A(p) x - b(p) \|^2 \label{eq:Fsub} \\
+    \subto f(x) = f_\text{ideal}. \notag \EA
+This problem is convex, and actually quadratic,
+    which means that it can even be solved in the same way 
+    as a simple least-squares problem.
 
 \subsection{Structure sub-problem}
-\BA \minimize{p} \| B(x) p - d(x) \|^2 \\
-    \subto 0 \le p \le 1 \EA
+The second sub-problem is formulated by fixing $x$ and
+    independently optimizing $p$.
+At the same time, we use the bi-linearity property
+    of the physics residual from \ER{bilinear}
+    to rewrite the problem in a way that makes
+    its convexity explicit,
+\BA \minimize{p} \| B(x) p - d(x) \|^2 \label{eq:Ssub} \\
+    \subto p_0 \le p \le p_1. \notag \EA
+
+The structure sub-problem is also convex, but not quadratic.
+However, use of the CVX package still allows us to obtain the result
+    quickly and reliably.
+
+\subsection{Alternating directions algorithm}
+We use a simple alternating directions scheme 
+    to peice together \ER{Fsub} and \ER{Ssub},
+    which is to say that we simply
+    alternately solve each and continue until we reach some stopping point,
+    normally measured by how much the physics residual has decreased.
+
+The advantage of such the alternating directions method
+    is that the physics residual is guaranteed to
+    monotonically decrease with every iteration,
+    which is useful in that no safeguards
+    are needed to guard against ``rogue'' steps
+    in the optimization procedure.
+Note that this robustness stems from the fact that,
+    among other things,
+    each sub-problem does not rely on previous values of 
+    the variable which is being optimized,
+    but only on the variable which is held constant.
+
+The disadvantage of such a simple scheme is that 
+    the convergence is quite slow,
+    although we have found it to be sufficient in our cases.
+See ref % cite!
+    for related methods that exhibit far better convergence.

### 2012-05-31 presentations/meta_book/wave_eq.tex
New pictures added.

--- 2012-05-31 presentations/meta_book/wave_eq.tex
@@
 \section{The electromagnetic wave equation}
-
-We start by understanding the underlying physical equation.
-We extend it beyond its usual use in simulation, 
-    and use it for design.
 
@@
 Namely that,
-\BE A(p)x-b(p) = B(x)p - d(x). \EE
+\BE A(p)x-b(p) = B(x)p - d(x). \label{eq:bilinear} \EE
 In other words, fixing $p$ makes solving the wave equation for $x$

### 2012-06-04 presentations/meta_book/cloak.tex
Pushing on book chapter.

\section{Optical cloak design}
In the previous section,
    we showed that couplers between virtually any two waveguide modes
    could be constructed using the objective-first design method,
    and based on the generality of the method
    one can guess that it may also be
    able to generate designs for any linear nanophotonic device.

Now, we extend the applicability of our method
    to the design of metamaterial devices which operate in free-space.
In particular,
    we adapt the waveguide coupler algorithm to the 
    to the design of optical cloaks.

\subsection{Application of the objective-first strategy}
Adapting the method used in \sR{wg} to the design of optical cloaks
    really only requires one to change the simulation environment
    to allow for free-space modes.
This is accomplished by modifying the upper and lower boundaries
    of the simulation domain from absorbing boundary conditions
    to periodic boundary conditions,
    which allows for plane-wave modes to propagate without loss
    until reaching the left or right boundaries,
    where absorbing boundary conditions are still maintained.

In terms of the design objective, 
    we allow the device to span the entire height of the simulation domain,
    and thus consider only the leftmost and rightmost planes as boundary values.

An additional modification, as compared to \sR{wg}, is that
    we now disallow the structure to be modified in certain areas
    which, naturally, contain the object to be cloaked.

With these simple changes we continue to solve \ER{ob1}
    with the alternating directions method
    in order to now design optical cloaks
    instead of waveguide couplers.
Once again, as in \sR{wg}, each design is run for 400 iterations
    with a uniform initial value of $p = 1/9$ for the structure
    (where the structure is allowed to vary).

Lastly,

\myfig{cloak/c6}{test}
\myfig{cloak/c1}{test}
\myfig{cloak/c2}{test}
\myfig{cloak/c3}{test}
\myfig{cloak/c4}{test}
\myfig{cloak/c5}{test}
\myfig{cloak/c7}{test}

### 2012-06-04 presentations/meta_book/mimic.tex
Pushing on book chapter.

\section{Optical mimic design}
\myfig{mimic/m1}{test}
\myfig{mimic/m2}{test}
\myfig{mimic/m3}{test}
\myfig{mimic/m4}{test}
\myfig{mimic/m5}{test}
\myfig{mimic/m6}{test}

### 2012-06-04 presentations/meta_book/ob1.tex
Pushing on book chapter.

@@
 
-\subsection{Design objectives}
+\subsection{Design objectives} \label{sec:desobj}
 A design objective, $f(x)$, is simply defined as
@@
 
-\subsection{Alternating directions algorithm}
+\subsection{Alternating directions}
 We use a simple alternating directions scheme 

### 2012-06-04 presentations/meta_book/wg.tex
Pushing on book chapter.

@@
-\section{Waveguide coupler design}
-Finally, we now implement 
-    the full objective-first design strategy
-    by doing an alternating directions solve.
+\section{Waveguide coupler design}\label{sec:wg}
+We first apply the objective-first formulation
+    with the alternating directions algorithm
+    to the design of nanophotonic waveguide couplers
+    in two dimensions,
+    where our goal is to couple light from
+    a single input waveguide mode
+    to a single output waveguide mode
+    with as close to unity efficiency as possible.
+We would also like to allow the user to choose arbitrary
+    input and output waveguides,
+    as well as to select 
+    arbitrary modes within those waveguides
+    (as opposed to allowing only the fundamental mode, for example).
+
+This problem is very general and, in essence,
+    encompasses the design of all linear nanophotonic components,
+    because the function or performance of all such components
+    is simply to convert a defined set of input modes
+    into a defined set of output modes.
+Such a broad, general problem is ideally suited for 
+    an objective-first strategy,
+    since no approximations or simplifications
+    of the electromagnetic fields are required;
+    we only make the simplification of working in two dimensions
+    and dealing only with a single input and output mode.
+
+Say something about TE mode in 2D.
 
 \subsection{Choice of design objective}
-We choose, for generality,
-
+As mentioned in \sR{desobj} multiple equivalent choices
+    of design objective exist which should allow one
+    to achieve the same device performance;
+    however, we will choose, for generality, the following design objective,
 \BE f(x) = \begin{cases}
         x & \text{at boundary}, \\
-        0 & \text{elsewhere}.
+        0 & \text{elsewhere},
         \end{cases} \EE
+That is, $f(x)$ simply selects the outermost values of the field
+    in the design space.
 
-    where the boundary denotes the two outermost layers of the design space.
-This means
-
+When placed into the objective-first problem \ER{ob1},
+    this will result in fixing the boundary values of the field
+    at the edge of the design space
+    to those of an ideal device,
+    as shown in \fR{wg/intro}.
+In this case, we choose such an ideal device
+    to have perfect (unity) coupling efficiency,
 \BE f_\text{ideal} = \begin{cases}
@@
         \end{cases} \EE
+These ideal fields are simply obtained by using
+    the input and output mode profiles at the corresponding ports
+    and using values of zero at the remaining ports.
 
-We then do
+\myfig{wg/intro}{Formulation of the design objective.}
 
+Such a design objective is general
+    in the sense that the boundary values of the device 
+    contain all the information necessary to determine
+    how the device will interact with its environment,
+    when excited with the input mode in question.
+In other words,
+    we only need to know the boundary field values,
+    and not the interior field values to determine 
+    the performance of the device;
+    and thus, it would be conceivable that such a scheme
+    might be generally applied to linear nanophotonic devices beyond 
+    just waveguide mode couplers.
+
+In our case,
+    we only need to know the value of $H_z$ and 
+    its derivative along the normal direction, $\partial H_z / \partial n$,
+    along the design boundary
+    in order to completely characterize its performance.
+Alternatively,
+    one can, of course, use the outermost two layers of the $H_z$
+    instead of calculating a spatial derivative.
+
+\subsection{Application of the objective-first strategy}
+Having chosen our design objective we apply
+    alternating directions to \ER{ob1} which 
+    results in solving the following two sub-problems iteratively.
 \BA \minimize{x} \| A(p) x - b(p) \|^2 \\
-    \subto f(x) = f_\text{ideal} \EA
+    \subto x = x_\text{perfect} \text{, at boundary} \notag \EA
+\BA \minimize{p} \| B(x) p - d(x) \|^2 \\
+    \subto p_0 \le p \le p_1 \notag \EA
 
-\BA \minimize{p} \| B(x) p - d(x) \|^2 \\
-    \subto 0 \le p \le 1 \EA
+For the results throughout this chapter, 
+    we uniformily choose $p_0 = 1/12.25$ and $p_0 = 1$,
+    corresponding to $\epsilon^{-1}$ of silicon and air respectively.
+Additionally, since a starting value for $p$ is initially required,
+    we always choose to use a uniform value of $p = 1/9$ 
+    across the entire design space.
+There is nothing really unique about such a choice,
+    although we have noticed that initial value of $p$ near 1 
+    often result in poor designs.
+Note, that, unlike $p$, we do not require an initial guess for $x$.
 
-\subsection{Coupling between dielectric waveguide modes}
-\myfig{wg/1}{test}
-\myfig{wg/2}{test}
-\myfig{wg/3}{test}
+The only other significant value that needs to be set initially
+    is the frequency, or wavelength of light.
+We use wavelengths in the range of 25 to 42 grid points for
+    the results in this chapter.
 
-\subsection{Coupling to plasmonic waveguide modes}
-\myfig{wg/4}{test}
-\myfig{wg/5}{test}
+Lastly, for all the examples presented in the chapter,
+    we run the alternating directions algorithm for 400 iterations.
+Although we do not present the convergence results here,
+    such information can be obtained by inspecting the source. %Ref!
+
+Also, small footprint and computation time need to be mentioned.
+\subsection{Coupling to a wide, low-index waveguide}
+As a first example, we design a coupler from 
+    the fundamental mode of a narrow, high-index waveguide
+    to the fundamental mode of a wide, low-index waveguide.
+Such a coupler would be useful for coupling from 
+    an on-chip nanophotonic waveguide to
+    an off-chip fiber for example.
+
+\myfig{wg/1}{Coupler to a wide low-index waveguide.
+            Efficiency: 99.8\%, 
+            footprint: $36 \times 76$ grid points, 
+            wavelength: 42 grid points.}
+
+The input and output mode profiles used as
+    the ideal fields are shown in the upper-left corner of \fR{wg/1}.
+The final structure is shown in the upper right plot, and
+    the simulated $H_z$ fields,
+    under excitation of the input mode,
+    are shown in the bottom plots.
+
+\FR{wg/1} then shows that the design structure has nearly unity efficiency
+    and converts between the input and output modes
+    within a very small footprint.
+
+\subsection{Mode converter}
+In addition to coupling to a low-index waveguide,
+    we show that we can successfully apply the objective-first method
+    to convert between modes of a waveguide.
+We do this by simply selecting the output mode 
+    in the design objective to be the second-order waveguide mode,
+    as seen in \fR{wg/2}.
+\myfig{wg/2}{Mode converter.
+            Efficiency: 98.0\%, 
+            footprint: $36 \times 76$ grid points, 
+            wavelength: 42 grid points.}
+
+Note that the design of this coupler is made challenging
+    because of the opposite symmetries of the input and output modes.
+Moreover, because our initial structure is symmetric,
+    we initially have exactly 0\% efficiency to begin with.
+Fortunately, the objective-first method can still design
+    an efficient coupler in this case as well.
+
+\subsection{Coupling to an air-core waveguide mode}
+We can then continue to elucidate the generality of our method
+    by coupling between waveguides which confine light 
+    in completely different ways.
+\myfig{wg/3}{Coupler to a wide low-index waveguide.
+            Efficiency: 98.9\%, 
+            footprint: $36 \times 76$ grid points, 
+            wavelength: 25 grid points.}
+
+\FR{wg/3} shows  a high-efficiency coupling device between 
+    an index-guided input waveguide and
+    a ``air-core'' output waveguide, 
+    in which the waveguiding effect is achieved using distributed Bragg reflection.
+
+\subsection{Coupling to a metal-insulator-metal waveguide }
+Additionally, our design method can also generate couplers
+    between different material systems such as 
+    between dielectric and metallic (plasmonic) waveguides,
+    as shown in \fR{wg/4}.
+\myfig{wg/4}{Coupler to a wide low-index waveguide.
+            Efficiency: 97.5\%, 
+            footprint: $36 \times 76$ grid points, 
+            wavelength: 25 grid points.}
+
+In this case, the permittivity of the metal ($\epsilon = -2$) is chosen to be 
+    near the plasmonic resonance ($\epsilon = -1$).
+
+\subsection{Coupling to a metal wire plasmonic waveguide mode}
+\myfig{wg/5}{Coupler to a wide low-index waveguide.
+            Efficiency: 99.1\%, 
+            footprint: $36 \times 76$ grid points, 
+            wavelength: 25 grid points.}
+Lastly, \fR{wg/5} shows that efficiently coupling to a plasmonic wire
+    is achievable as well.

### 2012-06-04 presentations/meta_book/cloak.tex
Cloak section draft finished.

@@
     and thus consider only the leftmost and rightmost planes as boundary values.
+Specifically, for this section the input and output modes are plane waves
+    with normal incidence, 
+    as can be expected for good cloaking devices.
+The achieved results all yield high efficiency,
+    although we note that the cloaking effect is only measured
+    for a specific input mode.
+That is to say, just as the waveguide couplers previously designed
+    were single-mode devices,
+    so the cloaks designed in this section are also ``single-mode'' cloaks.
 
@@
     with a uniform initial value of $p = 1/9$ for the structure
-    (where the structure is allowed to vary).
+    (where the structure is allowed to vary),
+    and the range of $p$ is limited to $1/12.25 \le p \le 1$.
 
-Lastly,
+\subsection{Anti-reflection coating}
+As a first example,
+    we attempt to design the simplest and most elementary ``cloaking'' device available,
+    which, we argue, is a simple anti-reflection coating;
+    in which case the object to be cloaked is nothing more than
+    the interface between two dielectric materials.
+In this case we use the interface between air and silicon, as shown in \fR{cloak/c1}
+\myfig{cloak/c1}{Anti-reflection coating.
+                Efficiency: 99.99\%,
+                footprint: $60 \times 100$ grid points,
+                wavelength: 63 grid points.}
 
-\myfig{cloak/c6}{test}
-\myfig{cloak/c1}{test}
-\myfig{cloak/c2}{test}
-\myfig{cloak/c3}{test}
-\myfig{cloak/c4}{test}
-\myfig{cloak/c5}{test}
-\myfig{cloak/c7}{test}
+Unsurprisingly for such a simple case, 
+    we achieve a very high efficiency device.
+Note also that the efficiency of the device can be deduced by eye,
+    based on the absence of reflections or standing waves 
+    in bottom two plots of \fR{cloak/c1}.
+
+\subsection{Wrap-around cloak}
+Next, we design a cloak for a plasmonic cylinder,
+    which is quite effective at scattering light
+    as can be seen from \fR{cloak/c6}.
+\myfig{cloak/c6}{Plasmonic cylinder to be cloaked. 
+                68.5\% of light is diverted away from the desired output mode.}
+
+In designing the wrap-around cloak,
+    we allow the structure to vary at all points within the design area
+    except in the immediate vicinity of the plasmonic cylinder.
+Application of the objective-first strategy results
+    in an efficient device as seen in \fR{cloak/c2}.
+\myfig{cloak/c2}{Wrap-around cloak.
+                Efficiency: 99.99\%,
+                footprint: $60 \times 100$ grid points,
+                wavelength: 42 grid points.}
+
+Note that our cloak employs only isotropic, non-magnetic materials,
+    and at the same time it is specific to a particular input
+    and to a particular object.
+
+\subsection{Open-channel cloak}
+With a simple modification, from the previous section,
+    we can design a cloak which features an open channel
+    to the exterior electromagnetic environment.
+This simple modification is forcing an air tunnel
+    to be opened which connects the cylinder to the outside world
+    both toward its front and back.
+\myfig{cloak/c4}{Open-channel cloak.
+                Efficiency: 99.8\%,
+                footprint: $60 \times 100$ grid points,
+                wavelength: 42 grid points.}
+
+Such a design is still very efficient
+    and exhibits the usefulness of the objective-first strategy
+    in cases where other methods, such as transformation optics,
+    may not be able to be applied.
+
+\subsection{Channeling cloak}
+Our last cloaking example replaces the plasmonic cylinder 
+    with a thin metallic wall in which is etched a sub-wavelength channel.
+Such a metallic wall is very effective at blocking incoming light
+    (as can be seen from \fR{cloak/c7}) 
+    because of its large negative permittivity ($\epsilon = -20$),
+    meaning that any cloaking device would be forced to channel
+    all the input light into a very small aperture
+    and then to flatten that light out into a plane wave again.
+\myfig{cloak/c7}{Metallic wall with sub-wavelength channel to be cloaked.
+                99.9\% of the light is blocked from the desired output plane-wave.}
+
+Once again, our method is still able to produce a very efficient design,
+    as shown in \fR{cloak/c5}.
+\myfig{cloak/c5}{Channeling cloak.
+                Efficiency: 99.9\%,
+                footprint: $60 \times 100$ grid points,
+                wavelength: 42 grid points.}

### 2012-06-04 presentations/meta_book/mimic.tex
Started on mimics.

@@
 \section{Optical mimic design}
-\myfig{mimic/m1}{test}
-\myfig{mimic/m2}{test}
-\myfig{mimic/m3}{test}
-\myfig{mimic/m4}{test}
-\myfig{mimic/m5}{test}
-\myfig{mimic/m6}{test}
+We now apply our objective-first strategy to the design of optical mimics.
+
+We define an optical mimic to be a linear nanophotonic device which 
+    mimics the output field of another device.
+In this sense optical mimics are the anti-cloak;
+    whereas cloaks strive to make an object's electromagnetic presence vanish,
+    mimics strive to implement an object's presence without that 
+    object actually being there.
+
+As such, the design of optical mimics provides a tantalyzing approach
+    to the realization of practical metamaterial devices.
+That is to say, if one can reliably produce practical optical mimics,
+    then producing metamaterials (which are often based on fictitious materials)
+    can be accomplished by simply producing an optical mimic of that material.
+
+In a more general sense, 
+    optical mimics is really just a recasting of the thrust of 
+    the objective-first design strategy in its purest form:
+    the design of a nanophotonic device based purely 
+    on the electromagnetic fields one wishes to have it produce.
+As such, devices which perform well-known optical functions
+    (e.g. focusing, lithography) can also be designed.
+
+\subsection{Application of the objective-first strategy}
+The objective-first design of optical mimics proceeds in virtually
+    an identical way to the design of optical cloaks,
+    the only difference being that the output modes are 
+    specifically chosen to be those which produce the desired function.
+For most of the examples provided, the input illumination is still an incident plane wave.
+
+Lastly, instead of measuring efficiency, 
+    we measure the relative error of the simulated field
+    against that of a perfect target field
+    at a relevant plane of some distance away from the device.
+The location of this plane is identified as a dotted line in the subsequent figures.
+
+\subsection{Plasmonic cylinder mimic}
+Our first mimic is simply to mimic the plasmonic cylinder 
+    which we cloaked in the previous section.
+\myfig{mimic/m1}{Plasmonic cylinder mimic. 
+                Error: 8.1\%,
+                footprint: $40 \times 120$ grid points,
+                wavelength: 42 grid points.}
+
+\subsection{Diffraction-limited lens mimic}
+\myfig{mimic/m3}{Full-width-half-max at focus: 1.5 $\lambda$,
+                focus depth: 100 grid points.
+                Error: 12.0\%,
+                footprint: $40 \times 120$ grid points,
+                wavelength: 25 grid points.}
+\myfig{mimic/m4}{Full-width-half-max at focus: 0.5 $\lambda$,
+                focus depth: 50 grid points.
+                Error: 5.6\%,
+                footprint: $40 \times 120$ grid points,
+                wavelength: 25 grid points.}
+\myfig{mimic/m5}{Full-width-half-max at focus: 0.5 $\lambda$,
+                focus depth: 150 grid points.
+                Error: 1.4\%,
+                footprint: $40 \times 120$ grid points,
+                wavelength: 25 grid points.}
+
+\subsection{Sub-diffraction lithographic mask}
+\myfig{mimic/m6}{Error: 19.8\%}
+
+\subsection{Perfect lens mimic}
+\myfig{mimic/m2}{Perfect lens mimic.
+                Error: 28.6\%}

### 2012-06-04 presentations/meta_book/mimic.tex
Draft 1 of meta book chapter done.

@@
 
+\FR{mimic/m1} shows the result of the design.
+The final structure is shown in the upper right plot,
+    while the ideal field and the simulated field
+    are shown in the middle and bottom plots.
+Note that the ideal field is cut off to emphasize 
+    the fields to the right of the device (the output fields).
+Also, the magnitude of the fields are compared at the 
+    dotted black line at which point the relative error
+    is also calculated.
+For this simple, initial mimic, the simulated field is
+    quite closely imitates that produced by a single plasmonic cylinder.
+
 \subsection{Diffraction-limited lens mimic}
+We now design a mimic for a typical diffraction-limited lens.
+In this case, the object which we wish to mimic does not require simulation
+    since the fields of a lens can be readily computed.
+For the three figures below, 
+    the computed ideal fields are shown as the target fields.
+
+\FR{mimic/m3} shows the mimic of a lens with a moderate focus spot. 
+In such a lens, the focusing action is gradual and easily discernable
+    by eye.
+
 \myfig{mimic/m3}{Full-width-half-max at focus: 1.5 $\lambda$,
@@
                 wavelength: 25 grid points.}
+
+In constrast, \fR{mimic/m4} and \fR{mimic/m5} are both mimics of
+    a lens with a smaller half-wavelength spot size.
+Such a lens is much harder to design, 
+    because of the high-frequency spatial components involved;
+    and yet, we show that an objective-first strategy can 
+    produce successful designs with both smaller and larger focus depths.
 \myfig{mimic/m4}{Full-width-half-max at focus: 0.5 $\lambda$,
@@
                 wavelength: 25 grid points.}
+\clearpage
 
-\subsection{Sub-diffraction lithographic mask}
-\myfig{mimic/m6}{Error: 19.8\%}
+\subsection{Sub-diffraction lens mimic}
+Our method is now employed to mimic the effect of a sub-diffraction lens.
+Since such a lens can be created using a negative-index material
+    this mimic can be viewed as an imitation of a negative-index material,
+    in that the following device recreates the sub-diffraction target-field 
+    at the output plane (dotted line)
+    when illuminated by the same target field at the input of the device.
+In other words,
+    this device is an image-specific sub-diffraction imager,
+    which is another way of saying that it is a single-mode imager.
+\myfig{mimic/m2}{Sub-diffraction lens mimic.
+                The target field has a full-width half-maximum of 0.14 $\lambda$.
+                Error: 28.6\%,
+                footprint: $60 \times 120$ grid points,
+                wavelength: 42 grid points.}
 
-\subsection{Perfect lens mimic}
-\myfig{mimic/m2}{Perfect lens mimic.
-                Error: 28.6\%}
+As \fR{mimic/m2} shows,
+   we are able to recreate the target field at the output.
+Note that the target field is created simply by placing 
+    the imaging field at the output plane.
+Also note that, as expected, 
+    the output field decays very quickly since,
+    for such a deeply subwavelength field,
+    it is composed primarily of evanescently decaying modes.
+
+\subsection{Sub-diffraction optical mask}
+Lastly, we extend the idea of a sub-diffraction lens mimic
+    one step further and
+    design a sub-diffraction optical mask.
+Such a device takes a plane wave as its input and
+    produces a sub-diffraction image at its output plane.
+Of course, akin to its lens counterpart,
+    this output plane must lie within the near-field of the device
+    because of its sub-wavelength nature.
+\myfig{mimic/m6}{Sub-diffraction optical mask.
+                The three central peaks in the target field are each
+                separated by 0.28 $\lambda$.
+                Error: 19.8\%,
+                footprint: $40 \times 120$ grid points,
+                wavelength: 25 grid points.}
+
+\FR{mimic/m6} shows the design of a simple mask which 
+    successfully produces three peaks at its output.

### 2012-06-13 presentations/meta_book/my_chapter.tex
Small commit.
Included pictures.
Added lo-fi jpgs.
Pushing on book chapter.
Draft 1 of meta book chapter done.
Updated book.

--- 2012-05-29 presentations/meta_book/my_chapter.tex
@@
 \newcommand{\subto}{\text{subject to}\;&}
-\newcommand{\myfig}[2]{\begin{figure}[!h]\includegraphics[width=\textwidth]{fig/#1}\caption{#2}\label{#1}\end{figure}}
 
+% Custom figures.
+\newcommand{\myfig}[2]{\begin{figure}[!h]\includegraphics[width=0.95\textwidth]{fig/#1.jpg}\caption{#2}\label{fig:#1}\end{figure}}
+
+\newcommand{\BI}{\begin{itemize}\item}
+\renewcommand{\I}{\item}
+\newcommand{\EI}{\end{itemize}}
+
+\newcommand{\ER}[1]{\eqref{eq:#1}}
+\newcommand{\SR}[1]{Section~\ref{sec:#1}}
+\newcommand{\sR}[1]{section~\ref{sec:#1}}
+\newcommand{\FR}[1]{Figure~\ref{fig:#1}}
+\newcommand{\fR}[1]{figure~\ref{fig:#1}}
 \chapter{Objective-First Nanophotonic Design}
@@
 
-\abstract{The abstract for the book.}
+\abstract{We introduce an ``objective-first'' strategy 
+    for designing nanophotonic devices,
+    and we demonstrate the design of nanophotonic
+    coupler, cloak, and mimic devices.}
 
-Introductory paragraph.
+Our initial foray into design methods for nanophotonic devices
+    began with a very simple and naive question: that is,
+    if, when presented with a nanophotonic structure,
+    we can solve for the electromagnetic fields it produces;
+    then, why don't we just make an inverse solver which,
+    when given the electromagnetic fields we desire,
+    returns the nanophotonic structure that will produce them? %ref.
+In other words, since we already know how to solve for $E$ and $H$ 
+    in Maxwell's equations, why can't we solve for $\epsilon$
+    or even $\mu$ instead?
+
+Not surprisingly, it did not take us long to find that such
+    a simple strategy would inevitably run into many problems.
+
+Over the subsequent years, we were able to come up with a better solution,
+    which we call an ``objective-first'' strategy for nanophotonic design,
+    and which we present in this chapter.
+Although it is much more advanced than our original idea,
+    objective-first design still carries the same fundamental concept;
+    which is to specify the electromagnetic fields, and then
+    to solve for a structure to produce them.
+
+In this chapter, we present the simple theoretical underpinnings of 
+    objective-first design in the first two sections,
+    and then show examples of the method in action in the rest of the chapter.
+We also include the source code that was used to generate
+    all results presented herein. %ref!
 
@@
 \input{ob1}
-\input{1d}
-\input{res}
 \input{wg}
-
-\section{Metamaterials design}
-\subsection{Modification of the design objective}
-\subsection{Cloak devices}
-\subsection{Mimic devices}
+\input{cloak}
+\input{mimic}
 
 \section{Extending the method}
+The objective-first method, as applied in the examples in this chapter,
+    really only represent a small foray into the area of nanophotonic design.
+Several key extensions to what is presented here are needed to
+    fully address real-world nanophotonic design challenges.
+
 \subsection{3D}
+The first of these is the need to design fully three-dimensional structures.
+Doing so provides no inherent difficulties aside from the matrices in
+    \ER{Ab} becoming very large.
+This is not insurmountable as electromagnetic simulation software for 
+    three-dimensional nanophotonic structures already exists.
+
+Also software to solve \ER{Bd} in three-dimensions does not exist,
+    the size of matrix $B(x)$ can be greatly compressed by considering
+    only fabrication processes which modify a structure in-plane.
+Thus, the degrees of freedom in $p$ can be greatly reduced and the original
+    methods used in this chapter can still be applied.
+
 \subsection{Multi-mode}
+A second necessary extension is to be able to consider the multiple fields
+    that a structure produces.
+This includes fields of different frequencies and inputs.
+
 \subsection{Robustness}
-
-\section{Appendix}
-\subsection{Full 3D curl}
-\subsection{1D}
-\subsection{2D}
-\subsection{2.5D}
+\subsection{Binary structure}

### 2012-06-13 presentations/meta_book/ob1.tex
Updated book.

@@
 \section{The objective-first design problem}
-We now build off of the field-solver and the structure-solver,
-    as previously outlined,
-    by formulating the design problem
-    and outlining the objective-first strategy.
+We now describe the remaining machinery used in the objective-first method,
+    in addition to the field-solver and the structure-solver,
+    as previously outlined.
+Specifically, we introduce the idea of a design objective and a physics residual,
+    and we reference the mathematical notion of convexity
+    in order to motivate the need to divide the 
+    objective-first problem into two separately convex sub-problems.
 
@@
     and will be able to numerically prove global optimality as well.
-Thus, formulating a design problem in terms of convex optimization problems
-    virtually eliminates any ideas of chance or randomness.
+Thus, the advantage in formulating a design problem 
+    in terms of convex optimization problems
+    is to eliminate both the need to circumvent local optima and 
+    any notion of randomness.
 
-For the examples presented in this chapter,
-    we use CVX, a convex optimization software written for Matlab. % Ref.
+On a practical level, there exist mature convex optimization software packages
+    among which is CVX, a convex optimization package written for Matlab, % Ref.
+    which we use for the examples in this chapter.
 
 \subsection{Typical design formulation}
-The typical, and most straightforward formulation
-    of the design problem is
-\BA \minimize{x,p} f(x) \\
-    \subto A(p)x - b(p) = 0, \label{eq:typ:eqcon} \EA
+We now examine the typical, and most straightforward formulation
+    of the design problem,
+    in order to relate and contrast it to the objective-first formulation.
+The design problem for a physical structure is typically formulated as
+\BA \minimize{x,p} f(x) \label{eq:typform} \\
+    \subto A(p)x - b(p) = 0, \notag \EA
     which states that we would like to vary $x$ and $p$ simultaneously
     in order to decrease $f(x)$
-    while always satisfying physics (the electromagnetic wave equation).
-Such a formulation, if solved using a steepest-descent method,
-    is the well-known adjoint optimization method. % Ref.
+    while always satisfying physics (e.g. the electromagnetic wave equation).
+
+Since solving \ER{typform} is quite difficult in the general sense
+    (simultaneously varying $x$ and $p$ makes the problem non-convex)
+    traditional approaches have relied on either brute-force parameter search,
+    or a gradient-descent method utilizing first-order derivatives.
+In the gradient-descent case, solving \ER{typform} results in the
+    well-known adjoint optimization method. % Ref.
 
 \subsection{Objective-first design formulation}
-In contrast, the objective-first formulation switches
-    the roles of the wave equation and the design objective
-    with one another,
+In contrast with the typical formulation, the objective-first formulation 
+    simply switches the roles of 
+    the wave equation and the design objective with one another,
 \BA \minimize{x,p} \| A(p) x - b(p) \|^2 \label{eq:ob1:1} \\
     \subto f(x) = f_\text{ideal}. \label{eq:ob1:2} \EA
+Although such a switch may seem trivial,
+    and even silly at first,
+    we show that it fundamentally changes the nature of the design problem
+    and actually gains us advantages in our efforts at finding a solution.
 
-This first means that, as seen from \ER{ob1:1},
-    we allow for non-zero residual in the electromagnetic wave equation.
+This first fundamental change, as seen from \ER{ob1:1},
+    is that we allow for non-zero residual in the electromagnetic wave equation.
 This literally means that we allow for \emph{non-physical} $x$ and $p$,
-    since $A(p) x - b(p) \ne 0$ is now allowed.
-For this reason, we denote $A(p) x - b(p)$ the \emph{physics residual}.
-
-Secondly, we see from \ER{ob1:2} that we always force the device
-    to exhibit ideal performance,
-    even if doing so means breaking the laws of physics.
+    since $A(p) x - b(p) \ne 0$ is permissible.
+And since $A(p) x - b(p)$ can now be a non-zero entity, 
+    we choose to call it the \emph{physics residual}.  
+The second fundamental change
+    is that we always force the device to exhibit ideal performance,
+    as seen from \ER{ob1:2}.
+This, of course, ties in very closely with \ER{ob1:1} since
+    ideal performance is usually not obtainable unless one
+    allows for some measure of error in the underlying physics
+    (non-zero physics residual).
 As such, our strategy will be to vary $x$ and $p$
@@
 
-Our initial motivation for doing this 
-    was that it allowed us to solve for $x$ and $p$ separately,
-    as will be outlined below,
-    and that always forcing ideal performance
-    might provide a mechanism to ``override'' local optima 
+The primary advantage in the objective-first formulation is that,
+    although the full problem is still non-convex,
+    it allows us to form two convex sub-problems, as we outline below.
+In contrast to an adjoint method approach,
+    in so doing we can still access information regarding
+    second-order derivatives, which greatly speeds up finding a solution.
+An additional advantage is that our insistence
+    that ideal performance be always attained
+    provides a mechanism
+    which can potentially ``override'' local optima 
     in the optimization process.
@@
 
-From a numerical standpoint, 
-    although the objective-first formulation is still non-convex 
-    in its original form,
-    the bi-linearity of the physics residual term allows us to 
-    naturally break the original problem into two sub-problems
-    which we outline below.
+% From a numerical standpoint, 
+%     although the objective-first formulation is still non-convex 
+%     in its original form,
+%     the bi-linearity of the physics residual term allows us to 
+%     naturally break the original problem into two sub-problems
+%     which we outline below.
 
-Lastly, we add an additional constraint to the original formulation,
+In practice, we add an additional constraint to the original formulation,
     which is to set hard-limits on the allowable values of $p$,
@@
     \subto f(x) = f_\text{ideal} \label{eq:ob1} \\
-        & p_0 \le p \le p_1. \notag \EA
+        & p_0 \le p \le p_1, \notag \EA
+    which is still non-convex, but can be broken down into 
+    two convex sub-problems, 
+    the motivation being that each of these will be 
+    able to be easily and reliably solved.
 
 \subsection{Field sub-problem}
-Since the objective-first problem in its original form is still non-convex,
-    we break it down into two convex sub-problems.
 The first of these is the field sub-problem, 
@@
 This problem is convex, and actually quadratic,
-    which means that it can even be solved in the same way 
+    which means that it can even be solved 
+    using standard numerical tools, in the same way 
     as a simple least-squares problem.
+
+The field sub-problem can be thought of as an update to $x$
+    where we try to ``fit'' the electromagnetic fields to the structure.
+Of course, if it were not for the hard-constraint on the design objective,
+    the field sub-problem would be able to perfectly fit $x$ to $p$.
+This, it turns out, would exactly be a simulation.
 
@@
     \subto p_0 \le p \le p_1. \notag \EA
-
 The structure sub-problem is also convex, but not quadratic.
@@
     quickly and reliably.
+
+Note that in an analogous fashion to the field sub-problem,
+    the structure sub-problem attempts to fit $p$ to $x$,
+    and is prevented from perfectly doing so by it's own constraint.
+
+Because neither sub-problem is capable of completely reducing the physics residual
+    to zero, they must be used in an iterative manner in order to
+    gradually decrease the physics residual.
+To this end, we employ the alternating directions optimization method.
 
@@
     normally measured by how much the physics residual has decreased.
+\BA \text{Loop:} & & \notag \\ 
+& \minimize{x} \| A(p) x - b(p) \|^2 \notag \\
+ &    \subto f(x) = f_\text{ideal}. \notag \\ 
+    \\
+& \minimize{p} \| B(x) p - d(x) \|^2 \notag \\
+    & \subto p_0 \le p \le p_1. \notag \EA
+The alternating directions scheme is extremely simple
+    and does not require additional processing
+    of $x$ or $p$ outside of the two sub-problems,
+    nor does it require the use of auxiliary variables.
 

### 2012-06-13 presentations/meta_book/wave_eq.tex
Updated book.

@@
 \section{The electromagnetic wave equation}
+In this section, we outline the wave equation
+    that is central to the application of our method,
+    with the end-result being to show that it is 
+    separably linear (bi-linear) in the field and structure variables.
+We do this by first formulating this wave equation in the language of physics,
+    and then discretizing it in order to achieve numerical solutions.
+We then show how one can not only obtain the solution for the field,
+    but how one can obtain the solution for the structure using
+    simple, standard numerical tools.
 
@@
 
-For time dependence $\exp(-i \omega t)$, 
+We use the time dependence $\exp(-i \omega t)$, 
     where $\omega$ is the angular frequency,
@@
     \curl H = J + i \epsilon \omega E, \label{eq:H2E} \EA
-    which we can combine to form our wave equation,
+    which we can combine to form our (time-harmonic) wave equation,
 \BE \curl \epsilon^{-1} \curl H - \mu_0 \omega^2 H = \curl \epsilon^{-1} J. 
     \label{eq:wave} \EE
-For further information,
-    as well as simplifications to the wave equation in reduced dimensions,
-    please see the Appendix. % TODO: Use reference.
+
+In this chapter, we are going to only consider the two-dimensional form
+    of this equation; and specifically 
+    the two-dimensional transverse magnetic (TM) mode. % Ref.
+In this case \ER{wave} is simplified not only in that
+    the vector fields are two-dimensional, 
+    but that only the $z$-component of $H$ is non-zero.
+
+Nevertheless, \ER{wave}, in a single equation,
+    represents all the physics which we take into account in this chapter.
 
@@
     we will now add a numerical, or discretized, formulation.
-This will be needed in order to solve for arbitrary structures.
+This will be needed in order to solve for arbitrary structures
+    for which there are not analytical solutions.
 
-First, we discretize our computational space 
-    according to the Yee grid, % TODO: Reference!
+The salient step in order to do so
+    is to the use of the Yee grid, % TODO: Reference!
     which allows us to easily define the curl $(\curl)$
-    operators in \ER{wave} as described in the Appendix. % TODO: ref.
-This allows us, with a change of variables to formulate \ER{wave} as
+    operators in \ER{wave}. % TODO: ref.
+Since both the individual curl operators and the equation as a whole
+    is linear in $H$, it naturally follows to formulate \ER{wave},
+    with a change of variables, as
 \BE A(p)x = b(p), \label{eq:Ab} \EE 
@@
 
-Additionally,  we use periodic boundary conditions
-    with stretched-coordinate % TODO: ref.
-    perfectly matched layers where necessary for our examples.
+Apart from using the Yee grid, the only other salient implementation detail
+    is the use of
+    stretched-coordinate perfectly matched layers %ref
+    where necessary, in order to prevent unwanted reflections
+    at the boundaries of the simulation domain.
+The effect of such layers is to modify the curl operators,
+    although their linear property is still maintained.
 
@@
     (the $E$-field can be computed from the $H$-field using \ER{H2E})
-    by using general linear algebra solvers.
-Doing so is also simply known as a time-harmonic or 
-    a finite-difference frequency-domain (FDFD) simulation.
+    by applying general linear algebra solvers to \ER{Ab}.
+Recall that since we have chosen a time-harmonic formulation,
+    solving for $x$ in \ER{Ab} is actually performing what is simply known as
+    a time-harmonic or a finite-difference frequency-domain (FDFD) simulation.
+Furthermore, since we have limited ourselves to the two-dimensional case,
+    \ER{Ab} is easily solved using the standard sparse solver
+    included in Matlab on a single desktop computer.
 
-Now, while a full three-dimensional problem
-    is computationally quite taxing;
-    in one- and two-dimensions, 
-    \ER{Ab} is easily solved using the standard sparse solver
-    included in Matlab,
-    and this technique is regularly employed 
-    in the examples which follow.
+We call the routine that solves for $x$ in \ER{Ab} given $p$ a field-solver,
+    or a simulator.
 
 \subsection{Solving for $\epsilon^{-1}$}
-The next step,
+Now, the next step,
     after having built a field-solver or simulator
@@
 
-Solving this system would now seem to allow us
-    to choose an electromagnetic field
-    and then find the structure to produce it;
-    which strongly suggests that it will be useful in
-    the design of nanophotonic devices.
-
-In terms of computational complexity, as with \ER{Ab}, 
-    \ER{Bd} in its current form can be solved using standard tools.
+With this extremely simple trick,
+    we have shown that we can seemingly solve for $p$ given $x$
+    with approximately the same ease as solving for $x$ given $p$!
+We see this because the dimensions and complexity of $B(x)$ is basically
+    equivalent to that of $A(p)$,
+    and this implies that the same simple tools used in our field-solver
+    should be applicable to solving \ER{Bd}.
+This is indeed what we find, although the later addition of constraints on $p$
+    will require the use of more powerful (but just as dependable) numerical tools.
 
@@
 The bi-linearity of the wave equation
-    is fundamental in our objective-first strategy
-    which relies on the fact
-    that we already know how to solve linear systems well,
-    and is the reason why we chose $\epsilon^{-1} \to p$
-    instead of the more natual $\epsilon \to p$.
-Indeed, this property forms a natural division of labor
-    in the objective-first scheme, which we outline below.
+    is \emph{absolutely fundamental} in our objective-first strategy
+    because it relies on the fact
+    that, although simultaneously solving for $x$ and $p$ is very difficult,
+    we already know how to solve linear systems ($x$ and $p$ separately) well.
+In fact, it is this very property which forms the natural division of labor
+    which the objective-first method, which we now present, exploits.

### 2012-06-13 presentations/meta_book/wg.tex
Updated book.

@@
     we only make the simplification of working in two dimensions
+    (transverse magnetic mode)
     and dealing only with a single input and output mode.
-
-Say something about TE mode in 2D.
 
@@
 \BE f(x) = \begin{cases}
-        x & \text{at boundary}, \\
+        x - x_\text{perfect} & \text{at boundary}, \\
         0 & \text{elsewhere},
@@
 That is, $f(x)$ simply selects the outermost values of the field
-    in the design space.
+    in the design space
+    and compares them to values of a perfect device.
 
-When placed into the objective-first problem \ER{ob1},
+Furthermore, we choose $f_\text{ideal} = 0$ so that
+    when placed into the objective-first problem \ER{ob1},
     this will result in fixing the boundary values of the field
@@
     to have perfect (unity) coupling efficiency,
-\BE f_\text{ideal} = \begin{cases}
-        x_\text{perfect} & \text{at boundary}, \\
-        0 & \text{elsewhere}.
-        \end{cases} \EE
-These ideal fields are simply obtained by using
+and these ideal fields are simply obtained by using
     the input and output mode profiles at the corresponding ports
@@
     is the frequency, or wavelength of light.
-We use wavelengths in the range of 25 to 42 grid points for
+We use wavelengths in the range of 25 to 63 grid points for
     the results in this chapter.
@@
 
-Also, small footprint and computation time need to be mentioned.
+% Also, small footprint and computation time need to be mentioned.
 \subsection{Coupling to a wide, low-index waveguide}

### 2012-06-14 resume/cover_letter.tex
Made a cover letter for job apps.

\documentclass[12pt]{article}
\usepackage{fullpage}
\addtolength{\textheight}{2cm}

\newcommand{\B}{\begin{description}}
\newcommand{\I}[1]{\item[#1]}
\newcommand{\E}{\end{description}}

\title{Jesse Lu}
\date{}

\begin{document}
% \maketitle
\thispagestyle{empty}
\part*{\center Jesse Lu}
\section*{Who am I? A problem solver.}
Not every problem, not all problems, and not by myself;
    but at the heart of it, solving problems is what I do well,
    it's what I enjoy doing, and it's what I would like to do at
    COMPANY.

I want to join COMPANY in solving technically-challenging, world-changing problems.

\section*{A solver: technologist, innovator, and communicator.}
\subsection*{\emph{Technologist}: has a deep proficiency in 
                            a unique set of technical areas.}
\B  \I{GPUs} I have developed multiple electromagnetic simulation packages
                for the GPU, the latest being a multi-GPU, dynamically-compiled
                electromagnetic solver based on CUDA.

    \I{Physics} I did my PhD in nanophotonics and have a deep expertise 
                in electromagnetics, as well as a general proficiency
                in all things scientific.

    \I{Optimization} During that PhD I developed an optimization paradigm
                for nanophotonic structures, and understood the power of
                convex optimization and related techniques.
\E

\subsection*{\emph{Innovator}: finds and combines the technical pieces needed 
                            to create something amazing.}
\B  \I{Learns fast} I intentionally expose myself to other disciplines
                in order to ``connect the dots'' in a powerful way, 
                and I quickly incorporate their salient ideas into my own projects.

    \I{Fails fast} When you innovate, you suceed only after many failures.
                I wittle down new features/methods into
                their simplest viable test cases in order 
                to fail as fast as possible.
\E

\subsection*{\emph{Communicator}: disseminates the results of innovation and 
                            engages others in furthering innovation.}
\B  \I{Public speaking} Stand me up in front of a crowd, and I'll love it.
                One of my passions is to be able to bring others to that
                ``Aha!'' moment, especially concerning complex
                technical subjects.

    \I{Connecting} Or put my in a room with a single person, 
                and I'll love that too.
                I am always eager to learn and I've found that questioning and
                exploring someone else's knowledge and perspectives is often 
                the best way to do so.
\E

In conclusion, I believe that great companies are simply a collection of great problem-solvers
    tackling great problems and I hope to join COMPANY in doing 
    so\footnote{\texttt{jesselu@stanford.edu, (408)568-9356, East Palo Alto, CA.}}.
\end{document}

### 2012-06-14 resume/bina/cover_letter.tex
Cover letters and resumes for 4 job applications done.

--- 2012-06-14 resume/cover_letter.tex
@@
     it's what I enjoy doing, and it's what I would like to do at
-    COMPANY.
+    Bina.
 
-I want to join COMPANY in solving technically-challenging, world-changing problems.
+I want to join Bina in solving technically-challenging, world-changing problems.
 
@@
 In conclusion, I believe that great companies are simply a collection of great problem-solvers
-    tackling great problems and I hope to join COMPANY in doing 
+    tackling great problems and I hope to join Bina in doing 
     so\footnote{\texttt{jesselu@stanford.edu, (408)568-9356, East Palo Alto, CA.}}.

### 2012-06-14 resume/bina/res1.tex
Cover letters and resumes for 4 job applications done.

% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass{res} 
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\setlength{\textheight}{9.5in} % increase text height to fit on 1-page

\begin{document}

\name{Jesse Lu\\[12pt]}
\address{\texttt{jesselu@stanford.edu} \\ 66 Newell Rd. Apt. O \\ East Palo Alto, CA \\ (408) 568-9356}

\begin{resume}

\section{JOB OBJECTIVE}          
    A full-time software engineering position at Bina with starting date of November 2012 
    (upon completion of doctoral degree).

\section{EDUCATION}          
    Stanford University, PhD, Electrical Engineering, November 2012 (in progress) \\
    Stanford University, Masters of Science, Electrical Engineering, May 2012 \\
    University of California Los Angeles, Bachelor of Science, Electrical Engineering, June 2006

\section{HONORS}
    Stanford Graduate Fellowship, Stanford University, 2007 \\
    Dean's Honors List, University of California Los Angeles, five quarters

\section{EXPERIENCE}
   \vspace{-0.1in}	
   \begin{tabbing}
   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
    {\bf Graduate Researcher} \>Jelena Vuckovic Group \>2007-Present\\
                             \>Stanford University
   \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
    Existing nanophotonic design process consisted of trial-and-error
        where each simulation about 24 hours to complete.
    Implemented FDTD and FDFD simulation software on Nvidia GPUs to bring 
        simulation times down to 10 minutes.
    Also developed a novel ``objective-first'' nanophotonic design algorithm
        and demonstrated automated design of 
        small-footprint, high-efficiency waveguide couplers.
   \begin{tabbing}
   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
    {\bf Undergraduate Researcher} \>Eli Yablonovitch Group \> 2005-2006\\
                          \>University of California, Los Angeles
   \end{tabbing}\vspace{-20pt}
    Surface plasmon focusing device required a grating coupler to inject energy
        into the surface plasmon mode.
    Wrote a Matlab program interfacing with a FEM package (COMSOL),
        developed a hierarchal optimization routine as well as an extended 
        transfer matrix model to produce first-ever thoroughly optimized 
        grating coupler design.
   \begin{tabbing}%
   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions          
   {\bf Research Assistant Intern}  \>Inko Pellicles \> Summer 2003\\
                          \>Sunnyvale, CA
   \end{tabbing}\vspace{-20pt}
    Pellicle removal left residue on expensive lithography masks.
    Assisted in researching and developing a UV irradition process
        to modify the adhesive properties of the glue.

\section{PROGRAMMING}          
    Fluent in Python, CUDA, and Matlab. \\
    Currently working with Git and Amazon EC2.

\section{PUBLICATIONS}          
    ``Objective-first design of high-efficiency, small-footprint couplers between arbitrary nanophotonic waveguide modes'' Jesse Lu, Jelena Vuckovic (Optics Express, 2012). \\
    ``Inverse design of a three-dimensional nanophotonic resonator'' Jesse Lu, Stephen Boyd, Jelena Vuckovic (Optics Express, 2011). \\
    ``Inverse design of nanophotonic structures using complementary convex optimization'' Jesse Lu, Jelena Vuckovic (Optics Express, 2010). \\
    ``Numerical optimization of a grating coupler for the efficient excitation of surface plasmons at an Ag-SiO2 interface'' Jesse Lu, Csaba Petre, Josh Conway, Eli Yablonovitch (JOSA B, 2007).

\end{resume}
\end{document}

### 2012-06-14 resume/nvidiaresearch/nvidia-resume.tex
Cover letters and resumes for 4 job applications done.

--- 2012-06-14 resume/bina/res1.tex
@@
 \section{JOB OBJECTIVE}          
-    A full-time software engineering position at Bina with starting date of November 2012 
+    A full-time Research Scientist position with Nvidia Research with starting date of November 2012 
     (upon completion of doctoral degree).

### 2012-07-09 presentations/meta_book/extensions.tex
Finished draft of meta book chapter.

\section{Extending the method}
The objective-first method, as applied in the examples in this chapter,
    really only represent a small foray into the area of nanophotonic design.
Several key extensions to what is presented here are needed to
    fully address real-world nanophotonic design challenges.

\subsection{Three-dimensional design}
The first of these is the need to design fully three-dimensional structures.
Doing so provides no inherent difficulties aside from the matrices in
    \ER{Ab} becoming very large.
This is not insurmountable as electromagnetic simulation software for 
    three-dimensional nanophotonic structures already exists.

In fact, for certain choices of the design objective 
    (i.e. those of low-rank) 
    \ER{Fsub} can be efficiently solved by a small number of calls
    to unmodified simulation software. 
Of course, for general design objectives, such software will need 
    to be modified in order to solve \ER{Fsub}.

On the other hand, specialized software to solve \ER{Bd} in 
    any number of dimensions does not exist,
    although this was not a problem in two dimensions since generic 
    linear algebra solvers are more than accurate.
In three dimensions, 
    the large size of matrix $B(x)$ can be greatly compressed by considering
    only fabrication processes which modify a structure in-plane.
In this way, the degrees of freedom in $p$ can be greatly reduced and the original
    methods used in this chapter can still be applied.
This work-around is especially viable since in-plane structures are 
    of most interest from a practical standpoint.

\subsection{Multi-mode}
A second necessary extension is to be able to consider the multiple fields
    that a structure produces in response to input fields of differing frequency
    and spatial distribution.
Such an extension is straightforward in the objective-first formulation
    and results in the following modified problem statement,
\BA \minimize{x_i,p} \sum_i \| A(p) x_i - b(p) \|^2 \notag \\
    \subto f(x_i) = f_{i,\text{ideal}} \quad \text{i = 1, \ldots, n} \\
        & p_0 \le p \le p_1, \notag \EA
    which can be separated into field and structure sub-problems 
    as in the single-mode formulation.
In the multi-mode case, this results in one structure sub-problem 
    and $n$ field sub-problems.
Interestingly, the $n$ field sub-problems lend themselves 
    naturally to parallelization
    since they can be solved independently,
    leading to the possibility that a multi-mode design completing in
    roughly the same time as a single-mode design.

\subsection{Binary structure}
Another necessary extension of our method is to force 
    the values of $p$ to be discrete.
This is not trivial since a naive restatement of \ER{ob1}
    which includes such a constraint,
\BA \minimize{x,p} \| A(p) x - b(p) \|^2 \notag \\
    \subto f(x) = f_\text{ideal} \\
        & p \in \{p_0, p_1\}, \notag \EA
    results in a very difficult combinatorial problem.

Tractable approaches include penalizing intermediate values of $p$\cite{simp}
    or even transferring to a level-set method\cite{miller}
    where the distinction between materials is explicit.

\subsection{Robustness}
Lastly, the design of structures which are robust to both
    fabrication imperfections and fluctuations in environmental parameters
    is also a necessity for practical real-world devices.

It seems likely in this case that a heurestic approach may
    be most successful in this case, rather than to tackle 
    the problem head-on.
For instance, to account for fluctuating material parameters
    induced by temperature changes
    one may design a device to operate for a larger-than-necessary 
    frequency range.

### 2012-07-09 presentations/meta_book/mimic.tex
Finished draft of meta book chapter.

@@
     mimics the output field of another device.
-In this sense optical mimics are the anti-cloak;
+In this sense optical mimics are the anti-cloaks;
     whereas cloaks strive to make an object's electromagnetic presence vanish,
@@
 In a more general sense, 
-    optical mimics is really just a recasting of the thrust of 
+    designing optical mimics is really just a recasting of the thrust of 
     the objective-first design strategy in its purest form:
@@
     which we cloaked in the previous section.
-\myfig{mimic/m1}{Plasmonic cylinder mimic. 
+\myfig{mimic/m1}{Plasmonic cylinder mimic (see \fR{cloak/c6} for the original object). 
                 Error: 8.1\%,
-                footprint: $40 \times 120$ grid points,
+                device footprint: $40 \times 120$ grid points,
                 wavelength: 42 grid points.}
@@
                 Error: 12.0\%,
-                footprint: $40 \times 120$ grid points,
+                device footprint: $40 \times 120$ grid points (1.6 $\lambda$ thick),
                 wavelength: 25 grid points.}
@@
                 Error: 5.6\%,
-                footprint: $40 \times 120$ grid points,
+                device footprint: $40 \times 120$ grid points (1.6 $\lambda$ thick),
                 wavelength: 25 grid points.}
@@
                 Error: 1.4\%,
-                footprint: $40 \times 120$ grid points,
+                device footprint: $40 \times 120$ grid points (1.6 $\lambda$ thick),
                 wavelength: 25 grid points.}
@@
                 Error: 28.6\%,
-                footprint: $60 \times 120$ grid points,
+                device footprint: $60 \times 120$ grid points (1.43 $\lambda$ thick),
                 wavelength: 42 grid points.}
@@
 Of course, akin to its lens counterpart,
-    this output plane must lie within the near-field of the device
+    this output plane must lie within the near-field 
+    of the device (specifically, two computational cells away)
     because of its sub-wavelength nature.
@@
                 Error: 19.8\%,
-                footprint: $40 \times 120$ grid points,
+                device footprint: $40 \times 120$ grid points,
                 wavelength: 25 grid points.}

### 2012-07-09 presentations/meta_book/my_chapter.tex
Finished draft of meta book chapter.

--- 2012-05-29 presentations/meta_book/my_chapter.tex
@@
 
-\abstract{The abstract for the book.}
+\abstract{We introduce an ``objective-first'' strategy 
+    for designing nanophotonic devices,
+    and we demonstrate the design of nanophotonic
+    coupler, cloak, and mimic devices.}
 
-Introductory paragraph.
+Our initial foray into design methods for nanophotonic devices
+    began with a very simple and naive question: 
+    could we make an inverse solver which,
+    when given the electromagnetic fields we desire,
+    returns the nanophotonic structure that will produce them\cite{opex3}?
+In other words, since we already know how to solve for $E$ and $H$ 
+    in Maxwell's equations, why can't we solve for $\epsilon$
+    or even $\mu$ instead?
+
+Not surprisingly, it did not take us long to find that such
+    a simple strategy would inevitably run into many problems.
+
+Over the subsequent years, we were able to come up with a better solution,
+    which we call an ``objective-first'' strategy for nanophotonic design,
+    and which we present in this chapter.
+Although it is much more advanced than our original idea,
+    objective-first design still carries the same fundamental concept,
+    which is to specify the electromagnetic fields, and then
+    to solve for a structure to produce them.
+
+In this chapter, we present the simple theoretical underpinnings of 
+    objective-first design in the first two sections,
+    and then show examples of the method in action in the rest of the chapter.
+We also include the source code that was used to generate
+    all results presented herein\cite{code}.
 
@@
 \input{ob1}
-\input{1d}
-\input{res}
 \input{wg}
+\input{cloak}
+\input{mimic}
+\input{extensions}
 
-\section{Metamaterials design}
-\subsection{Modification of the design objective}
-\subsection{Cloak devices}
-\subsection{Mimic devices}
+\section{Conclusion}
+We have introduced an objective-first approach
+    to the design of nanophotonic components, and
+    applied it to the design of waveguide couplers,
+    optical cloaks, and optical mimics.
+In doing so, we hope to have exhibited both the simplicity
+    and the breadth of our method to the design of a broad
+    class of linear, single-mode devices.
+In addition to posting the source code for all the examples online\cite{code}, 
+    we have outlined the necessary extensions to our method in order
+    to design practical, three-dimensional devices.
 
-\section{Extending the method}
-\subsection{3D}
-\subsection{Multi-mode}
-\subsection{Robustness}
+\section{Acknowledgements}
+This work has been supported by the 
+    AFOSR MURI for Complex and Robust On-chip Nanophotonics 
+    (Dr. Gernot Pomrenke), grant number FA9550-09-1-0704; 
+    and the Alexander von Humboldt Foundation.
 
-\section{Appendix}
-\subsection{Full 3D curl}
-\subsection{1D}
-\subsection{2D}
-\subsection{2.5D}
+\begin{thebibliography}{99.}%
+\bibitem{boyd} S. Boyd, and L. Vandenberghe, 
+    \emph{Convex Optimization} 
+    (Cambridge University Press, 2004)
+\bibitem{cvx} M. Grant and S. Boyd, \emph{CVX: Matlab software for disciplined convex programming}, version 1.21. \verb+http://cvxr.com/cvx+, January 2011.
+\bibitem{admm} S. Boyd, N. Parikh, E. Chu, B. Peleato, and J. Eckstein, 
+    ``Distributed Optimization and Statistical
+    Learning via the Alternating Direction
+    Method of Multipliers,''
+    Foundations and Trends in Machine Learning, \textbf{3} 1–122 (2011).
+\bibitem{pml} S. G. Johnson, ``Notes on Perfectly Matched Layers (PMLs),''
+    http://math.mit.edu/~stevenj/18.369/pml.pdf, (2010). 
+\bibitem{opex1} J. Lu, and J. Vuckovic, 
+    ``Inverse design of nanophotonic structures using complementary convex optimization,''
+    Opt. Express \textbf{18}, 3793--3804 (2011). 
+% \bibitem{opex2} J. Lu, S. Boyd, and J. Vuckovic, 
+%     ``Inverse design of a three-dimensional nanophotonic resonator,''
+%     Opt. Express \textbf{19}, 10563--10750 (2011). 
+\bibitem{opex3} J.Lu, and J. Vuckovic,
+    ``Objective-first design of high-efficiency, small-footprint couplers between arbitrary nanophotonic waveguide modes,''
+    Opt. Express \textbf{20}, 7221--7236 (2012).
+\bibitem{code} https://github.com/JesseLu/objective-first
+\bibitem{miller} O. D. Miller, ``Photonic Design: From Fundamental Solar Cell Physics to Computational Inverse Design,''
+    U. C. Berkeley, (2012).
+\bibitem{shin} W. Shin, S. Fan, ``Choice of the perfectly matched layer boundary condition for frequency-domain Maxwell’s equations solvers,''
+    J. Comp. Phys. \textbf{231}, 3406--3431 (2012).
+\bibitem{simp} M. P. Bendsoe, and O. Sigmund, 
+    ``Material interpolation schemes in topology optimization,''
+    Archive of Applied Mechanics \textbf{69}, 635--654 (1999).
+\bibitem{taflove} A. Taflove, and S. C. Hagness, 
+    \emph{Computational Electrodynamics, Third Ed.}
+    Section 3.3.2, (Artech House, 2005).
+\bibitem{yee} K. S. Yee,
+    ``Numerical Solution of Initial Boundary Value Problems Involving
+    Maxwell's Equations in Isotropic Media,''
+    IEEE Trans. Antennas and Propagation \textbf{14}, 802--807 (1966).
+\end{thebibliography}

### 2012-07-09 presentations/meta_book/ob1.tex
Finished draft of meta book chapter.

@@
     which must transmit efficiently into a particular mode,
-    we could choose $f(x)$ to be the negative power transmitted into that mode.
+    we could choose $f(x)$ to be the negative power flow into that mode.
 Or, if the device was to be a low-loss resonator,
@@
 Before formulating the design problem,
-    we would like to inject a note regarding the complexity of various 
+    we would like to add a note regarding the complexity of various 
     optimization problems.
 
-Specifically, we want to introduce the notion of \emph{convexity} %TODO: ref.
+Specifically, we want to introduce the notion of \emph{convexity}\cite{boyd}
     and to simply note the difference between problems that
@@
 On a practical level, there exist mature convex optimization software packages
-    among which is CVX, a convex optimization package written for Matlab, % Ref.
+    among which is CVX, a convex optimization package written for Matlab\cite{cvx}, 
     which we use for the examples in this chapter.
@@
 Since solving \ER{typform} is quite difficult in the general sense
-    (simultaneously varying $x$ and $p$ makes the problem non-convex)
+    (simultaneously varying $x$ and $p$ makes the problem non-convex),
     traditional approaches have relied on either brute-force parameter search,
@@
 In the gradient-descent case, solving \ER{typform} results in the
-    well-known adjoint optimization method. % Ref.
+    well-known adjoint optimization method\cite{miller}.
 
@@
 In contrast to an adjoint method approach,
-    in so doing we can still access information regarding
+    in doing we can still access information regarding
     second-order derivatives, which greatly speeds up finding a solution.
@@
 
-In practice, we add an additional constraint to the original formulation,
+In practice, we add an additional constraint to the original formulation, \cite{opex1}
     which is to set hard-limits on the allowable values of $p$,
@@
 
-The field sub-problem can be thought of as an update to $x$
-    where we try to ``fit'' the electromagnetic fields to the structure.
+The field sub-problem can be thought of as an update to $x$ (field)
+    where we try to ``fit'' the electromagnetic fields to the structure ($p$).
 Of course, if it were not for the hard-constraint on the design objective,
@@
     \subto p_0 \le p \le p_1. \notag \EA
-The structure sub-problem is also convex, but not quadratic.
+The structure sub-problem is also convex, but not quadratic because of the 
+    inequality constraints on $p$.
 However, use of the CVX package still allows us to obtain the result
@@
     the structure sub-problem attempts to fit $p$ to $x$,
-    and is prevented from perfectly doing so by it's own constraint.
+    and is prevented from perfectly doing so by its own constraint.
 
@@
     although we have found it to be sufficient in our cases.
-See ref % cite!
-    for related methods that exhibit far better convergence.
+Related methods, such as the Alternating Directions Method of Multipliers\cite{admm}, 
+    exhibit far better convergence.

### 2012-07-09 presentations/meta_book/wave_eq.tex
Finished draft of meta book chapter.

@@
 We then show how one can not only obtain the solution for the field,
-    but how one can obtain the solution for the structure using
+    but also obtain the solution for the structure using
     simple, standard numerical tools.
@@
     where $E$, $H$, and $J$ are 
-    the electric, magnetic and electric current % TODO: Check this.
+    the electric, magnetic and electric current
     vector fields, respectively,
@@
 
-We use the time dependence $\exp(-i \omega t)$, 
+Assuming the time dependence $\exp(-i \omega t)$, 
     where $\omega$ is the angular frequency,
@@
 In this chapter, we are going to only consider the two-dimensional form
-    of this equation; and specifically 
-    the two-dimensional transverse magnetic (TM) mode. % Ref.
-In this case \ER{wave} is simplified not only in that
-    the vector fields are two-dimensional, 
-    but that only the $z$-component of $H$ is non-zero.
+    of this equation, and specifically 
+    the two-dimensional transverse electric (TE) mode\cite{taflove}.
+In this case \ER{wave} is simplified 
+    because only the $z$-component of $H$ is non-zero.
 
-Nevertheless, \ER{wave}, in a single equation,
+Nevertheless,  a single equation \ER{wave},
     represents all the physics which we take into account in this chapter.
@@
 \subsection{Numerical formulation}
-Now, on top of the analytical formulation of the wave equation \ER{wave}
+On top of the analytical formulation of the wave equation \ER{wave}
     we will now add a numerical, or discretized, formulation.
@@
 The salient step in order to do so
-    is to the use of the Yee grid, % TODO: Reference!
+    is to the use of the Yee grid\cite{yee}, 
     which allows us to easily define the curl $(\curl)$
-    operators in \ER{wave}. % TODO: ref.
+    operators in \ER{wave}. 
 Since both the individual curl operators and the equation as a whole
@@
     is the use of
-    stretched-coordinate perfectly matched layers %ref
+    stretched-coordinate perfectly matched layers \cite{pml}
     where necessary, in order to prevent unwanted reflections
@@
     solving for $x$ in \ER{Ab} is actually performing what is simply known as
-    a time-harmonic or a finite-difference frequency-domain (FDFD) simulation.
+    a time-harmonic or a finite-difference frequency-domain (FDFD) simulation\cite{shin}. 
 Furthermore, since we have limited ourselves to the two-dimensional case,
@@
 \subsection{Solving for $\epsilon^{-1}$}
-Now, the next step,
-    after having built a field-solver or simulator
-    (finds $x$ given $p$) for our wave equation,
-    is to build a structure-solver for it.
+    After having built a field-solver or simulator
+    (which finds $x$ given $p$) for our wave equation,
+    the next step is to build a structure-solver for it.
 In other words, we need to be able to solve for $p$ given $x$.
@@
     $\epsilon^{-1} J = J \epsilon^{-1}$ 
-    since scalar multiplication is communicative.
+    since scalar multiplication is commutative.
 This allows us to rearrange \ER{wave} as
@@
     with approximately the same ease as solving for $x$ given $p$!
-We see this because the dimensions and complexity of $B(x)$ is basically
+We see this because the dimensions and complexity of $B(x)$ are basically
     equivalent to that of $A(p)$,
@@
     in order to get a useful design tool,
-    we have really shown so far is that the wave equation is 
-    separately linear or \emph{bi-linear} in $x$ and $p$.
-Namely that,
+    we have shown so far that the wave equation is 
+    separately linear or in $x$ and $p$ (i.e. bilinear).
+Namely,
 \BE A(p)x-b(p) = B(x)p - d(x). \label{eq:bilinear} \EE
@@
 In fact, it is this very property which forms the natural division of labor
-    which the objective-first method, which we now present, exploits.
+    which our objective-first method exploits.

### 2012-07-09 presentations/meta_book/wg.tex
Finished draft of meta book chapter.

@@
     alternating directions to \ER{ob1} which 
-    results in solving the following two sub-problems iteratively.
+    results in solving the following two sub-problems iteratively:
 \BA \minimize{x} \| A(p) x - b(p) \|^2 \\
@@
     is the frequency, or wavelength of light.
-We use wavelengths in the range of 25 to 63 grid points for
+We use free space wavelengths in the range of 25 to 63 grid points for
     the results in this chapter.
@@
 Although we do not present the convergence results here,
-    such information can be obtained by inspecting the source. %Ref!
+    such information can be obtained by inspecting the source code\cite{code}.
 
@@
             Efficiency: 99.8\%, 
-            footprint: $36 \times 76$ grid points, 
+            device footprint: $36 \times 76$ grid points, 
             wavelength: 42 grid points.}
@@
     the simulated $H_z$ fields,
-    under excitation of the input mode,
+    under excitation of the input mode in this final structure,
     are shown in the bottom plots.
@@
             Efficiency: 98.0\%, 
-            footprint: $36 \times 76$ grid points, 
+            device footprint: $36 \times 76$ grid points, 
             wavelength: 42 grid points.}
@@
             Efficiency: 98.9\%, 
-            footprint: $36 \times 76$ grid points, 
+            device footprint: $36 \times 76$ grid points, 
             wavelength: 25 grid points.}
@@
     a ``air-core'' output waveguide, 
-    in which the waveguiding effect is achieved using distributed Bragg reflection.
+    in which the waveguiding effect is achieved using distributed Bragg reflection
+    (instead of total internal reflection as in the input waveguide).
 
@@
     as shown in \fR{wg/4}.
-\myfig{wg/4}{Coupler to a wide low-index waveguide.
+\myfig{wg/4}{Coupler to a plasmonic metla-insulator-metal waveguide.
             Efficiency: 97.5\%, 
-            footprint: $36 \times 76$ grid points, 
+            device footprint: $36 \times 76$ grid points, 
             wavelength: 25 grid points.}
@@
 \subsection{Coupling to a metal wire plasmonic waveguide mode}
-\myfig{wg/5}{Coupler to a wide low-index waveguide.
+\myfig{wg/5}{Coupler to a plasmonic wire waveguide.
             Efficiency: 99.1\%, 
-            footprint: $36 \times 76$ grid points, 
+            device footprint: $36 \times 76$ grid points, 
             wavelength: 25 grid points.}

### 2012-07-10 presentations/meta_book/extensions.tex
Sent draft to Ken.

@@
 The objective-first method, as applied in the examples in this chapter,
-    really only represent a small foray into the area of nanophotonic design.
+    represents only a small foray into the area of nanophotonic design.
 Several key extensions to what is presented here are needed to
@@
 
-Tractable approaches include penalizing intermediate values of $p$\cite{simp}
-    or even transferring to a level-set method\cite{miller}
+Tractable approaches include penalizing intermediate values of $p$ \cite{simp}
+    or even transferring to a level-set method \cite{miller}
     where the distinction between materials is explicit.

### 2012-07-18 scribblings/plan.tex
Started a plan.

\documentclass{article}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{hyperref}
\input defs.tex
\newcommand{\inv}[1]{\frac{1}{#1}}
\newcommand{\tC}{\tilde{C}}
\newcommand{\BSE}{\begin{subequations}\begin{align}}
\newcommand{\EA}{\end{align}}
\newcommand{\ESE}{\end{subequations}\end{align}}
\newcommand{\env}[2]{\begin{#1}#2\end{#1}}
\newcommand{\E}[1]{\begin{subequations}\begin{align}#1\end{align}\end{subequations}}
\DeclareMathOperator*{\minimize}{\text{minimize}\quad}
\newcommand{\subto}{\text{subject to}\quad}
\title{Objective-First Nanophotonic Design Plan} 
\author{Jesse Lu}
\begin{document}
\maketitle
\tableofcontents

\section{Goal}
    Software to solve the following general inverse design problem in nanophotonics.
    \E{ \minimize&  f(x) + g(z) \\
        \subto&     A(z)x - b(z) = 0}
% \end{align}\end{subequations}
    The software will include two 
\end{document}

### 2012-07-18 presentations/meta_book/cloak.tex

@@
     (where the structure is allowed to vary),
-    and the range of $p$ is limited to $1/12.25 \le p \le 1$.
+    and the range of $p$ is limited to $1/12.25 \le p \le 1$,
+    implying a dielectric cloak.
 
@@
                 Efficiency: 99.99\%,
-                footprint: $60 \times 100$ grid points,
+                device footprint: $60 \times 100$ grid points,
                 wavelength: 63 grid points.}
@@
                 Efficiency: 99.99\%,
-                footprint: $60 \times 100$ grid points,
+                device footprint: $60 \times 100$ grid points,
                 wavelength: 42 grid points.}
@@
                 Efficiency: 99.8\%,
-                footprint: $60 \times 100$ grid points,
+                device footprint: $60 \times 100$ grid points,
                 wavelength: 42 grid points.}
@@
 Our last cloaking example replaces the plasmonic cylinder 
-    with a thin metallic wall in which is etched a sub-wavelength channel.
+    with a thin metallic wall in which a sub-wavelength channel is etched.
 Such a metallic wall is very effective at blocking incoming light
@@
                 Efficiency: 99.9\%,
-                footprint: $60 \times 100$ grid points,
+                device footprint: $60 \times 100$ grid points,
                 wavelength: 42 grid points.}

### 2012-07-18 presentations/meta_book/my_chapter.tex

@@
 % Custom figures.
-\newcommand{\myfig}[2]{\begin{figure}[!h]\includegraphics[width=0.95\textwidth]{fig/#1.jpg}\caption{#2}\label{fig:#1}\end{figure}}
+% \newcommand{\myfig}[2]{\begin{figure}[!h]\includegraphics[width=0.95\textwidth]{fig/#1.jpg}\caption{#2}\label{fig:#1}\end{figure}}
+\newcommand{\myfig}[2]{\begin{figure}[!h]\includegraphics[width=0.95\textwidth]{fig/#1}\caption{#2}\label{fig:#1}\end{figure}}
 
@@
     when given the electromagnetic fields we desire,
-    returns the nanophotonic structure that will produce them\cite{opex3}?
+    returns the nanophotonic structure that will produce them \cite{opex3}?
 In other words, since we already know how to solve for $E$ and $H$ 
@@
 We also include the source code that was used to generate
-    all results presented herein\cite{code}.
+    all results presented herein \cite{code}.
 
@@
     class of linear, single-mode devices.
-In addition to posting the source code for all the examples online\cite{code}, 
+In addition to posting the source code for all the examples online \cite{code}, 
     we have outlined the necessary extensions to our method in order

### 2012-07-18 presentations/meta_book/ob1.tex

@@
 Specifically, we want to introduce the notion of \emph{convexity}\cite{boyd}
-    and to simply note the difference between problems that
+    and to note the difference between problems that
     are convex and those which are not.
@@
 We use a simple alternating directions scheme 
-    to peice together \ER{Fsub} and \ER{Ssub},
+    to piece together \ER{Fsub} and \ER{Ssub},
     which is to say that we simply

### 2012-07-18 resume/lytro/cover_letter.tex

--- 2012-06-14 resume/bina/cover_letter.tex
@@
     it's what I enjoy doing, and it's what I would like to do at
-    Bina.
+    Lytro.
 
-I want to join Bina in solving technically-challenging, world-changing problems.
+I want to join Lytro in solving technically-challenging, world-changing problems.
 
@@
 In conclusion, I believe that great companies are simply a collection of great problem-solvers
-    tackling great problems and I hope to join Bina in doing 
+    tackling great problems and I hope to join Lytro in doing 
     so\footnote{\texttt{jesselu@stanford.edu, (408)568-9356, East Palo Alto, CA.}}.

### 2012-07-18 resume/nvidiaresearch/cover_letter.tex

--- 2012-06-14 resume/bina/cover_letter.tex
@@
     it's what I enjoy doing, and it's what I would like to do at
-    Bina.
+    Nvidia.
 
-I want to join Bina in solving technically-challenging, world-changing problems.
+I want to join Nvidia Research as a Research Scientist and solve technically-challenging, world-changing problems.
 
@@
 In conclusion, I believe that great companies are simply a collection of great problem-solvers
-    tackling great problems and I hope to join Bina in doing 
+    tackling great problems and I hope to join Nvidia Research in doing 
     so\footnote{\texttt{jesselu@stanford.edu, (408)568-9356, East Palo Alto, CA.}}.

### 2012-07-18 resume/pixel/cover_letter.tex

--- 2012-06-14 resume/bina/cover_letter.tex
@@
     it's what I enjoy doing, and it's what I would like to do at
-    Bina.
+    Perceptive Pixel.
 
-I want to join Bina in solving technically-challenging, world-changing problems.
+I want to join Perceptive Pixel in solving technically-challenging, world-changing problems.
 
@@
 In conclusion, I believe that great companies are simply a collection of great problem-solvers
-    tackling great problems and I hope to join Bina in doing 
+    tackling great problems and I hope to join Perceptive Pixel in doing 
     so\footnote{\texttt{jesselu@stanford.edu, (408)568-9356, East Palo Alto, CA.}}.

### 2012-07-18 resume/pixel/res1.tex

--- 2012-06-14 resume/bina/res1.tex
@@
 \section{JOB OBJECTIVE}          
-    A full-time software engineering position at Bina with starting date of November 2012 
+    A full-time software engineering position in Perceptive Pixel with starting date of November 2012 
     (upon completion of doctoral degree).

### 2012-07-18 scribblings/plan.tex
Updated the PLAN.

@@
 \newcommand{\env}[2]{\begin{#1}#2\end{#1}}
-\newcommand{\E}[1]{\begin{subequations}\begin{align}#1\end{align}\end{subequations}}
+\newcommand{\E}[2]{\begin{subequations}\begin{align}#1\end{align}\label{eq:#2}\end{subequations}}
 \DeclareMathOperator*{\minimize}{\text{minimize}\quad}
 \newcommand{\subto}{\text{subject to}\quad}
+\newcommand{\er}[1]{\eqref{eq:#1}}
+\newcommand{\BI}{\begin{itemize}\item}
+\newcommand{\EI}{\end{itemize}}
+\newcommand{\I}{\item}
 \title{Objective-First Nanophotonic Design Plan} 
@@
 \section{Goal}
-    Software to solve the following general inverse design problem in nanophotonics.
+    Software to solve the following general inverse design problem, specfically for nanophotonics.
     \E{ \minimize&  f(x) + g(z) \\
-        \subto&     A(z)x - b(z) = 0}
-% \end{align}\end{subequations}
-    The software will include two 
+        \subto&     A(z)x - b(z) = 0}{prob}
+    where $f(x)$ and $g(z)$ are the \emph{design objectives} for the field ($x$) and structure ($z$) variables respectively,
+    and $A(z)x - b(z)$ is the \emph{physics residual} of the problem.
+
+\section{Strategy}
+    The general strategy is to divide the problem 
+        into field and structure sub-problems,
+        which can be tackled separately and in a modular fashion
+        by using various
+        \emph{optimization paradigms} and 
+        \emph{structure parameterizations}
+        interchangeably.
+
+    Specifically, the available optimization paradigms are
+    \BI adjoint
+    \I  ob-1    \EI
+    and the available structure parameterizations include
+    \BI point
+    \I  boundary
+    \I  shape
+    \I  include/exclude \EI
+
 \end{document}

### 2012-07-19 sermons/Revelation1:4.tex
Started new sermon.

--- 2012-04-27 sermons/Revelation1:1b-3.tex
@@
 \begin{document}
-\part*{Revelation 1:1b-3 --- The Power and Promise of the Revelation of Jesus Christ}
+\part*{Revelation 1:4 --- Grace and Peace from God, Part 1}
 \tableofcontents
 \BI
-\section*{Notes}
-\I  The point of this sermon is:
-        \begin{quote} 
-        You need to know and obey the Revelation of Jesus Christ.
-        \end{quote}
-\I  Remember that with every subsection, your job is to answer three questions:
-    \begin{enumerate}
-    \I  What does it mean?
-    \I  Why does it matter?
-    \I  How does it change my life?
-    \end{enumerate}
+\section*{The Need for Grace and Peace}
+\I one
 
-\section*{Introduction}
-\I  The purpose of John's prologue is to prepare us to read, understand, and 
-    obey the rest of the book.
-\I  John does so by telling us (from last time)
-\BI \I  the Person of Revelation, and
-    \I  the purpose of Revelation. \EI
+\section*{The Source of Grace and Peace}
+\I two
+\EI
 
-\section{The Power of Revelation}
-\I  Lead: There is a reason why verse 2 doesn't simply say, ``who wrote it down.''
-\I  John wants to emphasize the power of what follows, and he does so by describing it in three ways.
-
-\subsection{Eternal: the word of God}
-\I  Lead: Isn't it obvious that Revelation is the word of God?
-\BI \I It should be to us, but not necessarily to the original recipients. \EI
-\I  That Revelation is the word of God means that it is both eternal and living.
-    Eternal in that 
-\BI \I  it does not decay (Isaiah 40:8),
-    \I  is complete, with no part missing or ommitted (22:18-19),
-    \I  is perfect, and nothing can be added to it (Psalm 19:7);
-\EI
-    and living in that it
-\BI \I  transforms, converting the soul (Psalm 19:7),
-    \I  purifies, cleansing from sin (Psalm 119:9-10), and
-    \I  strengthens, producing endurance for trials (Matthew 7:24-27).
-\EI
-\I  And so Revelation does not merely point to the truth, it \emph{is} the truth.
-
-\subsection{Essential: the testimony of Jesus Christ}
-\I  Lead: The next issue, is Revelation essential?
-\BI \I Foundational or secondary?
-    \I Part of the Christian's core curriculum, or an optional specialty?
-\EI
-\I  Holding to the testimony of Jesus Christ is the essence of what a Christian is. It was 
-\BI \I  the reason for John's exile on Patmos (1:9), and
-    \I  the reason why the saints were killed (6:9) and beheaded (20:4).
-    \I  Believers are described as those who have the testimony of Jesus Christ (12:17),
-    \I  and they overcome Satan by clinging to it, even to death (12:11).
-\EI
-\I  Testimony means a legally-binding witness as submitted to a judge.
-\BI \I  As if Jesus is on the witness stand of a courtroom, and outlines 
-        who He is, what He has done, and what He will do. \EI
-\I  That Revelation is the testimony of Jesus Christ means that it is the essential truth of Jesus 
-    (who He is, what He has done, and what He will do)
-    that every Christian must cling to.
-
-\subsection{Eyewitness: all things that he saw}
-\I  John emphasizes that Revelation is a personal eyewitness account,
-\BI \I  Not something he thought up or figured out. \EI
-\I  Highlights the divine origin of the letter.
-\BI \I  Revelation does not depend at all on John's ability to pastor, preach, interpret, or organize.
-    \I  John only needs to see/hear and copy it down.
-    \I  He is effectively Jesus' scribe/typist.
-\EI
-\I  Allows us to step into John's shoes and see what he saw.
-
-\section{The Promise of Revelation}
-\I  Revelation is unique in that it promises and emphasizes blessing from the very beginning.
-\BI \I  ``he who reads and those who hear'', the proclaimer and the hearer,
-    \I  ``and keep those things which are written in it'', above all, the doer,
-    \I  ``for the time is near.'', there is an urgency to know and obey. \EI
-\I  The blessings are concentrated in the 7 letters to the churches in Asia Minor.
-\BI \I  Evaluation, ``I know your works'',
-    \I  Command, repent and hold fast,
-    \I  Blessing, ``to him who overcomes''. \EI
-
-\subsection{What is the blessing?}
-\I  Lead: We need to answer three questions regarding the blessing\ldots
-\I  New life in Christ, that you have Christ fully: 
-\BI \I  Jesus confesses you before the Father,
-    \I  not hurt by the second death,
-    \I  clothed in white garments, 
-    \I  to eat from the tree of life,
-    \I  to be given hidden manna to eat, and
-    \I  given the morning star. \EI
-\I  New identity in Christ, that Christ has you fully:
-\BI \I  given a white stone with a new name no one else knows,
-    \I  inscribed with the names of the Father, the Son, and the new Jerusalem,
-    \I  to be a pillar in the temple of God and never leave,
-    \I  to have power over the nations like Jesus, and
-    \I  to sit with Christ on His throne. \EI
-\I  Note: The blessing is attractive to the extent that we are attracted to Jesus.
-\BI \I  Which is why seeing Him in all His glory (as Revelation reveals Him to us)
-        is so critical to living a victorious Christian life. \EI
-
-\subsection{Who is the blessing for?}
-\I  Lead: Is it for select believers, or for the Church universal?
-\I  The blessing, essentially salvation in Jesus Christ, shows that it is for
-    all Christians.
-\I  At the same time, the blessing is for those who overcome.
-\BI \I This is confirmed by 1 John 5:4-5, 
-        which tells us that all true believers overcome the world (1 John 5:5). \EI
-\I  This means that there is no such thing as a 
-    perpetually disobedient or continually defeated Christian.
-\BI \I  Not that a believer does not sin, but that he repents when he sins.
-    \I  The two repeated commands in chapters 2 and 3 are to repent of the wrong,
-        and to hold fast to the good. \EI
-
-\subsection{How does the blessing matter?}
-\I  Lead: Casts the Christian life in an entirely different light from what we often consider; 
-        it shows us 
-\BI \I  what we are fighting for,
-    \I  who we are fighting against,
-    \I  how we must be victorious. \EI
-\I  Christ's commands are not optional.
-\I  The blessing gices us he power and motivation to overcome.
-
-\EI
 \end{document}

### 2012-07-22 sermons/Revelation1:4.tex
Updated sermon.

@@
 \BI
-\section*{The Need for Grace and Peace}
-\I one
+\section*{Introduction}
+\I Review v. 1-3:
+\BI \I  Person of Revelation: Jesus Christ,
+    \I  Purpose of Revelation: to show His servants,
+    \I  Power of Revelation: the word of God,
+    \I  Promise of Revelation: Blessed are those who hear and obey. \EI
 
-\section*{The Source of Grace and Peace}
-\I two
+\I  John then identifies Himself and His recipients and greets them with a blessing.
+\I  Read v. 4-8, and introduce the two main points.
+
+\section{The blessing of grace and peace}
+\subsection{What is the blessing?}
+\I  We can ask if the blessing is 
+\BI \I  a well-wishing? No.
+    \I  a prayer? No.
+    \I  referring to some past or future event? No. 
+    \I  the letter itself? Yes. \EI
+\I  Revelation itself is grace and peace to believers.
+\BI \I  In a way, John is saying ``Grace to you and peace'' while thrusting the letter into our hands. \EI
+\I  John tells us what category the letter belongs in, and what effect it should have in our lives,
+    namely grace and peace.
+\BI \I  Not fear and anxiety, or
+    \I  distress and mourning. \EI
+
+\subsection{Why are these important?}
+\I  These are two of the most dire needs of the believer.
+\BI \I  Grace: Undeserved favor from God.
+    \I  Peace: Steadfastness in trials. \EI
+\I  In what areas of your life do you most need grace and peace?
+\BI \I  In a family or marriage relationship?
+    \I  In a difficult situation at work?
+    \I  Dealing with a besetting sin?
+    \I  Health issue? \EI
+\I  John tells us that the source of grace and peace is God.
+\BI \I  That is to say Revelation is grace and peace to us because it points us to God. \EI
+\I  And so our most dire need is to know God, worship God, and obey God.
+\BI \I  John immediately gives us help in this passage by showing us who God is. \EI
+
+\section{The source of grace and peace}
+\I  The source of grace and peace is the triune God.
+\I  We will focus on the Father
+\BI \I  The phrase ``Him who is and who was and who is to come'' is unique to Revelation.
+    \I  Pregnant with meaning and endless in glory. \EI
+\I  That God is ``Him who is nad who was and who is to come'' means
+\BI \I  that He is eternal,
+    \I  that He is transcendent,
+    \I  that He is self-existent. \EI
+
+\subsection{God is eternal}
+\I  That is, He is eternally existent, He lives forever.
+\BI \I    
+\subsection{God is transcendent}
+\subsection{God is present}
 \EI

### 2012-07-22 sermons/Revelation1:4.tex
Finished sermon.

@@
 \BI
+\section*{Notes}
+\I  Remember to focus on...
+
 \section*{Introduction}
@@
 \BI \I  John immediately gives us help in this passage by showing us who God is. \EI
+\I Our problem is that our ``god'' is too small.
 
@@
     \I  Pregnant with meaning and endless in glory. \EI
-\I  That God is ``Him who is nad who was and who is to come'' means
+\I  That God is ``Him who is and who was and who is to come'' means
 \BI \I  that He is eternal,
@@
 \I  That is, He is eternally existent, He lives forever.
-\BI \I    
+\BI \I  ``who was'' stretches infinitely into the past,
+    \I  ``who is to come'' stretches infinitely into the future, and
+    \I  ''who is'' covers every moment in-between. \EI
+\I  And so the psalmist cries out in Psalm 90:2 \Q{Even from everlasting to everlasting, You are God.}
+\I  And it is because He is eternal that God can say in Revelation 1:8
+    \Q{``I am the Alpha and the Omega, the Beginning and the End,''
+        says the Lord, ``who is and who was and who is to come, the Almighty.''}
+\BI \I  Nothing and noone can exist before or after Him. \EI
+
+\I  Hand-in-hand with His eternality is that God is self-existent.
+\BI \I  If no one is before you, then there is nothing to support you.
+    \I  God simply \emph{is}. He is the self-existent One. \EI
+\I  This is what was revealed to Moses in Exodus 3:14 
+    \Q{And God said to Moses, ``I AM WHO I AM.'' And He said, 
+    ``Thus you shall say to the children of Israel, `I AM has sent me to you.' ''}
+\I  Colossians 1:17 shows us that God is both eternal and self existent
+    \Q{And He is before all things, and in Him all things consist.}
+\BI \I  He is the only truly independent One,
+    \I  Everything else depends on Him who is and who was and who is to come. \EI
+\I  This is our great God, the eternal One from whom we receive grace and peace.
+
 \subsection{God is transcendent}
+\I  Not just that He stretches across all time and eternity,
+    but that He is exalted above and beyond time itself.
+\I  To explain this, imagine that we had a string that represented all of time.
+\BI \I  That God is Him who is and who was and who is to come is not only that He is encompasses all of time and eternity,
+        but that He utterly transcends time.
+    \I  In other words, He is not just a thread that runs the length, and beyond, of the string,
+        but He is even the One who upholds the string. 
+    \I  He is outside (or transcendent above) time. \EI
+\I  James 1:17 \Q{\ldots with whom there is no variation or shadow of turning.}
+\I  Hebrews 13:8 \Q{Jesus Christ is the same yesterday, today, and forever.}
+\BI \I  Which does not simply mean that He passes through time without changing.
+    \I  No, He is outside of time.
+    \I  He stays the same because when we encounter Him, we are meeting One who transcends time itself. \EI
+\I  We are meeting Him who is and who was and who is to come,
+\BI \I  the eternal One, and
+    \I  the One who transcends time. \EI
+\I  The One who is outside of time and therefore the psalmist declares in Psalm 139:16
+    \Q{Your eyes saw my substance, being yet unformed. \\
+        And in Your book they all were written, \\
+        The days fashioned for me, \\
+        When as yet there were none of them.}
+\BI \I  Who else can say such things? \EI
+\I  A profound example of God's transcendence above time is found in John 8:58
+    \Q{Jesus said to them, ``Most assuredly, I say to you, before Abraham was, I AM.''}
+\BI \I  Not I was but I \emph{AM}.
+    \I  We could say that God is He who at this moment 
+    \BI \I  \emph{is} right now,
+        \I  \emph{is} in the past,
+        \I  \emph{is} in the future. \EI
+        \EI
+\I  Revelation 13:8 describes Jesus as
+    \Q{\ldots the Lamb slain from the foundation of the world.}
+    which really only makes sense for a God who transcends time.
+
 \subsection{God is present}
+\I  The title ``Him who is and who was and who is to come'' above accenting God's eternality and transcendence,
+    highlights his presence.
+\BI \I  Note that it does not say, ``who exists and who existed and who will exist''
+    \I  The emphasis is that ``He is'', that He is present. \EI
+\I  Although He transcends time, He is not removed from it, or out of contact with it.
+\BI \I  On the contrary, He is fully present at every point in space and time. \EI
+\I  The apostle Paul says this is Acts 17:27-28
+    \Q{\ldots He is not far from each one of us; for in Him we live and move and have our being, \ldots}
+\I  Psalm 139:8
+    \Q{If I ascend to heaven, You are there, \\ If I make my bed in hell, behold, You are there;}
+\BI \I  Not just that You know I'm there, but that You Yourself are there. \EI
+\I How is this possible? God is infinite
+\BI \I  Jeremiah 23:24 \Q{``Do I not fill heaven and earth?'' says the Lord.}
+    \I  1 Kings 8:27    \Q{But will God indeed dwell on the earth? Behold, heaven and the heaven of heavens cannot contain You.
+                How much less this temple which I have built!} 
+    \I There is no distance between us and God. \EI
+
+\I Revelation 14:10 \Q{He shall be tormented with fire and brimstone in the presence of the holy angels and in the presence of the Lamb.}
+\I  Revelation 21:3 \Q{\ldots He will dwell with them, and they shall be His people. God Himself will be with them and be their God.}
+
 \EI

### 2012-08-30 bible/Psalm1.tex
Added Psalm 1 notes.

\documentclass{article}
\newcommand{\BI}{\begin{itemize}\item}
\newcommand{\I}{\item}
\newcommand{\EI}{\end{itemize}}
\title{Psalm 1}

\begin{document}
\maketitle

\section{Summary of the text}
\subsection{What does it say?}
Psalm 1 contrasts the righteous and the wicked by
    \BI identifying who they are,
    \I  describing how they will live, and
    \I explaining why the contrast is so great. \EI
\subsection{Why is it there?}
This psalm is intentionally placed first
    in order to prepare us to worship God
    by first bringing us to repentance.
\subsection{How does it matter?}
Psalm 1 plays a critical role in the believers life in
    \BI discerning whether we are living 
            the life of the righteous or the wicked,
    \I  increasing our desire to live righteously, and
    \I  teaching how to do so. \EI

\end{document}

### 2012-09-22 sermons/Luke9:23-26.tex
Unfinished version of Luke 9 message.

\documentclass[12pt]{article}
\newcommand{\BI}{\begin{itemize}}
\newcommand{\EI}{\end{itemize}}
\newcommand{\I}{\item}
\newcommand{\Q}[1]{\begin{quote} #1 \end{quote}}
\begin{document}
\part*{Luke 9:23-26 -- Family Breakfast 2012}
\tableofcontents
\BI
\section*{Notes}
\I  Remember to drive the point home so that hearts are changed.
\I  Give comprehensive practical examples (application!).

\section{The radical, self-denying love we are to have for one another}
\I  We must first realize that, as His children, 
        God demands that we have 
        a radical, self-abasing love for one another.
\I  Philippians 2:3
    \Q{ Let nothing be done through selfish ambition or conceit, 
        but in lowliness of mind let each esteem others better than himself.}
\BI \I  It is a love that considers myself to be 
            the least important person in the room.
    \I  Everyone goes before me, because everyone is 
            more important and better than me.
    \I  Their needs, preferences, opinions, interests, and what they have to say
            are all more important than mine.
    \I  Last to be pleased, heard, considered, thanked, recognized, \ldots
    \I  First to serve, sacrifice, give way \dots 
        Since I am the most dispensable and least important one.
    \I  Goes against every part of my fleshly, worldly \EI

\I  John 13:14-15
    \Q{ If I then, your Lord and Teacher, have washed your feet, 
        you also ought to wash one another's feet.
        For I have given you an example, 
        that you should do as I have done to you.}
\BI \I  Not just an act of love on Jesus' behalf whereby He
            ``loved them to the end'' (John 13:1).
    \I  On the contrary, also an example for us to do as He did.
    \I  To be a common occurrence, even a pattern, among believers.
    \I  Similar to shining another's shoes,
            cleaning another's car,
            taking out another's garbage, or
            cleaning another's toilet -- but to the nth degree.
    \I  Jesus calls us to humiliate and debase ourselves for the good of another.
    \I  To treat ourselves as unworthy of respect and dignity,
            in order to work for the good of another. \EI

\I  1 John 3:16
    \Q{ By this we know love, because He laid down His life for us.
        And we also ought to lay down our lives for the brethren.}
\BI \I  The essence and definition of love.
    \I  Simply put, we are to die so that others may live,
            just as Christ laid down His life for us. \EI

\I  Is this what is missing in our churches, in our families, in our marriages, 
        and in our fellowship with one another?

\I  Namely, a lack of love in that we are not denying ourselves for one another?

\I  This is what our Lord Jesus Christ 
        calls, commands, and demands that we do for one another
        -- to die for one another.
\BI \I  This is what it means for a wife to submit to her husband:
    \BI \I  her preferences, desires, dreams 
        \I  where to go, what to do, how to live 
        \I  what she finds comfort and security in \EI
            all are sacrificed and lost in order to
            follow, obey, and submit to her husband.
    \I  This is what it means for a husband 
            to love his wife as Christ loved the Church:
    \BI \I  That your attitude is not that she exists to serve you,
            but that you exist to serve her.
        \I  That her needs, her wants, her likes and dislikes,
            her health, her happiness, and her well-being
            are more important than your own.
        \I  And so you give up your preferences, your ambitions,
            your dreams, your goals, your hobbies, your entertainment,
            and all rights to your time, and you die for her. \EI 
    \I  This is what it means for children to honor their parents:
    \BI \I  That you no longer decide what to do, how late to stay up, 
                who to hang out with, what to wear. \EI
        You give those up and die for your parents. \EI

\I  This kind of radical, self-debasing love does not come easy.

\I  We find the necessary help to obey God's Word \emph{in} God's Word --
        He supplies what He commands.

\section{The source of self-denying love}
\I  I want to take us upstream to see where this kind of love originates from,
    in the hope that it might be stirred up in us.

\I  Luke 9:23-26
    \Q{ Then He said to them all, 
        ``If anyone desires to come after Me,
        let him deny himself, and take up his cross daily, and follow Me.
        For whoever desires to save his life will lose it,
        but whoever loses his life for My sake will save it.
        For what profit is it to a man if he gains the whole world,
        and is himself destroyed or lost?
        For whoever is ashamed of Me and My words,
        of him the Son of Man will be ashamed when He comes in His own glory,
        and in His Father's, and of the holy angels.}

\subsection{The context}
\Q{ Then He said to them all, ``If anyone desires to come after Me, \ldots}
\I  The topic is \emph{salvation}, not sanctification.
\BI \I  He is speaking to those who are deciding whether to follow Him,
            not to those who are following Him already.
    \I  Laying out the terms of discipleship.
    \I  Reinforced by the fact that Jesus is speaking to the crowd, 
            not just to the twelve disciples. \EI
\I  Rewinding the tape back to salvation (and specifically to this passage), 
        in order to find the power to love one another in sanctification.

\subsection{The terms of discipleship}
\Q{ \ldots let him deny himself, and take up his cross daily, and follow Me.}
\I  Jesus gives two conditions that must be met in order to be his disciple.
\BI \I  To deny himself: unconditional surrender, and
    \I  To take up his cross: unconditional service.
    \I  Note that following Jesus only comes \emph{after} the two conditions. \EI

\I  The first term, ``\ldots let him deny himself, \ldots''
\BI \I  A casting off and forfeiting of all that you are.
    \I  An unconditional surrender of 
    \BI \I  what we want to do, 
        \I  how and when we want to do it,
        \I  where we want to go,
        \I  how we want to live. \EI
    \I  Jesus demands that we disown ourselves and 
            cast off any right to our own lives.
    \BI \I  When a father disowns a son, 
                that son no longer has a share in the father's inheritance.
        \I  When we disown ourselves,
                we no longer have a share \emph{in ourselves}. \EI
    \I  To strip ourselves of every right and freedom,
            and to come to Jesus as a helpless child. \EI

\I  The second term, ``\ldots and take up his cross daily, \ldots''
\BI \I  The first term was a casting off and the second is a taking up.
    \I  Unconditional service wherever and in whatever Jesus commands,
            even unto death. 
    \I  The disciple's life is not a stroll in the park but a death march where
    \BI \I  we must faithfully bear whatever cross our Lord lays upon us, and
        \I  we must faithfully go wherever our Lord leads us, 
        \I  to whatever end He has chosen for us. \EI
    \I  The term is, ``You must faithfully do whatever I have for you,
            even unto death''
    \BI \I  Revelation 2:10b
            \Q{ Be faithful until death, and I will give you the crown of life.} \EI
\EI

\ldots and follow Me.
\I  The conditions must be met before salvation and discipleship start.

\subsection{The principle}
For whoever desires to save his life will lost it, \ldots
\I  Note that no one can actually save their own life, 
        they can only desire/attempt to.

\ldots but whoever loses his life for My sake will save it.
\I  It must be for His sake!

\subsection{The reasoning}
For what profit is it to a man if he gains the whole world,
    and is himself destroyed or lost?
\I  We sacrifice only what we would inevitably lose anyways. 
    We make no \emph{true} sacrifice.

For whoever is ashamed of Me and My words,
    of him the Son of Man will be ashamed when He comes in His own glory,
    and in His Father's, and of the holy angels.

\section{The power of brotherly love}

\EI

\end{document}

### 2012-09-22 sermons/Luke9:23-26.tex
More sermon.

@@
 
-\ldots and follow Me.
-\I  The conditions must be met before salvation and discipleship start.
+\I  ``\ldots and follow Me.''
+\BI \I  These terms are universal. 
+        No one gets into God's kingdom without first submitting to these terms. 
+    \I  They are Jesus' prerequisite to becoming His disciple.
+    \I  And these are the terms you agreed to when 
+            God saved you and imputed His Son's righteousness on your behalf
+            if you are a true disciple of the Lord Jesus Christ. \EI
 
-\subsection{The principle}
-For whoever desires to save his life will lost it, \ldots
+\subsection{The disciple's treasure}
+\I  Now you may be wondering where the good news is,
+        and it is in verse 24.
+\Q{ For whoever desires to save his life will lose it,
+    but whoever loses his life for My sake will save it.}
+\I  ``For'' means that Jesus is explaining the previous verse.
+    He is giving the principle that undergirds verse 23.
+\I  He explains this principle from both a negative and positive
+        perspective.
+\I  Jesus starts with the negative,
+    ``For whoever desires to save his life will lose it,''
+\BI \I  This is the one who was unwilling to surrender his life 
+            to serve Jesus.
+    \I  Instead, he desired to save it, 
+    \EI
+
 \I  Note that no one can actually save their own life, 
@@
 
-\ldots but whoever loses his life for My sake will save it.
 \I  It must be for His sake!

### 2012-09-22 sermons/Luke9:23-26.tex
M.

@@
         perspective.
+
 \I  Jesus starts with the negative,
-    ``For whoever desires to save his life will lose it,''
-\BI \I  This is the one who was unwilling to surrender his life 
-            to serve Jesus.
-    \I  Instead, he desired to save it, 
+    ``For whoever desires to save his life will lose it,\ldots''
+\BI \I  Here, Jesus describes the one who, 
+            upon hearing the terms of discipleship,
+            no longer desires to be His disciple.
+    \I  He is unwilling to surrender his life to serve Jesus.
+    \I  Instead, this one desires to save his life.
+    \BI \I  To use his time to pursue his own goals and to do his own will. 
+        \I  Note the vanity of such a pursuit, that he cannot succeed in it,
+                but he can only \emph{desire} to save his life. \EI
+    \I  Instead, his end is that he loses the very life 
+            he was attempting to save.
+    \BI \I  Everything he gathered in this life is scattered upon his death, and
+        \I  he now experiences eternal judgement in hell. \EI
     \EI
 
-\I  Note that no one can actually save their own life, 
-        they can only desire/attempt to.
+\I  Jesus then explains the positive, 
+        ``\dots but whoever loses his life for My sake will save it.''
+\BI \I  This is the one who agrees to Jesus' terms of unconditional 
+            surrender and unconditional service.
+    \I  He loses his life because he has denied himself and 
+            has instead taken up a cross.
+    \BI \I  He may no longer please himself, or
+                even decide how to live.
+        \I  However, note that he has not simply thrown his life away,
+                but he has lost if \emph{for Jesus' sake}. \EI  
+    \I  His outcome is salvation and eternal life. \EI
 
-\I  It must be for His sake!
+\I  This answers the question of why someone would
+\BI \I  deny themselves,
+    \I  take up their cross, and
+    \I  lose their lives, \EI
+    to follow Jesus.
 
-\subsection{The reasoning}
-For what profit is it to a man if he gains the whole world,
-    and is himself destroyed or lost?
-\I  We sacrifice only what we would inevitably lose anyways. 
-    We make no \emph{true} sacrifice.
+\I  It is all in order to gain eternal life!
+\BI \I  In fact, their sacrifice was never truly a sacrifice
+            because of the surpassing value of the treasure
+            they received in return. \EI
 
-For whoever is ashamed of Me and My words,
-    of him the Son of Man will be ashamed when He comes in His own glory,
-    and in His Father's, and of the holy angels.
+\I  Was this not true of you?
+\BI \I  At the point of your salvation,
+            what drove you to renounce all that you were,
+            and to submissively commit yourself to all that Jesus
+            would have for you?
+    \I  Was it not because you were overwhelmed by the value of
+            salvation, so that your loss seemed very small indeed?
+    \I  Were you not willing, because of the riches of the treasure,
+            to part with all that you had in order to obtain it? \EI
 
-\section{The power of brotherly love}
+\I  The believer is empowered to deny himself by
+        beholding the surpassing riches of God's promised blessing.
+\BI \I  It is the greatness, extravagance, and sureness,
+            of God's promise that empowers the believer to
+            follow and obey! \EI
+
+\I  And if so at the moment of salvation,
+        should not it be ever more so after salvation?
+
+\section{The power to love}
+\I  Yes! Just as the power to deny ourselves and take up our cross was in
+        the promise of eternal life,
+        so the power to deny ourselves and obediently love one another now
+        lies in \emph{the promise of eternal life now}.
+
+\I  Remember, eternal life is not simply living forever, it is fellowship with God.
+\BI \I John 17:3
+        \Q{ And this is eternal life, that they may know You, 
+            the only true God, and Jesus Christ whom You have sent.} 
+    \I  Heaven is knowing God without any sin in the way! \EI
+
+\I  Therefore, what empowers a believer unto obedience is 
+        the blessing of a deeper and fuller communion with God.
+\BI \I  Or, the believer obeys in order to 
+            more richly experience eternal life \emph{now}. \EI
+
+\I  Philippians 3:8
+    \Q{ Yet indeed I also count all things loss for the excellence
+            of the knowledge of Christ Jesus my Lord,
+            and count them as rubbish, that I may gain Christ \ldots}
 

### 2012-09-22 sermons/Luke9:23-26.tex
Done.

@@
 
+\I  Jeremiah 9:23-24, man's greatest glory
+    \Q{ Thus says the LORD: "Let not the wise man glory in his wisdom, 
+        let not the mighty man glory in his might, 
+        nor let the rich man glory in his riches; 
+        but let him who glories glory in this, 
+        that he understands and knows Me, 
+        That I am the LORD, exercising lovingkindness, judgment, 
+        and righteousness in the earth. For in these I delight," says the LORD.}
+
+\I  Ephesians 4:13, the goal of the Church
+    \Q{ And He Himself gave some to be apostles, some prophets, 
+        some evangelists, and some pastors and teachers, 
+        for the equipping of the saints for the work of ministry, 
+        for the edifying of the body of Christ, till we all come 
+            to the unity of the faith 
+        and of the knowledge of the Son of God, to a perfect man, 
+        to the measure of the stature of the fullness of Christ; \ldots}
+
 \EI

### 2012-10-07 sermons/Revelation1:4b.tex
First part of new sermon done.

\documentclass[12pt]{article}
\newcommand{\BI}{\begin{itemize}}
\newcommand{\EI}{\end{itemize}}
\newcommand{\I}{\item}
\newcommand{\Q}[1]{\begin{quote} #1 \end{quote}}
\begin{document}
\part*{Revelation 1:4 --- Grace and Peace from God, Part 2}
    \Q{\ldots and from the seven Spirits who are before His throne, \ldots}

\tableofcontents
\BI
\section*{Notes}
\I  The goal of this sermon is
\BI \I  to show who the Holy Spirit is
    \I  and to persuade us to be filled with Him. \EI

\section*{Introduction}
\I  The greeting in Revelation 1:4-8 is very unique.
\I  The majority of similar greetings in New Testament letters
    are concise and do not contain deep theology.
\BI \I  For instance, in the majority of Paul's epistles,
        he greets his recipients with a version of 
        \Q{Grace to you and peace from God our Father and the Lord Jesus Christ.}
    \I  And we find similar greetings used by Peter, Jude, and John. \EI
\I  However, Revelation 1:4-8 is much longer and contains deep theology. 
\BI \I  In fact, the two phrases in verse 4, 
        ``Him who is and who was and who is to come'' and 
        ``the seven Spirits before His throne''
        are first mentioned here and are only found in Revelation. \EI
\I  John is pointing to the God he just experienced as the
    source and substance of the believer's grace and peace.

\section{What it means}
\subsection{His identity}
\I  He is divine.
\BI \I  Revelation 1:4 
    \BI \I  He is sandwiched between the first and second members of the Trinity.
        \I  The source of blessing of grace and peace in every epistle is 
            God and God alone. \EI
    \I  Revelation 4:5, the scene John is most directly referring to,
        \Q{\ldots Seven lamps of fire were burning before the throne,
            which are the seven Spirits of God.} \EI
\I  Although seen as seven He is a single entity.
\BI \I  He appears as seven only in Revelation and only 
        when He is \emph{visually seen}.
    \I  When He speaks or works, He is always one.
    \BI \I  Revelation 14:13
            \Q{ Then I heard a voice from heaven saying to me,
                ``Write: `Blessed are the dead who die in the Lord from now on.' ''
                ``Yes,'' says the Spirit, 
                ``that they may rest from their labors, 
                and their works follow them.''} 
        \I  Revelation 22:17
            \Q{ And the Spirit and the bride say, ``Come!''
                And let him who thirsts come.
                Whoever desires, let him take the water of life freely.} \EI \EI
\I  Therefore we conclude, along with the rest of the Scripture,
    that the seven Spirits is the one Holy Spirit.

\subsection{His perfection}
\I  Note first that the sight of the Spirit as seven or seven-fold is
    \emph{not} a mistake.
\BI \I  The Spirit did not make a mistake in showing Himself to John
        as being seven-fold.
        In fact, he intentionally revealed Himself to John as such multiple times.
    \I  Moreover, John understood its importance and intentionally mentions
        the seven-fold Spirit at the very very outset of the letter.
    \I  Therefore, it must be important for us to understand what
        it means that the Spirit is seven-fold. \EI
\I  We can understand the significance of the seven-fold Spirit
    by observing the Biblical pattern 
    in which God uses a seven-fold repetition or progression to 
    signify completion or perfection.
\BI \I  Psalm 12:6, the perfection of God's word.
        \Q{ The words of the Lord are pure words, \\
            Like silver tried in a furnace of earth, \\
            Purified seven times.}
    \I  Genesis 1, the perfect, finished work of creation in seven days.
    \I  Leviticus 4:6, the finished atonement for a particular sin
        (of the high priest in this case),
        \Q{ The priest shall dip his finger in the blood and sprinkle some 
            of the blood seven times before the Lord, in front of the veil 
            of the sanctuary} \EI
\I  Of course, just because something is repeated or progresses in seven parts
    does not automatically make it perfect.
\BI \I  Matthew 18:21
        \Q{ Then Peter came to Him and said,
            ``Lord, how often shall my brother sin against me,
            and I forgive him? 
            Up to seven times?''} 
    \I  Rather, it is used by God to signify that something is perfect or complete. 
    \I  God sometimes uses a seven-fold repetition or progression
        to communicate perfection or completion to us. \EI
\I  It should be no surprise, then, that God working in a seven-fold manner
    abounds in Revelation, since it is a book of consummation.
\BI \I  This is most prominent in the three sets (seals, trumpets, bowls)
        of seven-fold judgements of God upon wicked humanity.
    \I  Revelation 15:1
        \Q{ Then I saw another sign in heaven, great and marvelous;
            seven angels having seven last plagues,
            for in them the wrath of God is complete.} \EI
\I  From this pattern, we understand that the seven-fold nature of the Spirit 
    communicates His perfection and completeness.
\BI \I  Not in any way lacking in any attribute of God.
    \I  He posesses all of the attributes of the Godhead to the fullest extent.
    \I  He is God undiminished and unabridged. 
        Nothing of God is toned down or omitted in Him.
    \I  He is an eternal, infinite being since 
        to be completely and perfectly divine is to be infinite.
    \I  He is all-knowing, all-powerful, all-capable.
    \I  He is holy, loving, and sovereign.
    \I  There is nothing He does not know, or does not control.
    \I  He is the complete infinity of Almighty God. \EI
\I  That He has a seven-fold nature means that
\BI \I  He is infinite in glory, and
    \I  that He is deserving of an eternity of worship. \EI
\I  It also means that if we were to study the Holy Spirit, 
    there would always be more to learn, and experience of Him.
\I  Show that He is all-capable in the salvation and sanctification of the believer.

\subsection{His submission}
\I  The Bible shows that the seven-fold Spirit of God is equal in person to 
    the Father and Son;
    however, it does not necessarily mean that He is equal in position, or role.
\I  From Revelation, we learn that He is lesser in authority than the Father.
\BI \I  From 1:4 and 4:5 we see the Father as being on the throne,
        and the Spirit as being in front of it.
    \I  Of course, the One on the throne has the supreme authority. \EI
\I  We also learn that He is under the authority of the Son.
\BI \I  Revelation 5:6
        \Q{ And I looked, and behold, in the midst of the throne and 
            of the four living creatues,
            and in the midst of the elders,
            stood a Lamb as though it had been slain,
            having seven horns and seven eyes,
            which are the seven Spirits of God sent out into all the earth.}
        The Spirit is pictured as belonging to the Lamb.
    \I  Revelation 3:1 is explicit.
        \Q{ These things says He who has the seven Spirits of God and 
            the seven stars: \ldots} \EI
\I  While equal in person, the Spirit joyfully submits in position/authority
    to both the Father and the Son.
\BI \I  No explicit mention in any worship scene in Revelation.
    \I  Does not appear on a throne, as the Father and Son do.
    \I  Instead, he directs worship to the Father and Son,
        as Galatians 4:6 says,
        \Q{ And because you are sons, God has sent forth the Spirit of His Son
            into your hearts, crying out, ``Abba, Father!''}
        The Holy Spirit does not direct us to worship Him, but the Father. \EI

\subsection{His ministry}
\I  Revelation not only reveals the submissiveness of the Spirit
    but also His working.
\I  He is, in a sense, God on the move, or God on the offensive.
\BI \I  First notice that Revelation 1:4 and 5:6 show 
        that He is in front of the throne.
    \I  And then Revelation 5:6 tells us that He is ``sent out into all the earth''.
    \EI
\I  And from John's gospel we know that,
\BI \I  John 3:8, He is the One whose working is compared to the wind which
        \Q{ \ldots blows where it wishes, and you hear the sound of it,
            but cannot tell where it comes from and where it goes.
            So is everyone who is born of the Spirit.}
    \I  and, John 16:8, who convicts
        \Q{\ldots the world of sin, and of righteousness, and of judgement: \ldots}
    \EI
\I  We could say that his work is a constant, global, invisible assault 
    to the glory of the Father and the Son.
\I  Specifically, His ministry on earth is the propagation and application
    of the word of God.
\BI \I  In other words, to bring the Word forth and 
        to bring it to bear on the hearts of men. \EI
\I  In Revelation, He brings forth the Word by ministering to John.
\BI \I  Revelation 1:10 \Q{I was in the Spirit on the Lord's Day, \dots}
    \I  Revelation 4:2 \Q{Immediately I was in the Spirit; and behold,
                        a throne set in heaven, and One sat on the throne.}
    \I  Revelation 17:3 \Q{So he [the angel] carried me away in the Spirit
                        in the wilderness.}
    \I  Revelation 21:10 \Q{And he [the angel] carried me away in the Spirit to 
                            a great and high mountain,} 
    \I  This is an extremely direct case of 2 Peter 1:21
        \Q{ \ldots for prophecy nevercame by the will of man,
            but holy men of God spoke as they were moved by the Holy Spirit.} \EI
\I  In Revelation, we also see that He ministers to the churches by bringing
    the Word to bear on their hearts.
\BI \I  Revelation 2:7, 2:11, 2:17, 2:29, 3:6, 3:13, 3:22
        \Q{He who has an ear, let him hear what the Spirit says to the churches.}
    \I  The words spoken by Jesus, written down by John, and
        ultimately communicated and delivered with power by the Spirit. 
    \I  John 16:13-14
        \Q{However, when He, the Spirit of truth, has come,
            He will guide you into all truth;
            for He will not speak on His own authority,
            but whatever He hears He will speak;
            and He will tell you things to come.
            He will glorify Me,
            for He will take of what is Mine and declare it to you.} \EI

\section{Application -- How it matters}
\subsection{The Spirit indwells the believer}
\subsection{Be filled with the Spirit}
\EI

\end{document}

### 2012-10-07 sermons/Revelation1:4b.tex
.:wq

@@
     there would always be more to learn, and experience of Him.
-\I  Show that He is all-capable in the salvation and sanctification of the believer.
+\I  His perfection is manifest in that He provides virtually all that
+    we need as believers
+\BI \I  Titus 3:5, by the Spirit we experience the new birth (regeneration).
+        \Q{ \ldots but according to His mercy He saved us,
+            through the washing of regeneration and renewing of the Holy Spirit,
+            \ldots}
+    \I  Romans 8:16, the Spirit gives us assurance of our salvation.
+        \Q{The Spirit Himself bears witness with our spirit that we are children
+            of God, \ldots}
+    \I  Romans 8:13, by the Spirit we have victory of sin.
+        \Q{ \ldots but if by the Spirit you put to death the deeds of the body,
+            you will live}
+    \I  Galatians 5:22, the Spirit sanctifies us.
+        \Q{ But the fruit of the Spirit is love, joy, peace, longsuffering,
+            kindness, goodness, faithfulness, gentleness, self-control.}
+    \I  Romans 8:26, the Spirit intercedes for us.
+        \Q{ \ldots the Spirit Himself makes intercession for us with 
+            groanings which cannot be uttered.} \EI
 
@@
             into your hearts, crying out, ``Abba, Father!''}
-        The Holy Spirit does not direct us to worship Him, but the Father. \EI
+        The Holy Spirit does not direct us to worship Himself, but the Father. \EI
 
@@
 \subsection{The Spirit indwells the believer}
+\I  The Spirit indwells us, Colossian 1:27
+    \Q{To them God willed to make known what are the riches of the glory
+        of this mystery among the Gentiles: which is Christ in you,
+        the hope of glory.}
+\I  What does this mean
+\BI \I  Not physically, He is spirit after all.
+    \I  It is that the Spirit interacts and works through our
+        thoughts, attitudes and emotions.
+        He works at the core of our being.
+    \I  God is not simply making all things work together for our good
+        through external means.
+    \I  But the Spirit is directing our hearts and shaping our minds 
+        to bring us comfort and strengthen us within. \EI
+\I  Our greatest comfort and strength
+\BI \I  It assures us of His love for us, Ephesians 1:13-14
+        \Q{ In Him you also trusted, after you heard the word of truth,
+            the gospel of our salvation; in whom also,
+            having believed, you were sealed with the Holy Spirit of promise,
+            who is a guarantee of our inheritance until the redemption
+            of the purchased possession, to the praise of His glory.}
+        We will never be vanquished by an outside foe.
+    \I  It assures us that  \EI
+
 \subsection{Be filled with the Spirit}
+\I  Ephesians 4:18 
+    \Q{ And do not be drunk with wine, in which is dissipation;
+        but be filled with the Spirit.}
 \EI

### 2012-10-08 presentations/meta_book/Inverse_Methods.tex
Revised book chapter.

\documentclass[graybox]{svmult}

% choose options for [] as required from the list
% in the Reference Guide

\usepackage{mathptmx}       % selects Times Roman as basic font
\usepackage{helvet}         % selects Helvetica as sans-serif font
\usepackage{courier}        % selects Courier as typewriter font
\usepackage{type1cm}        % activate if the above 3 fonts are
                            % not available on your system
%
\usepackage{epic}
\usepackage{makeidx}         % allows index generation
\usepackage{graphicx}        % standard LaTeX graphics tool
                             % when including figure files
\usepackage{multicol}        % used for the two-column index
\usepackage[bottom]{footmisc}% places footnotes at page bottom

\usepackage{moreverb}

\usepackage{color}
\usepackage[table]{xcolor}
\definecolor{lightgray}{gray}{0.8}

%Flow Diagram Package
\usepackage[latin1]{inputenc}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows}

% see the list of further useful packages
% in the Reference Guide

\makeindex             % used for the subject index
                       % please use the style svind.ist with
                       % your makeindex program

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%-------------------------------------------%
\usepackage{hyperref}
\hypersetup{
    unicode = false,
    pdftoolbar = true,
    pdfmenubar = true,
    pdffitwindow = true,
    pdftitle = {Introduction},
    pdfauthor = {Kenneth Diest},
    pdfsubject = {Optimization},
    pdfnewwindow = true,
    pdfkeywords = {Optimization},
    colorlinks = true,
    linkcolor = blue,
    citecolor = blue,
    filecolor = blue,
    urlcolor = blue,
    breaklinks = true
}
%-------------------------------------------%

\usepackage[english]{babel}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{nicefrac}
\usepackage{wasysym}
\usepackage{multirow}
\usepackage{rotating}
%\usepackage[table]{xcolor}
%\definecolor{lightgray}{gray}{0.9}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{pgf}
\usepackage{geometry}
\usepackage{xspace}
\usepackage[justification=centering]{caption}

% Some custom commands.
\DeclareMathOperator*{\JLUminimize}{\text{minimize}}

\newcommand{\BE}{\begin{equation}}
\newcommand{\EE}{\end{equation}}
\newcommand{\BA}{\begin{eqnarray}}
\newcommand{\EA}{\end{eqnarray}}
\newcommand{\curl}{\nabla\times}
\newcommand{\minimize}[1]{\JLUminimize_{#1}\;&}
\newcommand{\subto}{\text{subject to}\;&}

% Custom figures.
% \newcommand{\myfig}[2]{\begin{figure}[!h]\includegraphics[width=0.95\textwidth]{fig/#1.jpg}\caption{#2}\label{fig:#1}\end{figure}}
\newcommand{\myfig}[2]{\begin{figure}[!h]\begin{center}\includegraphics[width=0.85\textwidth]{fig/#1}\caption{#2}\label{fig:#1}\end{center}\end{figure}}
\newcommand{\myfiglarge}[2]{\begin{figure}[!h]\begin{center}\includegraphics[width=0.95\textwidth]{fig/#1}\caption{#2}\label{fig:#1}\end{center}\end{figure}}
\newcommand{\myfigthree}[2]{\begin{figure}[!h]\begin{center}\includegraphics[width=0.73\textwidth]{fig/#1}\caption{#2}\label{fig:#1}\end{center}\end{figure}}

\newcommand{\BI}{\begin{itemize}\item}
%\newcommand{\I}{\item}
%\newcommand{\EI}{\end{itemize}}

\newcommand{\ER}[1]{\eqref{eq:#1}}
\newcommand{\SR}[1]{Section~\ref{sec:#1}}
\newcommand{\sR}[1]{section~\ref{sec:#1}}
\newcommand{\FR}[1]{Figure~\ref{fig:#1}}
\newcommand{\fR}[1]{figure~\ref{fig:#1}}

%-------------------------------------------%
\begin{document}
%-------------------------------------------%

%-------------------------------------------%
%          TITLE and AUTHORS         %
%-------------------------------------------%
\title*{
    Objective-First Nanophotonic Design
}
\author{
Jesse Lu and Jelena Vuckovic
}
\institute{Jesse Lu \at Department of Electrical Engineering, Stanford University, Palo Alto, CA 94305 \email{jesselu@stanford.edu}
\and  Jelena Vuckovic \at Department of Electrical Engineering, Stanford University, Palo Alto, CA 94305 \email{jela@stanford.edu}
}

%\setcounter{page}{0}
%\pdfbookmark[1]{Front page}{sec-front}
%\label{sec-front}

%\thispagestyle{empty}
\maketitle

%%-------------------------------------------%
                  ABSTRACT                 
%%-------------------------------------------%

We introduce an ``objective-first'' strategy 
    for designing nanophotonic devices,
    and we demonstrate the design of nanophotonic
    coupler, cloak, and mimic devices.  Our initial foray into design methods for nanophotonic devices
    began with a very simple and naive question: 
    could we make an inverse solver which,
    when given the electromagnetic fields we desire,
    returns the nanophotonic structure that will produce them?
In other words, since we already know how to solve for $E$ and $H$ 
    in Maxwell's equations, why can't we solve for $\epsilon$
    or even $\mu$ instead?  Not surprisingly, it did not take us long to find that such
    a simple strategy would inevitably run into many problems.

Over the subsequent years, we were able to come up with a better solution,
    which we call an ``objective-first'' strategy for nanophotonic design,
    and which we present in this chapter.
Although it is much more advanced than our original idea,
    objective-first design still carries the same fundamental concept,
    which is to specify the electromagnetic fields, and then
    to solve for a structure to produce them.  In this chapter, we present the simple theoretical underpinnings of 
    objective-first design in the first two sections,
    and then show examples of the method in action in the rest of the chapter.
We also include the source code that was used to generate
    all results presented herein.

\tableofcontents

%---------------------------------------------------------%
\section{Introduction}
\label{sec-intro}
%---------------------------------------------------------%

We introduce an ``objective-first'' strategy 
    for designing nanophotonic devices,
    and we demonstrate the design of nanophotonic
    coupler, cloak, and mimic devices.  Our initial foray into design methods for nanophotonic devices
    began with a very simple and naive question: 
    could we make an inverse solver which,
    when given the electromagnetic fields we desire,
    returns the nanophotonic structure that will produce them \cite{opex3}?
In other words, since we already know how to solve for $E$ and $H$ 
    in Maxwell's equations, why can't we solve for $\epsilon$
    or even $\mu$ instead?  Not surprisingly, it did not take us long to find that such
    a simple strategy would inevitably run into many problems.

Over the subsequent years, we were able to come up with a better solution,
    which we call an ``objective-first'' strategy for nanophotonic design,
    and which we present in this chapter.
Although it is more advanced than our original idea,
    objective-first design still carries the same fundamental concept,
    which is to specify the electromagnetic fields, and then
    to solve for a structure to produce them.

One of the strengths of this approach is that it recasts 
    the optimization problem into separably convex problems
    whose global optima can be reliably determined.  
Additionally, we show that our formulation is general enough 
    to encompasses the design of all linear nanophotonic structures 
    and is not limited to the design of optical metamaterials.
While this approach typically produces designs with very efficiencies 
    (typically 99/%)
    our solutions rely on continuously varying values of the dielectric constant 
    with respect to position across the optical structure being designed.  
Future approaches for dealing with this constraint are discussed 
    in Section \ref{sec:binary}.

In this chapter, we present the simple theoretical underpinnings of 
    objective-first design in the first two sections --
    namely the numerical discretization of the electromagnetic wave equation, and
    the formulation of the objective-first design problem.
Then, in Sections \ref{sec:wg}-\ref{sec:mimic}
    we show examples of the method in action in designing nanophotonic devices
    in three broad categories:
    waveguide couplers, optical cloaks, and optical mimics;
    the source code for which is available online\cite{code}.
Finally, in Section \ref{sec:extensions}, 
    we conclude by commenting on possible extensions to our method.

%---------------------------------------------------------%
\section{The Electromagnetic Wave Equation}
\label{sec-EWE}
%---------------------------------------------------------%

In this section, we outline the wave equation
    that is central to the application of our method,
    with the end-result being to show that it is 
    separably linear (bi-linear) in the field and structure variables.
We do this by first formulating this wave equation in the language of physics,
    and then discretizing it in order to achieve numerical solutions.
We then show how one can not only obtain the solution for the fields,
    but also obtain the solution for the structure using
    simple, standard numerical tools.

%---------------------------------------------------------%
\subsection{Physics Formulation}
%---------------------------------------------------------%

First, let's derive our wave equation,
    starting with the differential form of Maxwell's equations, 
\BA \curl E = - \mu_0 \frac{\partial H}{\partial t} \\
    \curl H = J + \epsilon \frac{\partial E}{\partial t}, \EA
    where $E$, $H$, and $J$ are 
    the electric, magnetic and electric current
    vector fields, respectively,
    $\epsilon$ is the permittivity
    and $\mu_0$ is the permeability, which we assume to be 
    that of vacuum everywhere.

Assuming the time dependence $\exp(-i \omega t)$, 
    where $\omega$ is the angular frequency,
    these become
\BA \curl E = - i \mu_0 \omega H \\
    \curl H = J + i \epsilon \omega E, \label{eq:H2E} \EA
    which we can combine to form our (time-harmonic) wave equation,
\BE \curl \epsilon^{-1} \curl H - \mu_0 \omega^2 H = \curl \epsilon^{-1} J. 
    \label{eq:wave} \EE

In this chapter, we are only going to consider the two-dimensional form
    of this equation, and specifically 
    the two-dimensional transverse electric (TE) mode \cite{taflove}.
In this case \ER{wave} is simplified 
    because only the $z$-component of $H$ is non-zero.
Nevertheless,  a single equation \ER{wave},
    represents all the physics which we take into account in this chapter.

%---------------------------------------------------------%
\subsection{Numerical Formulation}
%---------------------------------------------------------%

On top of the analytical formulation of the wave equation \ER{wave}
    we will now add a numerical, or discretized, formulation.
This will be needed in order to solve for arbitrary structures
    for which there are not analytical solutions.

The salient step in order to do so
    is to use the Yee grid \cite{yee}, 
    which allows us to easily define the curl $(\curl)$
    operators in \ER{wave}. 
Since both the individual curl operators and the equation as a whole
    is linear in $H$, we can reformulate \ER{wave}
    with a change of variables, as
\BE A(p)x = b(p), \label{eq:Ab} \EE 
    where $H \to x$, $\epsilon^{-1} \to p$; 
    and where
\BE A(p) = \curl \epsilon^{-1} \curl - \mu_0 \omega^2 \EE 
    and
\BE b(p) = \curl \epsilon^{-1} J. \EE
Note that our use of $A(p)$ and $b(p)$ instead of $A$ and $b$
    simply serves to clarify the dependence
    of both $A$ and $b$ on $p$.

Apart from using the Yee grid, the only other salient implementation detail
    is the use of
    stretched-coordinate perfectly matched layers \cite{pml}
    where necessary, in order to prevent unwanted reflections
    at the boundaries of the simulation domain.
The effect of such layers is to modify the curl operators,
    although their linear property is still maintained.

%---------------------------------------------------------%
\subsection{Solving for $H$}
%---------------------------------------------------------%

With our numerical formulation, we can now solve for the $H$-field
    (the $E$-field can be computed from the $H$-field using \ER{H2E})
    by applying general linear algebra solvers to \ER{Ab}.
Recall that since we have chosen a time-harmonic formulation,
    solving for $x$ in \ER{Ab} is actually performing what is simply known as
    a time-harmonic or a finite-difference frequency-domain (FDFD) simulation \cite{shin}. 
Furthermore, since we have limited ourselves to the two-dimensional case,
    \ER{Ab} is easily solved using the standard sparse solver
    included in Matlab on a single desktop computer.

We call the routine that solves for $x$ in \ER{Ab} given $p$ a field-solver,
    or a simulator.

%---------------------------------------------------------%
\subsection{Solving for $\epsilon^{-1}$}
%---------------------------------------------------------%

    After having built a field-solver or simulator
    (which finds $x$ given $p$) for our wave equation,
    the next step is to build a structure-solver for it.
In other words, we need to be able to solve for $p$ given $x$.

To do so, we return to \ER{wave}
    and remark that 
    $\epsilon^{-1} (\curl H) = (\curl H) \epsilon^{-1}$ and
    $\epsilon^{-1} J = J \epsilon^{-1}$ 
    since scalar multiplication is commutative.
This allows us to rearrange \ER{wave} as
\BE \curl (\curl H) \epsilon^{-1} - \curl J \epsilon^{-1}  = \mu_0 \omega^2 H  \EE
which we now write as 
\BE B(x)p = d(x), \label{eq:Bd} \EE 
    where
\BE B(x) = \curl (\curl H) - \curl J\EE
    and 
\BE d(x)  = \mu_0 \omega^2 H.  \EE

With this extremely simple trick,
    we have shown that we can seemingly solve for $p$ given $x$
    with approximately the same ease as solving for $x$ given $p$!
We see this because the dimensions and complexity of $B(x)$ are basically
    equivalent to that of $A(p)$,
    and this implies that the same simple tools used in our field-solver
    should be applicable to solving \ER{Bd}.
This is indeed what we find, although the later addition of constraints on $p$
    will require the use of more powerful (but just as dependable) numerical tools.

%---------------------------------------------------------%
\subsection{Bi-linearity of the Wave Equation}
%---------------------------------------------------------%

Although additional mathematical machinery must still be added
    to obtain a useful design tool,
    we have shown so far that the wave equation is 
    separately linear in $x$ and $p$ (i.e. bilinear).
Namely,
\BE A(p)x-b(p) = B(x)p - d(x). \label{eq:bilinear} \EE
In other words, fixing $p$ makes solving the wave equation for $x$
    a linear problem, and vice versa.
Note that the joint problem,
    where both $x$ and $p$ are allowed to vary,
    is not linear.

The bi-linearity of the wave equation
    is \emph{absolutely fundamental} in our objective-first strategy
    because it relies on the fact
    that, although simultaneously solving for $x$ and $p$ is very difficult,
    we already know how to solve linear systems ($x$ and $p$ separately) well.
In fact, it is this very property that forms the natural division of labor
    which our objective-first method exploits.

%---------------------------------------------------------%
\section{The Objective-first Design Problem}
%---------------------------------------------------------%

We now describe the remaining machinery used in the objective-first method,
    in addition to the field-solver and the structure-solver,
    as previously outlined.
Specifically, we introduce the idea of a design objective and a physics residual,
    and we reference the mathematical notion of convexity
    in order to motivate the need to divide the 
    objective-first problem into two separately convex sub-problems.

%---------------------------------------------------------%
\subsection{Design Objectives}
\label{sec:desobj}
%---------------------------------------------------------%

Our design objective or objective function, $f(x)$, is simply defined as
    a function we wish to be minimal 
    for the design to be produced.
For instance, in the design of a device
    which must transmit efficiently into a particular mode,
    we could choose $f(x)$ to be the negative power flow into that mode.
Or, if the device was to be a low-loss resonator,
    we could choose $f(x)$ to be the amount of power leaking 
    out of the device.
In general, there are multiple choices of $f(x)$
    which can be used to describe the same objective.
For example, $f(x)$ for a transmissive device 
    may not only be the negative power transmitted into the desired output mode,
    but it could also be the amount of power lost to other modes,
    or even the error in the field values at the output port
    relative to the field values needed for perfect transmission.
These design objectives are equivalent in the sense that, if minimized, 
    all would produce structures with good performance.
At the same time, we must consider that the computational cost and complexity
    of using one $f(x)$ over another may indeed vary greatly.

%---------------------------------------------------------%
\subsection{Convexity}
%---------------------------------------------------------%

Before formulating the design problem,
    we would like to add a note regarding the complexity of various 
    optimization problems.
Specifically, we want to introduce the notion of \emph{convexity} \cite{boyd}
    and to note the difference between problems that
    are convex and those which are not.
The difference is simply this:
    convex problems have a single optimum point
    (only one local optimum, which is therefore the global optimum)
    which we can reliably find using existing numerical software,
    whereas non-convex problems typically have multiple optima 
    and are thus much more difficult to reliably solve.

That a convex problem can be reliably solved, in this case, 
    means that regardless of the starting guess,
    convex optimization software will 
    always arrive at the globally optimal solution
    and will be able to numerically prove global optimality as well.
Thus, the advantage in formulating a design problem 
    in terms of convex optimization problems
    is to eliminate both the need to circumvent local optima and 
    any notion of randomness.
On a practical level, there exist mature convex optimization software packages
    among which is CVX, a convex optimization package written for Matlab \cite{cvx}, 
    which we use for the examples in this chapter.

%---------------------------------------------------------%
\subsection{Typical Design Formulation}
%---------------------------------------------------------%

We now examine the typical, and most straightforward formulation
    of the design problem,
    in order to relate and contrast it to the objective-first formulation.
The design problem for a physical structure is typically formulated as
\BA \minimize{x,p} f(x) \label{eq:typform} \\
    \subto A(p)x - b(p) = 0, \notag \EA
    \noindent which states that we would like to vary $x$ and $p$ simultaneously
    in order to decrease $f(x)$
    while always satisfying physics (e.g. the electromagnetic wave equation).

Since solving \ER{typform} is quite difficult in the general sense
    (simultaneously varying $x$ and $p$ makes the problem non-convex),
    traditional optimization approaches, such as those described in previous chapters, have relied on either a brute-force parameter search,
    or a gradient-descent method utilizing first-order derivatives.
In the gradient-descent case, solving \ER{typform} results in the
    well-known adjoint optimization method \cite{miller}.

%---------------------------------------------------------%
\subsection{Objective-first Design Formulation}
%---------------------------------------------------------%

In contrast with the typical formulation, the objective-first formulation 
    simply switches the roles of 
    the wave equation and the design objective with one another,
\BA \minimize{x,p} \| A(p) x - b(p) \|^2 \label{eq:ob1:1} \\
    \subto f(x) = f_\text{ideal}. \label{eq:ob1:2} \EA
Although such a switch may seem trivial,
    and even silly at first,
    we show that it fundamentally changes the nature of the design problem
    and actually gives us advantages in our efforts at finding a solution.

This first fundamental change, as seen from \ER{ob1:1},
    is that we allow for a non-zero residual in the electromagnetic wave equation.
This literally means that we allow for \emph{non-physical} $x$ and $p$,
    since $A(p) x - b(p) \ne 0$ is permissible.
And since $A(p) x - b(p)$ can now be a non-zero entity, 
    we choose to call it the \emph{physics residual}.  
The second fundamental change
    is that we always force the device to exhibit ideal performance,
    as seen from \ER{ob1:2}.
This, of course, ties in very closely with \ER{ob1:1} since
    ideal performance is usually not obtainable unless one
    allows for some measure of error in the underlying physics
    (non-zero physics residual).
As such, our strategy will be to iteratively vary $x$ and then $p$
    in order to decrease the physics residual \ER{ob1:1} to zero,
    while always maintaining ideal performance.

The primary advantage of the objective-first formulation is that,
    although the full problem is still non-convex,
    it allows us to form two convex sub-problems, as outlined below.
In contrast to an adjoint method,
    here we can still access information regarding
    second-order derivatives, which decreases the time it takes to 
    obtain a solution.
An additional advantage of this approach is that our insistence
    that ideal performance be always attained
    provides a mechanism
    which can potentially ``override'' local optima 
    in the optimization process.

To this end we have found that such a strategy
    results in surprisingly non-intuitive devices
    which exhibit highly efficient performance,
    even when the starting point of the design 
    problem is completely non-functional.
Furthermore, we have found this to be true
    even when the physics residual fails to be completely removed.

% From a numerical standpoint, 
%     although the objective-first formulation is still non-convex 
%     in its original form,
%     the bi-linearity of the physics residual term allows us to 
%     naturally break the original problem into two sub-problems
%     which we outline below.

In practice, we add an additional constraint to the original formulation, \cite{opex1}
    which is to set hard-limits on the allowable values of $p$,
    namely $p_0 \le p \le p_1$.
This is actually a relaxation of the ideal constraint,
    which would be to allow $p$ to only have discrete values,
    $p \in p_0, p_1$,
    but such a constraint would essentially force us to only
    perform brute force trial-and-error.

Our objective-first formulation is thus,
\BA \minimize{x,p} \| A(p) x - b(p) \|^2 \notag \\
    \subto f(x) = f_\text{ideal} \label{eq:ob1} \\
        & p_0 \le p \le p_1, \notag \EA
    which is still non-convex, but can be broken down into 
    two convex sub-problems, 
    the motivation being that each of these will be 
    able to be easily and reliably solved.

%---------------------------------------------------------%
\subsection{Field Sub-problem}
%---------------------------------------------------------%

The first of these is the field sub-problem, 
    which simply involves fixing $p$ and independently optimizing $x$,
\BA \minimize{x} \| A(p) x - b(p) \|^2 \label{eq:Fsub} \\
    \subto f(x) = f_\text{ideal}. \notag \EA
This problem is convex, and actually quadratic,
    which means that it can even be solved 
    using standard numerical tools, in the same way 
    as a simple least-squares problem.

The field sub-problem can be thought of as an update to $x$ (H-field)
    where we try to ``fit'' the electromagnetic fields to the structure ($p$).
Of course, if it were not for the hard-constraint on the design objective,
    the field sub-problem would be able to perfectly fit $x$ to $p$.

%---------------------------------------------------------%
\subsection{Structure Sub-problem}
%---------------------------------------------------------%

The second sub-problem is formulated by fixing $x$ and
    independently optimizing $p$.
At the same time, we use the bi-linearity property
    of the physics residual from \ER{bilinear}
    to rewrite the problem in a way that makes
    its convexity explicit,
\BA \minimize{p} \| B(x) p - d(x) \|^2 \label{eq:Ssub} \\
    \subto p_0 \le p \le p_1. \notag \EA
The structure sub-problem is also convex, but not quadratic because of the 
    inequality constraints on $p$.
However, use of the CVX package still allows us to obtain results
    quickly and reliably.

Note that in an analogous fashion to the field sub-problem,
    the structure sub-problem attempts to fit $p$ to $x$,
    and is prevented from perfectly doing so by its own constraint.
Because neither sub-problem is capable of completely reducing the physics residual
    to zero, they must be used in an iterative manner in order to
    gradually decrease the physics residual.
To this end, we employ the alternating directions optimization method.

%---------------------------------------------------------%
\subsection{Alternating Directions}
%---------------------------------------------------------%

We use a simple alternating directions scheme 
    to piece together \ER{Fsub} and \ER{Ssub},
    which is to say that we simply
    continually alternate between solving each equation until we reach some stopping point,
    normally measured by how much the physics residual has decreased.
\BA \text{Loop:} & & \notag \\ 
& \minimize{x} \| A(p) x - b(p) \|^2 \notag \\
 &    \subto f(x) = f_\text{ideal}. \notag \\ 
    \\
& \minimize{p} \| B(x) p - d(x) \|^2 \notag \\
    & \subto p_0 \le p \le p_1. \notag \EA
The alternating directions scheme is extremely simple
    and does not require additional processing
    of $x$ or $p$ outside of the two sub-problems,
    nor does it require the use of auxiliary variables.

The advantage of the alternating directions method
    is that the physics residual is guaranteed to
    monotonically decrease with every iteration,
    which is useful in that no safeguards
    are needed to protect against ``rogue'' steps
    in the optimization procedure.
Note that this robustness stems from the fact that,
    among other things,
    each sub-problem does not rely on previous values of 
    the variable which is being optimized,
    but only on the variable which is held constant.

The disadvantage of such a simple scheme is that 
    the convergence is quite slow,
    although we have found it to be sufficient in our cases.
Related methods, such as the Alternating Directions Method of Multipliers \cite{admm}, 
    exhibit far better convergence.

%---------------------------------------------------------%
\section{Waveguide coupler design}
\label{sec:wg}
%---------------------------------------------------------%

We first apply the objective-first formulation
    with the alternating directions algorithm
    to the design of nanophotonic waveguide couplers
    in two dimensions,
    where our goal is to couple light from
    a single input waveguide mode
    to a single output waveguide mode
    with as close to unity efficiency as possible.
We would also like to allow the user to choose arbitrary
    input and output waveguides,
    as well as to select 
    arbitrary modes within those waveguides
    (as opposed to allowing only the fundamental mode, for example).

This problem is very general and, in essence,
    encompasses the design of all linear nanophotonic components,
    because the function or performance of all such components
    is simply to convert a defined set of input modes
    into a defined set of output modes.
Such a broad, general problem is ideally suited for 
    an objective-first strategy,
    since no approximations or simplifications
    of the electromagnetic fields are required;
    we only make the simplification of working in two dimensions
    (transverse magnetic mode)
    and dealing only with a single input and output mode.

Since the electromagnetic wave equation is scale-invariant
    (e.g. double the length scale and half the frequency and
    you obtain the same equation)
    we state all dimensions terms of the vacuum wavelength itself.
Therefore, our solutions are applicable to regions of the electromagnetic spectrum
    where the dielectric constants used are achievable.
In most cases, values between 1 and 12.25 are chosen because these are realizable
    for semiconductor devices operating at telecommunication frequencies.
Finally, note that dispersive effects are ignored for all results in this chapter
    since we always consider device performance at a single, fixed frequency.

%---------------------------------------------------------%
\subsection{Choice of Design Objective}
%---------------------------------------------------------%

As mentioned in \SR{desobj} multiple equivalent choices
    of design objective exist which should allow one
    to achieve the same device performance;
    however, we will choose, for generality, the following design objective,
\BE f(x) = \begin{cases}
        x - x_\text{perfect} & \text{at boundary}, \\
        0 & \text{elsewhere},
        \end{cases} \EE
That is, $f(x)$ simply selects the outermost values of the field
    in the design space
    and compares them to values of a perfect device.

Furthermore, we choose $f_\text{ideal} = 0$ so that
    when placed into the objective-first problem \ER{ob1},
    this will result in fixing the boundary values of the field
    at the edge of the design space
    to those of an ideal device,
    as shown in \FR{wg/intro}.
In this case, we choose such an ideal device
    to have perfect (unity) coupling efficiency,
and these ideal fields are simply obtained by using
    the input and output mode profiles at the corresponding ports
    and using values of zero at the remaining ports.

\myfiglarge{wg/intro}{Formulation of the design objective.}

Such a design objective is general
    in the sense that the boundary values of the device 
    contain all the information necessary to determine
    how the device will interact with its environment,
    when excited with the input mode in question.
In other words,
    we only need to know the boundary field values,
    and not the interior field values to determine 
    the performance of the device;
    and thus, it would be conceivable that such a scheme
    might be generally applied to linear nanophotonic devices beyond 
    just waveguide mode couplers.

In our case,
    we only need to know the value of $H_z$ and 
    its derivative along the normal direction, $\partial H_z / \partial n$,
    along the design boundary
    in order to completely characterize its performance.
Alternatively,
    one can, of course, use the outermost two layers of the $H_z$
    instead of calculating a spatial derivative.

%---------------------------------------------------------%
\subsection{Application of the Objective-first Strategy}
%---------------------------------------------------------%

Having chosen our design objective we apply
    the alternating directions algorithm to \ER{ob1} which 
    results in solving the following two sub-problems iteratively:
\BA \minimize{x} \| A(p) x - b(p) \|^2 \\
    \subto x = x_\text{perfect} \text{, at boundary} \notag \EA
\BA \minimize{p} \| B(x) p - d(x) \|^2 \\
    \subto p_0 \le p \le p_1 \notag \EA

For the results throughout this chapter, 
    we uniformly choose $p_0 = 1/12.25$ and $p_0 = 1$,
    corresponding to $\epsilon^{-1}$ of silicon and air respectively.
Additionally, since a starting value for $p$ is initially required,
    we always choose to use a uniform value of $p = 1/9$ 
    across the entire design space.
There is nothing really unique about such a choice,
    although we have noticed that an initial value of $p$ near 1 
    often results in poor designs.
Note, that, unlike $p$, we do not require an initial guess for $x$.
The only other significant value that needs to be set initially
    is the frequency, or wavelength of light.
We use free space wavelengths in the range of 25 to 63 grid points for
    the results in this chapter.
Lastly, for all the examples presented in the chapter,
    we run the alternating directions algorithm for 400 iterations.
Although we do not present the convergence results here,
    such information can be obtained by inspecting the source code \cite{code}.

%---------------------------------------------------------%
\subsection{Coupling to a Wide, Low-index Waveguide}
%---------------------------------------------------------%

As a first example, we design a coupler from 
    the fundamental mode of a narrow, high-index waveguide
    to the fundamental mode of a wide, low-index waveguide.
Such a coupler would be useful for coupling from 
    an on-chip nanophotonic waveguide to
    an off-chip fiber for example.

\myfig{wg/1}{Coupler to a wide low-index waveguide.
            Efficiency: 99.8\%, 
            device footprint: $36 \times 76$ grid points, 
            wavelength: 42 grid points.}

The input and output mode profiles used as
    the ideal fields are shown in the upper-left corner of \FR{wg/1}.
The final structure is shown in the upper right plot, and
    the simulated $H_z$ fields,
    under excitation of the input mode in this final structure,
    are shown in the bottom plots.

\FR{wg/1} then shows that the design structure has nearly unity efficiency (99.8\%)
    and converts between the input and output modes
    within a very small footprint (roughly 1.5 square vacuum wavelengths).

%---------------------------------------------------------%
\subsection{Mode Converter}
%---------------------------------------------------------%

In addition to coupling to a low-index waveguide,
    we show that we can successfully apply the objective-first method
    to convert between modes of a waveguide.
We do this by simply selecting the output mode 
    in the design objective to be the second-order waveguide mode,
    as seen in \FR{wg/2}.
    Note that the design of this coupler is made challenging
    because of the opposite symmetries of the input and output modes.
Moreover, because our initial structure is symmetric,
    we initially have 0\% efficiency to begin with.
Fortunately, the objective-first method can still design
    an efficient (98.0\%) coupler in this case as well
    in a footprint of less than two square vacuum wavelengths.
\myfig{wg/2}{Mode converter.
            Efficiency: 98.0\%, 
            device footprint: $36 \times 76$ grid points, 
            wavelength: 42 grid points.}

%---------------------------------------------------------%
\subsection{Coupling to an Air-core Waveguide Mode}
%---------------------------------------------------------%

We can then continue to elucidate the generality of our method
    by coupling between waveguides which confine light 
    in completely different ways.
    \FR{wg/3} shows  a high-efficiency coupling device between 
    an index-guided input waveguide and
    a ``air-core'' output waveguide, 
    in which the waveguiding effect is achieved using distributed Bragg reflection
    (instead of total internal reflection as in the input waveguide).

In this case, the device footprint is increased to 4.3 square vacuum wavelengths
    and the final efficiency is 98.9\%.

\myfig{wg/3}{Coupler to a wide low-index waveguide.
            Efficiency: 98.9\%, 
            device footprint: $36 \times 76$ grid points, 
            wavelength: 25 grid points.}

%---------------------------------------------------------%
\subsection{Coupling to a metal-insulator-metal and metal wire plasmonic waveguides }
%---------------------------------------------------------%

Additionally, our design method can also generate couplers
    between different material systems such as 
    between dielectric and metallic (plasmonic) waveguides,
    as shown in \FR{wg/4} (97.5\% efficiency).
In this case, the permittivity of the metal ($\epsilon = -2$) is chosen to be 
    near the plasmonic resonance ($\epsilon = -1$).

Extending this method to include plasmonic wire waveguides, 
    \FR{wg/5} shows that efficiently coupling to this type of structure 
    is achievable as well (99.1\% efficiency).

\myfig{wg/4}{Coupler to a plasmonic metla-insulator-metal waveguide.
            Efficiency: 97.5\%, 
            device footprint: $36 \times 76$ grid points, 
            wavelength: 25 grid points.}
\myfig{wg/5}{Coupler to a plasmonic wire waveguide.
            Efficiency: 99.1\%, 
            device footprint: $36 \times 76$ grid points, 
            wavelength: 25 grid points.}

%---------------------------------------------------------%
\section{Optical Cloak Design}
%---------------------------------------------------------%

In the previous section,
    we showed that couplers between virtually any two waveguide modes
    could be constructed using the objective-first design method,
    and based on the generality of the method
    one can guess that it may also be
    able to generate designs for any linear nanophotonic device.
Now, we extend the applicability of our method
    to the design of metamaterial devices which operate in free-space.
In particular,
    we adapt the waveguide coupler algorithm to the 
    to the design of optical cloaks.

%---------------------------------------------------------%
\subsection{Application of the Objective-first Strategy}
%---------------------------------------------------------%

Adapting the method used in \SR{wg} to the design of optical cloaks
    really only requires one to change the simulation environment
    to allow for free-space modes.
This is accomplished by modifying the upper and lower boundaries
    of the simulation domain from absorbing boundary conditions
    to periodic boundary conditions,
    which allows for plane-wave modes to propagate without loss
    until reaching the left or right boundaries,
    where absorbing boundary conditions are still maintained.

In terms of the design objective, 
    we allow the device to span the entire height of the simulation domain,
    and thus consider only the leftmost and rightmost planes as boundary values.
Specifically, for this section the input and output modes are plane waves
    with normal incidence, 
    as can be expected for good cloaking devices.
The achieved results all yield high efficiency,
    although we note that the cloaking effect is only measured
    for a specific input mode.
That is to say, just as the waveguide couplers previously designed
    were single-mode devices,
    so the cloaks designed in this section are also ``single-mode'' cloaks.
An additional modification, as compared to \SR{wg}, is that
    we now prevent the structure from being modified in certain areas
    which contain the object to be cloaked.
With these simple changes we continue to solve \ER{ob1}
    with the alternating directions algorithm
    in order to design optical cloaks
    instead of waveguide couplers.
Once again, as in \SR{wg}, each design is run for 400 iterations
    with a uniform initial value of $p = 1/9$ for the structure
    (where the structure is allowed to vary),
    and the range of $p$ is limited to $1/12.25 \le p \le 1$,
    implying a dielectric cloak.

%---------------------------------------------------------%
\subsection{Anti-reflection Coating}
%---------------------------------------------------------%

As a first example,
    we attempt to design the simplest and most elementary ``cloaking'' device available,
    which, we argue, is a simple anti-reflection coating;
    in which case the object to be cloaked is nothing more than
    the interface between two dielectric materials.
In this case we use the interface between air and silicon, as shown in \FR{cloak/c1}
\myfig{cloak/c1}{Anti-reflection coating.
                Efficiency: 99.99\%,
                device footprint: $60 \times 100$ grid points,
                wavelength: 63 grid points.}

Unsurprisingly for such a simple case, 
    we achieve a very high efficiency device.
Note also that the efficiency of the device can be deduced by eye,
    based on the absence of reflections or standing waves 
    in bottom two plots of \FR{cloak/c1}.

%---------------------------------------------------------%
\subsection{Wrap-around Cloak}
%---------------------------------------------------------%

Next, we design a cloak for a plasmonic cylinder,
    which is quite effective at scattering light
    as can be seen from \FR{cloak/c6},
    where we show that the uncloaked cylnder,
    although subwavelength in size, scatters
    the majority of light away from the desire output (plane-wave) mode.
\myfig{cloak/c6}{Plasmonic cylinder to be cloaked. 
                68.5\% of light is diverted away from the desired output mode.}

In designing the wrap-around cloak,
    we allow the structure to vary at all points within the design area
    except in the immediate vicinity of the plasmonic cylinder.
Application of the objective-first strategy results
    in an efficient (greater than 99\%) device as seen in \FR{cloak/c2}.
\myfig{cloak/c2}{Wrap-around cloak.
                Efficiency: 99.99\%,
                device footprint: $60 \times 100$ grid points,
                wavelength: 42 grid points.}
Note that our cloak employs only isotropic, non-magnetic materials,
    and at the same time it is specific to a particular input
    and to a particular object.
That is to say, it is a single-frequency, single-mode, and single-object 
    cloaking device.

%---------------------------------------------------------%
\subsection{Open-channel Cloak}
%---------------------------------------------------------%

With a simple modification, from the previous example,
    we can design a cloak which features an open channel
    to the exterior electromagnetic environment (\FR{cloak/c4}).
This simple modification creates an air gap that
    connects the cylinder to the outside world
    both from the front and back and
    may be useful in the case where one would like to
    remove or replace the cloaked object.

\myfig{cloak/c4}{Open-channel cloak.
                Efficiency: 99.8\%,
                device footprint: $60 \times 100$ grid points,
                wavelength: 42 grid points.}
Such a design is still very efficient (greater than 99\% efficiency)
    and demonstrates the usefulness of the objective-first strategy
    in cases where other methods, such as transformation optics,
    may require use of the entire space around the object
    to be cloaked.

%---------------------------------------------------------%
\subsection{Channeling Cloak}
%---------------------------------------------------------%

Our last cloaking example replaces the plasmonic cylinder 
    with a thin metallic wall in which a sub-wavelength channel is etched.
Such a metallic wall is very effective at blocking incoming light
    (as can be seen from \FR{cloak/c7} where more than 99\%
    of the incoming light is blocked) 
    because of its large negative permittivity ($\epsilon = -20$),
    meaning that any cloaking device would be forced to channel
    all the input light into a very small aperture
    and then to flatten that light out into a plane wave again.
\myfig{cloak/c7}{Metallic wall with sub-wavelength channel to be cloaked.
                99.9\% of the light is blocked from the desired output plane-wave.}

Once again, our method is able to produce a design with efficiency greater
    than 99\%, as shown in \FR{cloak/c5}.
\myfig{cloak/c5}{Channeling cloak.
                Efficiency: 99.9\%,
                device footprint: $60 \times 100$ grid points,
                wavelength: 42 grid points.}

%---------------------------------------------------------%
\section{Optical Mimic Design}
\label{sec:mimic}
%---------------------------------------------------------%

We now apply our objective-first strategy to the design of optical mimics.
We define an optical mimic to be a linear nanophotonic device which 
    mimics the output field of another device.
In this sense optical mimics are anti-cloaks;
    where cloaks strive to make an object's electromagnetic presence vanish,
    mimics strive to implement an object's presence without that 
    object actually being there.

As such, the design of optical mimics provides a tantalyzing approach
    to the realization of practical metamaterial devices.
That is to say, if one can reliably produce practical optical mimics,
    then producing metamaterials can be accomplished by 
    simply producing an optical mimic of that material.
In a more general sense, 
    designing optical mimics is really just a recasting of the thrust of 
    the objective-first design strategy in its purest form:
    the design of a nanophotonic device based purely 
    on the electromagnetic fields one wishes to produce.
As such, devices which perform well-known optical functions
    (e.g. focusing, lithography) can also be designed.

%---------------------------------------------------------%
\subsection{Application of the Objective-first Strategy}
%---------------------------------------------------------%

The objective-first design of optical mimics proceeds in virtually
    an identical way to the design of optical cloaks,
    the only difference being that the output modes are 
    specifically chosen to be those that produce the desired function.
For most of the examples provided, the input illumination is still an incident plane wave.
Lastly, instead of measuring efficiency, 
    we measure the relative error of the simulated field
    against that of a perfect target field
    at a relevant plane some distance away from the device.
The location of this plane is identified as a dotted line in the subsequent figures.

%---------------------------------------------------------%
\subsection{Plasmonic Cylinder Mimic}
%---------------------------------------------------------%

Our first design is simply to mimic the plasmonic cylinder 
    which we cloaked in the previous section.
\FR{mimic/m1} shows the result of the design.

The final structure is shown in the upper right plot,
    while the ideal field and the simulated field
    are shown in the middle and bottom plots.
Note that the ideal field is cut off to emphasize 
    the fields to the right of the device (the output fields).
Also, the magnitude of the fields are compared at the 
    dotted black line at which point the relative error
    is also calculated.
For this simple, initial mimic, the simulated field
    quite closely imitates that produced by a single plasmonic cylinder (8.1\% error)

    \myfig{mimic/m1}{Plasmonic cylinder mimic (see \FR{cloak/c6} for the original object). 
                Error: 8.1\%,
                device footprint: $40 \times 120$ grid points,
                wavelength: 42 grid points.}
\clearpage

%---------------------------------------------------------%
\subsection{Diffraction-limited Lens Mimic}
%---------------------------------------------------------%

We now design a mimic for a typical diffraction-limited lens.
In this case, the object which we wish to mimic does not require simulation
    since the fields of a lens can be readily computed.
For the three figures below, 
    the computed ideal fields are shown as the target fields.

\FR{mimic/m3} shows the mimic of a lens with relatively moderate focusing. 
In such a lens, the focusing action is gradual and easily discernible
    by eye.
The computed error in this case is 12.0\%.

In constrast, \FR{mimic/m4} and \FR{mimic/m5} are both mimics of
    a lens with a smaller half-wavelength spot size.
Such a lens is much harder to design, 
    because of the high-frequency spatial components involved;
    and yet, we show that an objective-first strategy can 
    produce successful designs (5.6\% and 1.4\% error)
    and that this is achievable at both shorter and longer focal depths.
\myfigthree{mimic/m3}{Full-width-half-max at focus: 1.5 $\lambda$,
                focus depth: 100 grid points.
                Error: 12.0\%,
                device footprint: $40 \times 120$ grid points (1.6 $\lambda$ thick),
                wavelength: 25 grid points.}

\myfigthree{mimic/m4}{Full-width-half-max at focus: 0.5 $\lambda$,
                focus depth: 50 grid points.
                Error: 5.6\%,
                device footprint: $40 \times 120$ grid points (1.6 $\lambda$ thick),
                wavelength: 25 grid points.}
\myfigthree{mimic/m5}{Full-width-half-max at focus: 0.5 $\lambda$,
                focus depth: 150 grid points.
                Error: 1.4\%,
                device footprint: $40 \times 120$ grid points (1.6 $\lambda$ thick),
                wavelength: 25 grid points.}
\clearpage

%---------------------------------------------------------%
\subsection{Sub-diffraction Lens Mimic}
%---------------------------------------------------------%

Our method is now employed to mimic the effect of a sub-diffraction lens.
Since such a lens can be created using a negative-index material
    this mimic can be viewed as an imitation of a negative-index material,
    in that the following device recreates the sub-diffraction target-field 
    at the output plane (dotted line)
    when illuminated by the same target field at the input of the device.
In other words,
    this device is an image-specific sub-diffraction imager,
    which is another way of saying that it is a single-mode imager.
\myfig{mimic/m2}{Sub-diffraction lens mimic.
                The target field has a full-width half-maximum of 0.14 $\lambda$.
                Error: 28.6\%,
                device footprint: $60 \times 120$ grid points (1.43 $\lambda$ thick),
                wavelength: 42 grid points.}

As \FR{mimic/m2} shows,
   we are able to recreate the target field at the output,
   albeit with higher error (28.6\%).
Although the error in this example is larger,
    the field produced by the device has a full-width half-maximum
    nearly equal to that of the target field.

Note that the target field is created simply by placing 
    the imaging field at the output plane.
Also note that, as expected, 
    the output field decays very quickly since,
    for such a deeply subwavelength field,
    it is composed primarily of evanescently decaying modes.

%---------------------------------------------------------%
\subsection{Sub-diffraction Optical Mask}
%---------------------------------------------------------%

Lastly, we extend the idea of a sub-diffraction lens mimic
    one step further and
    design a sub-diffraction optical mask.
Such a device takes a plane wave as its input and
    produces a sub-diffraction image at its output plane.
Of course, akin to its lens counterpart,
    this output plane must lie within the near-field 
    of the device (specifically, two computational cells away)
    because of its sub-wavelength nature.
    \FR{mimic/m6} shows the design of a simple mask which 
    successfully produces three peaks at its output
    with an error of 19.8\%.
\myfig{mimic/m6}{Sub-diffraction optical mask.
                The three central peaks in the target field are each
                separated by 0.28 $\lambda$.
                Error: 19.8\%,
                device footprint: $40 \times 120$ grid points,
                wavelength: 25 grid points.}

%---------------------------------------------------------%
\section{Extending the Method}
\label{sec:extensions}
%---------------------------------------------------------%

The objective-first method, as applied in the examples in this chapter,
    represents only a small foray into the area of nanophotonic design.
Several key extensions to what is presented here are needed to
    fully address real-world nanophotonic design challenges.

%---------------------------------------------------------%
\subsection{Three-dimensional Design}
%---------------------------------------------------------%

The first of these is the need to design fully three-dimensional structures.
Doing so provides no inherent difficulties aside from the matrices in
    \ER{Ab} becoming very large.
This is not insurmountable as electromagnetic simulation software for 
    three-dimensional nanophotonic structures already exists.

In fact, for certain choices of the design objective 
    (i.e. those of low-rank) 
    \ER{Fsub} can be efficiently solved by a small number of calls
    to unmodified simulation software. 
Of course, for general design objectives, such software will need 
    to be modified in order to solve \ER{Fsub}.

On the other hand, specialized software to solve \ER{Bd} in 
    any number of dimensions does not exist,
    although this was not a problem in two dimensions since generic 
    linear algebra solvers are more than accurate.
In three dimensions, 
    the large size of matrix $B(x)$ can be greatly compressed by considering
    only fabrication processes which modify a structure in-plane.
In this way, the degrees of freedom in $p$ can be greatly reduced and the original
    methods used in this chapter can still be applied.
This work-around is especially appealing since in-plane structures are 
    significantly less challenging to fabricate.

%---------------------------------------------------------%
\subsection{Multi-mode}
%---------------------------------------------------------%

A second necessary extension is to be able to consider the multiple fields
    that a structure produces in response to input fields of differing frequency
    and spatial distribution.
Such an extension is straightforward in the objective-first formulation
    and results in the following modified problem statement,
\BA \minimize{x_i,p} \sum_i \| A(p) x_i - b(p) \|^2 \notag \\
    \subto f(x_i) = f_{i,\text{ideal}} \quad \text{i = 1, \ldots, n} \\
        & p_0 \le p \le p_1, \notag \EA
    which can be separated into field and structure sub-problems 
    as in the single-mode formulation.
In the multi-mode case, this results in one structure sub-problem 
    and $n$ field sub-problems.
Interestingly, the $n$ field sub-problems lend themselves 
    naturally to parallelization
    since they can be solved independently,
    leading to the possibility that a multi-mode design completing in
    roughly the same time as a single-mode design.

%---------------------------------------------------------%
\subsection{Binary Structure}
\label{sec:binary}
%---------------------------------------------------------%

Another necessary extension of our method is to force 
    the values of $p$ to be discrete.
This is not trivial since a naive restatement of \ER{ob1}
    which includes such a constraint,
\BA \minimize{x,p} \| A(p) x - b(p) \|^2 \notag \\
    \subto f(x) = f_\text{ideal} \\
        & p \in \{p_0, p_1\}, \notag \EA
    results in a very difficult combinatorial problem.

Tractable approaches include penalizing intermediate values of $p$ \cite{simp}
    or even transferring to a level-set method \cite{miller}
    where the distinction between materials is explicit.

%---------------------------------------------------------%
\subsection{Robustness}
%---------------------------------------------------------%

Lastly, the design of structures which are robust to both
    fabrication imperfections and fluctuations in environmental parameters
    is also a necessity for practical real-world devices.

It seems likely in this case that a heurestic approach may
    be most successful in this case, rather than tackling 
    the problem head-on.
For instance, to account for fluctuating material parameters
    induced by temperature changes
    one may design a device that operates over a 
    larger bandwidth than is actually required.

%---------------------------------------------------------%
\section{Conclusions}
%---------------------------------------------------------%

We have introduced an objective-first approach
    to the design of nanophotonic components, and
    applied it to the design of waveguide couplers,
    optical cloaks, and optical mimics.
In doing so, we hope to have exhibited both the simplicity
    and the breadth of our method to the design of a broad
    class of linear, single-mode devices.
In addition to posting the source code for all the examples online \cite{code}, 
    we have outlined the necessary extensions of our method in order
    to design practical, three-dimensional devices.

%---------------------------------------------------------%
\begin{acknowledgement}
This work has been supported by the 
    AFOSR MURI for Complex and Robust On-chip Nanophotonics 
    (Dr. Gernot Pomrenke), grant number FA9550-09-1-0704; 
    and the Alexander von Humboldt Foundation.
\end{acknowledgement}
%---------------------------------------------%
%                REFERENCES                 %
%----------------------------------------------%

%--------------------------------------------------%
%\bibliographystyle{plain}
%\bibliography{GAbib}
%\pdfbookmark[1]{References}{sec-refs}
\begin{thebibliography}{99.}%

\bibitem{opex3} J.Lu, and J. Vuckovic,
    ``Objective-first design of high-efficiency, small-footprint couplers between arbitrary nanophotonic waveguide modes,''
    Opt. Express \textbf{20}, 7221--7236 (2012).

\bibitem{code} https://github.com/JesseLu/objective-first

\bibitem{taflove} A. Taflove, and S. C. Hagness, 
    \emph{Computational Electrodynamics, Third Ed.}
    Section 3.3.2, (Artech House, 2005).

\bibitem{yee} K. S. Yee,
    ``Numerical Solution of Initial Boundary Value Problems Involving
    Maxwell's Equations in Isotropic Media,''
    IEEE Trans. Antennas and Propagation \textbf{14}, 802--807 (1966).

\bibitem{pml} S. G. Johnson, ``Notes on Perfectly Matched Layers (PMLs),''
    http://math.mit.edu/~stevenj/18.369/pml.pdf, (2010).

\bibitem{shin} W. Shin, S. Fan, ``Choice of the perfectly matched layer boundary condition for frequency-domain Maxwells equations solvers,''
    J. Comp. Phys. \textbf{231}, 3406--3431 (2012).

\bibitem{boyd} S. Boyd, and L. Vandenberghe, 
    \emph{Convex Optimization} 
    (Cambridge University Press, 2004)

\bibitem{cvx} M. Grant and S. Boyd, \emph{CVX: Matlab software for disciplined convex programming}, version 1.21. \verb+http://cvxr.com/cvx+, January 2011.

\bibitem{miller} O. D. Miller, ``Photonic Design: From Fundamental Solar Cell Physics to Computational Inverse Design,''
    U. C. Berkeley, (2012).

\bibitem{opex1} J. Lu, and J. Vuckovic, 
    ``Inverse design of nanophotonic structures using complementary convex optimization,''
    Opt. Express \textbf{18}, 3793--3804 (2011).

\bibitem{admm} S. Boyd, N. Parikh, E. Chu, B. Peleato, and J. Eckstein, 
    ``Distributed Optimization and Statistical
    Learning via the Alternating Direction
    Method of Multipliers,''
    Foundations and Trends in Machine Learning, \textbf{3} 1â1122 (2011).

% \bibitem{opex2} J. Lu, S. Boyd, and J. Vuckovic, 
%     ``Inverse design of a three-dimensional nanophotonic resonator,''
%     Opt. Express \textbf{19}, 10563--10750 (2011).

\bibitem{simp} M. P. Bendsoe, and O. Sigmund, 
    ``Material interpolation schemes in topology optimization,''
    Archive of Applied Mechanics \textbf{69}, 635--654 (1999).

\end{thebibliography}
%--------------------------------------------------%

%--------------------------------------------------%
\end{document}
%--------------------------------------------------%

### 2012-10-08 presentations/meta_book/Inverse_Methods.tex
Minor changes.

@@
     normally measured by how much the physics residual has decreased.
-\BA \text{Loop:} & & \notag \\ 
-& \minimize{x} \| A(p) x - b(p) \|^2 \notag \\
- &    \subto f(x) = f_\text{ideal}. \notag \\ 
+\BA \text{Loop:} & \notag \\ 
+ \minimize{x} \| A(p) x - b(p) \|^2 \notag \\
+     \subto f(x) = f_\text{ideal}. \notag \\ 
     \\
-& \minimize{p} \| B(x) p - d(x) \|^2 \notag \\
-    & \subto p_0 \le p \le p_1. \notag \EA
+ \minimize{p} \| B(x) p - d(x) \|^2 \notag \\
+     \subto p_0 \le p \le p_1. \notag \EA
 The alternating directions scheme is extremely simple
@@
     the results in this chapter.
+
 Lastly, for all the examples presented in the chapter,
     we run the alternating directions algorithm for 400 iterations.
-Although we do not present the convergence results here,
+In terms of convergence,
+    the physics residual never fully vanishes, and 
+    seems to asymptopically approach a non-zero value.
+Even so, we seem to obtain good performance from the produced designs.
+Note that although we do not present the convergence results here,
     such information can be obtained by inspecting the source code \cite{code}.
@@
 Our method is now employed to mimic the effect of a sub-diffraction lens.
-Since such a lens can be created using a negative-index material
+Since such a lens can be created using a negative-index material \cite{pendry}
     this mimic can be viewed as an imitation of a negative-index material,
@@
 
+\bibitem{pendry} J. B. Pendry, ``Negative refraction makes a perfect lens,''
+    Physical Review Letters, \textbf{85}, 3966-3969 (2000).
+
 \bibitem{simp} M. P. Bendsoe, and O. Sigmund, 

### 2012-10-09 presentations/meta_book/Inverse_Methods.tex
Fixed typos in intro.

@@
 Additionally, we show that our formulation is general enough 
-    to encompasses the design of all linear nanophotonic structures 
+    to encompass the design of all linear nanophotonic structures 
     and is not limited to the design of optical metamaterials.
-While this approach typically produces designs with very efficiencies 
-    (typically 99/%)
-    our solutions rely on continuously varying values of the dielectric constant 
-    with respect to position across the optical structure being designed.  
+While this approach typically produces designs with very high efficiencies 
+    (typically 99\%)
+    our solutions do feature continuously varying values of the 
+    dielectric constant.
 Future approaches for dealing with this constraint are discussed 

### 2012-10-19 presentations/maxwell_documentation/pres.tex
Started another group presentation.

--- 2011-07-30 presentations/group-pres_2011-08-04.tex
@@
 
-\title{Objective-first optimization for nanophotonics}
+\title{Maxwell: bringing cloud-powered electromagnetic simulations to Matlab}
 \author{}
@@
 \BIT \itemsep -1pt
-\item adjoint method
-\item objective-first approach
-\item field constraint: boundary-value problem
-\item structure constraint: level-set formulation
-\item example
-\item ongoing and future work
+\item Quick-start
+\item How Maxwell works
+\item How the frequency-domain solver works
+\item Examples
 \EIT
@@
 
-\oursection{Adjoint method}
-Typical formulation of a structural optimization problem:
-\begin{align}
-\mbox{decrease} & \quad f(x) \\
-\subjectto & \quad g(x,p) = 0
-\end{align}
-\BIT
-\item $f(x): \comps^n \to \reals$ is the \emph{design objective}
-\item $g(x,p): \comps^n \times \reals^n \to \comps^n$ is the \emph{governing physics}
-\item $x \in \comps^n$ is the field 
-\item $p \in \reals^n$ is the structure 
-\item $x$ is the dependent variable, $p$ is the independent variable
-\EIT
-\newpage
-
-\BIT
-\item problem is generally non-convex, so we optimize using only the first-order approximations,
-\begin{align}
-f(x_0+dx) & \approx f(x_0) + \pf{f}{x} dx \\
-g(x_0+dx,p_0+dp) & \approx g(x_0,p_0) + \pf{g}{x} dx + \pf{g}{p} dp
-\end{align}
-\item assuming that $g(x_0,p_0) = 0$, the equality constraint is satisfied via
-    \BEQ  dx = -\left(\pf{g}{x}\right)^{-1} \pf{g}{p} dp \EEQ
-\EIT
-\newpage
-
-\BIT
-\item now we can decrease $f(x_0+dx)$,
-    \begin{align} 
-    f(x_0+dx) & \approx f(x_0) + \pf{f}{x} dx \\
-        & \approx f(x_0) - \pf{f}{x} \left(\pf{g}{x}\right)^{-1} \pf{g}{p} dp \\
-        & \approx f(x_0) + \pf{f}{p} dp
-    \end{align}
-    by choosing $dp$ in the direction of $dp \propto -\pf{f}{p}$
-\item computing $\pf{f}{p}$ can be reduced to a single field solve (\ie solving $g(x,p)$ for $x$, given $p$)
-\EIT
-\newpage
-
-Characteristics of the adjoint method:
-\BIT
-\item can use existing field solvers 
-\item each iteration requires two solves, one to calculate $\pf{f}{p}$, and the other to calculate the new $x$
-\item need good initial guess, since this heavily influences what the final structure will be
-\item optimization generally ``stalls'' on local minima
-\EIT
-
-\oursection{Objective-first approach}
-ob-1 means that we prioritize the design objective over satisfying physics
-\begin{align}
-\mbox{decrease} & \quad \|g(x,p)\|^2 \\
-\subjectto & \quad f(x) = 0
-\end{align}
-\BIT
-\item $r(x,p) = \|g(x,p)\|^2$ is the \emph{physics residual}
-\item $x$ always satisfies our design objective, we change $x$ and $p$ only to increasingly satisfy physics
-\item $x$ and $p$ are both independent variables
-\EIT
-\newpage
-
-\BIT
-\item this problem is still non-convex, use linear approximation 
-\begin{align}
-r(x_0+dx,p_0+dp) & \approx r(x_0,p_0) + \pf{r}{x} dx + \pf{r}{p} dp \\
-f(x_0+dx) & \approx f(x_0) + \pf{f}{x} dx 
-\end{align}
-\item decrease $r$ by choosing $dp \propto -\pf{r}{p}$
-\item decrease $r$ by choosing 
-    $dx \propto - (I - P_{f_x}) \pf{r}{x}$
-\item $P_{f_x}$ is the projector onto the vector space defined by $\pf{f}{x}$, used to satisfy equality constraint
-\item computing $P_{f_x}$ requires solving for $\left(\pf{f}{x}^T \pf{f}{x}\right)^{-1}$, but this is often \emph{trivial}
-\EIT
-\newpage
-
-ob-1 requires only matrix multiplication (and trivial matrix solve)
-\BIT
-\item For 3D structures, most field solvers are based on (often $>10,000$) matrix multiplies
-\item this means that is may be possible to solve larger design problems in the same amount of time needed for a field solve
-\EIT
-
-\vspace{3ex}
-
-ob-1 should be less dependent on starting guess 
-\BIT
-\item some previous problems (using a similar approach) did not depend at all on initial structure
-\item such a formulation may result in fewer local minima to stall on
-\EIT
-\vfill
-
-\oursection{Field constraint: boundary-value problem}
-\BIT
-\item our problem is
-\begin{align}
-\mbox{decrease} & \quad \|g(x,p)\|^2 \\
-\subjectto & \quad f(x) = 0
-\end{align}
-\item physics residual is the error in Maxwell's sourceless, time-harmonic equations
-\BEQ \|g(x,p)\|^2 = \|A(p)x\|^2 = 
-    \left\| \left[ 
-    \begin{array}{cc}
-        \nabla\times & i\mu\omega \\
-        -ip\omega & \nabla\times
-    \end{array}
-    \right] 
-    \left[ \begin{array}{c} x_E \\ x_H \end{array} \right] 
-    \right\|^2
-\EEQ
-\item here $p$ determines the values of $\epsilon$
-\EIT
-\newpage
-
-\BIT
-\item key issue: formulation of the constraint
-\item a sufficient constraint for most devices is to match field values along the border
-\BEQ f(x) = \| x^\text{border} - x^\text{border}_0 \|^2 = 0 \EEQ
-\begin{center}
-\includegraphics[width=0.8\textwidth]{../figures/waveguide.jpg}
-\end{center}
-\item here, $p$ is a waveguide structure, and the design objective is a perfect waveguide mode at input and output
-\EIT
-\newpage
-
-\BIT
-\item to experiment, we fix $p = p_0$, which convexifies the ob-1 formulation
-\begin{align}
-\mbox{minimize} & \quad \|A(p_0)x\|^2 \\
-\subjectto & \quad x^\text{border} = x^\text{border}_0
-\end{align}
-\item for general structures and design objectives, this results in a ``soft physics'' field solve
-\begin{center}
-\includegraphics[width=0.8\textwidth]{../figures/crossbar.jpg}
-\end{center}
-\EIT
-\newpage
-
-\BIT
-\item prioritizing the design objective means we allow physics to be ``bent''
-\item here, reflected waves from the junction magically disappear as they approach the border
-\begin{center}
-\includegraphics[width=0.8\textwidth]{../figures/mode_converter.jpg}
-\end{center}
-\item matlab files available at \url{https://github.com/JesseLu/wave-tools}, look for \texttt{em\_bval\_2dte/demo.m}
-\EIT
-
-\oursection{Structure constraint: level-set method}
-\BIT
-\item a more detailed statement of our problem is
-\begin{align}
-\mbox{decrease} & \quad \|g(x,p)\|^2 \\
-\subjectto & \quad f(x) = 0 \\
-        & \quad p \in \{p_\text{manufacturable}\}
-\end{align}
-\item need to constrain possible $p$ to what can be fabricated
-\item for nanophotonics this means two distinct materials only
-\item however, using $p_i \in \{\epsilon_1, \epsilon_2\}$ defeats the purpose of using linear approximations
-\EIT
-\newpage
-
-\BIT
-\item need ability to \emph{incrementally} update the topology of the structure
-\item describe $p$ using the \emph{interface} between the two materials
-\item implicitly describe boundary using the \emph{level-set} of higher-dimensional function $\phi$
-\begin{center}
-\includegraphics[width=0.45\textwidth]{../figures/level-set.jpg} \\
-source: \url{http://en.wikipedia.org/wiki/Level_set_method}
-\end{center}
-\EIT
-\newpage
-
-\BIT
-\item updating $p(\phi)$ proceeds in the following way:
-\BEQ
-\phi^n \xrightarrow{\text{interp.}} \gamma 
-    \xrightarrow{\text{ratio}} p
-    \xrightarrow{-\pf{r}{p}} dp
-    \xrightarrow{\left(\pf{p}{\phi}\right)^{-1}dp} d\phi
-    \xrightarrow{\phi + d\phi} \phi^{n+1}
-\EEQ
-\item $\phi = 0$ defines the boundary between materials
-\item boundary points $\gamma$ are linearly interpolated between adjacent $\phi$ of opposite sign
-\item $p_i$ approximated by ratio of each material within cell
-\item solve least-squares problem $\pf{p}{\phi} d\phi = dp$ to obtain $d\phi$
-\EIT
-\newpage
-
-\BIT
-\item to test, hold $x$ constant, and update $p$ 
-\begin{center}
-\includegraphics[width=0.6\textwidth]{../figures/structure-progression.jpg} \\
-\end{center}
-\item code at \url{https://github.com/JesseLu/level-set} (\texttt{demo.m})
-\item new code at \url{https://github.com/JesseLu/lset-opt}
-\EIT
-
-\oursection{Example}
-put it all together and let'er rip!
-
+\oursection{Problem Statement}
+% \oursection{Plan}
+% \BIT
+% \item Software to solve $A^{-1}z$.
+% \item Adjoint
+% \EIT
 \end{document}

### 2012-10-22 presentations/maxwell_documentation/pres.tex
Format of group presentation set.
Going on pres.

@@
 \usepackage{hyperref}
+\usepackage{pstricks}
+\usepackage{pst-grad}
 \input defs.tex
@@
 \title{Maxwell: bringing cloud-powered electromagnetic simulations to Matlab}
-\author{}
+\author{Advanced user interface tutorial}
 \MyLogo{Jesse Lu, Jelena Vuckovic group, Stanford University}
@@
 \BIT \itemsep -1pt
-\item Quick-start
-\item How Maxwell works
-\item How the frequency-domain solver works
-\item Examples
+\I  Quick-start
+\I  How Maxwell uses the cloud (EC2)
+\I  How Maxwell solves electromagnetics
+\I  Examples
 \EIT
@@
 
-\oursection{Problem Statement}
-% \oursection{Plan}
-% \BIT
-% \item Software to solve $A^{-1}z$.
-% \item Adjoint
-% \EIT
+\oursection{Definitions}
+\BIT
+\I  What is Maxwell?
+    \BIT
+    \I  a Matlab toolset 
+    \I  that uses Amazon's Elastic Compute Cloud (EC2)
+    \I  to solve frequency-domain electromagnetic simulations.
+    \EIT
+\I  Maxwell provides two user interfaces: advanced and other
+    \BIT
+    \I  advanced:
+    \I  other:
+    \EIT
+\I  This presentation covers the advanced interface 
+\EIT
+
+\oursection{Quick-start}
+\BIT \I Sign up at \EIT
+\begin{verbatim}
+% Download maxwell.m
+>> urlwrite('m.lightlabs.co', 'maxwell.m');
+
+% Provide AWS credentials and launch a 2-node cluster.
+>> maxwell.aws_credentials('aws-access-id', 'aws-secret-key');
+>> maxwell.launch('cluster-name', 2);
+
+% Run a 1-node simulation.
+>> [E, H] = maxwell.solve('cluster-name', 1, ...);
+
+% Terminate cluster
+>> maxwell.terminate('cluster-name');
+\end{verbatim}
+
+{Wait, what just happened?}
+\BIT
+\I  \verb=urlwrite()= downloaded the advanced interface for Maxwell,
+\I  \verb=maxwell.aws_credentials()= provided the AWS credentials that
+\I  \verb=maxwell.launch()= needed to create a cluster on EC2.
+\I  \verb=maxwell.solve()= solved the electromagnetic simulation on
+    the cluster and downloaded the resulting electromagnetic fields, and
+\I  \verb=maxwell.terminate()= terminated the EC2 cluster.
+\EIT
+
+\oursection{How Maxwell uses the cloud (EC2)}
+
+\newpage
+\begin{center}
+
+\psset{unit=2cm}
+\begin{pspicture}(6,4)(-5,-2)
+\psset{gridcolor=green, subgridcolor=yellow}
+    % \let\psgrid\relax
+    \psgrid
+    \psframe[linestyle=none,
+            fillstyle=gradient,
+            gradbegin=white,gradend=lightgray,
+            gradmidpoint=0.5,
+            gradangle=0](0,-1.5)(6,3.5)
+    \psline[linestyle=dotted](0,3)(0,-1)
+    \rput(-2.5,3.5){Matlab}
+    \rput(3,3.5){Amazon EC2}
+
+    \psline(-1.5,2.5)(3,2.5)
+    \psline{->}(3,2.5)(3,2)
+
+\end{pspicture}
+\end{center}
+\BIT
+\I  Wait, what's going on here?
+\EIT
+
+\oursection{How Maxwell solves electromagnetics}
+\oursection{Examples}
+
 \end{document}

### 2012-10-22 presentations/maxwell_documentation/pres.tex
More progress on presentation.

@@
 \I  Quick-start
+\I  Examples
 \I  How Maxwell uses the cloud (EC2)
 \I  How Maxwell solves electromagnetics
-\I  Examples
 \EIT
@@
     \I  that uses Amazon's Elastic Compute Cloud (EC2)
-    \I  to solve frequency-domain electromagnetic simulations.
+    \I  to solve 3D frequency-domain electromagnetic simulations.
     \EIT
-\I  Maxwell provides two user interfaces: advanced and other
+
+\I  Features:
+    \BIT
+    \I  Cryptographically-secure communication (https)
+    \I  Full control over all simulation parameters
+    \I  GPU-acceleration provided by Nvidia Tesla GPUs
+    \I  Queueing system to allow for full usage of cluster
+    \I  Scalable to hundreds of simultaneous simulations 
+        running on hundreds of nodes.
+    \EIT
+\EIT
+
+\newpage
+Maxwell provides two user interfaces: advanced and other
 \BIT
@@
 \EIT
-\I  This presentation covers the advanced interface 
-\EIT
+This presentation covers the advanced interface
 
@@
 
-% Run a 1-node simulation.
+% Run simulation on 1 node.
 >> [E, H] = maxwell.solve('cluster-name', 1, ...);
@@
 
+\oursection{Examples}
+
 \oursection{How Maxwell uses the cloud (EC2)}
+\BIT
+\I  Maxwell uses your Amazon Web Services (AWS) account to
+    \BIT
+    \I  Create a custom Amazon EC2 cluster, and
+    \I  Solve electromagnetic simulations on it;
+    \EIT
+    all without leaving your local Matlab environment.
+
+\I  To get started, you need to
+    \BIT
+    \I  sign up for an AWS account,
+    \I  retrieve your AWS security credentials, and
+    \I  purchase the custom Maxwell Amazon Machine Image (AMI).
+    \EIT
+    For detailed instructions see Website.
 
 \newpage
+\I  Maxwell's advanced interface comprises of just five commands:
+    \BIT
+    \I  \verb+maxwell.aws_credentials()+
+    \I  \verb+maxwell.launch()+
+    \I  \verb+maxwell.solve()+
+    \I  \verb+maxwell.solve_async()+
+    \I  \verb+maxwell.terminate()+
+    \EIT
+
+\I  \verb+maxwell.aws_credentials('aws-key-id', 'aws-secret-key');+
+    \BIT
+    \I  Stores the security credentials linked to your AWS account locally
+    \I  Security credentials are used to launch and terminate clusters
+    \I  Transmitted over https and never stored on server-side
+    \I  Tutorial on obtaining your credentials at Website.
+    \EIT
+\EIT
+
+\newpage
+% Launch diagram.
 \begin{center}
-
 \psset{unit=2cm}
-\begin{pspicture}(6,4)(-5,-2)
+\begin{pspicture}(6,4)(-5,-1.0)
 \psset{gridcolor=green, subgridcolor=yellow}
-    % \let\psgrid\relax
-    \psgrid
+    \let\psgrid\relax
+    % \psgrid
     \psframe[linestyle=none,
@@
             gradmidpoint=0.5,
-            gradangle=0](0,-1.5)(6,3.5)
-    \psline[linestyle=dotted](0,3)(0,-1)
+            gradangle=0](0,-1.0)(6,3.8)
+    \psline[linestyle=dotted](0,3)(0,-0.2)
     \rput(-2.5,3.5){Matlab}
@@
 
-    \psline(-1.5,2.5)(3,2.5)
-    \psline{->}(3,2.5)(3,2)
+    \psverbboxtrue
+    \rput(-2.5,2.5){\small \verb=>> maxwell.launch(...)=}
+    \psverbboxfalse
+
+    \psline[linewidth=1pt](-0.6,2.5)(3,2.5) \rput[b](1.45, 2.6){\small{launch 3-node cluster}}
+    \psline{->, linewidth=1pt}(3,2.5)(3,2)
+
+    \psframe[linestyle=dashed](2.2,1.8)(3.8,0.8) \rput(3,1.3){master}
+
+    \psframe[linestyle=dashed](0.4,0.6)(2,-0.4) \rput(1.2,0.1){node001}
+    \psframe[linestyle=dashed](2.2,0.6)(3.8,-0.4) \rput(3,0.1){node002}
+    \psframe[linestyle=dashed](4.0,0.6)(5.6,-0.4) \rput(4.8,0.1){node003}
+\end{pspicture}
+\end{center}
+
+\BIT
+\I  \verb+maxwell.launch('cluster-name', num_nodes);+
+    \BIT
+    \I  Creates an EC2 cluster consisting of 1 master node and \verb+num_nodes+ worker nodes
+    \I  \verb+'cluster-name'+ parameter allows for using multiple clusters at once.
+    \I  The launch can be monitored manually from the EC2 Management Console at \url{console.aws.amazon.com/ec2}
+    \EIT
+\I  The master node is launched 
+    \BIT
+    \I  with the paid Maxwell Amazon Machine Image (AMI),
+    \I  as an on-demand instance, and 
+    \I  as an \texttt{m1.medium} instance.
+    \EIT
+\I  The worker nodes are launched
+    \BIT
+    \I  using a public (free) AMI,
+    \I  as spot request instances (in order to achieve up to 80\% savings), and
+    \I  as \texttt{cg1.4xlarge} instances.
+    \EIT
+\EIT
+Note that the use of spot requests for worker nodes may result in sudden cluster termination, 
+in this case the cluster will need to be terminated and a new cluster should be started.
+
+\newpage
+% Solve diagram.
+\begin{center}
+\psset{unit=2cm}
+\begin{pspicture}(6,4)(-5,-1.0)
+\psset{gridcolor=green, subgridcolor=yellow}
+    \let\psgrid\relax
+    % \psgrid
+    \psframe[linestyle=none,
+            fillstyle=gradient,
+            gradbegin=white,gradend=lightgray,
+            gradmidpoint=0.5,
+            gradangle=0](0,-1.0)(6,3.8)
+    \psline[linestyle=dotted](0,3)(0,-0.2)
+    \rput(-2.5,3.5){Matlab}
+    \rput(3,3.5){Amazon EC2}
+
+    \psverbboxtrue
+    \rput(-2.5,2.5){\small \verb+>> [E, H] = maxwell.solve(...)+}
+    \psverbboxfalse
+
+    \psline{->, linewidth=1pt}(-0.1,2.5)(2.4,2.5) \rput[b](1.15,2.55){\small inputs}
+    \psline[linewidth=1.0pt](2.4,2.1)(-3.9,2.1) \rput [t](0.6,2.0){\small solution}
+    \psline{->, linewidth=1pt}(-3.9,2.1)(-3.9,2.3)
+    \psframe[linestyle=solid](2.2,2.8)(3.8,1.8) \rput(3,2.3){master}
+
+    \psline[linestyle=dashed](3,1.8)(3,1)
+    \psline[linestyle=dashed](3,1.2)(1.6,1.2)
+    \psline[linestyle=dashed](1.6,1.2)(1.6,1)
+    \rput[br](2.9,1.3){\small 2 nodes used}
+    \psframe[linestyle=solid](0.4,1.0)(2,0.0) \rput(1.2,0.5){node001}
+    \psframe[linestyle=solid](2.2,1.0)(3.8,0.0) \rput(3,0.5){node002}
+    \psframe[linestyle=solid](4.0,1.0)(5.6,0.0) \rput(4.8,0.5){node003}
 
@@
 \BIT 
-\I  Wait, what's going on here?
+\I  \verb+[E, H] = maxwell.solve('cluster-name', n, ...);+
+    \BIT
+    \I  Solves an electromagnetic simulation on \verb+n+ nodes of cluster \verb+'cluster-name'+
+    \I  Additional simulation parameters ``\verb+...+'' described in following section
+    \I  Returns as solution both electric and magnetic fields
+    \I  For full documentation of this function see Website
+    \EIT
+
+\I  \verb+maxwell.solve()+ proceeds as follows:
+    \BIT
+    \I  Transfers simulation parameters to the specified cluster
+    \I  Waits for worker nodes to be provisioned for the simulation
+    \I  Continues to wait as simulation is executed on worker nodes
+    \I  Retrieves simulation results back to Matlab
+    \EIT
+
+\I  Although attempting to use more nodes than available in the cluster will
+    result in an error, the provided queueing system does allow for the 
+    \emph{total} number of requested nodes to exceed the number of nodes in the cluster.
+\EIT
+
+\newpage
+% Solve_async diagram.
+\begin{center}
+\psset{unit=2cm}
+\begin{pspicture}(6,4)(-5,-1.0)
+\psset{gridcolor=green, subgridcolor=yellow}
+    \let\psgrid\relax
+    % \psgrid
+    \psframe[linestyle=none,
+            fillstyle=gradient,
+            gradbegin=white,gradend=lightgray,
+            gradmidpoint=0.5,
+            gradangle=0](0,-1.0)(6,3.8)
+    \psline[linestyle=dotted](0,3)(0,-0.2)
+    \rput(-2.5,3.5){Matlab}
+    \rput(3,3.5){Amazon EC2}
+
+    \psverbboxtrue
+    \rput[l](-5.2,2.5){\small \verb+>> cb = maxwell.solve_async(...)+}
+    \rput[l](-5.2,1.5){\small \verb+>> [done, E, H] = cb()+}
+    \psverbboxfalse
+
+    \psline{->, linewidth=1.0pt}(-0.1,2.5)(2.4,2.5) \rput[b](1.15,2.55){\small inputs}
+    \psline[linewidth=1.0pt](2.4,2.1)(-3.5,2.1) \rput [t](0.6,2.0){\small solution}
+    \psline{->, linewidth=1.0pt}(-3.5,2.1)(-3.5,1.8)
+    \psframe[linestyle=solid](2.2,2.8)(3.8,1.8) \rput(3,2.3){master}
+
+    \psline[linestyle=dashed](3,1.8)(3,1)
+    \psline[linestyle=dashed](3,1.2)(1.6,1.2)
+    \psline[linestyle=dashed](1.6,1.2)(1.6,1)
+    \rput[br](2.9,1.3){\small 2 nodes used}
+    \psframe[linestyle=solid](0.4,1.0)(2,0.0) \rput(1.2,0.5){node001}
+    \psframe[linestyle=solid](2.2,1.0)(3.8,0.0) \rput(3,0.5){node002}
+    \psframe[linestyle=solid](4.0,1.0)(5.6,0.0) \rput(4.8,0.5){node003}
+
+\end{pspicture}
+\end{center}
+
+\BIT 
+\I  \verb+callback = maxwell.solve_async('cluster-name', n, ...);+
+    \BIT
+    \I  Asynchronous solve that returns a callback function instead of waiting
+        for the simulation to complete 
+    \I  The callback function is then used to check for solve completion and 
+        to retrieve the simulation results:
+        \begin{verbatim}
+        [is_finished, E, H] = callback();
+        \end{verbatim}
+    \I  If the solve has not finished, \verb+is_finished+ returns \verb+false+ and 
+        \verb+E+ and \verb+H+ both return empty cell arrays.
+    \I  The additional simulation parameters ``\verb+...+'' are identical to those 
+        used in \verb+maxwell.solve()+ and are detailed in the following section
+    \EIT
+\I  \verb+maxwell.solve_async()+ allows even single-threaded Matlab users to simultaneously execute
+    a virtually unlimited number of simulations.
+    \BIT
+    \I  \verb+maxwell.solve_async()+ proceeds by uploading the simulation to the cluster
+        and then immediately returns the function \verb+callback+.
+    \EIT
+\EIT
+
+\newpage
+\BIT
+\I  \verb+maxwell.terminate('cluster-name');+
+    \BIT
+    \I  Terminates the cluster \verb+'cluster-name'+
+    \I  Note that AWS instances are charged by the hour and that partial hours
+        are charged the full hour.
+    \EIT
 \EIT
@@
 \oursection{How Maxwell solves electromagnetics}
-\oursection{Examples}
+\BIT
+\I  In this section we detail the simulation parameters used by the 
+    \verb+maxwell.solve()+ and \verb+maxwell.solve_async()+ functions
+\EIT
 

### 2012-10-22 presentations/maxwell_documentation/pres.tex
More stuffs...

@@
     \verb+maxwell.solve()+ and \verb+maxwell.solve_async()+ functions
+\I  Along with the \verb+'cluster-name'+ and \verb+n+ parameters, both
+    functions support the following parameters which describe the physical simulation:
+    \BIT
+    \I  \verb+omega+
+    \I  \verb+d_prim, d_dual, s_prim, s_dual+
+    \I  \verb+mu, epsilon+
+    \I  \verb+E, J+
+    \I  \verb+max_iters, err_thresh+
+    \EIT
+    and can be understood from the master equation:
+    \BEQ
+    \nabla \times \mu^{-1} \nabla \times E - \omega^2 \epsilon E = -i \omega J
+    \EEQ
+
+\newpage
+\I  Frequency parameter: \verb+omega+
+\I  Spatial grid parameters: \verb+d_prim, d_dual, s_prim, s_dual+
+\I  Material parameters: \verb+mu, epsilon+
+\I  Field parameters: \verb+E, J+
+\I  Convergence parameters: \verb+max_iters, err_thresh+
+%  [E, H, err] = fds(omega, d_prim, d_dual, s_prim, s_dual, mu, epsilon, E, J, max_iters, err_thresh, view_progress)
 \EIT

### 2012-10-23 presentations/maxwell_documentation/pres.tex
Finished draft of group presentation.

@@
 \title{Maxwell: bringing cloud-powered electromagnetic simulations to Matlab}
-\author{Advanced user interface tutorial}
+\author{Advanced interface tutorial}
 \MyLogo{Jesse Lu, Jelena Vuckovic group, Stanford University}
@@
 \BIT \itemsep -1pt
-\I  Quick-start
-\I  Examples
+\I  Advanced interface quick-start
+\I  Examples: Maxwell in action
 \I  How Maxwell uses the cloud (EC2)
@@
 \newpage
-Maxwell provides two user interfaces: advanced and other
+Maxwell provides two user interfaces: Advanced and other
 \BIT
@@
 
-\oursection{Quick-start}
+\oursection{Advanced interface quick-start}
 \BIT \I Sign up at \EIT
@@
 
-\oursection{Examples}
+\oursection{Examples: Maxwell in action}
 
@@
     \EIT
+    for full documentation use ``\verb+doc maxwell.command+'' in Matlab.
 
@@
 in this case the cluster will need to be terminated and a new cluster should be started.
+\BIT
+\I  Naturally, a cluster can only run simulations on the nodes that it contains
+    (i.e. you can't run a 5-node simulation on a 4-node cluster)
+\I  However, each cluster contains a built-in queueing system that allows for 
+    multiple jobs to be handled simultaneously (i.e. 10 2-node simulations on a 4-node cluster is okay)
+\I  Lastly, Amazon, by default, caps the number of worker nodes allows at 10;
+    to request more, go to \url{aws.amazon.com/contact-us/ec2-request/}
+    and request the limit of \verb+cg1.4xlarge+ spot requests to be increased for your account.
+\EIT
 
@@
 
-\I  Although attempting to use more nodes than available in the cluster will
-    result in an error, the provided queueing system does allow for the 
-    \emph{total} number of requested nodes to exceed the number of nodes in the cluster.
+\I  \verb+maxwell.solve()+ features
+    \BIT
+    \I  complete integration within Matlab
+    \I  no need to deal with simulations files
+    \I  real-time plot of simulation progress
+    \EIT
+% 
+% \I  Although attempting to use more nodes than available in the cluster will
+%     result in an error, the provided queueing system does allow for the 
+%     \emph{total} number of requested nodes to exceed the number of nodes in the cluster.
 \EIT
@@
         \end{verbatim}
-    \I  If the solve has not finished, \verb+is_finished+ returns \verb+false+ and 
-        \verb+E+ and \verb+H+ both return empty cell arrays.
+    \I  If the solve has not finished, \verb+is_finished+ is set to \verb+false+ and 
+        \verb+E+ and \verb+H+ both return empty cell arrays
+    \I  If the solve has indeed finished, \verb+is_finished+ is set to \verb+true+
+        and \verb+E+ and \verb+H+ contain the solution fields to the problem
     \I  The additional simulation parameters ``\verb+...+'' are identical to those 
@@
     \EIT
-\I  \verb+maxwell.solve_async()+ allows even single-threaded Matlab users to simultaneously execute
-    a virtually unlimited number of simulations.
-    \BIT
-    \I  \verb+maxwell.solve_async()+ proceeds by uploading the simulation to the cluster
-        and then immediately returns the function \verb+callback+.
-    \EIT
+\newpage
+\I  The purpose of \verb+maxwell.solve_async()+ is to allow even single-threaded Matlab users 
+    to simultaneously execute a virtually unlimited number of simulations.
+        \begin{verbatim}
+        % Start n simulations.
+        cb{1} = maxwell.solve_async(...);
+        ...
+        cb{n} = maxwell.solve_async(...);
+
+        % Wait for the simulations to complete.
+        [is_finished, E, H] = cb{1}();
+        ...
+        CHECK THIS!!
+        \end{verbatim}
+%     \BIT
+%     \I  \verb+maxwell.solve_async()+ proceeds by uploading the simulation to the cluster
+%         and then immediately returns the function \verb+callback+.
+%     \EIT
 \EIT
@@
     \EIT
+\I  Terminations (and launches) can be monitored manually from the EC2 management
+    console at \url{console.aws.amazon.com/ec2}
+\I  Terminations can also be executed manually from the console, 
+    although it is recommended to perform the full termination from Matlab
+    in order to tie up all loose ends.
 \EIT
@@
 \I  Frequency parameter: \verb+omega+
+    \BIT
+    \I  The angular frequency of the simulation
+    \I  Since Maxwell employs a frequency-domain solver, the exact frequency for the simulation
+        can be set with this parameter
+    \I  is equal to $2 \pi f$ where $f$ is in units of Hz
+    \EIT
+    \newpage
+
+\begin{center}
+The Yee cell \\
+\psset{unit=1.3cm}
+\begin{pspicture}(-2,-2)(7,7)
+\psset{gridcolor=green, subgridcolor=yellow}
+    \let\psgrid\relax
+
+    % Origin.
+    \psdot(0,0) \rput[br](-0.1,0.1){$(0,0,0)$}
+
+    % Principle axes.
+    \psline[linestyle=dashed](-1,0)(6,0) \rput(6.3,0){$x$}
+    \psline[linestyle=dashed](0,-1)(0,6) \rput(0,6.3){$z$}
+    \psline[linestyle=dashed](-0.8,-0.6)(4.8,3.6) \rput(5.05,3.75){$y$}
+
+    % Intermediate axes.
+    \psline[linestyle=dashed](0,3)(3,3) % Hy point.
+    \psline[linestyle=dashed](3,3)(3,0)
+
+    \psline[linestyle=dashed](0,3)(2.4,4.8) % Hx point.
+    \psline[linestyle=dashed](2.4,4.8)(2.4,1.8)
+
+    \psline[linestyle=dashed](2.4,1.8)(5.4,1.8) % Hz point.
+    \psline[linestyle=dashed](5.4,1.8)(3,0)
+
+    % E-field vectors.
+    \psline{->, linewidth=2pt}(2.6,0)(3.4,0) \rput(3,-0.4){$E_x$}
+    \psline{->, linewidth=2pt}(0,2.6)(0,3.4) \rput(-0.4,3){$E_z$}
+    \psline{->, linewidth=2pt}(2.1,1.55)(2.7,2.05) \rput(2.05,2.05){$E_y$}
+
+    % H-field vectors.
+    \psline{->, linewidth=2pt}(2,4.8)(2.8,4.8) \rput(2.4,5.2){$H_x$}
+    \psline{->, linewidth=2pt}(5.4,1.4)(5.4,2.2) \rput(5.8,1.8){$H_z$}
+    \psline{->, linewidth=2pt}(2.7,2.75)(3.3,3.25) \rput(2.7,3.3){$H_y$}
+\end{pspicture}
+\end{center}
+
+\newpage
 \I  Spatial grid parameters: \verb+d_prim, d_dual, s_prim, s_dual+
+    \BIT 
+    \I  Controls the spatial grid of the simulation
+    \I  \verb+d_prim+ and \verb+d_dual+ are typically used to set 
+        the spatial grid within the simulation
+    \I  \verb+s_prim+ and \verb+s_dual+ are typically used to set 
+        the spatial grid within the absorbing layers at the edges of the simulation.
+    \I  In the end, both \verb+d+ and \verb+s+ parameters are essentially interchangeable
+    \I  \verb+d_prim+ and \verb+s_prim+ refer to the distances between $E_w$ in direction $w$ 
+        where $w = x,y,z$ (e.g. distances between $E_x$ in the $x$ direction)
+    \I  \verb+d_dual+ and \verb+s_dual+ refer to the distances in directions other than $w$ of 
+        adjacent $E_w$ (e.g. distances between $E_y$ in the $x$ direction)
+    \I  Lastly, Maxwell uses a periodic wrap-around grid, so that the first \verb+_prim+
+        and last \verb+_dual+ entries correspond to the the wrap-around distances from 
+        the last to the first Yee cells
+    \EIT
+
+\newpage
 \I  Material parameters: \verb+mu, epsilon+
+    \BIT
+    \I  defined at $H$- and $E$- field points on the Yee grid respectively
+    \EIT
+
 \I  Field parameters: \verb+E, J+
+    \BIT
+    \I  \verb+E+ allows you to set the initial value of the E-field for the solver.
+    \I  \verb+E = 0+ works for most cases, but a random initial field is needed
+        in other cases.
+    \I  \verb+J+ describes the current source in the master equation and is situated
+        at the $E$-field point on the Yee grid.
+    \EIT
+
 \I  Convergence parameters: \verb+max_iters, err_thresh+
+    \BIT
+    \I  \verb+max_iters+ determines the maximum number of iterations before the solver terminates
+    \I  \verb+err_thresh+ determines the error threshold below with the solver termiantes,
+        typically set to \verb+1e-6+.
+    \EIT
 %  [E, H, err] = fds(omega, d_prim, d_dual, s_prim, s_dual, mu, epsilon, E, J, max_iters, err_thresh, view_progress)

### 2013-02-09 sandbox/don_memorial/don_penhale.tex
Added Don Penhale's memorial service.

\documentclass{article}
\title{Don Penhale Memorial}
\begin{document}
\maketitle
\section{Outline for Don's Memorial}
(Above all present the service as an occasion for rejoicing.)
\begin{enumerate}
\item Music just before the service: 
        The Adagietto from Gustav Mahler's Symphony \#5 (CD)
\item Wally to sing: The Love of God
\item Read my brief history
\item Wally sing: He Took My Place
\item Read my testimony
\item Wally sing: Finally Home
\item Congregation sing: How Great Thou Art
\item Read Jude 24-25
\item Benediction de Deux by Franz Liszt played by Steven Hough (CD)
\end{enumerate}

\section{A brief history}
(A brief history of my life that you will give.)

Don was born in in Oakland, CA on July 25, 1922.
He lived on a chicken farm in Novato, Marin County, CA in an area
    known as Indian Valley.
It was rather primitive living initially, with an out-house,
    no electricity and a shallow well.
It was during the depression years.
He was given piano lessons, with the intent of making him a concert pianist.
When World Was II came along that put an end to that endeavor.
He enlisted in the Nacy and served with the amphibious forces
    in the Pacific theater.
Upon retirement in 1946 he resumed school at the University of California
    in Berkeley.
He roomed at a student rooming house owned by Stella whom he eventually married
    and adopted her daughter Mary.
He worked as an auditor for 
    the National Service Life Insurance office for 2 years,
    as a surveyor for the City of San Pablo for 2 years,
    as a laboratory assistant for Shell Development Company for 19 years,
    as a chemist fo Alza Corporation in Palo Alto for 5 years,
    and for SRI International in Menlo Park for 14 years.
He retired in 1989.
Stella passed away in 1993.

\section{A testimony}
(This is my testimony to be read by you)

Don left with me his testimony which he wanted me to read to you:\\

When I retired from the service I resumed school at UC Berkeley.
I married Stella, the owner of a rooming house for students.
She introduced me to Bible study and
    we attended First Prebyterian Church of Berkeley.

Now I would like to look back in retrospect and
    tell you how I discovered the absolute Sovereignty of God over my life.
I however will not bore you with the many trivial incidents 
    which constituted this discovery.

While in the Navy I was assigned as a deck officer on the crew 
    of an amphibious ship LST599.
We, with 150 Marines, were in on the invasion of Okinawa.
We were hit by a Japanese bomber who suicided into us by diving the bomber
    through our deck.
We had a raging fire but lost no lives.
When I was staring straight down the fuselage of that plane
    coming in at us I thought I was surely facing death.
When the commotion subsided I was alive.

After, I was troubled by the thoughts of what would have happened?
What was my destiny if I had any?
Those thoughts pervaded my thinking ever after until one evening,
    during an evangelistic meeting at First Prebyterian Church, Berkeley,
    where the speaker, Dr. Harold Okenga, 
    then president of the American Bible Society,
    spoke on the verse in the Bible in the book of John, verse 3:16,
    ``For God so loved the world that He gave His only begotten Son,
    that whosoever believeth in Him should not perish 
    but have everlasting life.''
The Holy Spirit led me to go forward and make a profession of faith,
    repenting of my sin,
    believing by God's gift of faith,
    that Jesus Christ was crucified in payment of my debt of sin,
    and was buried and rose again as the Victor over sin and death.

I knew I had been born again to a new life in Christ 
    and that I had received the answer to the question on my mind 
    as to my destiny.
Since then it has been a continuing process of learning 
    about the person of Jesus Christ.

Mind you, I have been everything but a perfect person
    but thanks be to God,
    I experience God's grace and mercy daily 
    for there is not a righteous bone in me.
I do not deserve it but He does it for me,
I know it and can testify to it with certainty.
As Paul wrote in Philippians 1:6,
    ``I can be confident of this very thing,
    that He who has begun a good work in you
    will complete it unto the day of Jesus Christ.''
I praise Him and thank Him for it.

I have found that the word of God is sufficient and practical 
    to be my guide to deal with the vicissitudes of life.
Paul knew whereof he spoke when he wrote these words 
    in his first letter to the Corinthians in chapter 10, verses 12 and 13,
    ``When ye think ye stand beware lest ye fall.
    There hath no temptation taken you but such as is common to man,
    but God is faithful who will not suffer you to be tempted
    above what ye are able,
    but with the temptation make a way of escape,
    that ye may be able to bear it.''
God's promises, admonitions, and doctrine from Scripture provide our means
    by which we meet and escape temptation.

I would like to share with you three favorite passages from Scripture.
\begin{itemize}
\item Philippians 3:7-15
\item Romans 8:28-39
\item Hebrews 13:5-6
\end{itemize}
I now rejoice in the incorruptible inheritance I possess.

I love all of you who are hearing these and sincerely admonish you:
    if you have not done so,
    to consider your position before God and repent of your sins,
    because Scripture does declare that,
    ``All have sinned and fall short of the glory of God.''
God gives you the faith to believe and receive Jesus Christ 
    as your personal Savior 
    so that we can all have a joyful reunion in Heaven for eternity.
I give thanks and praise to Jesus Christ. 
Amen.

\section{He Took My Place}

\begin{verse}
Sometimes I see through mists of bitter tears \\
A distant hill on which a cross appears; \\
And on that cross, where I myself should be, \\
I see the lowly man of Galilee.
\end{verse}

\begin{verse}
\emph{Chorus} \\
He took my place, His life He freely gave. \\
O boundless grace, my soul from sin to save. \\
He took my place upon the cruel tree. \\
He took a guilty sinner's place and I am free.
\end{verse}

\begin{verse}
O that my lips might speak His worthy praise; \\
And that my hands might serve Him all my days; \\
Until at last through His redeeming grace \\
I meet and greet the Man who took my place.
\end{verse}

\end{document}

### 2013-03-11 resume/cv.tex
Added cv.

--- 2012-06-14 resume/bina/res1.tex
@@
 
-\name{Jesse Lu\\[12pt]}
+\name{Jesse Lu -- Curriculum Vitae\\[12pt]}
 \address{\texttt{jesselu@stanford.edu} \\ 66 Newell Rd. Apt. O \\ East Palo Alto, CA \\ (408) 568-9356}
@@
 
-\section{JOB OBJECTIVE}          
-    A full-time software engineering position at Bina with starting date of November 2012 
-    (upon completion of doctoral degree).
-
-\section{EDUCATION}          
-    Stanford University, PhD, Electrical Engineering, November 2012 (in progress) \\
+\section{Education}          
+    Stanford University, PhD, Electrical Engineering, June 2013 (in progress) \\
     Stanford University, Masters of Science, Electrical Engineering, May 2012 \\
@@
 
-\section{HONORS}
+\section{Honors}
     Stanford Graduate Fellowship, Stanford University, 2007 \\
@@
 
-\section{EXPERIENCE}
+\section{PhD Research: Computational design of nanophotonic components}
+Specifically, the development of software which can
+    design arbitrary linear nanophotonic devices which 
+    are fully three-dimensional and multi-modal,
+    exhibit novel functionality,
+    have very compact footprints,
+    exhibit high efficiency, 
+    are strongly robust to fluctuations in 
+    wavelength, temperature and fabrication error, and
+    are manufacturable.
+Critically, the developed software 
+    does not require the user to be a nanophotonic expert or 
+    to perform any manual tuning. 
+Instead, devices are designed
+    solely based on the user's desired performance specification for the device.
+
+\section{Publications}          
+    ``Objective-first design of high-efficiency, small-footprint couplers between arbitrary nanophotonic waveguide modes'' Jesse Lu, Jelena Vuckovic (Optics Express, 2012). \\
+    ``Inverse design of a three-dimensional nanophotonic resonator'' Jesse Lu, Stephen Boyd, Jelena Vuckovic (Optics Express, 2011). \\
+    ``Inverse design of nanophotonic structures using complementary convex optimization'' Jesse Lu, Jelena Vuckovic (Optics Express, 2010). \\
+    ``Numerical optimization of a grating coupler for the efficient excitation of surface plasmons at an Ag-SiO2 interface'' Jesse Lu, Csaba Petre, Josh Conway, Eli Yablonovitch (JOSA B, 2007).
+
+\section{Programming}          
+    Fluent in Python, CUDA, and Matlab. \\
+    Implemented cloud-based simulation service on Amazon EC2. \\
+    Developed hardware-accelerated time- and frequency-domain
+        electromagnetic solvers. \\
+    Matlab library for the design of arbitrary linear nanophotonic components.
+
+\section{Research Experience}
    \vspace{-0.1in}	
@@
     Also developed a novel ``objective-first'' nanophotonic design algorithm
-        and demonstrated automated design of 
-        small-footprint, high-efficiency waveguide couplers.
+        and demonstrated automated design of arbitrary linear nanophotonic 
+        devices.
    \begin{tabbing}
@@
         grating coupler design.
-   \begin{tabbing}%
-   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions          
-   {\bf Research Assistant Intern}  \>Inko Pellicles \> Summer 2003\\
-                          \>Sunnyvale, CA
-   \end{tabbing}\vspace{-20pt}
-    Pellicle removal left residue on expensive lithography masks.
-    Assisted in researching and developing a UV irradition process
-        to modify the adhesive properties of the glue.
-
-\section{PROGRAMMING}          
-    Fluent in Python, CUDA, and Matlab. \\
-    Currently working with Git and Amazon EC2.
-
-\section{PUBLICATIONS}          
-    ``Objective-first design of high-efficiency, small-footprint couplers between arbitrary nanophotonic waveguide modes'' Jesse Lu, Jelena Vuckovic (Optics Express, 2012). \\
-    ``Inverse design of a three-dimensional nanophotonic resonator'' Jesse Lu, Stephen Boyd, Jelena Vuckovic (Optics Express, 2011). \\
-    ``Inverse design of nanophotonic structures using complementary convex optimization'' Jesse Lu, Jelena Vuckovic (Optics Express, 2010). \\
-    ``Numerical optimization of a grating coupler for the efficient excitation of surface plasmons at an Ag-SiO2 interface'' Jesse Lu, Csaba Petre, Josh Conway, Eli Yablonovitch (JOSA B, 2007).
 

### 2013-03-13 resume/cv.tex
Modified cv.

@@
 
-\section{PhD Research: Computational design of nanophotonic components}
-Specifically, the development of software which can
+\section{PhD Research: Nanophotonic computational design}
+Developed software to 
     design arbitrary linear nanophotonic devices which 
@@
         electromagnetic solvers. \\
-    Matlab library for the design of arbitrary linear nanophotonic components.
+    Developed Matlab library for the design of arbitrary linear nanophotonic components.
 
@@
         where each simulation about 24 hours to complete.
-    Implemented FDTD and FDFD simulation software on Nvidia GPUs to bring 
-        simulation times down to 10 minutes.
+    Implemented FDTD and FDFD simulation software on hardware-accelerated platforms 
+    to bring simulation times down to 10 minutes.
     Also developed a novel ``objective-first'' nanophotonic design algorithm

### 2013-03-18 sandbox/pb_cleanup/cleanup.tex
Added cleaning schedule.

\documentclass[12pt]{article}
\usepackage{fullpage}
\title{PBC Cleaning Schedule}
\date{2013}
\newcommand{\BI}{\begin{itemize}\item}
\newcommand{\I}{\item}
\newcommand{\EI}{\end{itemize}}
\begin{document}
\maketitle
\section{What is this?}
A simple plan to be faithful to maintain the property that God has given us.
Pairs of members are assigned a specific month in which
    to clean the main church building.
Cleanings should occur \textbf{the week leading up to the 4th Sunday} 
    of the given month 
    (in order to be best spaced from the work day cleaning).
Pairs are assigned so that this time can also be used as a time of fellowship.

\section{What needs to be cleaned?}
\BI Restrooms
    \BI Toilet paper available in each stall
    \I  Paper towel dispensers filled
    \I  Soap dispensers filled
    \I  Toilets flushed and presentable \EI
\I  Pews
    \BI Bibles and hymnals straightened
    \I  Pens in each alotted space
    \I  Guest cards ($\sim2$) in each alotted space \EI
\I  Nursery and Training Room
    \BI Toys in appropriate place (e.g. bins)
    \I  Chairs straightened
    \I  Bibles and hymnals available on Nursery end table \EI
\I  Plants
    \BI Watered (only for those which are real)
    \I  Plants near pulpit look good and presentable \EI
\EI
\section{Assignments}
\BI These dates are for 2013.
\I  Date ranges denote Monday to Saturday of the week leading 
        up to the fourth Sunday of the month.
    This was chosen in order to space this cleaning between
        successive word day cleanings. \EI
\begin{center}
\begin{tabular}{|c|c|}
    \hline
    Date range & Assignment \\
    \hline \hline
    April 22-27 & Davis \& Hardin \\ \hline
    May 20-25 & Lu \& Mixsell \\ \hline
    June 17-22 & Owens \& Sheldon \\ \hline
    July  22-27 & Sisson \& Torrefranca \\ \hline
    August 19-24 & IBBC \& Davis \\ \hline
    September 23-28 & Hardin \& Lu \\ \hline
    October 21-26 & Mixsell \& Owens \\ \hline
    November 18-23 & Sheldon \& Sisson \\ \hline
    December 16-21 & Torrefrance \& IBBC \\ \hline
\end{tabular}
\end{center}
\end{document}

### 2013-04-02 sandbox/pb_cleanup/cleanup.tex
Updated cleaning schedule.

@@
     to clean the main church building.
-Cleanings should occur \textbf{the week leading up to the 4th Sunday} 
+Cleanings should occur \textbf{the week leading up to or following the 4th Sunday} 
     of the given month 
@@
 \BI These dates are for 2013.
-\I  Date ranges denote Monday to Saturday of the week leading 
-        up to the fourth Sunday of the month.
+\I  Date ranges start on Monday of the week leading up to 
+    the fourth Sunday of the month, and
+    end on Saturday of the week following the fourth Sunday of the month.
     This was chosen in order to space this cleaning between
-        successive word day cleanings. \EI
+        successive work day cleanings. \EI
 \begin{center}
@@
     \hline \hline
-    April 22-27 & Davis \& Hardin \\ \hline
-    May 20-25 & Lu \& Mixsell \\ \hline
-    June 17-22 & Owens \& Sheldon \\ \hline
-    July  22-27 & Sisson \& Torrefranca \\ \hline
-    August 19-24 & IBBC \& Davis \\ \hline
-    September 23-28 & Hardin \& Lu \\ \hline
-    October 21-26 & Mixsell \& Owens \\ \hline
-    November 18-23 & Sheldon \& Sisson \\ \hline
-    December 16-21 & Torrefrance \& IBBC \\ \hline
+    April 22 to May 4 & Davis \& Hardin \\ \hline
+    May 20 to June 1 & Lu \& Mixsell \\ \hline
+    June 17 to June 29 & Owens \& Sheldon \\ \hline
+    July  22 to August 3 & Sisson \& Torrefranca \\ \hline
+    August 19 to August 31 & IBBC \& Davis \\ \hline
+    September 23 to October 5 & Hardin \& Lu \\ \hline
+    October 21 to November 2 & Mixsell \& Owens \\ \hline
+    November 18 to November 30 & Sheldon \& Sisson \\ \hline
+    December 16 to December 28 & Torrefranca \& IBBC \\ \hline
 \end{tabular}

### 2013-05-07 resume/cv.tex
New CV.

@@
 \section{Education}          
-    Stanford University, PhD, Electrical Engineering, June 2013 (in progress) \\
+    Stanford University, PhD, Electrical Engineering, June 2013 \\
     Stanford University, Masters of Science, Electrical Engineering, May 2012 \\
@@
 
-\section{PhD Research: Nanophotonic computational design}
-Developed software to 
-    design arbitrary linear nanophotonic devices which 
-    are fully three-dimensional and multi-modal,
-    exhibit novel functionality,
-    have very compact footprints,
-    exhibit high efficiency, 
-    are strongly robust to fluctuations in 
-    wavelength, temperature and fabrication error, and
-    are manufacturable.
-Critically, the developed software 
-    does not require the user to be a nanophotonic expert or 
-    to perform any manual tuning. 
-Instead, devices are designed
-    solely based on the user's desired performance specification for the device.
+\section{PhD Research: Nanophotonic Computational Design and Optimization}
+\begin{itemize}
+\item Nanophotonic design and optimization was 
+    a brute force, trial-and-error process
+    which took \emph{weeks to months} to improve a single structure---even with 
+    a good initial guess.
+\item I had to build a system to design structures within a day,
+    solely based on the performance specification of the desired device,
+    and without good initial guesses.
+\item I applied methods from the field of convex optimization 
+    to the physical problem of linear nanophotonic design. 
+    I sped up computation by implementing my method on GPUs,
+    and achieved scale by leveraging the cloud (Amazon EC2).
+\item This resulted in the design 
+    of nanophotonic devices that were either
+    more compact, more robust, or more efficient 
+    than all previous designs.
+    Critically, these designs only required a day (or two) of computation,
+    and a specification for the intended performance (no good initial guess).
+    \end{itemize}
 
@@
    \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
-    Existing nanophotonic design process consisted of trial-and-error
-        where each simulation about 24 hours to complete.
-    Implemented FDTD and FDFD simulation software on hardware-accelerated platforms 
-    to bring simulation times down to 10 minutes.
-    Also developed a novel ``objective-first'' nanophotonic design algorithm
-        and demonstrated automated design of arbitrary linear nanophotonic 
-        devices.
+%   Existing nanophotonic design process consisted of trial-and-error
+%       where each simulation about 24 hours to complete.
+%   Implemented FDTD and FDFD simulation software on hardware-accelerated platforms 
+%   to bring simulation times down to 10 minutes.
+%   Also developed a novel ``objective-first'' nanophotonic design algorithm
+%       and demonstrated automated design of arbitrary linear nanophotonic 
+%       devices.
    \begin{tabbing}
@@
    \end{tabbing}\vspace{-20pt}
-    Surface plasmon focusing device required a grating coupler to inject energy
-        into the surface plasmon mode.
-    Wrote a Matlab program interfacing with a FEM package (COMSOL),
-        developed a hierarchal optimization routine as well as an extended 
-        transfer matrix model to produce first-ever thoroughly optimized 
-        grating coupler design.
+%   Surface plasmon focusing device required a grating coupler to inject energy
+%       into the surface plasmon mode.
+%   Wrote a Matlab program interfacing with a FEM package (COMSOL),
+%       developed a hierarchal optimization routine as well as an extended 
+%       transfer matrix model to produce first-ever thoroughly optimized 
+%       grating coupler design.
 

### 2013-05-21 presentations/fdtd_gpu/pres.tex
Added fdtd gpu presentation

\documentclass[landscape]{foils}
\usepackage{graphicx}
\usepackage{amsmath}

\raggedright
\special{! TeXDict begin /landplus90{true}store end }

\newcommand{\oursection}[1]{
\foilhead[-1.0cm]{#1}
}

\newcommand{\myfig}[1]{
    \begin{figure}[!h]
    \centerline{\includegraphics[height=6.5cm]{fig/#1.jpg}}
    \end{figure}
}
\newcommand{\widefig}[1]{
    \begin{figure}[!h]
    \centerline{\includegraphics[width=\textwidth]{fig/#1.jpg}}
    \end{figure}
}
\newcommand{\tallfig}[1]{
    \begin{figure}[!h]
    \centerline{\includegraphics[height=0.8\textheight]{fig/#1.jpg}}
    \end{figure}
}
\newcommand{\medfig}[1]{
    \begin{figure}[!h]
    \centerline{\includegraphics[height=10cm]{fig/#1.jpg}}
    \end{figure}
}
\newcommand{\bigfig}[1]{
    \begin{figure}[!h]
    \centerline{\includegraphics[height=12cm]{fig/#1.jpg}}
    \end{figure}
}
\newcommand{\BI}{\begin{itemize}\item}
\newcommand{\I}{\item}
\newcommand{\EI}{\end{itemize}}

\title{FDTD on the GPU}
\author{Jesse Lu}
\MyLogo{Jesse Lu, Jelena Vuckovic group, Stanford University}
\date{May 21, 2013}

\begin{document}
\setlength{\parskip}{0cm}
\maketitle

\begin{itemize} \itemsep -1pt
\I  The GPU today
\I  CPU vs GPU 
\I  Programming the GPU
\I  Implementing FDTD on the GPU
\I  Optimizing FDTD on the GPU
\EI

\vfill
\newpage

\oursection{The GPU today}
\BI GPU (Graphical Processing Unit) once only for 3D gaming, now everywhere.
\I  Present in virtually all computing form factors
    \BI Raspberry Pi: 24 GFLOPS Broadcom GPU
    \I  Titan Supercomputer: 20 PetaFLOPS, 18K+ Nvidia GPUs \EI
\I  Plays key role in numerous applications
    \BI graphics: games, video encoding/decoding, \ldots
    \I  science: protein folding, FDTD simulations, \ldots
    \I  misc.: bitcoin mining, password cracking, \ldots \EI
\vfill

\oursection{CPU vs. GPU}
\widefig{comp}
\newpage
% \I  Each of the GPU's 15 scalar multiprocessors contains 196 cores 
%     (almost 3000 total cores!)
% \tallfig{smx-block}
\begin{tabular}{r|c c}
     & CPU (Intel Xeon E7) & GPU (Nvidia Kepler) \\ \hline
    Number of cores & 10 & 2940 \\
    Cache size & 30MB & $\sim$2MB \\
    FLOPS (single-precision) & 0.67 TFLOPS & 3.7 TFLOPS \\
    FLOPS (double-precision) & 0.33 TFLOPS & 1.2 TFLOPS \\
    Memory bandwidth & 102 GB/s & 250 GB/s \\
    Power draw & 130 W & 250 W
\end{tabular}
\I  Spec comparison needs to always be taken with a grain of salt
    (e.g. ``theoretical maximums'')
\I  Question: What kind of workloads are most suitable for the CPU? the GPU?

\oursection{Programming the GPU}
\I  Will focus on Nvidia GPUs and the CUDA programming language
\I  CUDA uses the SIMD (Single Instruction Multiple Data) model for parallelization
\I  Programming model mirrors GPU architecture

\begin{tabular}{c c c}
Computational & Memory & Software \\ \hline\hline
core & registers & thread \\ \hline
multiprocessor & cache/shared memory & thread block \\ \hline
GPU & global memory & block grid
\end{tabular}
\oursection{Implementing FDTD on the GPU}
\I  We'll just look at a 1D $E$-field update:
    \begin{equation}
    E^i = c_0 E^i + c_1 (H^i - H^{i-1}) 
    \end{equation}
\I  This is how we would normally do it on the CPU
    \begin{verbatim}
    for (int i=0 ; i < N ; i++) {
        E[i] = c0 * E[i] + c1 * (H[i] - H[i-1]); 
    }
    \end{verbatim}

\newpage
\I  The simplest CUDA version of the update would be:
    \begin{verbatim}
    E_update<<<1, N>>>();
    ...

    __global__ update_E () {
        i = threadId;
        E[i] = c0 * E[i] + c1 * (H[i] - H[i-1]); 
    }
    \end{verbatim}
\I  Each cell is updated by a single thread
\I  All threads grouped in a single thread block

\newpage
\I  Launching multiple blocks will allow us to utilize
        multiple multiprocessors
    \begin{verbatim}
    E_update<<<N/16, 16>>>();
    ...

    __global__ update_E () {
        i = blockId * 16 + threadId;
        E[i] = c0 * E[i] + c1 * (H[i] - H[i-1]); 
    }
    \end{verbatim}

\oursection{Optimizing FDTD on the GPU}
\I  Basic optimization question to answer:
    Are we limited by the memory-bandwidth or by computational power?
\I  Optimizing memory access patterns is often the key to faster GPU codes
\I  \emph{Shared memory} resides at the multiprocessor level,
        and quickly accessed by all cores within the multiprocessor
\I  We can optimize memory access by eliminating redundant $H$-field loads

\newpage
\I  Shared memory version of the update function
    \begin{verbatim}
    E_update<<<N/16, 16>>>();
    ...

    __global__ update_E () {
        i = blockId * 16 + threadId;
        s_i = threadId;
        __shared__ float s_H[17];
        s_H[s_i+1] = H[i];
        if (threadId == 0) { s_H[0] = H[i-1] };
        __syncthreads();
        E[i] = c0 * E[i] + c1 * (s_H[s_i+1] - H[s_i]); 
    }
    \end{verbatim}

\EI
\end{document}

### 2013-05-21 resume/cv.tex
Added fdtd gpu presentation

@@
     a good initial guess.
-\item I had to build a system to design structures within a day,
+\item I built a system to design structures within a day,
     solely based on the performance specification of the desired device,
@@
 \section{Publications}          
+    ``Nanophotonic Computational Design'' Jesse Lu, Jelena Vuckovic (Optics Express, 2013 \emph{in process}). \\
     ``Objective-first design of high-efficiency, small-footprint couplers between arbitrary nanophotonic waveguide modes'' Jesse Lu, Jelena Vuckovic (Optics Express, 2012). \\

### 2013-06-08 sandbox/pbc-workday/2013-06.tex
Added workday document.

\documentclass[12pt]{article}
\newcommand{\BI}{\begin{enumerate}\item}
\newcommand{\I}{\item}
\newcommand{\EI}{\end{enumerate}}
\title{Work Day}
\begin{document}
\maketitle
Items are listed in order of \emph{approximate} priority. 
We probably won't come close to doing everything, that's okay.
You can ask me (Jesse) for clarification, if I'm not around my cell is (408) 568-9356.
\BI Main Sanctuary
    \BI Apply wood polish to pews
    \I  Vacuum pews and carpet
    \I  General cleaning (remove old bulletins...)
    \I  Replace pens with pencils
    \I  Restock visitor cards (remove old ones which have been written on) \EI
\I  Refinish exterior wood doors and paneling of main building (see Jesse for more details)
    \BI Remove doors from hinges
    \I  Sand using electric sander, then by hand
    \I  Apply finish to top and bottom
    \I  Re-hinge doors
    \I  Apply finish to remaining surfaces \EI
\I  Bathrooms: Regular cleaning and restocking
\I  Replace Air Filters of AC system (for both AC systems)
    \BI New filters likely need to be purchased. \EI
\I  Supply run
    \BI Colored paper for Sunday bulletins needs to be purchased \EI
\I  Annex
    \BI Sweep floors
    \I  Clean and restock bathroom (including better solution for hand soap) \EI
\I  Purchase and install rubber ring-boots for vent flashings (pipes sticking out of roof) near the roof by the main entrance of the main building.
    \BI Diameter of pipes (flashings) and approximate degree of roof need to first be measured in order to purchase the correct rubber boots.
    \I  Rubber boots then need to be installed. \EI
\I  Roof gutters in main building
    \BI  Clean gutters of debris \EI
\I  Park strips
    \BI  Check the park strips both at the front and back of the church for weeds and litter. \EI
\I  Water heater in main building
    \BI Purchase and install seismic restraint for the water heater of the main building
    \I  Purchase and install piping in order to route the Temperature/Pressure Relief valve (TPR valve) of the water heater to the adjacent floor sink. \EI
\I  Electrical Panel for main building
    \BI  The electrical panel (located “around the corner” from main entrance) has openings in it, which need to be covered. \EI
\EI
\end{document}

### 2013-07-13 sandbox/pbc-workday/2013-07.tex
Added workday.

--- 2013-06-08 sandbox/pbc-workday/2013-06.tex
@@
 Items are listed in order of \emph{approximate} priority. 
-We probably won't come close to doing everything, that's okay.
-You can ask me (Jesse) for clarification, if I'm not around my cell is (408) 568-9356.
 \BI Main Sanctuary
-    \BI Apply wood polish to pews
-    \I  Vacuum pews and carpet
-    \I  General cleaning (remove old bulletins...)
-    \I  Replace pens with pencils
-    \I  Restock visitor cards (remove old ones which have been written on) \EI
-\I  Refinish exterior wood doors and paneling of main building (see Jesse for more details)
-    \BI Remove doors from hinges
-    \I  Sand using electric sander, then by hand
-    \I  Apply finish to top and bottom
-    \I  Re-hinge doors
-    \I  Apply finish to remaining surfaces \EI
+    \BI Vacuum pews and carpet
+    \I  General cleaning (remove old bulletins...) \EI
+\I  Unplug Annex toilet.
+    \BI Toilet may need to be completely removed 
+        and then re-installed if conventional unplugging methods fail. \EI
 \I  Bathrooms: Regular cleaning and restocking
-\I  Replace Air Filters of AC system (for both AC systems)
-    \BI New filters likely need to be purchased. \EI
-\I  Supply run
-    \BI Colored paper for Sunday bulletins needs to be purchased \EI
+\I  Maintenance of the AC system for the sanctuary.
+    \BI Main AC system is the one that is ``tucked away'' in the attic,
+        \emph{not} the first one that you see when you go up there.
+    \I  New filters need to be installed, they are on top of the other AC system. 
+    \I  Also, attempt to find and fix the cause of the condensation
+        which is leaking through to the foyer. \EI
+\I  Purchase and install rubber ring-boots for vent flashings 
+    (pipes sticking out of roof) near the roof by the main entrance 
+    of the main building.
+    \BI Diameter of pipes (flashings) and approximate degree of roof 
+        need to first be measured in order to purchase the correct rubber boots.
+    \I  Rubber boots then need to be installed. \EI
 \I  Annex
@@
     \I  Clean and restock bathroom (including better solution for hand soap) \EI
-\I  Purchase and install rubber ring-boots for vent flashings (pipes sticking out of roof) near the roof by the main entrance of the main building.
-    \BI Diameter of pipes (flashings) and approximate degree of roof need to first be measured in order to purchase the correct rubber boots.
-    \I  Rubber boots then need to be installed. \EI
+\I  Water heater in main building
+    \BI Purchase and install seismic restraint for the water heater 
+        of the main building
+    \I  Purchase and install piping in order to route 
+        the Temperature/Pressure Relief valve (TPR valve) of the water heater 
+        to the adjacent floor sink. \EI
+\I  Electrical Panel for main building
+    \BI The electrical panel (located “around the corner” from main entrance) 
+        has openings in it, which need to be covered. \EI
+\I  Park strips
+    \BI Check the park strips both at the front and back of the church 
+        for weeds and litter. \EI
 \I  Roof gutters in main building
     \BI Clean gutters of debris \EI
-\I  Park strips
-    \BI  Check the park strips both at the front and back of the church for weeds and litter. \EI
-\I  Water heater in main building
-    \BI Purchase and install seismic restraint for the water heater of the main building
-    \I  Purchase and install piping in order to route the Temperature/Pressure Relief valve (TPR valve) of the water heater to the adjacent floor sink. \EI
-\I  Electrical Panel for main building
-    \BI  The electrical panel (located “around the corner” from main entrance) has openings in it, which need to be covered. \EI
 \EI

### 2013-07-17 resume/cv.tex
Updated cv.

@@
 \section{Education}          
-    Stanford University, PhD, Electrical Engineering, June 2013 \\
+    Stanford University, PhD, Electrical Engineering, June 2013 (GPA: 3.657)\\
     Stanford University, Masters of Science, Electrical Engineering, May 2012 \\
@@
 \section{Publications}          
-    ``Nanophotonic Computational Design'' Jesse Lu, Jelena Vuckovic (Optics Express, 2013 \emph{in process}). \\
+    ``Nanophotonic Computational Design'' Jesse Lu, Jelena Vuckovic (Optics Express, 2013). \\
     ``Objective-first design of high-efficiency, small-footprint couplers between arbitrary nanophotonic waveguide modes'' Jesse Lu, Jelena Vuckovic (Optics Express, 2012). \\
@@
 \section{Programming}          
-    Fluent in Python, CUDA, and Matlab. \\
+    Fluent in Python, CUDA, C, C++, and Matlab. \\
     Implemented cloud-based simulation service on Amazon EC2. \\

### 2013-07-26 resume/cv.tex
Updated cv with UCLA GPA.

@@
 \section{Education}          
-    Stanford University, PhD, Electrical Engineering, June 2013 (GPA: 3.657)\\
-    Stanford University, Masters of Science, Electrical Engineering, May 2012 \\
-    University of California Los Angeles, Bachelor of Science, Electrical Engineering, June 2006
+    Stanford University, Ph.D., Electrical Engineering, June 2013 (GPA: 3.657)\\
+    Stanford University, M.S. , Electrical Engineering, May 2012 (GPA: 3.657)\\
+    University of California Los Angeles, B.S., Electrical Engineering, June 2006 (GPA: 3.769)
 
@@
 \section{Programming}          
-    Fluent in Python, CUDA, C, C++, and Matlab. \\
+    Fluent in Python, CUDA, Linux, C, C++, and Matlab. \\
     Implemented cloud-based simulation service on Amazon EC2. \\

### 2013-08-10 sandbox/pbc-workday/2013-08.tex
August workday.

--- 2013-07-13 sandbox/pbc-workday/2013-07.tex
@@
     \BI Vacuum pews and carpet
+    \I  Restock visitor cards and pencils into pews.
     \I  General cleaning (remove old bulletins...) \EI
-\I  Unplug Annex toilet.
-    \BI Toilet may need to be completely removed 
-        and then re-installed if conventional unplugging methods fail. \EI
 \I  Bathrooms: Regular cleaning and restocking
-\I  Maintenance of the AC system for the sanctuary.
-    \BI Main AC system is the one that is ``tucked away'' in the attic,
-        \emph{not} the first one that you see when you go up there.
-    \I  New filters need to be installed, they are on top of the other AC system. 
-    \I  Also, attempt to find and fix the cause of the condensation
-        which is leaking through to the foyer. \EI
+\I  Annex carpet estimate 
+    \BI We haven't committed to carpeting the Annex, 
+        but it would be really beneficial to have a cost/work/style estimate.
+    \I  If unexperienced with carpeting rooms, you may want to consult someone
+        who does or the internet first.
+    \I  Determine amount of carpeting needed to cover annex dining room.
+    \I  Visit Lowe's (811 E Arques Ave) and choose around 3 carpet samples.
+    \I  Also, obtain cost estimates for each of the samples.
+    \I  Hopefully we can plan on a carpet to install next month. \EI
+\I  General restocking of needed items
+\I  Re-organize the janitor closet
+    \BI Feel free to throw away what does not appear useful
+        (e.g. bottles with only a little solution remaining). \EI
+\I  Annex
+    \BI Sweep floors
+    \I  Clean and restock bathroom (including better solution for hand soap) \EI
+\I  General outdoor cleaning
+    \BI Leaves in front of main church entryway.
+    \I  General weeding in the lawn area between the main building and annex. \EI
+\I  Annex soundproofing
+    \BI Research creative, cost-efficient ways to add soundproofing to the
+        Annex dining room. \EI
+\I  Remove or grind down the metal peice protruding from Annex.
 \I  Purchase and install rubber ring-boots for vent flashings 
@@
     \I  Rubber boots then need to be installed. \EI
-\I  Annex
-    \BI Sweep floors
-    \I  Clean and restock bathroom (including better solution for hand soap) \EI
-\I  Water heater in main building
-    \BI Purchase and install seismic restraint for the water heater 
-        of the main building
-    \I  Purchase and install piping in order to route 
-        the Temperature/Pressure Relief valve (TPR valve) of the water heater 
-        to the adjacent floor sink. \EI
-\I  Electrical Panel for main building
-    \BI The electrical panel (located “around the corner” from main entrance) 
-        has openings in it, which need to be covered. \EI
-\I  Park strips
-    \BI Check the park strips both at the front and back of the church 
-        for weeds and litter. \EI
-\I  Roof gutters in main building
-    \BI Clean gutters of debris \EI
+\I  Finish trimming hedges around the parking lot. 
 \EI

### 2013-09-15 sandbox/pbc-workday/2013-09.tex
iNew workday list.

--- 2013-08-10 sandbox/pbc-workday/2013-08.tex
@@
 \BI Main Sanctuary
-    \BI Vacuum pews and carpet
-    \I  Restock visitor cards and pencils into pews.
+    \BI Clean carpet using a carpet cleaner
+    \I  Clean pews using Pastor Josh's carpet/upholstery machine
+    \I  Vacuum pews and carpet
     \I  General cleaning (remove old bulletins...) \EI
 \I  Bathrooms: Regular cleaning and restocking
-\I  Annex carpet estimate 
-    \BI We haven't committed to carpeting the Annex, 
-        but it would be really beneficial to have a cost/work/style estimate.
-    \I  If unexperienced with carpeting rooms, you may want to consult someone
-        who does or the internet first.
-    \I  Determine amount of carpeting needed to cover annex dining room.
-    \I  Visit Lowe's (811 E Arques Ave) and choose around 3 carpet samples.
-    \I  Also, obtain cost estimates for each of the samples.
-    \I  Hopefully we can plan on a carpet to install next month. \EI
-\I  General restocking of needed items
-\I  Re-organize the janitor closet
-    \BI Feel free to throw away what does not appear useful
-        (e.g. bottles with only a little solution remaining). \EI
+\I  Tree trimming
+    \BI Trees between sidewalk and parking lot
+    \I  Trees near sign at parking lot entrance
+    \I  Hedges around the parking lot \EI
 \I  Annex
@@
     \I  Clean and restock bathroom (including better solution for hand soap) \EI
+\I  Replace fluorescent lights in pastor's office
+    \BI Bulb type is F50, soft white (may need to purchase at Lowe's) \EI
 \I  General outdoor cleaning
@@
     \I  Rubber boots then need to be installed. \EI
-\I  Finish trimming hedges around the parking lot. 
 \EI
